---
title: "Cowriters Survey EFA and Analysis Exports"
format: html
output-dir: "02_efa_exports"
editor: visual
---

# EFA and Paired Analysis Exports

This script starts from the cleaned long-format exports and the verified triage ledger. It creates:

-   primary EFA datasets with instrument-specific salvage cases
-   sensitivity EFA datasets on the strict paired sample only
-   the strict paired wide-format master dataset for downstream inferential models

------------------------------------------------------------------------

## Section 1: Setup

```{r setup}

#| message: false
library(tidyverse)
library(knitr)
source("scoring_helpers.R", local = knitr::knit_global())
script_dir <- "02_efa_exports"
audit_dir <- file.path(script_dir, "audit")
efa_dir <- file.path(script_dir, "efa")
efa_diagnostics_dir <- file.path(script_dir, "efa_diagnostics")
cleaned_dir <- file.path("01_audit_cleaning", "cleaned")
triage_dir <- file.path("01_audit_cleaning", "audit")
dir.create(audit_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(efa_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(efa_diagnostics_dir, recursive = TRUE, showWarnings = FALSE)
set.seed(42L)
```

------------------------------------------------------------------------

## Section 2: Load Cleaned, Raw, and Triage Data

```{r load-data}
rw_col_names <- c(
  "participant number order", "pid", "item_code", "score_raw",
  "qualtrics_qid", "item_subnum", "question_stem",
  "input_type", "input_subtype", "answer_type",
  "question_block", "item_subnum2", "item_text",
  "item_text_full", "submission_status"
)

llm_col_names <- c(
  "participant number order", "pid", "topic", "item_code", "score_raw",
  "qualtrics_qid", "item_subnum", "question_stem",
  "input_type", "input_subtype", "answer_type",
  "question_block", "item_num", "item_text",
  "item_text_full", "response_labeled", "response_label_short",
  "score_numeric", "response_label2", "response_html",
  "question_stem2", "item_text2", "submission_status"
)

instrument_expected <- tribble(
  ~question_block, ~instrument,       ~expected, ~source,
  "Q1",            "IMI",             18L,        "rw",
  "Q7",            "WritingEfficacy", 20L,        "rw",
  "Q25",           "AIReflection",    12L,        "llm",
  "Q2-23",         "BeliefsAboutAI",  22L,        "llm"
)

submission_resolution_expected <- tribble(
  ~source, ~question_block, ~expected, ~straight_line_sensitive,
  "rw",    "Q1",            18L,       TRUE,
  "rw",    "Q7",            20L,       TRUE,
  "rw",    "Q9",             1L,       FALSE,
  "llm",   "Q25",           12L,       TRUE,
  "llm",   "Q2-23",         22L,       TRUE
)

imi_clean <- read_csv(file.path(cleaned_dir, "IMI_cleaned.csv"), show_col_types = FALSE) |>
  mutate(participant_id = as.character(participant_id))
efficacy_clean <- read_csv(file.path(cleaned_dir, "WritingEfficacy_cleaned.csv"), show_col_types = FALSE) |>
  mutate(participant_id = as.character(participant_id))
refl_clean <- read_csv(file.path(cleaned_dir, "AI_Reflection_cleaned.csv"), show_col_types = FALSE) |>
  mutate(participant_id = as.character(participant_id))
beliefs_clean <- read_csv(file.path(cleaned_dir, "BeliefsAboutAI_cleaned.csv"), show_col_types = FALSE) |>
  mutate(participant_id = as.character(participant_id))

verified_triage_path <- file.path(triage_dir, "Triage_Rap_Sheet_Verified.csv")
legacy_verified_triage_path <- file.path("inputs", "audit", "Triage_Rap_Sheet_Verified.csv")
if (!file.exists(verified_triage_path) && file.exists(legacy_verified_triage_path)) {
  verified_triage_path <- legacy_verified_triage_path
}

verified_triage <- read_csv(verified_triage_path, show_col_types = FALSE) |>
  mutate(pid = as.character(pid))

rw_raw <- read_csv(
  "rw-survey-long-040726.csv",
  skip = 9, col_names = rw_col_names, show_col_types = FALSE,
  col_types = cols(
    pid = col_character(),
    question_block = col_character(),
    item_subnum2 = col_character(),
    score_raw = col_character(),
    submission_status = col_character()
  )
)

llm_raw <- read_csv(
  "llm-survey-long-040726.csv",
  skip = 9, col_names = llm_col_names, show_col_types = FALSE,
  col_types = cols(
    pid = col_character(),
    question_block = col_character(),
    item_num = col_character(),
    score_raw = col_character(),
    submission_status = col_character()
  )
)

tracking_clean <- read_csv(
  "Participant Tracking - IDs and Conditions Table.csv",
  show_col_types = FALSE,
  col_types = cols(
    ParticipantID = col_character(),
    `Condition 1` = col_character(),
    `Condition 2` = col_character()
  )
) |>
  select(ParticipantID, `Condition 1`, `Condition 2`) |>
  rename(
    pid         = ParticipantID,
    condition_1 = `Condition 1`,
    condition_2 = `Condition 2`
  ) |>
  filter(!is.na(pid))

assert_unique_pid_rows(tracking_clean, pid_col = "pid", context_label = "tracking_clean")
assert_no_missing_values(tracking_clean, c("pid", "condition_1", "condition_2"), "tracking_clean")
assert_allowed_values(tracking_clean$condition_1, c("Alone", "LLM"), "tracking_clean condition_1")
assert_allowed_values(tracking_clean$condition_2, c("Alone", "LLM"), "tracking_clean condition_2")
assert_nonempty_df(imi_clean, "imi_clean")
assert_nonempty_df(efficacy_clean, "efficacy_clean")
assert_nonempty_df(refl_clean, "refl_clean")
assert_nonempty_df(beliefs_clean, "beliefs_clean")
```

------------------------------------------------------------------------

## Section 3: Paired Sample and Best-Submission Sources

This section starts from the same duplicate-resolution rule used in the audit file. In other words, if a participant has multiple submissions in the same source file, we keep the single best whole-survey attempt rather than counting all of them. Raw target-block quality decides the winner first; Qualtrics labels are only a last-resort fallback.

```{r paired-and-dedup}

paired_imis  <- sort(unique(imi_clean$participant_id))
paired_wse   <- sort(unique(efficacy_clean$participant_id))
paired_refl  <- sort(unique(refl_clean$participant_id))
paired_bel   <- sort(unique(beliefs_clean$participant_id))

assert_identical_pid_sets(
  list(
    IMI = paired_imis,
    WritingEfficacy = paired_wse,
    AIReflection = paired_refl,
    BeliefsAboutAI = paired_bel
  ),
  context_label = "Paired cleaned PID consistency"
)

paired_analysis_pids <- paired_imis
assert_expected_count(length(paired_analysis_pids), 82L, "Strict paired analysis PID count")

rw_best  <- resolve_best_submission(rw_raw,  "rw", submission_resolution_expected)$best_data
llm_best <- resolve_best_submission(llm_raw, "llm", submission_resolution_expected)$best_data
```

------------------------------------------------------------------------

## Section 4: Locked EFA Inclusion Rules

```{r efa-inclusion}
efa_global_exclusions <- c(
  "N/A (RA practice)",
  "Sania Jain test",
  "y5lblN",
  "2192994",
  "hKpFTX"
)

rw_efa_override_pids <- verified_triage |>
  filter(verified_recommendation ==
           "Salvage RW-only with manual override to first-dup submission") |>
  pull(pid)

rw_efa_salvage_pids <- verified_triage |>
  filter(
    verified_recommendation %in% c(
      "Salvage RW-only",
      "Salvage RW-only with manual override to first-dup submission"
    ),
    !pid %in% efa_global_exclusions
  ) |>
  pull(pid)

llm_efa_salvage_pids <- verified_triage |>
  filter(
    verified_recommendation == "Salvage LLM-only",
    !pid %in% efa_global_exclusions
  ) |>
  pull(pid)

rw_efa_primary_pids  <- union(paired_analysis_pids, rw_efa_salvage_pids)
llm_efa_primary_pids <- union(paired_analysis_pids, llm_efa_salvage_pids)

# The improved raw-data resolver already catches the known RW straight-line
# tie cases, but the explicit first-dup override remains as a locked safeguard.
rw_efa_source <- rw_best |>
  filter(!pid %in% rw_efa_override_pids) |>
  bind_rows(
    rw_raw |>
      filter(
        pid %in% rw_efa_override_pids,
        submission_status == "first-dup"
      )
  )

missing_rw_override_pids <- setdiff(
  rw_efa_override_pids,
  unique(rw_efa_source$pid)
)

if (length(missing_rw_override_pids) > 0) {
  stop(
    paste0(
      "RW EFA override participants are missing after first-dup splice: ",
      paste(missing_rw_override_pids, collapse = ", ")
    ),
    call. = FALSE
  )
}

llm_efa_source <- llm_best

efa_inclusion_summary <- tribble(
  ~instrument,         ~primary_n, ~sensitivity_n,
  "IMI",               length(rw_efa_primary_pids),  length(paired_analysis_pids),
  "WritingEfficacy",   length(rw_efa_primary_pids),  length(paired_analysis_pids),
  "AIReflection",      length(llm_efa_primary_pids), length(paired_analysis_pids),
  "BeliefsAboutAI",    length(llm_efa_primary_pids), length(paired_analysis_pids)
)

cat("=== Locked EFA Inclusion Summary ===\n")
print(efa_inclusion_summary)
cat("\nRW first-dup overrides:", paste(rw_efa_override_pids, collapse = ", "), "\n")
```

------------------------------------------------------------------------

## Section 5: EFA Dataset Exports

**Sensitivity-check note:** the `primary` EFA files are the main measurement-structure datasets because they maximize usable `N` instrument-by-instrument. The matching `sensitivity` EFA files are a robustness check only: they rerun the same instrument on the strict paired `N = 82` sample to test whether adding salvage cases materially changes the factor structure.

In practice, the sensitivity check asks:

-   does the number of retained factors stay the same?
-   do the same items cluster together in roughly the same way?
-   do any major cross-loadings or interpretation problems appear only after salvage cases are added?

If the `primary` and `sensitivity` solutions are substantively similar, use the larger `primary` solution as the working EFA result. If they differ meaningfully, treat that instrument as unstable and prefer the stricter paired solution when interpreting the factor structure.

This sensitivity check is about **factor robustness**, not about expanding the inferential sample. Tool × Order models and the final paired wide dataset still stay on the strict paired sample only.

```{r export-efa}
imi_efa_primary <- rw_efa_source |>
  filter(
    question_block == "Q1",
    pid %in% rw_efa_primary_pids
  ) |>
  transmute(
    participant_id  = pid,
    item_code       = parse_integer_item_field(item_subnum2, "item_subnum2", "IMI EFA export"),
    item_text,
    score_raw_num   = as.numeric(score_raw),
    score           = score_imi_items(item_code, score_raw_num),
    inclusion_source = case_when(
      pid %in% paired_analysis_pids ~ "paired_clean",
      pid %in% rw_efa_override_pids ~ "rw_salvage_first_dup_override",
      TRUE                          ~ "rw_salvage"
    )
  ) |>
  inner_join(tracking_clean, by = c("participant_id" = "pid")) |>
  mutate(
    efa_sample = "primary",
    order = derive_order_from_conditions(condition_1, condition_2, "IMI EFA tracking join")
  ) |>
  select(
    participant_id, item_code, item_text, score, order,
    condition_1, condition_2, efa_sample, inclusion_source
  )

efficacy_efa_primary <- rw_efa_source |>
  filter(
    question_block == "Q7",
    pid %in% rw_efa_primary_pids
  ) |>
  transmute(
    participant_id  = pid,
    item_code       = parse_integer_item_field(item_subnum2, "item_subnum2", "WritingEfficacy EFA export"),
    item_text,
    score           = as.numeric(score_raw),
    inclusion_source = case_when(
      pid %in% paired_analysis_pids ~ "paired_clean",
      pid %in% rw_efa_override_pids ~ "rw_salvage_first_dup_override",
      TRUE                          ~ "rw_salvage"
    )
  ) |>
  inner_join(tracking_clean, by = c("participant_id" = "pid")) |>
  mutate(
    efa_sample = "primary",
    order = derive_order_from_conditions(condition_1, condition_2, "WritingEfficacy EFA tracking join")
  ) |>
  select(
    participant_id, item_code, item_text, score, order,
    condition_1, condition_2, efa_sample, inclusion_source
  )

refl_efa_primary <- llm_efa_source |>
  filter(
    question_block == "Q25",
    pid %in% llm_efa_primary_pids
  ) |>
  transmute(
    participant_id  = pid,
    item_num        = parse_integer_item_field(item_num, "item_num", "AIReflection EFA export"),
    item_text,
    score           = parse_number(score_raw),
    inclusion_source = case_when(
      pid %in% paired_analysis_pids ~ "paired_clean",
      TRUE                          ~ "llm_salvage"
    )
  ) |>
  inner_join(tracking_clean, by = c("participant_id" = "pid")) |>
  mutate(
    efa_sample = "primary",
    order = derive_order_from_conditions(condition_1, condition_2, "AIReflection EFA tracking join")
  ) |>
  select(
    participant_id, item_num, item_text, score, order,
    condition_1, condition_2, efa_sample, inclusion_source
  )

beliefs_efa_primary <- llm_efa_source |>
  filter(
    question_block == "Q2-23",
    pid %in% llm_efa_primary_pids
  ) |>
  transmute(
    participant_id  = pid,
    item_num        = parse_integer_item_field(item_num, "item_num", "Beliefs EFA export"),
    item_text,
    score_raw_num   = parse_number(score_raw),
    score           = score_beliefs_items(item_num, score_raw_num),
    inclusion_source = case_when(
      pid %in% paired_analysis_pids ~ "paired_clean",
      TRUE                          ~ "llm_salvage"
    )
  ) |>
  inner_join(tracking_clean, by = c("participant_id" = "pid")) |>
  mutate(
    efa_sample = "primary",
    order = derive_order_from_conditions(condition_1, condition_2, "Beliefs EFA tracking join")
  ) |>
  select(
    participant_id, item_num, item_text, score, order,
    condition_1, condition_2, efa_sample, inclusion_source
  )

imi_efa_sensitivity <- imi_clean |>
  mutate(
    efa_sample = "sensitivity",
    inclusion_source = "paired_clean"
  )

efficacy_efa_sensitivity <- efficacy_clean |>
  mutate(
    efa_sample = "sensitivity",
    inclusion_source = "paired_clean"
  )

refl_efa_sensitivity <- refl_clean |>
  mutate(
    efa_sample = "sensitivity",
    inclusion_source = "paired_clean"
  )

beliefs_efa_sensitivity <- beliefs_clean |>
  mutate(
    efa_sample = "sensitivity",
    inclusion_source = "paired_clean"
  )

if (anyNA(imi_efa_primary$item_code) || !all(imi_efa_primary$item_code %in% 1:18)) {
  stop("IMI EFA primary item_code values are invalid; expected integers 1-18.", call. = FALSE)
}
if (anyNA(efficacy_efa_primary$item_code) || !all(efficacy_efa_primary$item_code %in% 1:20)) {
  stop("WritingEfficacy EFA primary item_code values are invalid; expected integers 1-20.", call. = FALSE)
}
if (anyNA(refl_efa_primary$item_num) || !all(refl_efa_primary$item_num %in% 1:12)) {
  stop("AIReflection EFA primary item_num values are invalid; expected integers 1-12.", call. = FALSE)
}
if (anyNA(beliefs_efa_primary$item_num) || !all(beliefs_efa_primary$item_num %in% 1:22)) {
  stop("Beliefs EFA primary item_num values are invalid; expected integers 1-22.", call. = FALSE)
}

efa_export_summary <- tribble(
  ~instrument,       ~primary_n,                                 ~sensitivity_n,
  "IMI",             n_distinct(imi_efa_primary$participant_id), n_distinct(imi_efa_sensitivity$participant_id),
  "WritingEfficacy", n_distinct(efficacy_efa_primary$participant_id), n_distinct(efficacy_efa_sensitivity$participant_id),
  "AIReflection",    n_distinct(refl_efa_primary$participant_id), n_distinct(refl_efa_sensitivity$participant_id),
  "BeliefsAboutAI",  n_distinct(beliefs_efa_primary$participant_id), n_distinct(beliefs_efa_sensitivity$participant_id)
)

expected_efa_counts <- tribble(
  ~instrument,       ~primary_n, ~sensitivity_n,
  "IMI",             88L,        82L,
  "WritingEfficacy", 88L,        82L,
  "AIReflection",    91L,        82L,
  "BeliefsAboutAI",  91L,        82L
)

assert_expected_counts(
  observed_tbl = efa_export_summary,
  expected_tbl = expected_efa_counts,
  key_col = "instrument",
  context_label = "EFA export counts do not match the locked inclusion plan"
)

excluded_pid_checks <- tribble(
  ~dataset,                  ~pids,
  "IMI_EFA_Primary",         list(unique(imi_efa_primary$participant_id)),
  "WritingEfficacy_EFA_Primary", list(unique(efficacy_efa_primary$participant_id)),
  "AI_Reflection_EFA_Primary",   list(unique(refl_efa_primary$participant_id)),
  "BeliefsAboutAI_EFA_Primary",  list(unique(beliefs_efa_primary$participant_id))
)

unexpected_excluded_hits <- excluded_pid_checks |>
  rowwise() |>
  mutate(
    forbidden_found = list(intersect(efa_global_exclusions, pids))
  ) |>
  ungroup() |>
  filter(lengths(forbidden_found) > 0L) |>
  transmute(dataset, forbidden_found = map_chr(forbidden_found, ~ paste(.x, collapse = ", ")))

if (nrow(unexpected_excluded_hits) > 0) {
  stop(
    paste0(
      "Global exclusions check failed in primary EFA exports:\n",
      paste(capture.output(print(unexpected_excluded_hits)), collapse = "\n")
    ),
    call. = FALSE
  )
}

write_csv(efa_export_summary,       file.path(efa_diagnostics_dir, "EFA_Export_Summary.csv"))
write_csv(imi_efa_primary,          file.path(efa_dir, "IMI_EFA_Primary.csv"))
write_csv(efficacy_efa_primary,     file.path(efa_dir, "WritingEfficacy_EFA_Primary.csv"))
write_csv(refl_efa_primary,         file.path(efa_dir, "AI_Reflection_EFA_Primary.csv"))
write_csv(beliefs_efa_primary,      file.path(efa_dir, "BeliefsAboutAI_EFA_Primary.csv"))
write_csv(imi_efa_sensitivity,      file.path(efa_dir, "IMI_EFA_Sensitivity.csv"))
write_csv(efficacy_efa_sensitivity, file.path(efa_dir, "WritingEfficacy_EFA_Sensitivity.csv"))
write_csv(refl_efa_sensitivity,     file.path(efa_dir, "AI_Reflection_EFA_Sensitivity.csv"))
write_csv(beliefs_efa_sensitivity,  file.path(efa_dir, "BeliefsAboutAI_EFA_Sensitivity.csv"))

cat("=== EFA Export Counts ===\n")
print(efa_export_summary)
cat("\nExported:", file.path(efa_diagnostics_dir, "EFA_Export_Summary.csv"), "\n")
cat("Exported:", file.path(efa_dir, "IMI_EFA_Primary.csv"), "\n")
cat("Exported:", file.path(efa_dir, "WritingEfficacy_EFA_Primary.csv"), "\n")
cat("Exported:", file.path(efa_dir, "AI_Reflection_EFA_Primary.csv"), "\n")
cat("Exported:", file.path(efa_dir, "BeliefsAboutAI_EFA_Primary.csv"), "\n")
cat("Exported:", file.path(efa_dir, "IMI_EFA_Sensitivity.csv"), "\n")
cat("Exported:", file.path(efa_dir, "WritingEfficacy_EFA_Sensitivity.csv"), "\n")
cat("Exported:", file.path(efa_dir, "AI_Reflection_EFA_Sensitivity.csv"), "\n")
cat("Exported:", file.path(efa_dir, "BeliefsAboutAI_EFA_Sensitivity.csv"), "\n")
```

------------------------------------------------------------------------

## Section 6: Strict Paired Wide Dataset

This wide master dataset stays on the strict paired `N = 82` sample only. It is the dataset intended for Tool × Order and other crossover analyses.

```{r phase3-wide}
imi_wide <- imi_clean |>
  mutate(item_col = paste0("IMI_", item_code)) |>
  select(participant_id, item_col, score, order, condition_1, condition_2) |>
  pivot_wider(
    id_cols     = c(participant_id, order, condition_1, condition_2),
    names_from  = item_col,
    values_from = score
  )

efficacy_wide <- efficacy_clean |>
  mutate(item_col = paste0("Efficacy_", item_code)) |>
  select(participant_id, item_col, score) |>
  pivot_wider(
    names_from  = item_col,
    values_from = score
  )

refl_wide <- refl_clean |>
  mutate(item_col = paste0("Refl_", item_num)) |>
  select(participant_id, item_col, score) |>
  pivot_wider(
    names_from  = item_col,
    values_from = score
  )

beliefs_wide <- beliefs_clean |>
  mutate(item_col = paste0("Beliefs_", item_num)) |>
  select(participant_id, item_col, score) |>
  pivot_wider(
    names_from  = item_col,
    values_from = score
  )

assert_unique_pid_rows(imi_wide, "participant_id", "imi_wide")
assert_unique_pid_rows(efficacy_wide, "participant_id", "efficacy_wide")
assert_unique_pid_rows(refl_wide, "participant_id", "refl_wide")
assert_unique_pid_rows(beliefs_wide, "participant_id", "beliefs_wide")
assert_identical_pid_sets(
  list(
    IMI = imi_wide$participant_id,
    WritingEfficacy = efficacy_wide$participant_id,
    AIReflection = refl_wide$participant_id,
    BeliefsAboutAI = beliefs_wide$participant_id
  ),
  context_label = "Strict paired wide PID consistency"
)

master_wide_df <- imi_wide |>
  inner_join(efficacy_wide, by = "participant_id") |>
  inner_join(refl_wide,     by = "participant_id") |>
  inner_join(beliefs_wide,  by = "participant_id")

cat("=== Master Wide Dataset ===\n")
cat("Rows (should equal N clean participants):", nrow(master_wide_df), "\n")
cat("Columns:", ncol(master_wide_df), "\n")

duplicate_master_ids <- master_wide_df |>
  count(participant_id, name = "n") |>
  filter(n > 1L)

if (nrow(duplicate_master_ids) > 0) {
  stop(
    paste0(
      "Final_Master_Wide has duplicate participant_id rows: ",
      paste(duplicate_master_ids$participant_id, collapse = ", ")
    ),
    call. = FALSE
  )
}

cat("Any duplicate participant_id: FALSE\n")

assert_expected_count(nrow(master_wide_df), 82L, "Final_Master_Wide row count")
assert_unique_pid_rows(master_wide_df, "participant_id", "Final_Master_Wide participant_id")
assert_allowed_values(master_wide_df$order, c("Traditional_First", "AI_First"), "Final_Master_Wide order")
assert_allowed_values(master_wide_df$condition_1, c("Alone", "LLM"), "Final_Master_Wide condition_1")
assert_allowed_values(master_wide_df$condition_2, c("Alone", "LLM"), "Final_Master_Wide condition_2")

required_master_item_cols <- c(
  paste0("IMI_", 1:18),
  paste0("Efficacy_", 1:20),
  paste0("Refl_", 1:12),
  paste0("Beliefs_", 1:22)
)
assert_required_columns(
  master_wide_df,
  c("participant_id", "order", "condition_1", "condition_2", required_master_item_cols),
  "Final_Master_Wide contract"
)
assert_no_missing_values(
  master_wide_df,
  c("participant_id", "order", "condition_1", "condition_2", required_master_item_cols),
  "Final_Master_Wide contract"
)

cat("\nNAs per instrument group:\n")
master_wide_df |>
  summarise(
    IMI_NAs      = sum(is.na(pick(starts_with("IMI_")))),
    Efficacy_NAs = sum(is.na(pick(starts_with("Efficacy_")))),
    Refl_NAs     = sum(is.na(pick(starts_with("Refl_")))),
    Beliefs_NAs  = sum(is.na(pick(starts_with("Beliefs_"))))
  ) |>
  print()

write_csv(master_wide_df, file.path(script_dir, "Final_Master_Wide.csv"))
cat("\nExported:", file.path(script_dir, "Final_Master_Wide.csv"), "\n")

participant_count_reconciliation <- tribble(
  ~stage, ~count,
  "raw_rw_unique_pid", n_distinct(rw_raw$pid),
  "raw_llm_unique_pid", n_distinct(llm_raw$pid),
  "raw_union_unique_pid", n_distinct(c(rw_raw$pid, llm_raw$pid)),
  "rw_best_unique_pid", n_distinct(rw_best$pid),
  "llm_best_unique_pid", n_distinct(llm_best$pid),
  "strict_paired_clean_pid", length(paired_analysis_pids),
  "rw_primary_efa_pid", n_distinct(imi_efa_primary$participant_id),
  "llm_primary_efa_pid", n_distinct(refl_efa_primary$participant_id),
  "rw_sensitivity_pid", n_distinct(imi_efa_sensitivity$participant_id),
  "llm_sensitivity_pid", n_distinct(refl_efa_sensitivity$participant_id),
  "final_master_wide_pid", n_distinct(master_wide_df$participant_id)
)

write_csv(participant_count_reconciliation, file.path(audit_dir, "Participant_Count_Reconciliation.csv"))
cat("Exported:", file.path(audit_dir, "Participant_Count_Reconciliation.csv"), "\n")
```

------------------------------------------------------------------------

## Section 7: Output Manifest

```{r output-manifest}
efa_exports_manifest <- tibble(
  output_type = c(
    "efa_export_summary",
    "imi_efa_primary",
    "wse_efa_primary",
    "refl_efa_primary",
    "beliefs_efa_primary",
    "imi_efa_sensitivity",
    "wse_efa_sensitivity",
    "refl_efa_sensitivity",
    "beliefs_efa_sensitivity",
    "final_master_wide",
    "participant_count_reconciliation"
  ),
  path = c(
    file.path(efa_diagnostics_dir, "EFA_Export_Summary.csv"),
    file.path(efa_dir, "IMI_EFA_Primary.csv"),
    file.path(efa_dir, "WritingEfficacy_EFA_Primary.csv"),
    file.path(efa_dir, "AI_Reflection_EFA_Primary.csv"),
    file.path(efa_dir, "BeliefsAboutAI_EFA_Primary.csv"),
    file.path(efa_dir, "IMI_EFA_Sensitivity.csv"),
    file.path(efa_dir, "WritingEfficacy_EFA_Sensitivity.csv"),
    file.path(efa_dir, "AI_Reflection_EFA_Sensitivity.csv"),
    file.path(efa_dir, "BeliefsAboutAI_EFA_Sensitivity.csv"),
    file.path(script_dir, "Final_Master_Wide.csv"),
    file.path(audit_dir, "Participant_Count_Reconciliation.csv")
  ),
  description = c(
    "EFA primary/sensitivity participant counts per instrument",
    "IMI long-format scores, primary EFA sample (N = 88)",
    "WritingEfficacy long-format scores, primary EFA sample (N = 88)",
    "AIReflection long-format scores, primary EFA sample (N = 91)",
    "BeliefsAboutAI long-format scores, primary EFA sample (N = 91)",
    "IMI long-format scores, sensitivity EFA sample (paired N = 82)",
    "WritingEfficacy long-format scores, sensitivity EFA sample (paired N = 82)",
    "AIReflection long-format scores, sensitivity EFA sample (paired N = 82)",
    "BeliefsAboutAI long-format scores, sensitivity EFA sample (paired N = 82)",
    "Strict-paired wide dataset (N = 82); all item columns; consumed by 04, 06, 07, 08",
    "Participant count reconciliation from raw through final master wide"
  )
)

write_csv(efa_exports_manifest, file.path(audit_dir, "EFA_Exports_Manifest.csv"))
kable(efa_exports_manifest, caption = "02_efa_exports.qmd — Output Manifest")
```
