---
title: "Cowriters Survey EFA Analysis"
format: html
output-dir: "03_efa_analysis"
editor: visual
---

# EFA Analysis

This script runs a conservative, small-sample exploratory factor analysis workflow on the existing primary and sensitivity EFA exports. Instruments are analyzed separately, treated as ordinal, and estimated with polychoric correlations plus `minres` extraction and `oblimin` rotation.

`locked_k` controls whether final locked solutions are fit. Leave `NA` on the first pass to generate diagnostics and recommendations only. After review, set one or more locked values to fit final primary and sensitivity solutions and to export the final item-to-factor map.

In practice, this script has two stages:

1.  **First pass:** generate diagnostics, candidate solutions, recommended `k`, scree plots, and visual preview heatmaps for the recommended primary solution when one exists.
2.  **Locked pass:** after you manually choose `k`, fill in `locked_k`, rerun the file, and it will export the final loadings table, final item map, and sensitivity comparison for the locked solution.

So if `locked_k` is still all `NA`, that does **not** mean the script failed. It means the report is stopping at the review stage on purpose.

The scree plots live in `Section 5B` of this file.

------------------------------------------------------------------------

## Section 1: Setup

```{r setup}

#| message: false
library(tidyverse)
library(psych)
source("scoring_helpers.R", local = knitr::knit_global())
script_dir <- "03_efa_analysis"
efa_dir <- file.path("02_efa_exports", "efa")
efa_diagnostics_dir <- file.path(script_dir, "efa_diagnostics")
audit_dir <- file.path(script_dir, "audit")
dir.create(efa_diagnostics_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(audit_dir, recursive = TRUE, showWarnings = FALSE)

# Set global seed for reproducibility — minres EFA uses gradient-based
# optimisation (optim()) internally; oblimin rotation and factor.parallel()
# are also affected by random starting values. A fixed seed ensures
# bit-identical results across machines and R sessions.
set.seed(42L)
```

------------------------------------------------------------------------

## Section 2: Configuration

```{r config}

instrument_specs <- tribble(
  ~instrument,         ~primary_file,                      ~sensitivity_file,                     ~item_col,   ~scale_max, ~rescale_to_5,
  "IMI",               file.path(efa_dir, "IMI_EFA_Primary.csv"),             file.path(efa_dir, "IMI_EFA_Sensitivity.csv"),             "item_code",        7L, FALSE,
  # WritingEfficacy is a 0-100 slider upstream, but the observed cleaned data
  # use five anchored values (0/25/50/75/100). We standardize those anchors to
  # 1-5 here before ordinal/polychoric EFA and hard-stop if any off-grid values
  # appear.
  "WritingEfficacy",   file.path(efa_dir, "WritingEfficacy_EFA_Primary.csv"), file.path(efa_dir, "WritingEfficacy_EFA_Sensitivity.csv"), "item_code",        5L, TRUE,
  "AIReflection",      file.path(efa_dir, "AI_Reflection_EFA_Primary.csv"),   file.path(efa_dir, "AI_Reflection_EFA_Sensitivity.csv"),   "item_num",         5L, FALSE,
  "BeliefsAboutAI",    file.path(efa_dir, "BeliefsAboutAI_EFA_Primary.csv"),  file.path(efa_dir, "BeliefsAboutAI_EFA_Sensitivity.csv"),  "item_num",         5L, FALSE
)

# First pass: leave as NA to generate recommendations only.
# Second pass: replace NA with locked k values after manual review.
locked_k <- c(
  IMI = 3L,
  WritingEfficacy = 3L, #picked 3 because 4 was more messy
  AIReflection = 2L,
  BeliefsAboutAI = NA_integer_
)

# Prior hypothesis only: WSE previously looked 3-factor in this project.
prior_k_hypothesis <- c(
  IMI = NA_integer_,
  WritingEfficacy = 3L,
  AIReflection = NA_integer_,
  BeliefsAboutAI = NA_integer_
)

salient_loading_cutoff <- 0.40
cross_loading_cutoff <- 0.30
heatmap_strong_cutoff <- salient_loading_cutoff
heatmap_weak_cutoff <- cross_loading_cutoff
loading_gap_cutoff <- 0.15
sparse_category_threshold <- 5L
kmo_fail_cutoff <- 0.50
kmo_marginal_cutoff <- 0.60
congruence_cutoff <- 0.85
core_item_retention_cutoff <- 0.50
```

------------------------------------------------------------------------

## Section 3: Helper Functions

```{r helpers}

read_efa_input <- function(spec, sample_label) {
  file <- if (sample_label == "primary") spec$primary_file else spec$sensitivity_file

  raw_dat <- read_csv(file, show_col_types = FALSE)
  assert_required_columns(
    raw_dat,
    c("participant_id", spec$item_col, "item_text", "score"),
    glue::glue("{spec$instrument} {sample_label} input")
  )
  assert_nonempty_df(raw_dat, glue::glue("{spec$instrument} {sample_label} input"))

  dat <- raw_dat |>
    transmute(
      instrument = spec$instrument,
      participant_id = as.character(participant_id),
      item_id = as.integer(.data[[spec$item_col]]),
      item_text = as.character(item_text),
      score = as.numeric(score),
      efa_sample = sample_label
    )

  if (isTRUE(spec$rescale_to_5)) {
    dat <- dat |>
      mutate(
        score = case_when(
          is.na(score)                      ~ NA_real_,
          score == 0 | score == 25 | score == 50 | score == 75 | score == 100 ~ (score / 25) + 1,
          TRUE                              ~ NA_real_
        )
      )
  }

  dat |>
    mutate(score = as.integer(round(score)))
}

verify_long_export <- function(dat, spec, sample_label) {
  if (anyNA(dat$participant_id) || anyNA(dat$item_id) || anyNA(dat$score)) {
    stop(glue::glue("{spec$instrument} {sample_label}: missing participant_id, item_id, or score detected."))
  }

  dupes <- dat |>
    count(participant_id, item_id, name = "n") |>
    filter(n != 1L)

  if (nrow(dupes) > 0) {
    stop(glue::glue("{spec$instrument} {sample_label}: non-unique participant/item rows detected."))
  }

  n_participants <- n_distinct(dat$participant_id)
  n_items <- n_distinct(dat$item_id)

  expected_rows <- n_participants * n_items
  if (nrow(dat) != expected_rows) {
    stop(glue::glue(
      "{spec$instrument} {sample_label}: export is not rectangular (rows={nrow(dat)}, expected={expected_rows})."
    ))
  }

  item_coverage <- dat |>
    count(participant_id, name = "item_count")
  if (any(item_coverage$item_count != n_items)) {
    stop(glue::glue("{spec$instrument} {sample_label}: at least one participant is missing item rows."))
  }

  participant_coverage <- dat |>
    count(item_id, name = "participant_count")
  if (any(participant_coverage$participant_count != n_participants)) {
    stop(glue::glue("{spec$instrument} {sample_label}: at least one item is missing participant rows."))
  }

  invisible(TRUE)
}

build_wide_matrix <- function(dat) {
  dat |>
    select(participant_id, item_id, score) |>
    mutate(item_id = as.character(item_id)) |>
    pivot_wider(names_from = item_id, values_from = score) |>
    arrange(participant_id)
}

build_item_diagnostics <- function(wide_df, item_lookup, spec) {
  score_cols <- setdiff(names(wide_df), "participant_id")

  base_diag <- map_dfr(score_cols, function(col_name) {
    item_id <- as.integer(col_name)
    values <- wide_df[[col_name]]
    variance_val <- var(values, na.rm = TRUE)
    counts <- tabulate(values, nbins = spec$scale_max)

    count_cols <- rep(NA_integer_, 7)
    count_cols[seq_len(spec$scale_max)] <- counts

    tibble(
      item_id = item_id,
      n_nonmissing = sum(!is.na(values)),
      prop_nonmissing = mean(!is.na(values)),
      n_levels = n_distinct(values, na.rm = TRUE),
      item_variance = variance_val,
      kept_for_efa = !is.na(variance_val) && variance_val > 0 && n_distinct(values, na.rm = TRUE) >= 2,
      sparse_category_warning = any(counts[counts > 0] < sparse_category_threshold),
      category_count_1 = count_cols[1],
      category_count_2 = count_cols[2],
      category_count_3 = count_cols[3],
      category_count_4 = count_cols[4],
      category_count_5 = count_cols[5],
      category_count_6 = count_cols[6],
      category_count_7 = count_cols[7]
    )
  })

  base_diag |>
    left_join(item_lookup |> select(item_id, item_text), by = "item_id") |>
    relocate(item_text, .after = item_id) |>
    arrange(item_id)
}

extract_scree_data <- function(rho) {
  eig <- eigen(rho, symmetric = TRUE, only.values = TRUE)$values

  tibble(
    factor_number = seq_along(eig),
    eigenvalue = as.numeric(eig)
  )
}

summarize_loadings_matrix <- function(loadings_matrix, item_lookup) {
  L <- as.matrix(loadings_matrix)

  if (is.null(dim(L))) {
    L <- matrix(L, ncol = 1)
  }

  abs_L <- abs(L)
  primary_factor_num <- max.col(abs_L, ties.method = "first")
  primary_loading <- L[cbind(seq_len(nrow(L)), primary_factor_num)]
  primary_abs_loading <- abs(primary_loading)

  secondary_abs_loading <- if (ncol(L) > 1) {
    apply(abs_L, 1, function(x) sort(x, decreasing = TRUE)[2])
  } else {
    rep(0, nrow(L))
  }

  loading_gap <- primary_abs_loading - secondary_abs_loading
  salient_loading <- primary_abs_loading >= salient_loading_cutoff
  cross_loading <- if (ncol(L) > 1) {
    secondary_abs_loading >= cross_loading_cutoff & loading_gap < loading_gap_cutoff
  } else {
    rep(FALSE, nrow(L))
  }

  clean_item <- salient_loading & !cross_loading

  item_details <- tibble(
    item_id = as.integer(rownames(L)),
    primary_factor_num = primary_factor_num,
    primary_factor_id = paste0("F", primary_factor_num),
    primary_loading = primary_loading,
    primary_abs_loading = primary_abs_loading,
    secondary_abs_loading = secondary_abs_loading,
    loading_gap = loading_gap,
    salient_loading = salient_loading,
    cross_loading = cross_loading,
    clean_item = clean_item
  ) |>
    left_join(item_lookup, by = "item_id") |>
    arrange(item_id)

  factor_summary <- tibble(factor_num = seq_len(ncol(L))) |>
    left_join(
      item_details |>
        filter(clean_item) |>
        count(primary_factor_num, name = "clean_item_count"),
      by = c("factor_num" = "primary_factor_num")
    ) |>
    mutate(
      clean_item_count = replace_na(clean_item_count, 0L),
      factor_id = paste0("F", factor_num),
      clean_factor = clean_item_count >= 3L
    )

  list(
    item_details = item_details,
    factor_summary = factor_summary
  )
}

fit_fa_model <- function(rho, n_obs, k) {
  tryCatch(
    suppressWarnings(
      psych::fa(
        r = rho,
        nfactors = k,
        n.obs = n_obs,
        fm = "minres",
        rotate = if (k == 1L) "none" else "oblimin"
      )
    ),
    error = function(e) NULL
  )
}

variance_explained_from_fa <- function(fa_fit) {
  if (is.null(fa_fit) || is.null(fa_fit$Vaccounted)) {
    return(NA_real_)
  }

  va <- fa_fit$Vaccounted
  if ("Proportion Var" %in% rownames(va)) {
    return(sum(va["Proportion Var", ], na.rm = TRUE))
  }

  NA_real_
}

extract_candidate_row <- function(instrument, k, fa_fit, item_lookup) {
  if (is.null(fa_fit)) {
    return(tibble(
      instrument = instrument,
      k = k,
      fit_success = FALSE,
      heywood = NA,
      rmsea = NA_real_,
      tli = NA_real_,
      rmsr = NA_real_,
      bic = NA_real_,
      variance_explained = NA_real_,
      clean_item_total = NA_integer_,
      clean_factor_count = NA_integer_,
      cross_loading_items = NA_integer_,
      structurally_clean = FALSE
    ))
  }

  L <- unclass(fa_fit$loadings)
  if (is.null(dim(L))) {
    L <- matrix(L, ncol = 1)
  }

  structure_summary <- summarize_loadings_matrix(L, item_lookup)
  heywood <- any(fa_fit$communality > 1 + 1e-6, na.rm = TRUE) ||
    any(fa_fit$uniquenesses < -1e-6, na.rm = TRUE)

  tibble(
    instrument = instrument,
    k = k,
    fit_success = TRUE,
    heywood = heywood,
    rmsea = unname(fa_fit$RMSEA["RMSEA"]),
    tli = unname(fa_fit$TLI),
    rmsr = unname(fa_fit$rms),
    bic = unname(fa_fit$BIC),
    variance_explained = variance_explained_from_fa(fa_fit),
    clean_item_total = sum(structure_summary$item_details$clean_item, na.rm = TRUE),
    clean_factor_count = sum(structure_summary$factor_summary$clean_factor, na.rm = TRUE),
    cross_loading_items = sum(structure_summary$item_details$cross_loading, na.rm = TRUE),
    structurally_clean = !heywood &&
      sum(structure_summary$factor_summary$clean_factor, na.rm = TRUE) == k
  )
}

safe_parallel_k <- function(rho, n_obs) {
  # Defensive seed: fa.parallel() uses internal random draws. Resetting the

  # seed here ensures parallel-analysis results are reproducible regardless of
  # upstream code changes that may consume random numbers.
  set.seed(42L)
  pa <- NULL
  pa_error_message <- NULL

  tryCatch(
    suppressWarnings(
      invisible(
        capture.output(
          pa <- psych::fa.parallel(
            rho,
            n.obs = n_obs,
            fm = "minres",
            fa = "fa",
            plot = FALSE
          ),
          file = NULL
        )
      )
    ),
    error = function(e) {
      pa <<- NULL
      pa_error_message <<- conditionMessage(e)
    }
  )

  if (is.null(pa)) {
    if (is.null(pa_error_message) || is.na(pa_error_message)) {
      pa_error_message <- "unknown error"
    }
    message(glue::glue("Parallel analysis failed; returning NA for suggested k. Error: {pa_error_message}"))
    return(NA_integer_)
  }

  as.integer(pa$nfact)
}

factorability_flag <- function(kmo_overall, usable_item_count) {
  case_when(
    usable_item_count < 3L ~ "Too few usable items",
    is.na(kmo_overall) ~ "KMO unavailable",
    kmo_overall < kmo_fail_cutoff ~ "Not suitable (<0.50)",
    kmo_overall < kmo_marginal_cutoff ~ "Marginal (0.50-0.59)",
    TRUE ~ "Adequate"
  )
}

plot_scree <- function(scree_df, title_text, subtitle_text = "Gray line = eigenvalue 1; blue dashed = parallel-analysis k; red dotted = recommended k") {
  parallel_lines <- scree_df |>
    distinct(efa_sample, parallel_k_used) |>
    filter(!is.na(parallel_k_used))

  recommended_lines <- scree_df |>
    distinct(efa_sample, recommended_k) |>
    filter(!is.na(recommended_k))

  ggplot(scree_df, aes(x = factor_number, y = eigenvalue)) +
    geom_hline(yintercept = 1, color = "#7a7a7a", linewidth = 0.7) +
    geom_vline(
      data = parallel_lines,
      aes(xintercept = parallel_k_used),
      inherit.aes = FALSE,
      color = "#4f79b7",
      linetype = "longdash",
      linewidth = 0.8
    ) +
    geom_vline(
      data = recommended_lines,
      aes(xintercept = recommended_k),
      inherit.aes = FALSE,
      color = "#c73e3a",
      linetype = "dotted",
      linewidth = 1
    ) +
    geom_line(color = "#1f2f56", linewidth = 0.9) +
    geom_point(color = "#1f2f56", size = 2.2) +
    scale_x_continuous(breaks = scree_df$factor_number) +
    labs(
      title = title_text,
      subtitle = subtitle_text,
      x = "Factor Number",
      y = "Eigenvalue"
    ) +
    facet_wrap(
      ~ efa_sample,
      ncol = 2,
      labeller = as_labeller(c(primary = "Primary", sensitivity = "Sensitivity"))
    ) +
    theme_minimal(base_size = 12) +
    theme(
      panel.grid.minor = element_blank(),
      plot.title = element_text(face = "bold")
    )
}

recommend_k <- function(candidate_rows, k_pa_raw, k_pa_used, factorability_value) {
  if (factorability_value == "Too few usable items") {
    return(list(
      recommended_k = NA_integer_,
      recommendation_status = "No clean recommendation",
      recommendation_reason = "Too few usable items"
    ))
  }

  if (factorability_value == "Not suitable (<0.50)") {
    return(list(
      recommended_k = NA_integer_,
      recommendation_status = "No clean recommendation",
      recommendation_reason = "Overall KMO below 0.50"
    ))
  }

  clean_rows <- candidate_rows |>
    filter(fit_success, structurally_clean)

  if (nrow(clean_rows) == 0) {
    return(list(
      recommended_k = NA_integer_,
      recommendation_status = "No clean recommendation",
      recommendation_reason = "No candidate k produced a structurally clean solution"
    ))
  }

  if (!is.na(k_pa_used) && any(clean_rows$k == k_pa_used)) {
    return(list(
      recommended_k = k_pa_used,
      recommendation_status = "Recommended",
      recommendation_reason = "Parallel analysis suggestion was structurally clean"
    ))
  }

  if (!is.na(k_pa_used)) {
    downward <- clean_rows |>
      filter(k < k_pa_used) |>
      arrange(desc(k))

    if (nrow(downward) > 0) {
      return(list(
        recommended_k = downward$k[1],
        recommendation_status = "Recommended",
        recommendation_reason = "Parallel-analysis k was messy; chose nearest simpler clean solution below"
      ))
    }

    upward <- clean_rows |>
      filter(k > k_pa_used) |>
      arrange(k)

    if (nrow(upward) > 0) {
      return(list(
        recommended_k = upward$k[1],
        recommendation_status = "Recommended",
        recommendation_reason = "No clean solution below parallel-analysis k; chose nearest clean solution above"
      ))
    }
  }

  fallback <- clean_rows |>
    arrange(k)

  list(
    recommended_k = fallback$k[1],
    recommendation_status = "Recommended",
    recommendation_reason = "Parallel analysis unavailable; chose smallest clean solution"
  )
}

run_sample_analysis <- function(dat, spec, sample_label, run_candidates) {
  verify_long_export(dat, spec, sample_label)

  item_lookup <- dat |>
    distinct(item_id, item_text) |>
    arrange(item_id)

  wide_df <- build_wide_matrix(dat)
  item_diag <- build_item_diagnostics(wide_df, item_lookup, spec)

  keep_item_ids <- item_diag |>
    filter(kept_for_efa) |>
    pull(item_id)

  participant_n <- n_distinct(dat$participant_id)
  usable_item_count <- length(keep_item_ids)

  if (usable_item_count < 3L) {
    diag_rows <- item_diag |>
      mutate(
        instrument = spec$instrument,
        efa_sample = sample_label,
        participant_n = participant_n,
        retained_item_count = usable_item_count,
        n_item_ratio = if_else(usable_item_count > 0, participant_n / usable_item_count, NA_real_),
        kmo_overall = NA_real_,
        item_msa = NA_real_,
        bartlett_chisq = NA_real_,
        bartlett_df = NA_real_,
        bartlett_p = NA_real_,
        polychoric_repair_needed = NA,
        min_eigen_unsmoothed = NA_real_,
        factorability_flag = "Too few usable items"
      )

    return(list(
      diagnostics = diag_rows,
      candidate_rows = tibble(),
      recommendation = tibble(),
      wide_kept = NULL,
      rho = NULL,
      item_lookup_kept = item_lookup |> filter(item_id %in% keep_item_ids),
      participant_n = participant_n,
      retained_item_count = usable_item_count,
      kmo_overall = NA_real_,
      factorability_flag = "Too few usable items",
      k_max = NA_integer_
    ))
  }

  wide_kept <- wide_df |>
    select(participant_id, all_of(as.character(keep_item_ids))) |>
    arrange(participant_id)

  X_int_df <- wide_kept |>
    select(-participant_id) |>
    mutate(across(everything(), as.integer)) |>
    as.data.frame()

  poly_out <- compute_polychoric_safe(X_int_df)
  rho <- poly_out$rho
  kmo <- psych::KMO(rho)
  bart <- psych::cortest.bartlett(rho, n = nrow(X_int_df))
  factorability_value <- factorability_flag(kmo$MSA, usable_item_count)

  msa_tbl <- tibble(
    item_id = as.integer(names(kmo$MSAi)),
    item_msa = as.numeric(kmo$MSAi)
  )

  diag_rows <- item_diag |>
    left_join(msa_tbl, by = "item_id") |>
    mutate(
      instrument = spec$instrument,
      efa_sample = sample_label,
      participant_n = participant_n,
      retained_item_count = usable_item_count,
      n_item_ratio = participant_n / usable_item_count,
      kmo_overall = as.numeric(kmo$MSA),
      bartlett_chisq = as.numeric(bart$chisq),
      bartlett_df = as.numeric(bart$df),
      bartlett_p = as.numeric(bart$p.value),
      polychoric_repair_needed = poly_out$repair_needed,
      min_eigen_unsmoothed = poly_out$min_eigen_unsmoothed,
      factorability_flag = factorability_value
    ) |>
    arrange(item_id) |>
    select(
      instrument, efa_sample, participant_n, retained_item_count, n_item_ratio,
      factorability_flag, kmo_overall, item_msa,
      bartlett_chisq, bartlett_df, bartlett_p,
      polychoric_repair_needed, min_eigen_unsmoothed,
      item_id, item_text, kept_for_efa, n_nonmissing, prop_nonmissing,
      n_levels, item_variance, sparse_category_warning,
      category_count_1, category_count_2, category_count_3, category_count_4,
      category_count_5, category_count_6, category_count_7
    )

  item_lookup_kept <- item_lookup |>
    filter(item_id %in% keep_item_ids) |>
    arrange(item_id)

  scree_data <- extract_scree_data(rho)

  if (!run_candidates) {
    return(list(
      diagnostics = diag_rows,
      candidate_rows = tibble(),
      recommendation = tibble(),
      scree_data = scree_data,
      wide_kept = wide_kept,
      rho = rho,
      item_lookup_kept = item_lookup_kept,
      participant_n = participant_n,
      retained_item_count = usable_item_count,
      kmo_overall = as.numeric(kmo$MSA),
      factorability_flag = factorability_value,
      k_max = as.integer(min(6L, floor(usable_item_count / 3)))
    ))
  }

  k_max <- as.integer(min(6L, floor(usable_item_count / 3)))
  k_values <- seq_len(k_max)
  k_pa_raw <- safe_parallel_k(rho, nrow(X_int_df))
  k_pa_used <- if (!is.na(k_pa_raw)) {
    as.integer(min(max(k_pa_raw, 1L), k_max))
  } else {
    NA_integer_
  }

  candidate_rows <- purrr::map(k_values, function(k) {
    fa_fit <- fit_fa_model(rho, nrow(X_int_df), k)
    extract_candidate_row(spec$instrument, k, fa_fit, item_lookup_kept) |>
      mutate(fa_fit_obj = list(fa_fit))
  }) |>
    bind_rows() |>
    mutate(
      efa_sample = sample_label,
      participant_n = participant_n,
      retained_item_count = usable_item_count,
      n_item_ratio = participant_n / retained_item_count,
      parallel_k_raw = k_pa_raw,
      parallel_k_used = k_pa_used,
      factorability_flag = factorability_value
    )

  recommendation <- recommend_k(candidate_rows, k_pa_raw, k_pa_used, factorability_value)

  recommendation_tbl <- tibble(
    instrument = spec$instrument,
    participant_n = participant_n,
    retained_item_count = usable_item_count,
    n_item_ratio = participant_n / retained_item_count,
    candidate_k_min = min(k_values),
    candidate_k_max = max(k_values),
    parallel_k_raw = k_pa_raw,
    parallel_k_used = k_pa_used,
    prior_k_hypothesis = prior_k_hypothesis[[spec$instrument]],
    recommended_k = recommendation$recommended_k,
    manual_locked_k = as.integer(locked_k[[spec$instrument]]),
    factorability_flag = factorability_value,
    recommendation_status = recommendation$recommendation_status,
    recommendation_reason = recommendation$recommendation_reason
  )

  scree_data <- scree_data |>
    mutate(
      instrument = spec$instrument,
      efa_sample = sample_label,
      participant_n = participant_n,
      retained_item_count = usable_item_count,
      parallel_k_raw = k_pa_raw,
      parallel_k_used = k_pa_used,
      recommended_k = recommendation$recommended_k
    )

  list(
    diagnostics = diag_rows,
    candidate_rows = candidate_rows,
    recommendation = recommendation_tbl,
    scree_data = scree_data,
    wide_kept = wide_kept,
    rho = rho,
    item_lookup_kept = item_lookup_kept,
    participant_n = participant_n,
    retained_item_count = usable_item_count,
    kmo_overall = as.numeric(kmo$MSA),
    factorability_flag = factorability_value,
    k_max = k_max
  )
}

extract_final_solution <- function(fa_fit, item_lookup, instrument, sample_label, locked_value, factor_order = NULL) {
  L <- as.matrix(unclass(fa_fit$loadings))
  if (is.null(dim(L))) {
    L <- matrix(L, ncol = 1)
  }

  if (is.null(factor_order)) {
    factor_order <- order(colSums(L^2, na.rm = TRUE), decreasing = TRUE)
  }

  L <- L[, factor_order, drop = FALSE]
  colnames(L) <- paste0("F", seq_len(ncol(L)))

  structure_summary <- summarize_loadings_matrix(L, item_lookup)

  loadings_long <- as_tibble(L, rownames = "item_id") |>
    mutate(item_id = as.integer(item_id)) |>
    pivot_longer(
      cols = starts_with("F"),
      names_to = "factor_id",
      values_to = "loading"
    ) |>
    left_join(
      structure_summary$item_details |>
        select(
          item_id, primary_factor_id, primary_loading, primary_abs_loading,
          secondary_abs_loading, loading_gap, salient_loading, cross_loading,
          clean_item
        ),
      by = "item_id"
    ) |>
    left_join(item_lookup, by = "item_id") |>
    mutate(
      instrument = instrument,
      efa_sample = sample_label,
      locked_k = locked_value,
      factor_is_primary = factor_id == primary_factor_id
    ) |>
    select(
      instrument, efa_sample, locked_k, item_id, item_text, factor_id, loading,
      factor_is_primary, primary_factor_id, primary_loading, primary_abs_loading,
      secondary_abs_loading, loading_gap, salient_loading, cross_loading, clean_item
    ) |>
    arrange(item_id, factor_id)

  item_map <- structure_summary$item_details |>
    filter(clean_item) |>
    transmute(
      instrument = instrument,
      locked_k = locked_value,
      item_id,
      item_text,
      factor_id = primary_factor_id,
      loading = primary_loading,
      abs_loading = primary_abs_loading,
      secondary_abs_loading,
      loading_gap
    ) |>
    arrange(factor_id, desc(abs_loading), item_id)

  factor_summary <- structure_summary$factor_summary |>
    transmute(
      instrument = instrument,
      efa_sample = sample_label,
      locked_k = locked_value,
      factor_id,
      clean_item_count,
      clean_factor
    )

  list(
    loadings_long = loadings_long,
    item_map = item_map,
    factor_summary = factor_summary,
    loadings_matrix = L
  )
}

match_factors_by_congruence <- function(primary_matrix, sensitivity_matrix) {
  k <- ncol(primary_matrix)

  if (k == 1L) {
    congr <- psych::factor.congruence(primary_matrix, sensitivity_matrix)
    return(tibble(
      primary_factor_id = "F1",
      sensitivity_factor_original = "F1",
      congruence = abs(as.numeric(congr[1, 1]))
    ))
  }

  congr <- psych::factor.congruence(primary_matrix, sensitivity_matrix)
  perms <- as.matrix(do.call(expand.grid, rep(list(seq_len(k)), k)))
  perms <- perms[apply(perms, 1, function(x) length(unique(x)) == k), , drop = FALSE]

  perm_scores <- apply(perms, 1, function(perm) {
    sum(abs(congr[cbind(seq_len(k), perm)]))
  })

  best_perm <- perms[which.max(perm_scores), ]

  tibble(
    primary_factor_id = paste0("F", seq_len(k)),
    sensitivity_factor_original = paste0("F", best_perm),
    congruence = abs(congr[cbind(seq_len(k), best_perm)])
  )
}

remap_sensitivity_solution <- function(final_solution, matching_tbl) {
  remap <- setNames(
    matching_tbl$primary_factor_id,
    matching_tbl$sensitivity_factor_original
  )

  final_solution$loadings_long <- final_solution$loadings_long |>
    mutate(
      original_factor_id = factor_id,
      factor_id = unname(remap[factor_id]),
      primary_factor_id = unname(remap[primary_factor_id])
    ) |>
    arrange(item_id, factor_id)

  final_solution$item_map <- final_solution$item_map |>
    mutate(
      original_factor_id = factor_id,
      factor_id = unname(remap[factor_id])
    ) |>
    arrange(factor_id, desc(abs_loading), item_id)

  final_solution$factor_summary <- final_solution$factor_summary |>
    mutate(
      original_factor_id = factor_id,
      factor_id = unname(remap[factor_id])
    ) |>
    arrange(factor_id)

  final_solution
}

format_loading_label <- function(x) {
  suffix <- case_when(
    abs(x) >= heatmap_strong_cutoff ~ "**",
    abs(x) >= heatmap_weak_cutoff ~ "*",
    TRUE ~ ""
  )

  paste0(formatC(x, format = "f", digits = 2), suffix)
}

prepare_heatmap_df <- function(loadings_long) {
  if (is.null(loadings_long) || nrow(loadings_long) == 0) {
    return(tibble())
  }

  item_levels <- loadings_long |>
    distinct(item_id, item_text, primary_factor_id, primary_abs_loading) |>
    arrange(primary_factor_id, desc(primary_abs_loading), item_id) |>
    mutate(item_label = str_wrap(item_text, width = 58)) |>
    pull(item_label)

  loadings_long |>
    mutate(
      item_label = str_wrap(item_text, width = 58),
      item_label = factor(item_label, levels = rev(unique(item_levels))),
      factor_id = factor(factor_id, levels = unique(factor_id)),
      loading_label = format_loading_label(loading)
    )
}

plot_loadings_heatmap <- function(loadings_long, title_text, subtitle_text = glue::glue("* |loading| >= {heatmap_weak_cutoff}   ** |loading| >= {heatmap_strong_cutoff}")) {
  heat_df <- prepare_heatmap_df(loadings_long)

  if (nrow(heat_df) == 0) {
    return(
      ggplot() +
        annotate("text", x = 0, y = 0, label = "No loadings available for this view yet.") +
        theme_void()
    )
  }

  ggplot(heat_df, aes(x = factor_id, y = item_label, fill = loading)) +
    geom_tile(color = "white", linewidth = 0.6) +
    geom_text(aes(label = loading_label), size = 3.7) +
    scale_fill_gradient2(
      low = "#c73e3a",
      mid = "#f7f7f7",
      high = "#4f79b7",
      midpoint = 0,
      limits = c(-1, 1),
      name = "Loading"
    ) +
    labs(
      title = title_text,
      subtitle = subtitle_text,
      x = NULL,
      y = NULL
    ) +
    theme_minimal(base_size = 12) +
    theme(
      panel.grid = element_blank(),
      axis.text.x = element_text(size = 11),
      axis.text.y = element_text(size = 11),
      plot.title = element_text(face = "bold")
    )
}

fit_preview_solution <- function(result_obj, sample_name, k_value) {
  sample_obj <- result_obj[[sample_name]]

  if (is.na(k_value) || is.null(sample_obj$rho) || is.na(sample_obj$kmo_overall)) {
    return(NULL)
  }

  if (sample_obj$factorability_flag == "Too few usable items") {
    return(NULL)
  }

  if (!is.na(sample_obj$kmo_overall) && sample_obj$kmo_overall < kmo_fail_cutoff) {
    return(NULL)
  }

  if (is.na(sample_obj$k_max) || k_value < 1L || k_value > sample_obj$k_max) {
    return(NULL)
  }

  fa_fit <- fit_fa_model(sample_obj$rho, sample_obj$participant_n, k_value)

  if (is.null(fa_fit)) {
    return(NULL)
  }

  extract_final_solution(
    fa_fit = fa_fit,
    item_lookup = sample_obj$item_lookup_kept,
    instrument = result_obj$spec$instrument,
    sample_label = sample_name,
    locked_value = k_value
  )
}
```

------------------------------------------------------------------------

## Section 4: Run Diagnostics and Candidate Solutions

```{r run-analyses}

analysis_results <- instrument_specs |>
  split(instrument_specs$instrument) |>
  purrr::map(function(spec_df) {
    spec <- as.list(spec_df[1, ])

    primary_dat <- read_efa_input(spec, "primary")
    sensitivity_dat <- read_efa_input(spec, "sensitivity")

    list(
      spec = spec,
      primary = run_sample_analysis(primary_dat, spec, "primary", run_candidates = TRUE),
      sensitivity = run_sample_analysis(sensitivity_dat, spec, "sensitivity", run_candidates = TRUE)
    )
  })

efa_diagnostics_summary <- map_dfr(analysis_results, function(x) {
  bind_rows(x$primary$diagnostics, x$sensitivity$diagnostics)
})

efa_candidate_solutions <- map_dfr(analysis_results, function(x) {
  x$primary$candidate_rows |>
    select(-any_of("fa_fit_obj"))
})

efa_recommended_k <- map_dfr(analysis_results, function(x) {
  x$primary$recommendation
})

efa_sensitivity_recommended_k <- map_dfr(analysis_results, function(x) {
  x$sensitivity$recommendation
})

efa_scree_data <- map_dfr(analysis_results, function(x) {
  bind_rows(x$primary$scree_data, x$sensitivity$scree_data)
})

recommended_preview_solutions <- purrr::imap(analysis_results, function(result_obj, instrument_name) {
  rec_k <- efa_recommended_k |>
    filter(instrument == instrument_name) |>
    pull(recommended_k)

  if (length(rec_k) != 1L || is.na(rec_k)) {
    return(NULL)
  }

  fit_preview_solution(result_obj, "primary", as.integer(rec_k))
})

observed_sample_counts <- efa_diagnostics_summary |>
  distinct(instrument, efa_sample, participant_n) |>
  arrange(instrument, efa_sample)

expected_sample_counts <- tribble(
  ~instrument,         ~efa_sample,    ~participant_n,
  "AIReflection",      "primary",                  91L,
  "AIReflection",      "sensitivity",              82L,
  "BeliefsAboutAI",    "primary",                  91L,
  "BeliefsAboutAI",    "sensitivity",              82L,
  "IMI",               "primary",                  88L,
  "IMI",               "sensitivity",              82L,
  "WritingEfficacy",   "primary",                  88L,
  "WritingEfficacy",   "sensitivity",              82L
) |>
  arrange(instrument, efa_sample)

sample_count_check <- observed_sample_counts |>
  full_join(expected_sample_counts, by = c("instrument", "efa_sample"), suffix = c("_observed", "_expected")) |>
  mutate(
    participant_n_observed = as.integer(participant_n_observed),
    participant_n_expected = as.integer(participant_n_expected),
    mismatch = is.na(participant_n_observed) | is.na(participant_n_expected) |
      (participant_n_observed != participant_n_expected)
  )

if (any(sample_count_check$mismatch)) {
  mismatches <- sample_count_check |>
    filter(mismatch) |>
    select(instrument, efa_sample, participant_n_observed, participant_n_expected)
  stop(
    paste0(
      "EFA sample counts do not match expected locked values. Mismatches:\n",
      paste(capture.output(print(mismatches)), collapse = "\n")
    ),
    call. = FALSE
  )
}

cat("=== Recommended K Summary ===\n")
print(efa_recommended_k)
```

------------------------------------------------------------------------

## Section 5: Review Tables

```{r review-tables}

cat("=== Diagnostics Snapshot ===\n")
efa_diagnostics_summary |>
  distinct(
    instrument, efa_sample, participant_n, retained_item_count,
    n_item_ratio, factorability_flag, kmo_overall,
    bartlett_chisq, bartlett_df, bartlett_p, polychoric_repair_needed
  ) |>
  arrange(instrument, efa_sample) |>
  print(n = 20)

cat("\n=== Candidate Solutions ===\n")
efa_candidate_solutions |>
  arrange(instrument, k) |>
  print(n = 50)

cat("\n=== Locked K Settings ===\n")
tibble(
  instrument = names(locked_k),
  locked_k = as.integer(locked_k)
) |>
  print()
```

------------------------------------------------------------------------

## Section 5A: What Happens Next

```{r workflow-status}
workflow_status <- efa_recommended_k |>
  transmute(
    instrument,
    participant_n,
    retained_item_count,
    factorability_flag,
    recommended_k,
    manual_locked_k,
    current_stage = case_when(
      is.na(manual_locked_k) ~ "First-pass review only",
      TRUE ~ "Locked final solution requested"
    ),
    next_action = case_when(
      factorability_flag == "Not suitable (<0.50)" ~ "Do not lock k yet; instrument is not factorable enough",
      factorability_flag == "Too few usable items" ~ "No EFA possible with current retained items",
      is.na(recommended_k) ~ "Review diagnostics manually; no clean recommended k",
      is.na(manual_locked_k) ~ paste0("Review the preview heatmap, then set locked_k = ", recommended_k, " if you agree"),
      manual_locked_k == recommended_k ~ "Rerun complete; interpret final item map and sensitivity results",
      TRUE ~ "Rerun complete; interpret the locked final solution you chose"
    )
  )

knitr::kable(workflow_status)
```

`KMO` is important because it checks whether the items share enough common variance to justify factor analysis in the first place. In plain English: if `KMO` is very low, the items are not hanging together well enough for a factor solution to be trustworthy, even if you can still mathematically fit one. That is why this script uses `KMO` as a gatekeeper before recommending a final `k`.

```{r primary-vs-sensitivity-k}
sample_kmo <- efa_diagnostics_summary |>
  distinct(instrument, efa_sample, kmo_overall)

k_comparison <- efa_recommended_k |>
  left_join(
    sample_kmo |>
      filter(efa_sample == "primary") |>
      select(instrument, primary_kmo = kmo_overall),
    by = "instrument"
  ) |>
  select(
    instrument,
    primary_kmo,
    primary_parallel_k = parallel_k_used,
    primary_recommended_k = recommended_k,
    primary_reason = recommendation_reason
  ) |>
  left_join(
    efa_sensitivity_recommended_k |>
      left_join(
        sample_kmo |>
          filter(efa_sample == "sensitivity") |>
          select(instrument, sensitivity_kmo = kmo_overall),
        by = "instrument"
      ) |>
      select(
        instrument,
        sensitivity_kmo,
        sensitivity_parallel_k = parallel_k_used,
        sensitivity_recommended_k = recommended_k,
        sensitivity_reason = recommendation_reason
      ),
    by = "instrument"
  ) |>
  mutate(
    primary_kmo = round(primary_kmo, 3),
    sensitivity_kmo = round(sensitivity_kmo, 3),
    factor_count_changed_in_sensitivity = case_when(
      is.na(primary_recommended_k) & is.na(sensitivity_recommended_k) ~ "No recommendation either way",
      primary_recommended_k == sensitivity_recommended_k ~ "No",
      TRUE ~ "Yes"
    )
  )

knitr::kable(k_comparison)
```

This is a **robustness table**, not the main decision rule. The primary sample still drives the working recommendation, and the sensitivity column is there to show whether that recommendation looks stable in the stricter paired-only sample.

At the end of the EFA workflow, the goal is **not** to stop at a pretty loading pattern. The goal is to make a defendable item-to-factor map. Once you lock `k` and rerun:

- `03_efa_analysis/efa_diagnostics/EFA_Final_Loadings.csv` stores the full loading matrix for the locked solution
- `03_efa_analysis/EFA_Final_Item_Map.csv` keeps only clean items assigned to one factor
- `03_efa_analysis/efa_diagnostics/EFA_Sensitivity_Comparison.csv` tells you whether that structure survives the stricter paired sample

That final item map is what we use later to build **unit-weighted subscale means** for the ANOVAs.

## Section 5B: Scree Plots

Scree plots are a helpful **visual supplement**, not the main decision rule. In this workflow, the working recommendation still comes from the combination of parallel analysis, factorability checks, and whether the candidate loading pattern is structurally clean.

```{r scree-plots, results='asis', fig.width=11, fig.height=5.5}
for (instrument_name in unique(efa_scree_data$instrument)) {
  scree_df <- efa_scree_data |>
    filter(instrument == instrument_name)

  cat("\n\n### ", instrument_name, "\n\n", sep = "")

  print(
    plot_scree(
      scree_df,
      title_text = glue::glue("{instrument_name}: Scree Plot"),
      subtitle_text = "Gray line = eigenvalue 1; blue dashed = parallel-analysis k; red dotted = recommended k"
    )
  )

  cat("\n\n")
}
```

------------------------------------------------------------------------

## Section 5C: Recommended Solution Preview Heatmaps

These are **review-stage previews** of the recommended primary solutions. They help you see whether the proposed factor structure looks interpretable before you commit to a locked `k`.

```{r preview-heatmaps, results='asis', fig.width=12, fig.height=8}
for (instrument_name in names(recommended_preview_solutions)) {
  preview_solution <- recommended_preview_solutions[[instrument_name]]
  rec_row <- efa_recommended_k |>
    filter(instrument == instrument_name)

  cat("\n\n### ", instrument_name, "\n\n", sep = "")

  if (is.null(preview_solution)) {
    cat("No preview heatmap available because this instrument does not currently have a clean recommended `k`.\n\n")
    next
  }

  cat(
    glue::glue(
      "Recommended primary preview at `k = {rec_row$recommended_k[[1]]}`. This is for visual review only until `locked_k` is filled in.\n\n"
    )
  )

  print(
    plot_loadings_heatmap(
      preview_solution$loadings_long,
      title_text = glue::glue("{instrument_name}: Recommended Primary Preview"),
      subtitle_text = glue::glue("* |loading| >= {cross_loading_cutoff}   ** |loading| >= {salient_loading_cutoff}")
    )
  )

  cat("\n\n")
}
```

------------------------------------------------------------------------

## Section 6: Final Locked Solutions and Sensitivity Check

```{r final-solutions}
empty_final_loadings <- tibble(
  instrument = character(),
  efa_sample = character(),
  locked_k = integer(),
  item_id = integer(),
  item_text = character(),
  factor_id = character(),
  loading = numeric(),
  factor_is_primary = logical(),
  primary_factor_id = character(),
  primary_loading = numeric(),
  primary_abs_loading = numeric(),
  secondary_abs_loading = numeric(),
  loading_gap = numeric(),
  salient_loading = logical(),
  cross_loading = logical(),
  clean_item = logical(),
  original_factor_id = character()
)

empty_item_map <- tibble(
  instrument = character(),
  locked_k = integer(),
  item_id = integer(),
  item_text = character(),
  factor_id = character(),
  loading = numeric(),
  abs_loading = numeric(),
  secondary_abs_loading = numeric(),
  loading_gap = numeric(),
  original_factor_id = character()
)

empty_sensitivity <- tibble(
  instrument = character(),
  locked_k = integer(),
  factor_id = character(),
  matched_sensitivity_factor = character(),
  congruence = numeric(),
  primary_core_n = integer(),
  sensitivity_core_n = integer(),
  shared_core_n = integer(),
  shared_core_prop = numeric(),
  factor_sensitivity_failure = logical(),
  instrument_sensitivity_failure = logical(),
  sensitivity_note = character()
)

final_loadings_list <- list()
final_item_map_list <- list()
sensitivity_rows <- list()

fit_locked_primary <- function(result_obj, locked_value) {
  spec <- result_obj$spec
  primary <- result_obj$primary

  if (is.na(locked_value)) {
    return(NULL)
  }

  if (primary$factorability_flag == "Too few usable items") {
    stop(glue::glue("{spec$instrument}: locked k requested but fewer than 3 usable items remain."))
  }

  if (!is.na(primary$kmo_overall) && primary$kmo_overall < kmo_fail_cutoff) {
    stop(glue::glue("{spec$instrument}: locked k requested but overall KMO is below 0.50."))
  }

  if (locked_value < 1L || locked_value > primary$k_max) {
    stop(glue::glue(
      "{spec$instrument}: locked k={locked_value} is outside the tested range 1:{primary$k_max}."
    ))
  }

  candidate_row <- primary$candidate_rows |>
    filter(k == locked_value)

  if (nrow(candidate_row) != 1L || !candidate_row$structurally_clean) {
    stop(glue::glue(
      "{spec$instrument}: locked k={locked_value} does not produce a structurally clean primary solution."
    ))
  }

  fa_fit <- candidate_row$fa_fit_obj[[1]]
  if (is.null(fa_fit)) {
    fa_fit <- fit_fa_model(primary$rho, primary$participant_n, locked_value)
  }
  if (is.null(fa_fit)) {
    stop(glue::glue("{spec$instrument}: final primary EFA failed at locked k={locked_value}."))
  }

  extract_final_solution(
    fa_fit = fa_fit,
    item_lookup = primary$item_lookup_kept,
    instrument = spec$instrument,
    sample_label = "primary",
    locked_value = locked_value
  )
}

fit_locked_sensitivity <- function(result_obj, locked_value) {
  spec <- result_obj$spec
  sensitivity <- result_obj$sensitivity

  if (sensitivity$factorability_flag == "Too few usable items") {
    return(list(
      final_solution = NULL,
      failure_note = "Sensitivity sample had fewer than 3 usable items"
    ))
  }

  if (!is.na(sensitivity$kmo_overall) && sensitivity$kmo_overall < kmo_fail_cutoff) {
    return(list(
      final_solution = NULL,
      failure_note = "Sensitivity KMO was below 0.50"
    ))
  }

  if (locked_value < 1L || locked_value > sensitivity$k_max) {
    return(list(
      final_solution = NULL,
      failure_note = "Locked k was outside the tested sensitivity range"
    ))
  }

  candidate_row <- sensitivity$candidate_rows |>
    filter(k == locked_value)

  fa_fit <- NULL
  if (nrow(candidate_row) == 1L && "fa_fit_obj" %in% names(candidate_row)) {
    fa_fit <- candidate_row$fa_fit_obj[[1]]
  }
  if (is.null(fa_fit)) {
    fa_fit <- fit_fa_model(sensitivity$rho, sensitivity$participant_n, locked_value)
  }
  if (is.null(fa_fit)) {
    return(list(
      final_solution = NULL,
      failure_note = "Sensitivity EFA failed at the locked k"
    ))
  }

  list(
    final_solution = extract_final_solution(
      fa_fit = fa_fit,
      item_lookup = sensitivity$item_lookup_kept,
      instrument = spec$instrument,
      sample_label = "sensitivity",
      locked_value = locked_value
    ),
    failure_note = NA_character_
  )
}

for (instrument_name in names(analysis_results)) {
  locked_value <- locked_k[[instrument_name]]

  if (is.na(locked_value)) {
    next
  }

  result_obj <- analysis_results[[instrument_name]]
  primary_final <- fit_locked_primary(result_obj, locked_value)
  sensitivity_fit <- fit_locked_sensitivity(result_obj, locked_value)

  final_loadings_list[[instrument_name]] <- primary_final$loadings_long
  final_item_map_list[[instrument_name]] <- primary_final$item_map

  if (is.null(sensitivity_fit$final_solution)) {
    sensitivity_rows[[instrument_name]] <- tibble(
      instrument = instrument_name,
      locked_k = locked_value,
      factor_id = paste0("F", seq_len(locked_value)),
      matched_sensitivity_factor = NA_character_,
      congruence = NA_real_,
      primary_core_n = as.integer(
        table(factor(primary_final$item_map$factor_id, levels = paste0("F", seq_len(locked_value))))
      ),
      sensitivity_core_n = NA_integer_,
      shared_core_n = NA_integer_,
      shared_core_prop = NA_real_,
      factor_sensitivity_failure = TRUE,
      instrument_sensitivity_failure = TRUE,
      sensitivity_note = sensitivity_fit$failure_note
    )
    next
  }

  primary_matrix <- primary_final$loadings_matrix
  sensitivity_matrix <- sensitivity_fit$final_solution$loadings_matrix

  common_items <- intersect(rownames(primary_matrix), rownames(sensitivity_matrix))

  if (length(common_items) < 3L) {
    sensitivity_rows[[instrument_name]] <- tibble(
      instrument = instrument_name,
      locked_k = locked_value,
      factor_id = paste0("F", seq_len(locked_value)),
      matched_sensitivity_factor = NA_character_,
      congruence = NA_real_,
      primary_core_n = as.integer(
        table(factor(primary_final$item_map$factor_id, levels = paste0("F", seq_len(locked_value))))
      ),
      sensitivity_core_n = NA_integer_,
      shared_core_n = NA_integer_,
      shared_core_prop = NA_real_,
      factor_sensitivity_failure = TRUE,
      instrument_sensitivity_failure = TRUE,
      sensitivity_note = "Fewer than 3 common retained items across primary and sensitivity"
    )
    next
  }

  matching_tbl <- match_factors_by_congruence(
    primary_matrix[common_items, , drop = FALSE],
    sensitivity_matrix[common_items, , drop = FALSE]
  )

  sensitivity_final <- remap_sensitivity_solution(sensitivity_fit$final_solution, matching_tbl)
  final_loadings_list[[paste0(instrument_name, "_sensitivity")]] <- sensitivity_final$loadings_long

  factor_rows <- map_dfr(seq_len(locked_value), function(idx) {
    factor_id <- paste0("F", idx)
    matched_row <- matching_tbl |>
      filter(primary_factor_id == factor_id)

    primary_core <- primary_final$item_map |>
      filter(.data$factor_id == factor_id) |>
      pull(item_id)

    sensitivity_core <- sensitivity_final$item_map |>
      filter(.data$factor_id == factor_id) |>
      pull(item_id)

    shared_core <- intersect(primary_core, sensitivity_core)
    shared_prop <- if (length(primary_core) > 0) {
      length(shared_core) / length(primary_core)
    } else {
      NA_real_
    }

    factor_fail <- (matched_row$congruence < congruence_cutoff) ||
      (!is.na(shared_prop) && shared_prop < core_item_retention_cutoff)

    tibble(
      instrument = instrument_name,
      locked_k = locked_value,
      factor_id = factor_id,
      matched_sensitivity_factor = matched_row$sensitivity_factor_original,
      congruence = matched_row$congruence,
      primary_core_n = length(primary_core),
      sensitivity_core_n = length(sensitivity_core),
      shared_core_n = length(shared_core),
      shared_core_prop = shared_prop,
      factor_sensitivity_failure = factor_fail,
      sensitivity_note = NA_character_
    )
  })

  instrument_failure <- any(factor_rows$factor_sensitivity_failure, na.rm = TRUE)
  factor_rows <- factor_rows |>
    mutate(instrument_sensitivity_failure = instrument_failure)

  sensitivity_rows[[instrument_name]] <- factor_rows
}

efa_final_loadings <- if (length(final_loadings_list) > 0) {
  bind_rows(final_loadings_list) |>
    mutate(
      original_factor_id = coalesce(original_factor_id, factor_id)
    ) |>
    arrange(instrument, efa_sample, item_id, factor_id)
} else {
  empty_final_loadings
}

efa_final_item_map <- if (length(final_item_map_list) > 0) {
  bind_rows(final_item_map_list) |>
    mutate(original_factor_id = factor_id) |>
    arrange(instrument, factor_id, desc(abs_loading), item_id)
} else {
  empty_item_map
}

efa_sensitivity_comparison <- if (length(sensitivity_rows) > 0) {
  bind_rows(sensitivity_rows) |>
    arrange(instrument, factor_id)
} else {
  empty_sensitivity
}

if (all(is.na(locked_k))) {
  cat("No locked_k values set. Final loadings, final item map, and sensitivity comparison will be empty placeholders.\n")
}

assert_expected_count(nrow(efa_recommended_k), 4L, "EFA_Recommended_K row count")
assert_required_columns(
  efa_recommended_k,
  c("instrument", "recommended_k", "factorability_flag", "recommendation_status", "recommendation_reason"),
  "EFA_Recommended_K contract"
)
assert_unique_key_rows(efa_recommended_k, "instrument", "EFA_Recommended_K")

if (nrow(efa_final_item_map) > 0) {
  assert_required_columns(
    efa_final_item_map,
    c("instrument", "factor_id", "item_id"),
    "EFA_Final_Item_Map contract"
  )
  assert_factor_id_format(efa_final_item_map$factor_id, "EFA_Final_Item_Map factor_id")
  assert_unique_key_rows(efa_final_item_map, c("instrument", "item_id"), "EFA_Final_Item_Map unique clean items")
}
```

------------------------------------------------------------------------

## Section 6A: Locked Solution Heatmaps

```{r locked-heatmaps, results='asis', fig.width=12, fig.height=8}
if (nrow(efa_final_loadings) == 0) {
  cat("No locked-solution heatmaps yet because `locked_k` is still all `NA`. Use the preview heatmaps above to choose `k`, then rerun the file.\n")
} else {
  heatmap_groups <- efa_final_loadings |>
    group_by(instrument, efa_sample) |>
    group_split()

  for (heat_df in heatmap_groups) {
    instrument_name <- unique(heat_df$instrument)
    sample_name <- unique(heat_df$efa_sample)
    locked_value <- unique(heat_df$locked_k)

    cat("\n\n### ", instrument_name, " (", sample_name, ")\n\n", sep = "")

    print(
      plot_loadings_heatmap(
        heat_df,
        title_text = glue::glue("{instrument_name}: Locked {str_to_title(sample_name)} Solution (k = {locked_value})"),
        subtitle_text = glue::glue("* |loading| >= {cross_loading_cutoff}   ** |loading| >= {salient_loading_cutoff}")
      )
    )

    cat("\n\n")
  }
}
```

------------------------------------------------------------------------

## Section 7: Export Outputs

```{r export}
write_csv(efa_diagnostics_summary, file.path(efa_diagnostics_dir, "EFA_Diagnostics_Summary.csv"))
write_csv(efa_candidate_solutions, file.path(efa_diagnostics_dir, "EFA_Candidate_Solutions.csv"))
write_csv(efa_recommended_k, file.path(script_dir, "EFA_Recommended_K.csv"))
write_csv(efa_final_loadings, file.path(efa_diagnostics_dir, "EFA_Final_Loadings.csv"))
write_csv(efa_sensitivity_comparison, file.path(efa_diagnostics_dir, "EFA_Sensitivity_Comparison.csv"))
write_csv(efa_final_item_map, file.path(script_dir, "EFA_Final_Item_Map.csv"))

cat("Exported:", file.path(efa_diagnostics_dir, "EFA_Diagnostics_Summary.csv"), "\n")
cat("Exported:", file.path(efa_diagnostics_dir, "EFA_Candidate_Solutions.csv"), "\n")
cat("Exported:", file.path(script_dir, "EFA_Recommended_K.csv"), "\n")
cat("Exported:", file.path(efa_diagnostics_dir, "EFA_Final_Loadings.csv"), "\n")
cat("Exported:", file.path(efa_diagnostics_dir, "EFA_Sensitivity_Comparison.csv"), "\n")
cat("Exported:", file.path(script_dir, "EFA_Final_Item_Map.csv"), "\n")

efa_analysis_manifest <- tibble(
  output_type = c(
    "efa_diagnostics_summary",
    "efa_candidate_solutions",
    "efa_recommended_k",
    "efa_final_loadings",
    "efa_sensitivity_comparison",
    "efa_final_item_map"
  ),
  path = c(
    file.path(efa_diagnostics_dir, "EFA_Diagnostics_Summary.csv"),
    file.path(efa_diagnostics_dir, "EFA_Candidate_Solutions.csv"),
    file.path(script_dir, "EFA_Recommended_K.csv"),
    file.path(efa_diagnostics_dir, "EFA_Final_Loadings.csv"),
    file.path(efa_diagnostics_dir, "EFA_Sensitivity_Comparison.csv"),
    file.path(script_dir, "EFA_Final_Item_Map.csv")
  ),
  rows = c(
    nrow(efa_diagnostics_summary),
    nrow(efa_candidate_solutions),
    nrow(efa_recommended_k),
    nrow(efa_final_loadings),
    nrow(efa_sensitivity_comparison),
    nrow(efa_final_item_map)
  ),
  description = c(
    "Per-instrument EFA diagnostics: KMO, factorability flag, recommended k",
    "All candidate factor solutions (k=1..max) with fit statistics",
    "Locked recommended k per instrument; consumed by 05_beliefs and 06_findings",
    "Final factor loadings for locked solutions (primary + sensitivity samples)",
    "Tucker congruence coefficients comparing primary vs sensitivity solutions",
    "Final locked item-to-factor map (instrument, factor_id, item_id); consumed by 04_order_effects"
  )
)

write_csv(efa_analysis_manifest, file.path(efa_diagnostics_dir, "EFA_Analysis_Manifest.csv"))
knitr::kable(
  efa_analysis_manifest |> select(-rows),
  caption = "03_efa_analysis.qmd — Output Manifest"
)
```

Side tangent, looked at AI beliefs variance and found some interesting ones with this

```{r}
library(tidyverse)

# 1. Load the diagnostics file
diag <- read_csv(file.path(efa_diagnostics_dir, "EFA_Diagnostics_Summary.csv"),
                 show_col_types = FALSE)

# 2. Filter for Beliefs, select columns, and rank by Variance (High to Low)
beliefs_variance <- diag |>
  filter(
    instrument == "BeliefsAboutAI",
    efa_sample == "primary",
    kept_for_efa == TRUE
  ) |>
  select(item_id, item_text, item_variance, item_msa, n_levels) |>
  arrange(desc(item_variance)) # 'desc' puts the highest variance at the top

# 3. Export this to a new CSV for your records
write_csv(beliefs_variance, file.path(audit_dir, "Beliefs_Variance_Ranked.csv"))

# 4. Print it to the console so you can see it now
cat("=== BeliefsAboutAI Items Ranked by Variance (High to Low) ===\n")
print(beliefs_variance, n = 30)
```
