---
title: "Cowriters Survey Order Effects Analysis"
format:
  html:
    toc: true
    toc-depth: 2
output-dir: "04_order_effects"
execute:
  echo: false
  warning: false
  message: false
editor:
  markdown:
    wrap: 72
---

# Order Effects Analysis

This script is a downstream inferential step after the EFA
export/analysis pipeline. It builds composite scores from the locked EFA
item map, compares Traditional-First versus AI-First participants, and
tests Tool × Order interactions with a secondary topic-controlled model.

```{r setup}

library(tidyverse)
library(knitr)
if (!file.exists("scoring_helpers.R")) {
  stop("Required file scoring_helpers.R not found.", call. = FALSE)
}
source("scoring_helpers.R", local = knitr::knit_global())
set.seed(42L)
```

## Section 1: Paths and Input Data

```{r load-data}
order_levels <- c("Traditional_First", "AI_First")
topic_levels <- c("Metaphor", "Category")
adjustment_methods <- c("BH", "bonferroni")

script_dir <- "04_order_effects"
csv_dir <- file.path(script_dir, "csv")
plot_dir <- file.path(script_dir, "plots")
master_wide_file <- file.path("02_efa_exports", "Final_Master_Wide.csv")
final_item_map_file <- file.path("03_efa_analysis", "EFA_Final_Item_Map.csv")
factor_scores_all_file <- file.path("06_interesting_findings", "csv", "Factor_Scores_All_Instruments.csv")
beliefs_wide_file <- file.path("05_beliefs_item_analysis", "csv", "BeliefsAboutAI_Wide.csv")
factor_name_map_file <- file.path("06_interesting_findings", "csv", "Factor_Name_Map.csv")
beliefs_long_file <- file.path("02_efa_exports", "efa", "BeliefsAboutAI_EFA_Primary.csv")
dir.create(csv_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(plot_dir, recursive = TRUE, showWarnings = FALSE)

master_wide <- read_csv(master_wide_file, show_col_types = FALSE)
tracking <- read_csv(
  "Participant Tracking - IDs and Conditions Table.csv",
  show_col_types = FALSE
)
final_item_map <- read_csv(final_item_map_file, show_col_types = FALSE)

required_master_cols <- c("participant_id", "order", "condition_1", "condition_2")
missing_master_cols <- setdiff(required_master_cols, names(master_wide))
if (length(missing_master_cols) > 0) {
  stop(
    paste0(
      basename(master_wide_file), " is missing required columns: ",
      paste(missing_master_cols, collapse = ", ")
    ),
    call. = FALSE
  )
}

required_tracking_cols <- c("ParticipantID", "Topic 1", "Topic 2", "Condition 1", "Condition 2")
missing_tracking_cols <- setdiff(required_tracking_cols, names(tracking))
if (length(missing_tracking_cols) > 0) {
  stop(
    paste0(
      "Participant tracking file is missing required columns: ",
      paste(missing_tracking_cols, collapse = ", ")
    ),
    call. = FALSE
  )
}

assert_required_columns(final_item_map, c("instrument", "factor_id", "item_id"), "EFA_Final_Item_Map")
assert_factor_id_format(final_item_map$factor_id, "EFA_Final_Item_Map factor_id")
```

## Section 2: Build Analysis-Ready Participant Table (Order + Topic)

```{r build-participant-table}

tracking_topics <- tracking |>
  transmute(
    participant_id = as.character(ParticipantID),
    topic_1 = as.character(`Topic 1`),
    topic_2 = as.character(`Topic 2`),
    condition_1_track = as.character(`Condition 1`),
    condition_2_track = as.character(`Condition 2`)
  ) |>
  filter(!is.na(participant_id))

assert_unique_pid_rows(
  tracking_topics,
  pid_col = "participant_id",
  context_label = "tracking_topics"
)

participant_analysis <- master_wide |>
  mutate(participant_id = as.character(participant_id)) |>
  inner_join(tracking_topics, by = "participant_id") |>
  mutate(
    order = factor(order, levels = order_levels),
    traditional_topic = case_when(
      condition_1 == "Alone" ~ topic_1,
      condition_2 == "Alone" ~ topic_2,
      TRUE ~ NA_character_
    ),
    ai_topic = case_when(
      condition_1 == "LLM" ~ topic_1,
      condition_2 == "LLM" ~ topic_2,
      TRUE ~ NA_character_
    ),
    traditional_topic = factor(traditional_topic, levels = topic_levels),
    ai_topic          = factor(ai_topic,          levels = topic_levels),
    # first_topic = the article type in session 1 (between-subjects covariate).
    # Because design is fully counterbalanced, first_topic = traditional_topic
    # for Traditional-First participants and = ai_topic for AI-First participants.
    # It is constant per participant and goes outside Error() in the ANOVA.
    first_topic = factor(
      case_when(
        order == "Traditional_First" ~ as.character(traditional_topic),
        order == "AI_First"          ~ as.character(ai_topic),
        TRUE                         ~ NA_character_
      ),
      levels = topic_levels
    )
  )

assert_expected_count(nrow(participant_analysis), 82L, "participant_analysis row count")
assert_unique_pid_rows(participant_analysis, "participant_id", "participant_analysis")
assert_no_missing_values(
  participant_analysis,
  c("participant_id", "order", "condition_1", "condition_2", "topic_1", "topic_2", "first_topic"),
  "participant_analysis"
)

order_mismatch <- participant_analysis |>
  filter(
    !is.na(order),
    !is.na(condition_1),
    !is.na(condition_2),
    (
      order == "Traditional_First" & !(condition_1 == "Alone" & condition_2 == "LLM")
    ) |
      (
        order == "AI_First" & !(condition_1 == "LLM" & condition_2 == "Alone")
      )
  )

if (nrow(order_mismatch) > 0) {
  stop(
    paste0(
      "Order/condition mismatch detected for participants: ",
      paste(order_mismatch$participant_id, collapse = ", ")
    ),
    call. = FALSE
  )
}

participant_topic_summary <- participant_analysis |>
  summarise(
    n_participants = n(),
    traditional_topic_missing = sum(is.na(traditional_topic)),
    ai_topic_missing = sum(is.na(ai_topic)),
    order_missing = sum(is.na(order))
  )

write_csv(participant_topic_summary, file.path(csv_dir, "Participant_Topic_Summary.csv"))
```

## Section 3: Build Unit-Weighted Composite Scores from Locked Item Map

```{r build-composites}

instrument_prefix_map <- tribble(
  ~instrument,       ~item_prefix,
  "IMI",            "IMI_",
  "WritingEfficacy", "Efficacy_",
  "AIReflection",   "Refl_",
  "BeliefsAboutAI", "Beliefs_"
)

locked_item_map <- if ("efa_sample" %in% names(final_item_map)) {
  final_item_map |>
    filter(efa_sample == "primary")
} else {
  final_item_map
}

if ("clean_item" %in% names(locked_item_map)) {
  locked_item_map <- locked_item_map |> filter(clean_item)
}

locked_item_map <- locked_item_map |>
  filter(!is.na(instrument), !is.na(factor_id), !is.na(item_id)) |>
  distinct(instrument, factor_id, item_id)

if (nrow(locked_item_map) == 0) {
  stop(paste0("No locked clean items found in ", final_item_map_file, "."), call. = FALSE)
}

print(unique(locked_item_map$instrument))
print(filter(locked_item_map, grepl("rit", instrument, ignore.case = TRUE)))

composite_membership <- locked_item_map |>
  left_join(instrument_prefix_map, by = "instrument") |>
  mutate(
    item_col = paste0(item_prefix, item_id),
    composite = paste0(instrument, "_", factor_id)
  )

if (any(is.na(composite_membership$item_prefix))) {
  bad_instruments <- composite_membership |>
    filter(is.na(item_prefix)) |>
    distinct(instrument) |>
    pull(instrument)

  stop(
    paste0(
      "Instrument-to-prefix mapping missing for: ",
      paste(bad_instruments, collapse = ", ")
    ),
    call. = FALSE
  )
}

missing_item_cols <- setdiff(unique(composite_membership$item_col), names(participant_analysis))
if (length(missing_item_cols) > 0) {
  stop(
    paste0(
      "Composite item columns missing from Final_Master_Wide: ",
      paste(missing_item_cols, collapse = ", ")
    ),
    call. = FALSE
  )
}

composite_specs <- composite_membership |>
  group_by(instrument, factor_id, composite) |>
  summarise(
    item_cols = list(sort(unique(item_col))),
    n_items = n(),
    composite_meaning = paste0(
      first(instrument),
      " ",
      first(factor_id),
      " unit-weighted mean of clean items"
    ),
    rowmeans_na_rm = FALSE,
    .groups = "drop"
  )

assert_nonempty_df(composite_specs, "composite_specs")

participant_with_composites <- participant_analysis

for (i in seq_len(nrow(composite_specs))) {
  comp_name <- composite_specs$composite[[i]]
  item_cols <- composite_specs$item_cols[[i]]

  participant_with_composites[[comp_name]] <- rowMeans(
    participant_with_composites[, item_cols, drop = FALSE],
    # Hard stop on partial composites: because these are unit-weighted means of
    # locked EFA item sets, every contributing item must be present.
    na.rm = FALSE
  )
}

composite_cols <- composite_specs$composite

composite_score_summary <- participant_with_composites |>
  summarise(
    across(
      all_of(composite_cols),
      list(
        mean = ~ mean(.x, na.rm = TRUE),
        sd = ~ sd(.x, na.rm = TRUE),
        n_nonmissing = ~ sum(!is.na(.x))
      ),
      .names = "{.col}__{.fn}"
    )
  )

write_csv(composite_membership, file.path(csv_dir, "Composite_Item_Membership.csv"))
write_csv(composite_specs, file.path(csv_dir, "Composite_Specs.csv"))
write_csv(composite_score_summary, file.path(csv_dir, "Composite_Score_Summary.csv"))
```

## Section 4: Long Composite Table + Descriptives by Order

```{r descriptives}

composite_long <- participant_with_composites |>
  select(
    participant_id,
    order,
    traditional_topic,
    ai_topic,
    all_of(composite_cols)
  ) |>
  pivot_longer(
    cols = all_of(composite_cols),
    names_to = "composite",
    values_to = "score"
  )

order_descriptives <- composite_long |>
  group_by(composite, order) |>
  summarise(
    n = sum(!is.na(score)),
    mean = mean(score, na.rm = TRUE),
    sd = sd(score, na.rm = TRUE),
    median = median(score, na.rm = TRUE),
    iqr = IQR(score, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(composite, order)

write_csv(composite_long, file.path(csv_dir, "Composite_Long.csv"))
write_csv(order_descriptives, file.path(csv_dir, "Order_Descriptives_By_Composite.csv"))
```

```{r descriptive-plots, fig.width=10, fig.height=6}

make_filename_safe <- function(x) {
  stringr::str_replace_all(x, "[^A-Za-z0-9_\\-]+", "_")
}

for (comp in composite_cols) {
  p <- composite_long |>
    filter(composite == comp) |>
    ggplot(aes(x = order, y = score, fill = order)) +
    geom_violin(alpha = 0.35, width = 0.9, color = NA, na.rm = TRUE) +
    geom_boxplot(width = 0.18, outlier.alpha = 0.6, na.rm = TRUE) +
    scale_fill_manual(values = c(
      "Traditional_First" = "#4f79b7",
      "AI_First" = "#c96b3b"
    )) +
    labs(
      title = paste0("Order Split: ", comp),
      x = "Order Group",
      y = "Composite Score",
      fill = NULL
    ) +
    theme_minimal(base_size = 12)

  file_stub <- make_filename_safe(comp)

  ggsave(
    filename = file.path(plot_dir, paste0(file_stub, "_order_violin_box.png")),
    plot = p,
    width = 10,
    height = 6,
    units = "in",
    dpi = 300,
    bg = "white"
  )

  ggsave(
    filename = file.path(plot_dir, paste0(file_stub, "_order_violin_box.pdf")),
    plot = p,
    width = 10,
    height = 6,
    units = "in",
    bg = "white"
  )
}
```

## Section 5: Mann-Whitney U Tests by Order

**Multiple-comparison correction strategy:** Composite-level tests
(Section 5) form one correction family — all EFA-derived composites
tested for order effects. Item-level tests (Section 5b) use a two-tier
strategy: BH correction within each instrument (controls FDR per
instrument) and Bonferroni correction globally across all items. Mixed
ANOVA interaction p-values (Section 6) are corrected within each model
type (primary, topic-controlled) separately.

```{r mann-whitney}

# Two-vector wilcox: x = Trad-First scores, y = AI-First scores.
# wilcox.test() returns the rank-sum W statistic for x, not U directly.
# Convert W -> U before computing rank-biserial effect size.
#
# Sign convention: positive rb -> Traditional-First tends higher.
# This depends on W being the rank-sum for the Traditional-First group,
# which requires trad_vec to always be passed as x (first argument).
# The formula interface (used in the item-level section below) also produces
# W for the first factor level of `order`, which is "Traditional_First"
# because order_levels is defined with that level first.
rank_biserial_from_u <- function(u_stat, n1, n2) {
  (2 * as.numeric(u_stat) / (n1 * n2)) - 1
}

mann_whitney_results <- map_dfr(composite_cols, function(comp) {
  dat <- participant_with_composites |>
    select(order, all_of(comp)) |>
    rename(score = all_of(comp)) |>
    filter(!is.na(order), !is.na(score))

  trad_vec <- dat |> filter(order == "Traditional_First") |> pull(score)
  ai_vec   <- dat |> filter(order == "AI_First")          |> pull(score)

  n_trad <- length(trad_vec)
  n_ai   <- length(ai_vec)

  med_trad <- median(trad_vec)
  med_ai   <- median(ai_vec)

  if (n_trad < 2 || n_ai < 2) {
    return(tibble(
      composite = comp,
      n_traditional_first = n_trad,
      n_ai_first = n_ai,
      median_traditional_first = med_trad,
      median_ai_first = med_ai,
      w_stat = NA_real_,
      u_stat = NA_real_,
      p_value = NA_real_,
      estimate_hl = NA_real_,
      conf_low = NA_real_,
      conf_high = NA_real_,
      rank_biserial = NA_real_,
      note = "insufficient sample size"
    ))
  }

  test <- suppressWarnings(
    wilcox.test(
      x         = trad_vec,
      y         = ai_vec,
      exact     = FALSE,
      conf.int  = TRUE,
      conf.level = 0.95
    )
  )

  w <- as.numeric(unname(test$statistic))


  tibble(
    composite = comp,
    n_traditional_first = n_trad,
    n_ai_first = n_ai,
    median_traditional_first = med_trad,
    median_ai_first = med_ai,
    w_stat = w,
    u_stat = as.numeric(w),
    p_value = test$p.value,
    estimate_hl = if (!is.null(test$estimate)) as.numeric(test$estimate) else NA_real_,
    conf_low  = if (!is.null(test$conf.int)) as.numeric(test$conf.int[[1]]) else NA_real_,
    conf_high = if (!is.null(test$conf.int)) as.numeric(test$conf.int[[2]]) else NA_real_,
    rank_biserial = rank_biserial_from_u(w, n_trad, n_ai),
    note = NA_character_
  )
}) |>
  left_join(
    composite_specs |>
      select(composite, instrument, factor_id, n_items, composite_meaning, rowmeans_na_rm),
    by = "composite"
  ) |>
  mutate(
    p_bh = p.adjust(p_value, method = adjustment_methods[[1]]),
    p_bonferroni = p.adjust(p_value, method = adjustment_methods[[2]]),
    effect_size = rank_biserial
  ) |>
  select(
    composite, instrument, factor_id, n_items, composite_meaning, rowmeans_na_rm,
    n_traditional_first, n_ai_first, median_traditional_first, median_ai_first,
    w_stat, u_stat, p_value, p_bh, p_bonferroni, estimate_hl, conf_low, conf_high,
    effect_size, note
  ) |>
  arrange(p_bh, p_value)

write_csv(mann_whitney_results, file.path(csv_dir, "Mann_Whitney_Order_Comparisons.csv"))
```

```{r}
# ============================================================
# S5b: Item-Level Order Effects (Mann-Whitney per item)
# ============================================================

# Prefix map: instrument name → column prefix in master data
item_prefix_map <- tribble(
  ~instrument,       ~prefix,    ~n_items,
  "IMI",             "IMI_",         18,
  "WritingEfficacy", "Efficacy_",    20,
  "AIReflection",    "Refl_",        12,
  "BeliefsAboutAI",  "Beliefs_",     22
)

# Build long item-level dataframe
item_long <- item_prefix_map |>
  pmap_dfr(function(instrument, prefix, n_items) {
    cols <- paste0(prefix, seq_len(n_items))
    missing <- setdiff(cols, names(participant_with_composites))
    if (length(missing) > 0) {
      stop(
        paste0(
          "Item-level order effects are missing required columns for ",
          instrument, ": ", paste(missing, collapse = ", ")
        ),
        call. = FALSE
      )
    }
    participant_with_composites |>
      select(participant_id, order, all_of(cols)) |>
      pivot_longer(
        cols = all_of(cols),
        names_to  = "column",
        values_to = "score"
      ) |>
      mutate(
        instrument = instrument,
        item_num   = as.integer(str_extract(column, "\\d+$")),
        item_label = paste0(instrument, "_item", item_num)
      )
  })

# Mann-Whitney per item
item_mw_results <- item_long |>
  group_by(instrument, item_label, item_num) |>
  group_modify(function(df, keys) {
    trad <- df |> filter(order == "Traditional_First") |> pull(score)
    ai   <- df |> filter(order == "AI_First")          |> pull(score)
    
    if (length(trad) < 3 || length(ai) < 3) {
      return(tibble(
        n_traditional_first = length(trad),
        n_ai_first          = length(ai),
        w_stat = NA_real_, u_stat = NA_real_, p_value = NA_real_,
        estimate_hl = NA_real_, conf_low = NA_real_, conf_high = NA_real_,
        rank_biserial = NA_real_, note = "Insufficient data"
      ))
    }
    
    test <- wilcox.test(trad, ai, exact = FALSE, conf.int = TRUE)
    w    <- as.numeric(unname(test$statistic))
    r_rb <- rank_biserial_from_u(w, length(trad), length(ai))
    
    tibble(
      n_traditional_first = length(trad),
      n_ai_first          = length(ai),
      w_stat        = w,
      u_stat        = w,
      p_value       = test$p.value,
      estimate_hl   = test$estimate,
      conf_low      = test$conf.int[[1]],
      conf_high     = test$conf.int[[2]],
      rank_biserial = as.numeric(r_rb),
      note          = NA_character_
    )
  }) |>
  ungroup()

# BH correction within each instrument, Bonferroni global
item_mw_results <- item_mw_results |>
  group_by(instrument) |>
  mutate(p_bh_within = p.adjust(p_value, method = "BH")) |>
  ungroup() |>
  mutate(p_bonferroni_global = p.adjust(p_value, method = "bonferroni")) |>
  arrange(instrument, item_num)

# Flag significant items
item_mw_results <- item_mw_results |>
  mutate(
    sig_within_instrument = p_bh_within       < 0.05,
    sig_global            = p_bonferroni_global < 0.05
  )

# Export
write_csv(
  item_mw_results,
  file.path(csv_dir, "Item_Level_Order_Comparisons.csv")
)

# Summary table — significant items only
sig_items <- item_mw_results |>
  filter(sig_within_instrument) |>
  select(instrument, item_label, n_traditional_first, n_ai_first,
         w_stat, p_value, p_bh_within, p_bonferroni_global, rank_biserial)

cat("\n--- Significant items (BH within instrument) ---\n")
if (nrow(sig_items) == 0) {
  cat("None.\n")
} else {
  print(kable(sig_items))
}
```

## Section 6a: Approved Two-Way ANOVA Order Effects (One-Time Surveys)

```{r approved-lm-order-effects}

# ── Helper: run lm, extract terms, compute partial eta-sq ──────────────────
run_two_way_lm <- function(data, dv, formula_chr, survey_label) {
  dat <- data |> filter(!is.na(.data[[dv]]))
  
  if (nrow(dat) < 10) {
    warning(paste0("Skipping ", survey_label, "/", dv, ": n = ", nrow(dat)))
    return(NULL)
  }
  
  fit <- lm(as.formula(paste(dv, formula_chr)), data = dat)
  av  <- anova(fit)
  
  tibble(
    survey    = survey_label,
    composite = dv,
    term      = rownames(av),
    df        = av$Df,
    ss        = av$`Sum Sq`,
    ms        = av$`Mean Sq`,
    f_value   = av$`F value`,
    p_value   = av$`Pr(>F)`,
    partial_eta_sq = av$`Sum Sq` / (av$`Sum Sq` + av[nrow(av), "Sum Sq"])
  ) |>
    filter(term != "Residuals")
}

# ── Identify composites per survey ─────────────────────────────────────────
imi_composites <- composite_specs |>
  filter(instrument == "IMI") |>
  pull(composite)

wse_composites <- composite_specs |>
  filter(instrument == "WritingEfficacy") |>
  pull(composite)

air_composites <- composite_specs |>
  filter(instrument == "AIReflection") |>
  pull(composite)

beliefs_cols_present <- names(participant_with_composites)[
  str_starts(names(participant_with_composites), "Beliefs_") &
  !str_detect(names(participant_with_composites), "_F")
]

beliefs_efa_composites <- composite_specs |>
  filter(instrument == "BeliefsAboutAI") |>
  pull(composite)

if (length(beliefs_efa_composites) > 0) {
  beliefs_dvs <- beliefs_efa_composites
} else if (length(beliefs_cols_present) > 0) {
  participant_with_composites <- participant_with_composites |>
    mutate(BeliefsAboutAI_mean = rowMeans(
      pick(all_of(beliefs_cols_present)), na.rm = FALSE
    ))
  beliefs_dvs <- "BeliefsAboutAI_mean"
  message("BeliefsAboutAI: no EFA composites found, using item mean.")
} else {
  beliefs_dvs <- character(0)
  warning("BeliefsAboutAI: no item columns or composites found.")
}

# ── Run models ──────────────────────────────────────────────────────────────

# Model 1: IMI — score ~ Order * traditional_topic (Traditional session instrument)
imi_results <- map_dfr(
  imi_composites,
  ~ run_two_way_lm(
      participant_with_composites,
      dv = .x,
      formula_chr = "~ order * traditional_topic",
      survey_label = "IMI"
    )
)

# Model 2: WritingEfficacy — score ~ Order * traditional_topic (Traditional session instrument)
wse_results <- map_dfr(
  wse_composites,
  ~ run_two_way_lm(
      participant_with_composites,
      dv = .x,
      formula_chr = "~ order * traditional_topic",
      survey_label = "WritingEfficacy"
    )
)

# Model 3: AIReflection — score ~ Order * ai_topic (AI session instrument)
air_results <- map_dfr(
  air_composites,
  ~ run_two_way_lm(
      participant_with_composites,
      dv = .x,
      formula_chr = "~ order * ai_topic",
      survey_label = "AIReflection"
    )
)

# Model 4: BeliefsAboutAI — score ~ Order * ai_topic (AI session instrument)
beliefs_results <- map_dfr(
  beliefs_dvs,
  ~ run_two_way_lm(
      participant_with_composites,
      dv = .x,
      formula_chr = "~ order * ai_topic",
      survey_label = "BeliefsAboutAI"
    )
)

all_lm_results <- bind_rows(imi_results, wse_results, air_results, beliefs_results)

# ── BH correction — three separate families ─────────────────────────────────
term_family <- function(term_chr) {
  case_when(
    str_detect(term_chr, ":") ~ "interaction",
    str_detect(term_chr, "order") & !str_detect(term_chr, "topic") ~ "order_main",
    str_detect(term_chr, "topic") & !str_detect(term_chr, "order") ~ "topic_main",
    TRUE ~ "other"
  )
}

all_lm_corrected <- all_lm_results |>
  mutate(
    term_clean  = str_trim(term),
    term_family = term_family(term_clean)
  ) |>
  group_by(term_family) |>
  mutate(p_bh = p.adjust(p_value, method = "BH")) |>
  ungroup() |>
  arrange(survey, composite, term_clean)

write_csv(all_lm_corrected, file.path(csv_dir, "TwoWay_ANOVA_Order_Effects.csv"))

all_lm_corrected |>
  mutate(across(c(f_value, p_value, p_bh, partial_eta_sq), ~ round(.x, 4))) |>
  kable(caption = "Two-way ANOVA order effects. p_bh = BH-corrected within term family.")
```

```{r cell-means-tables}

make_cell_means <- function(data, dv, order_var, topic_var, label) {
  data |>
    filter(!is.na(.data[[dv]]), !is.na(.data[[order_var]]), !is.na(.data[[topic_var]])) |>
    group_by(.data[[order_var]], .data[[topic_var]]) |>
    summarise(
      n    = n(),
      mean = round(mean(.data[[dv]], na.rm = TRUE), 3),
      sd   = round(sd(.data[[dv]], na.rm = TRUE), 3),
      .groups = "drop"
    ) |>
    rename(Order = 1, Topic = 2) |>
    mutate(composite = dv, survey = label)
}

# IMI + WSE: topic = traditional_topic
trad_cell_means <- map_dfr(
  c(imi_composites, wse_composites),
  ~ make_cell_means(
      participant_with_composites,
      dv = .x,
      order_var = "order",
      topic_var = "traditional_topic",
      label = if (.x %in% imi_composites) "IMI" else "WritingEfficacy"
    )
)

# AIReflection + BeliefsAboutAI: topic = ai_topic
ai_session_cell_means <- map_dfr(
  c(air_composites, beliefs_dvs),
  ~ make_cell_means(
      participant_with_composites,
      dv = .x,
      order_var = "order",
      topic_var = "ai_topic",
      label = if (.x %in% air_composites) "AIReflection" else "BeliefsAboutAI"
    )
)

all_cell_means <- bind_rows(trad_cell_means, ai_session_cell_means)

write_csv(all_cell_means, file.path(csv_dir, "TwoWay_ANOVA_Cell_Means.csv"))

for (comp in unique(all_cell_means$composite)) {
  cat("\n\n###", comp, "\n")
  all_cell_means |>
    filter(composite == comp) |>
    select(survey, Order, Topic, n, mean, sd) |>
    kable(caption = paste("Cell means:", comp)) |>
    print()
}
```

## Section 6: Predeclared Tool-Comparable Pairs and 2×2 Mixed ANOVAs

```{r mixed-anovas}

extract_aov_table <- function(aov_fit) {
  # Flattens a nested summary(aov(..., Error(...))) object into one tidy table
  # with term-level statistics and the originating error stratum label.
  summary_obj <- summary(aov_fit)

  map2_dfr(summary_obj, names(summary_obj), function(stratum_obj, stratum_name) {
    if (!is.list(stratum_obj) || length(stratum_obj) == 0) {
      return(tibble())
    }

    tab <- stratum_obj[[1]]

    if (!is.data.frame(tab)) {
      return(tibble())
    }

    tab |>
      as.data.frame() |>
      tibble::rownames_to_column("term") |>
      as_tibble() |>
      mutate(stratum = stratum_name)
  })
}

extract_term <- function(aov_fit, term_name) {
  tbl <- extract_aov_table(aov_fit)

  if (nrow(tbl) == 0) {
    return(tibble(
      term = term_name,
      stratum = NA_character_,
      df = NA_real_,
      sum_sq = NA_real_,
      mean_sq = NA_real_,
      f_value = NA_real_,
      p_value = NA_real_
    ))
  }

  p_col <- names(tbl)[str_detect(names(tbl), "Pr\\(>F\\)")]
  f_col <- names(tbl)[str_detect(names(tbl), "F value")]

  if (length(p_col) > 1 || length(f_col) > 1) {
    stop(
      paste0(
        "ANOVA term extraction found ambiguous statistic columns. ",
        "Detected p columns: ", paste(p_col, collapse = ", "),
        " | F columns: ", paste(f_col, collapse = ", ")
      ),
      call. = FALSE
    )
  }

  row <- tbl |>
    filter(term == term_name) |>
    slice(1)

  if (nrow(row) == 0) {
    return(tibble(
      term = term_name,
      stratum = NA_character_,
      df = NA_real_,
      sum_sq = NA_real_,
      mean_sq = NA_real_,
      f_value = NA_real_,
      p_value = NA_real_
    ))
  }

  tibble(
    term = term_name,
    stratum = row$stratum,
    df = if ("Df" %in% names(row)) as.numeric(row$Df) else NA_real_,
    sum_sq = if ("Sum Sq" %in% names(row)) as.numeric(row$`Sum Sq`) else NA_real_,
    mean_sq = if ("Mean Sq" %in% names(row)) as.numeric(row$`Mean Sq`) else NA_real_,
    f_value = if (length(f_col) == 1) as.numeric(row[[f_col]]) else NA_real_,
    p_value = if (length(p_col) == 1) as.numeric(row[[p_col]]) else NA_real_
  )
}

# Predeclared tool-comparable pairs: each row declares one Traditional-side
# instrument and one AI-side instrument to compare at matched factor IDs (F1,
# F2, ...). This is intentionally explicit so the pairing logic can be edited
# without changing model code.
pairing_map <- tribble(
  ~traditional_instrument, ~ai_instrument,
  "IMI", "AIReflection",
  "WritingEfficacy", "BeliefsAboutAI"
)

composite_lookup <- composite_specs |>
  select(instrument, factor_id, composite) |>
  distinct()

pair_specs <- pairing_map |>
  left_join(
    composite_lookup |>
      rename(
        traditional_instrument = instrument,
        traditional_composite = composite
      ),
    by = "traditional_instrument"
  ) |>
  left_join(
    composite_lookup |>
      rename(
        ai_instrument = instrument,
        ai_composite = composite
      ),
    by = c("ai_instrument", "factor_id")
  ) |>
  filter(!is.na(traditional_composite), !is.na(ai_composite)) |>
  mutate(
    pair_id = paste0(traditional_instrument, "_", factor_id, "__vs__", ai_instrument, "_", factor_id),
    construct = factor_id
  ) |>
  distinct(pair_id, construct, traditional_instrument, ai_instrument, traditional_composite, ai_composite)

# Check if any declared pairs were dropped (e.g. BeliefsAboutAI has no locked
# EFA factors because KMO < 0.50 — its composite rows will be absent).
# This is expected for BeliefsAboutAI; a hard stop fires for anything else.
declared_instruments <- unique(c(pairing_map$traditional_instrument, pairing_map$ai_instrument))
available_locked_instruments <- unique(composite_lookup$instrument)
dropped_instruments   <- setdiff(declared_instruments, available_locked_instruments)
if (length(dropped_instruments) > 0) {
  expected_drops <- c("BeliefsAboutAI")
  unexpected_drops <- setdiff(dropped_instruments, expected_drops)

  cat(
    "NOTE: The following instruments were declared in pairing_map but have no ",
    "locked EFA composites and were dropped before pair_specs was built: ",
    paste(dropped_instruments, collapse = ", "), "\n"
  )

  if (length(unexpected_drops) > 0) {
    stop(
      paste0(
        "Unexpected instrument(s) dropped from pair_specs: ",
        paste(unexpected_drops, collapse = ", "),
        ". Check that locked_k is set for these instruments in 03_efa_analysis.qmd."
      ),
      call. = FALSE
    )
  }

  cat("BeliefsAboutAI drop is expected (KMO < 0.50, not factorable).\n")
}

write_csv(pair_specs, file.path(csv_dir, "Tool_Comparable_Pair_Specs.csv"))

tool_factor_levels <- c("Traditional", "AI")
traditional_score_col <- "traditional_score"
ai_score_col <- "ai_score"

mixed_anova_rows <- if (nrow(pair_specs) == 0) {
  tibble(
    pair_id = character(),
    construct = character(),
    traditional_composite = character(),
    ai_composite = character(),
    n_participants = integer(),
    model = character(),
    tool_order_f = numeric(),
    tool_order_p = numeric(),
    note = character()
  )
} else {
  map_dfr(seq_len(nrow(pair_specs)), function(i) {
    spec <- pair_specs[i, ]

   long_dat <- participant_with_composites |>
  transmute(
    participant_id,
    order,
    first_topic,           # ADD THIS
    traditional_topic,
    ai_topic,
    traditional_score = .data[[spec$traditional_composite[[1]]]],
    ai_score = .data[[spec$ai_composite[[1]]]]
  ) |>
      pivot_longer(
        cols = all_of(c(traditional_score_col, ai_score_col)),
        names_to = "tool_row",
        values_to = "score"
      ) |>
      mutate(
        Tool = factor(if_else(tool_row == traditional_score_col, tool_factor_levels[[1]], tool_factor_levels[[2]]),
                      levels = tool_factor_levels),
        # Topic intentionally omitted here — first_topic (between-subjects)
        # is carried from participant_with_composites and used in the ANOVA directly.
        Order = factor(order, levels = order_levels)
      ) |>
      filter(!is.na(score), !is.na(Order), !is.na(Tool))

    if (n_distinct(long_dat$participant_id) < 4) {
      return(bind_rows(
        tibble(
          pair_id = spec$pair_id,
          construct = spec$construct,
          traditional_composite = spec$traditional_composite,
          ai_composite = spec$ai_composite,
          n_participants = n_distinct(long_dat$participant_id),
          model = "primary",
          tool_order_f = NA_real_,
          tool_order_p = NA_real_,
          note = "insufficient overlap for mixed ANOVA"
        ),
        tibble(
          pair_id = spec$pair_id,
          construct = spec$construct,
          traditional_composite = spec$traditional_composite,
          ai_composite = spec$ai_composite,
          n_participants = n_distinct(long_dat$participant_id),
          model = "topic_controlled",
          tool_order_f = NA_real_,
          tool_order_p = NA_real_,
          note = "insufficient overlap for mixed ANOVA"
        )
      ))
    }

    fit_primary <- suppressWarnings(
      aov(score ~ Tool * Order + Error(participant_id / Tool), data = long_dat)
    )

    fit_topic <- suppressWarnings(
      # first_topic is between-subjects (constant per participant) so it goes
      # outside Error(). This controls for article-type assignment without
      # conflating topic with the within-subjects Tool factor.
      # Sphericity note: the within-subjects Tool factor has only two levels,
      # so the sphericity assumption is satisfied by definition.
      aov(score ~ Tool * Order + first_topic + Error(participant_id / Tool), data = long_dat)
    )

    primary_interaction <- extract_term(fit_primary, "Tool:Order")
    topic_interaction <- extract_term(fit_topic, "Tool:Order")

    bind_rows(
      tibble(
        pair_id = spec$pair_id,
        construct = spec$construct,
        traditional_composite = spec$traditional_composite,
        ai_composite = spec$ai_composite,
        n_participants = n_distinct(long_dat$participant_id),
        model = "primary",
        tool_order_f = primary_interaction$f_value,
        tool_order_p = primary_interaction$p_value,
        note = NA_character_
      ),
      tibble(
        pair_id = spec$pair_id,
        construct = spec$construct,
        traditional_composite = spec$traditional_composite,
        ai_composite = spec$ai_composite,
        n_participants = n_distinct(long_dat$participant_id),
        model = "topic_controlled",
        tool_order_f = topic_interaction$f_value,
        tool_order_p = topic_interaction$p_value,
        note = NA_character_
      )
    )
  })
}

mixed_anova_results <- mixed_anova_rows |>
  group_by(model) |>
  mutate(
    p_bh = p.adjust(tool_order_p, method = adjustment_methods[[1]]),
    p_bonferroni = p.adjust(tool_order_p, method = adjustment_methods[[2]])
  ) |>
  ungroup() |>
  mutate(
    sphericity_note = "Within-subject Tool factor has 2 levels; sphericity is met by definition."
  ) |>
  arrange(model, p_bh, tool_order_p)

interaction_summary <- mixed_anova_results |>
  select(
    pair_id, construct, model, n_participants,
    traditional_composite, ai_composite,
    tool_order_f, tool_order_p, p_bh, p_bonferroni
  ) |>
  mutate(model = factor(model, levels = c("primary", "topic_controlled"))) |>
  pivot_wider(
    names_from = model,
    values_from = c(tool_order_f, tool_order_p, p_bh, p_bonferroni),
    names_expand = TRUE
  ) |>
  mutate(
    persists_after_topic_control = case_when(
      is.na(p_bh_primary) | is.na(p_bh_topic_controlled) ~ NA_character_,
      p_bh_primary < 0.05 & p_bh_topic_controlled < 0.05 ~ "Yes (BH-adjusted)",
      p_bh_primary < 0.05 & p_bh_topic_controlled >= 0.05 ~ "No (drops after topic control)",
      TRUE ~ "Not significant in primary model (BH-adjusted)"
    )
  )

write_csv(mixed_anova_results, file.path(csv_dir, "Mixed_ANOVA_Tool_Order_Results.csv"))
write_csv(interaction_summary, file.path(csv_dir, "Tool_Order_Interaction_Summary.csv"))
```

## Section 7: Export Ready Tables

```{r final-exports}

analysis_ready <- participant_with_composites |>
  select(
    participant_id,
    order,
    condition_1,
    condition_2,
    traditional_topic,
    ai_topic,
    first_topic,
    ends_with("_F1"),
    ends_with("_F2"),
    ends_with("_F3")
  )


write_csv(analysis_ready, file.path(csv_dir, "Order_Effects_Analysis_Ready.csv"))

export_manifest <- tibble(
  output_type = c(
    "analysis_ready",
    "composite_membership",
    "composite_specs",
    "order_descriptives",
    "mann_whitney",
    "item_level_mann_whitney",
    "pair_specs",
    "mixed_anova",
    "interaction_summary"
  ),
  file = c(
    "Order_Effects_Analysis_Ready.csv",
    "Composite_Item_Membership.csv",
    "Composite_Specs.csv",
    "Order_Descriptives_By_Composite.csv",
    "Mann_Whitney_Order_Comparisons.csv",
    "Item_Level_Order_Comparisons.csv",
    "Tool_Comparable_Pair_Specs.csv",
    "Mixed_ANOVA_Tool_Order_Results.csv",
    "Tool_Order_Interaction_Summary.csv"
  )
)

write_csv(export_manifest, file.path(csv_dir, "Order_Effects_Export_Manifest.csv"))

kable(export_manifest)
```

## Section 8: Order-Stratified Correlation Analysis

This section asks whether key cross-instrument factor correlations and
Beliefs item correlations differ depending on which session participants
completed first. Each correlation is computed three ways: full sample,
Traditional-First only, AI-First only. Fisher's z-test formally tests
whether the two subgroup correlations differ significantly.

**Interpretation note:** Splitting N = 82 into \~45 and \~37 reduces
power substantially. A subgroup correlation going null does not
necessarily mean the effect changed — it may simply reflect reduced
sample size. Use Fisher's z p-value, not subgroup nullity alone, to
judge differences.

```{r order-strat-setup}
library(psych)  # for paired.r()

# --- Load inputs ---
# Factor scores: use the file produced by Script 06 (or 05 — same scores)
factor_scores_all <- read_csv(
  factor_scores_all_file,
  show_col_types = FALSE
) |>
  mutate(participant_id = as.character(participant_id))

# Beliefs item wide: produced by Script 05
beliefs_wide <- read_csv(
  beliefs_wide_file,
  show_col_types = FALSE
) |>
  mutate(participant_id = as.character(participant_id))

# Order labels: already built in Section 2 of this script as participant_analysis
# Pull just what we need
order_labels <- participant_analysis |>
  select(participant_id, order) |>
  mutate(participant_id = as.character(participant_id))

# --- Join everything ---
strat_base <- order_labels |>
  left_join(factor_scores_all, by = "participant_id") |>
  left_join(beliefs_wide,      by = "participant_id")

factor_cols_strat <- names(factor_scores_all) |> setdiff("participant_id")
belief_cols_strat <- names(beliefs_wide)       |> setdiff("participant_id")
```

```{r order-strat-helpers}

# Compute Spearman rho for one group subset
spearman_one_group <- function(data, col_x, col_y, group_label) {
  d <- data |>
    select(all_of(c(col_x, col_y))) |>
    filter(!is.na(.data[[col_x]]), !is.na(.data[[col_y]]))

  if (nrow(d) < 10 || n_distinct(d[[col_x]]) < 2 || n_distinct(d[[col_y]]) < 2) {
    return(tibble(
      group = group_label, n = nrow(d),
      rho = NA_real_, p = NA_real_, note = "insufficient data"
    ))
  }

  test <- suppressWarnings(
    cor.test(d[[col_x]], d[[col_y]], method = "spearman", exact = FALSE)
  )

  tibble(
    group = group_label,
    n     = nrow(d),
    rho   = unname(test$estimate),
    p     = test$p.value,
    note  = NA_character_
  )
}

# Compute full + stratified correlations + Fisher z-test for one pair
correlate_stratified <- function(data, col_x, col_y) {
  full  <- spearman_one_group(data,                              col_x, col_y, "Full")
  trad  <- spearman_one_group(filter(data, order == "Traditional_First"), col_x, col_y, "Traditional_First")
  ai    <- spearman_one_group(filter(data, order == "AI_First"),          col_x, col_y, "AI_First")

  # Fisher z-test comparing the two subgroup correlations
  fisher_p <- tryCatch({
    if (is.na(trad$rho) || is.na(ai$rho)) {
      NA_real_
    } else {
      psych::r.test(
      n   = trad$n,
      r12 = trad$rho,
      n2  = ai$n,
      r34 = ai$rho
    )$p 
    }
  }, error = function(e) NA_real_)

  bind_rows(full, trad, ai) |>
    mutate(
      col_x    = col_x,
      col_y    = col_y,
      fisher_p = fisher_p
    )
}
```

```{r factor-factor-stratified}
# --- Factor × Factor stratified correlations ---
# All unique factor pairs (same pairs as Section 6 factor map)

factor_pairs_strat <- t(combn(factor_cols_strat, 2)) |>
  as_tibble(.name_repair = "minimal") |>
  setNames(c("col_x", "col_y"))

factor_strat_results <- pmap_dfr(
  factor_pairs_strat,
  function(col_x, col_y) correlate_stratified(strat_base, col_x, col_y)
)

# Load factor name map for readable labels
factor_name_map_loaded <- read_csv(
  factor_name_map_file,
  show_col_types = FALSE
)

assert_lookup_covers_factor_columns(
  factor_lookup = factor_name_map_loaded,
  factor_cols = factor_cols_strat,
  context_label = "Script 04 factor-name-map handoff"
)

factor_label_lookup_strat <- factor_name_map_loaded |>
  transmute(factor = factor, display_label)

factor_strat_wide <- factor_strat_results |>
  pivot_wider(
    names_from  = group,
    values_from = c(n, rho, p),
    names_glue  = "{group}_{.value}"
  ) |>
  left_join(factor_label_lookup_strat |> rename(col_x = factor, label_x = display_label), by = "col_x") |>
  left_join(factor_label_lookup_strat |> rename(col_y = factor, label_y = display_label), by = "col_y") |>
  mutate(
    fisher_sig = case_when(
      is.na(fisher_p)  ~ "NA",
      fisher_p < 0.001 ~ "p < .001",
      fisher_p < 0.01  ~ "p < .01",
      fisher_p < 0.05  ~ "p < .05",
      TRUE             ~ paste0("p = ", round(fisher_p, 3))
    ),
    rho_diff = round(Traditional_First_rho - AI_First_rho, 3)
  ) |>
  arrange(fisher_p, desc(abs(rho_diff)))

write_csv(
  factor_strat_wide,
  file.path(csv_dir, "Factor_Factor_Order_Stratified_Correlations.csv")
)

# Display top pairs sorted by largest rho difference between order groups
factor_strat_wide |>
  select(
    label_x, label_y,
    Full_n, Full_rho, Full_p,
    Traditional_First_n, Traditional_First_rho, Traditional_First_p,
    AI_First_n, AI_First_rho, AI_First_p,
    fisher_p, fisher_sig, rho_diff
  ) |>
  mutate(across(where(is.numeric), ~ round(.x, 3))) |>
  kable(caption = "Factor × Factor correlations stratified by order group. fisher_p tests whether Traditional-First rho differs significantly from AI-First rho.")
```

```{r beliefs-factor-stratified}
# --- Beliefs Item × Factor stratified correlations ---
# Focus on items that survived BH correction in Script 05 full-sample analysis.
# Defined here explicitly so this section is self-contained.
# Update this vector if your significant item list changes.

sig_belief_items <- paste0("Beliefs_", c(1, 4, 8, 9, 10, 11, 12, 14, 15, 17, 19, 21, 22))
sig_belief_items <- intersect(sig_belief_items, belief_cols_strat)  # guard against missing cols

# Pairs to test: sig belief items × all factor cols
belief_factor_pairs <- expand_grid(
  col_x = sig_belief_items,
  col_y = factor_cols_strat
)

belief_strat_results <- pmap_dfr(
  belief_factor_pairs,
  function(col_x, col_y) correlate_stratified(strat_base, col_x, col_y)
)

# Belief item text lookup
belief_item_text <- beliefs_wide |>
  select(starts_with("Beliefs_")) |>
  names() |>
  tibble(belief_col = _) |>
  mutate(item_num = as.integer(str_extract(belief_col, "\\d+"))) |>
  arrange(item_num)

# Note: item text comes from the long file — load it here for labeling
beliefs_long_text <- read_csv(
  beliefs_long_file,
  show_col_types = FALSE
) |>
  distinct(item_num = as.integer(item_num), item_text) |>
  mutate(belief_col = paste0("Beliefs_", item_num))

belief_strat_wide <- belief_strat_results |>
  pivot_wider(
    names_from  = group,
    values_from = c(n, rho, p),
    names_glue  = "{group}_{.value}"
  ) |>
  left_join(beliefs_long_text |> select(belief_col, item_text) |> rename(col_x = belief_col), by = "col_x") |>
  left_join(factor_label_lookup_strat |> rename(col_y = factor, label_y = display_label), by = "col_y") |>
  mutate(
    fisher_sig = case_when(
      is.na(fisher_p)  ~ "NA",
      fisher_p < 0.001 ~ "p < .001",
      fisher_p < 0.01  ~ "p < .01",
      fisher_p < 0.05  ~ "p < .05",
      TRUE             ~ paste0("p = ", round(fisher_p, 3))
    ),
    rho_diff = round(Traditional_First_rho - AI_First_rho, 3)
  ) |>
  arrange(fisher_p, desc(abs(rho_diff)))

belief_factor_levels <- factor_label_lookup_strat$display_label[
  match(factor_cols_strat, factor_label_lookup_strat$factor)
]

if (any(is.na(belief_factor_levels))) {
  stop("Belief-item order plots: missing factor display labels for one or more factor columns.", call. = FALSE)
}

belief_plot_long <- belief_strat_results |>
  left_join(
    beliefs_long_text |>
      select(belief_col, item_text) |>
      rename(col_x = belief_col),
    by = "col_x"
  ) |>
  left_join(
    factor_label_lookup_strat |>
      rename(col_y = factor, label_y = display_label),
    by = "col_y"
  ) |>
  mutate(
    label_y = factor(label_y, levels = belief_factor_levels),
    group = factor(group, levels = c("Full", "Traditional_First", "AI_First"))
  )

belief_plot_annotations <- belief_strat_wide |>
  select(col_x, col_y, label_y, fisher_sig) |>
  mutate(label_y = factor(label_y, levels = belief_factor_levels))

for (belief_col in sig_belief_items) {
  plot_df <- belief_plot_long |>
    filter(col_x == belief_col)

  ann_df <- belief_plot_annotations |>
    filter(col_x == belief_col)

  if (nrow(plot_df) == 0 || all(is.na(plot_df$rho))) {
    next
  }

  item_title <- plot_df |>
    distinct(item_text) |>
    pull(item_text) |>
    first()

  belief_order_plot <- ggplot(
    plot_df,
    aes(x = label_y, y = rho, group = group, color = group, linetype = group, shape = group)
  ) +
    geom_hline(yintercept = 0, color = "#c7c7c7", linewidth = 0.8) +
    geom_hline(yintercept = c(-0.30, 0.30), color = "#bdbdbd", linewidth = 0.7, linetype = "dotted") +
    geom_line(linewidth = 1.2, alpha = 0.95) +
    geom_point(size = 3.7, alpha = 0.95) +
    geom_text(
      data = ann_df,
      aes(x = label_y, y = -1.07, label = fisher_sig),
      inherit.aes = FALSE,
      color = "#5a5a5a",
      size = 4.0
    ) +
    scale_color_manual(
      values = c(
        "Full" = "#7a7a7a",
        "Traditional_First" = "#c93e2c",
        "AI_First" = "#3a88bf"
      ),
      labels = c(
        "Full" = "Full sample",
        "Traditional_First" = "Traditional-First",
        "AI_First" = "AI-First"
      )
    ) +
    scale_linetype_manual(
      values = c(
        "Full" = "22",
        "Traditional_First" = "solid",
        "AI_First" = "solid"
      ),
      labels = c(
        "Full" = "Full sample",
        "Traditional_First" = "Traditional-First",
        "AI_First" = "AI-First"
      )
    ) +
    scale_shape_manual(
      values = c(
        "Full" = 16,
        "Traditional_First" = 17,
        "AI_First" = 15
      ),
      labels = c(
        "Full" = "Full sample",
        "Traditional_First" = "Traditional-First",
        "AI_First" = "AI-First"
      )
    ) +
    scale_y_continuous(
      limits = c(-1.1, 1.0),
      breaks = seq(-1, 1, by = 0.25),
      labels = scales::number_format(accuracy = 0.01)
    ) +
    labs(
      title = item_title,
      subtitle = "Spearman rho with each factor — Full sample (gray dashed), Traditional-First (red), AI-First (blue)",
      x = NULL,
      y = "Spearman rho",
      caption = "Fisher's z p-value shown below each factor label. Dotted lines at rho = +/-0.30."
    ) +
    theme_minimal(base_size = 14) +
    theme(
      legend.position = "none",
      panel.grid.minor = element_blank(),
      axis.text.x = element_text(angle = 35, hjust = 1, size = 10),
      axis.text.y = element_text(size = 11),
      plot.title = element_text(face = "bold", size = 17),
      plot.subtitle = element_text(size = 11, color = "#666666"),
      plot.caption = element_text(size = 10, color = "#7a7a7a"),
      plot.margin = margin(15, 20, 20, 15)
    )

  ggsave(
    filename = file.path(plot_dir, paste0("belief_", belief_col, "_order_corr.png")),
    plot = belief_order_plot,
    width = 16,
    height = 10,
    units = "in",
    dpi = 160,
    bg = "white"
  )
}

write_csv(
  belief_strat_wide,
  file.path(csv_dir, "Beliefs_Factor_Order_Stratified_Correlations.csv")
)

# Display: focus on Item 1 x WritingEfficacy F1 first (your key finding),
# then top hits by rho difference
belief_strat_wide |>
  select(
    item_text, label_y,
    Full_n, Full_rho, Full_p,
    Traditional_First_n, Traditional_First_rho, Traditional_First_p,
    AI_First_n, AI_First_rho, AI_First_p,
    fisher_p, fisher_sig, rho_diff
  ) |>
  mutate(
    item_text = str_trunc(item_text, 60),
    across(where(is.numeric), ~ round(.x, 3))
  ) |>
  kable(caption = "Beliefs item × Factor correlations stratified by order group. fisher_p tests subgroup rho difference.")
```

```{r order-strat-exports}
strat_export_manifest <- tibble(
  file = c(
    "Factor_Factor_Order_Stratified_Correlations.csv",
    "Beliefs_Factor_Order_Stratified_Correlations.csv"
  ),
  description = c(
    "Factor × factor Spearman correlations split by order group with Fisher z-test",
    "Beliefs item × factor Spearman correlations split by order group with Fisher z-test"
  )
)

write_csv(strat_export_manifest, file.path(csv_dir, "Order_Stratified_Export_Manifest.csv"))
kable(strat_export_manifest)
```
