---
title: "Beliefs Items vs Other Instrument Factors"
format:
  html:
    toc: true
    toc-depth: 2
output-dir: "05_beliefs_item_analysis"
execute:
  echo: false
  warning: false
  message: false
---

This is an exploratory side analysis for the `BeliefsAboutAI` block. Because `BeliefsAboutAI` did not support a clean factor solution in the main EFA workflow, this report treats the Beliefs items as **item-level outcomes** and asks how each item relates to factor scores from the currently valid instrument-level EFA solutions.

Before doing that item-level step, this report now also builds a **factor map** showing how the valid factors from `IMI`, `WritingEfficacy`, and `AIReflection` relate to each other.

Right now the factor sources are the canonical factor scores exported by
`06_interesting_findings.qmd` for `IMI`, `WritingEfficacy`, and
`AIReflection`.

The current defaults are:

-   factor source: `Factor_Scores_All_Instruments.csv` (variance-ordered,
    primary EFA solutions)
-   factor-score method: `tenBerge`
-   participant filter: intersection of order-effects sample, Beliefs
    responses, and available factor scores
-   item-factor association: Spearman correlation

```{r}

library(tidyverse)
library(psych)
library(glue)
library(knitr)
source("scoring_helpers.R", local = knitr::knit_global())

# Set global seed for reproducibility — psych::fa() (minres + oblimin) and
# psych::factor.scores() (tenBerge) are affected by random starting values.
set.seed(42L)
```

## Setup

```{r}
script_dir <- "05_beliefs_item_analysis"
csv_dir <- file.path(script_dir, "csv")
plot_dir <- file.path(script_dir, "plots")
dir.create(csv_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(plot_dir, recursive = TRUE, showWarnings = FALSE)

beliefs_file <- file.path("02_efa_exports", "efa", "BeliefsAboutAI_EFA_Primary.csv")
factor_scores_all_file <- file.path("06_interesting_findings", "csv", "Factor_Scores_All_Instruments.csv")
factor_name_map_file <- file.path("06_interesting_findings", "csv", "Factor_Name_Map.csv")
order_effects_analysis_ready_file <- file.path("04_order_effects", "csv", "Order_Effects_Analysis_Ready.csv")
factor_score_method <- "tenBerge"
traditional_session_instruments <- c("IMI", "WritingEfficacy")
ai_session_instruments <- c("AIReflection", "BeliefsAboutAI")

# compute_polychoric_safe() is sourced from scoring_helpers.R — not duplicated here.

transform_scores <- function(x, transform_name) {
  values <- as.numeric(x)

  if (transform_name == "identity") {
    return(values)
  }

  if (transform_name == "wse_to_5") {
    return(case_when(
      is.na(values) ~ NA_real_,
      values %in% c(0, 25, 50, 75, 100) ~ (values / 25) + 1,
      TRUE ~ NA_real_
    ))
  }

  stop(glue("Unknown score transform: {transform_name}"))
}

safe_spearman <- function(data, item_col, factor_col) {
  dat <- data |>
    select(all_of(c(item_col, factor_col))) |>
    filter(if_all(everything(), ~ !is.na(.x)))

  if (nrow(dat) < 10 || dplyr::n_distinct(dat[[item_col]]) < 2 || dplyr::n_distinct(dat[[factor_col]]) < 2) {
    return(tibble(
      belief_item = item_col,
      factor = factor_col,
      rho = NA_real_,
      p = NA_real_,
      n = nrow(dat),
      note = "insufficient variation or sample size"
    ))
  }

  test <- suppressWarnings(
    cor.test(dat[[item_col]], dat[[factor_col]], method = "spearman", exact = FALSE)
  )

  tibble(
    belief_item = item_col,
    factor = factor_col,
    rho = unname(test$estimate),
    p = test$p.value,
    n = nrow(dat),
    note = NA_character_
  )
}

safe_spearman_pair <- function(data, col_x, col_y) {
  dat <- data |>
    select(all_of(c(col_x, col_y))) |>
    filter(if_all(everything(), ~ !is.na(.x)))

  if (col_x == col_y) {
    return(tibble(
      factor_x = col_x,
      factor_y = col_y,
      rho = 1,
      p = NA_real_,
      n = nrow(dat),
      note = "diagonal"
    ))
  }

  if (nrow(dat) < 10 || dplyr::n_distinct(dat[[col_x]]) < 2 || dplyr::n_distinct(dat[[col_y]]) < 2) {
    return(tibble(
      factor_x = col_x,
      factor_y = col_y,
      rho = NA_real_,
      p = NA_real_,
      n = nrow(dat),
      note = "insufficient variation or sample size"
    ))
  }

  test <- suppressWarnings(
    cor.test(dat[[col_x]], dat[[col_y]], method = "spearman", exact = FALSE)
  )

  tibble(
    factor_x = col_x,
    factor_y = col_y,
    rho = unname(test$estimate),
    p = test$p.value,
    n = nrow(dat),
    note = NA_character_
  )
}

build_factor_scores <- function(instrument, file, item_id_col, score_transform, prefix, recommended_k) {
  long <- read_csv(file, show_col_types = FALSE) |>
    transmute(
      participant_id,
      item_id = as.integer(.data[[item_id_col]]),
      item_text,
      score = transform_scores(score, score_transform)
    )

  item_lookup <- long |>
    distinct(item_id, item_text) |>
    arrange(item_id)

  wide <- long |>
    select(participant_id, item_id, score) |>
    mutate(item_id = as.character(item_id)) |>
    pivot_wider(names_from = item_id, values_from = score) |>
    arrange(participant_id)

  matrix_df <- wide |>
    select(-participant_id) |>
    mutate(across(everything(), ~ as.integer(round(.x)))) |>
    as.data.frame()

  poly_out <- compute_polychoric_safe(matrix_df)

  # Defensive seed: ensures factor solution is reproducible regardless of
  # upstream code changes that may consume random numbers.
  set.seed(42L)

  # Conditional rotation: no rotation for single-factor solutions (matches
  # Script 03 and Script 06 convention).
  fa_fit <- suppressWarnings(
    psych::fa(
      r = poly_out$rho,
      nfactors = recommended_k,
      n.obs = nrow(matrix_df),
      fm = "minres",
      rotate = if (recommended_k == 1L) "none" else "oblimin"
    )
  )

  # Reorder factors by variance explained (descending) so F1 is always the

  # largest factor, matching Script 03's extract_final_solution() and
  # Script 06's build_factor_scores() convention. Without this, MR1/MR2
  # ordering from psych is arbitrary after oblimin rotation.
  if (!is.null(fa_fit$Vaccounted) && recommended_k > 1L) {
    prop_var     <- fa_fit$Vaccounted["Proportion Var", ]
    factor_order <- order(prop_var, decreasing = TRUE)
  } else {
    factor_order <- seq_len(recommended_k)
  }

  L_ordered <- unclass(fa_fit$loadings)[, factor_order, drop = FALSE]
  colnames(L_ordered) <- paste0("MR", seq_len(recommended_k))

  fa_fit_ordered           <- fa_fit
  fa_fit_ordered$loadings  <- L_ordered
  class(fa_fit_ordered$loadings) <- c("loadings")

  score_matrix <- psych::factor.scores(
    x = as.matrix(matrix_df),
    f = fa_fit_ordered,
    rho = poly_out$rho,
    method = factor_score_method
  )

  factor_scores <- bind_scores_with_ids(
      participant_ids = wide$participant_id,
      score_matrix = score_matrix$scores,
      context_label = paste0(instrument, " factor scores")
    ) |>
    rename_with(~ paste0(prefix, "_", .x), .cols = starts_with("MR"))

  factor_lookup <- tibble(
    factor = names(factor_scores)[names(factor_scores) != "participant_id"],
    instrument = instrument,
    factor_id = str_remove(factor, paste0("^", prefix, "_")),
    factor_label = paste0(prefix, " ", str_replace(factor_id, "MR", "F"))
  )

  model_summary <- tibble(
    instrument = instrument,
    recommended_k = recommended_k,
    participant_n = nrow(wide),
    retained_item_count = ncol(matrix_df),
    score_transform = score_transform,
    polychoric_repair_needed = poly_out$repair_needed,
    min_unsmoothed_eigen = poly_out$min_eigen_unsmoothed
  )

  list(
    instrument = instrument,
    item_lookup = item_lookup,
    factor_scores = factor_scores,
    factor_lookup = factor_lookup,
    model_summary = model_summary
  )
}
```

## Load Canonical Factor Scores

```{r}
if (!file.exists(factor_scores_all_file)) {
  stop(
    glue("Missing factor score file: {factor_scores_all_file}. Render 06_interesting_findings.qmd first."),
    call. = FALSE
  )
}

all_factor_scores_raw <- read_csv(factor_scores_all_file, show_col_types = FALSE) |>
  mutate(participant_id = as.character(participant_id))

factor_cols_raw <- names(all_factor_scores_raw) |> setdiff("participant_id")

factor_lookup <- if (file.exists(factor_name_map_file)) {
  factor_lookup_loaded <- read_csv(factor_name_map_file, show_col_types = FALSE)
  required_factor_cols <- c("factor", "instrument")
  missing_factor_cols <- setdiff(required_factor_cols, names(factor_lookup_loaded))
  if (length(missing_factor_cols) > 0) {
    stop(
      glue(
        "Factor name map is missing required columns: {paste(missing_factor_cols, collapse = ', ')}"
      ),
      call. = FALSE
    )
  }
  factor_lookup_loaded
} else {
  prefix_map <- tibble(
    prefix = c("IMI", "WSE", "AIRefl"),
    instrument = c("IMI", "WritingEfficacy", "AIReflection")
  )

  tibble(factor = factor_cols_raw) |>
    mutate(
      prefix = str_extract(factor, "^[^_]+"),
      factor_id = str_remove(factor, "^[^_]+_")
    ) |>
    left_join(prefix_map, by = "prefix") |>
    mutate(
      instrument = coalesce(instrument, prefix)
    )
}

if (!"factor_id" %in% names(factor_lookup)) {
  factor_lookup <- factor_lookup |>
    mutate(factor_id = NA_character_)
}
if (!"factor_num" %in% names(factor_lookup)) {
  factor_lookup <- factor_lookup |>
    mutate(factor_num = NA_integer_)
}
if (!"short_factor" %in% names(factor_lookup)) {
  factor_lookup <- factor_lookup |>
    mutate(short_factor = NA_character_)
}
if (!"factor_label" %in% names(factor_lookup)) {
  factor_lookup <- factor_lookup |>
    mutate(factor_label = NA_character_)
}

factor_lookup <- factor_lookup |>
  filter(factor %in% factor_cols_raw) |>
  mutate(
    factor_id = coalesce(factor_id, str_remove(factor, "^[^_]+_")),
    factor_num = coalesce(factor_num, as.integer(str_remove(factor_id, "MR"))),
    short_factor = coalesce(short_factor, paste0("F", factor_num)),
    factor_label = coalesce(factor_label, paste0(instrument, " ", short_factor))
  )

instrument_order <- c("IMI", "WritingEfficacy", "AIReflection")
```

## Build Beliefs Item Matrix

```{r}
beliefs_long <- read_csv(beliefs_file, show_col_types = FALSE) |>
  transmute(
    participant_id,
    item_id = as.integer(item_num),
    item_text,
    score = as.integer(round(as.numeric(score)))
  )

belief_item_lookup <- beliefs_long |>
  distinct(item_id, item_text) |>
  arrange(item_id)

beliefs_wide <- beliefs_long |>
  select(participant_id, item_id, score) |>
  mutate(item_id = paste0("Beliefs_", item_id)) |>
  pivot_wider(names_from = item_id, values_from = score) |>
  arrange(participant_id)

write_csv(beliefs_wide, file.path(csv_dir, "BeliefsAboutAI_Wide.csv"))
```

## Apply Analysis Sample Filter

```{r}
if (!file.exists(order_effects_analysis_ready_file)) {
  stop(
    glue("Missing order-effects file: {order_effects_analysis_ready_file}. Render 04_order_effects.qmd first."),
    call. = FALSE
  )
}

order_labels <- read_csv(order_effects_analysis_ready_file, show_col_types = FALSE) |>
  select(participant_id, order) |>
  mutate(participant_id = as.character(participant_id))

missing_order_cols <- setdiff(c("participant_id", "order"), names(order_labels))
if (length(missing_order_cols) > 0) {
  stop(
    glue("Order-effects file is missing required columns: {paste(missing_order_cols, collapse = ', ')}"),
    call. = FALSE
  )
}

analysis_participants <- beliefs_wide |>
  select(participant_id) |>
  inner_join(all_factor_scores_raw |> select(participant_id), by = "participant_id") |>
  inner_join(order_labels, by = "participant_id")

all_factor_scores <- all_factor_scores_raw |>
  inner_join(analysis_participants |> select(participant_id), by = "participant_id")

factor_cols <- names(all_factor_scores) |> setdiff("participant_id")

factor_levels <- factor_lookup |>
  arrange(match(instrument, instrument_order), factor_num) |>
  pull(factor)

factor_label_lookup <- factor_lookup |>
  transmute(
    factor,
    plot_factor_label = case_when(
      instrument == "WritingEfficacy" ~ paste0("WSE\n", short_factor),
      instrument == "AIReflection" ~ paste0("AIRefl\n", short_factor),
      TRUE ~ paste0(instrument, "\n", short_factor)
    )
  )

factor_model_summary <- factor_lookup |>
  group_by(instrument) |>
  summarise(factors = list(factor), .groups = "drop") |>
  mutate(
    factor_count = map_int(factors, length),
    participants_with_scores = map_int(
      factors,
      ~ all_factor_scores_raw |>
        select(participant_id, all_of(.x)) |>
        filter(if_any(all_of(.x), ~ !is.na(.x))) |>
        nrow()
    ),
    analysis_sample_n = map_int(
      factors,
      ~ all_factor_scores |>
        select(participant_id, all_of(.x)) |>
        filter(if_any(all_of(.x), ~ !is.na(.x))) |>
        nrow()
    )
  ) |>
  select(instrument, factor_count, participants_with_scores, analysis_sample_n) |>
  mutate(score_source = basename(factor_scores_all_file))

write_csv(all_factor_scores, file.path(csv_dir, "Other_Instrument_Factor_Scores.csv"))
write_csv(factor_model_summary, file.path(csv_dir, "Other_Instrument_Factor_Model_Summary.csv"))
```

```{r}
factor_model_summary |>
  kable()
```

## Factor Map Across the Valid Instruments

```{r}
factor_pair_matrix <- t(combn(factor_cols, 2))

factor_pairs <- tibble(
  factor_x = factor_pair_matrix[, 1],
  factor_y = factor_pair_matrix[, 2]
)

factor_correlations_unique <- factor_pairs |>
  mutate(result = map2(factor_x, factor_y, ~ safe_spearman_pair(all_factor_scores, .x, .y))) |>
  pull(result) |>
  bind_rows() |>
  mutate(
    p_bonferroni = p.adjust(p, method = "bonferroni"),
    p_bh = p.adjust(p, method = "BH"),
    abs_r = abs(rho)
  ) |>
  left_join(
    factor_lookup |>
      rename(
        factor_x = factor,
        instrument_x = instrument,
        factor_id_x = factor_id,
        factor_label_x = factor_label
      ),
    by = "factor_x"
  ) |>
  left_join(
    factor_lookup |>
      rename(
        factor_y = factor,
        instrument_y = instrument,
        factor_id_y = factor_id,
        factor_label_y = factor_label
      ),
    by = "factor_y"
  ) |>
  mutate(
    pair_type = if_else(instrument_x == instrument_y, "Within instrument", "Across instrument"),
    session_relation = case_when(
      instrument_x %in% traditional_session_instruments & instrument_y %in% traditional_session_instruments ~ "Within Traditional session",
      instrument_x %in% ai_session_instruments & instrument_y %in% ai_session_instruments ~ "Within AI session",
      TRUE ~ "Cross-session Traditional_vs_AI"
    ),
    survives_bonferroni = p_bonferroni < 0.05,
    survives_bh = p_bh < 0.05
  ) |>
  arrange(desc(abs_r), p_bh, p_bonferroni)

factor_correlations_diagonal <- tibble(
  factor_x = factor_cols,
  factor_y = factor_cols,
  rho = 1,
  p = NA_real_,
  n = map_int(factor_cols, ~ sum(!is.na(all_factor_scores[[.x]]))),
  note = "diagonal",
  p_bonferroni = NA_real_,
  p_bh = NA_real_,
  abs_r = 1
) |>
  left_join(
    factor_lookup |>
      rename(
        factor_x = factor,
        instrument_x = instrument,
        factor_id_x = factor_id,
        factor_label_x = factor_label
      ),
    by = "factor_x"
  ) |>
  left_join(
    factor_lookup |>
      rename(
        factor_y = factor,
        instrument_y = instrument,
        factor_id_y = factor_id,
        factor_label_y = factor_label
      ),
    by = "factor_y"
  ) |>
  mutate(
    pair_type = "Diagonal",
    survives_bonferroni = NA,
    survives_bh = NA
  )

factor_correlations_heat <- bind_rows(
  factor_correlations_unique,
  factor_correlations_unique |>
    rename(
      factor_x_orig = factor_x,
      factor_y_orig = factor_y,
      instrument_x_orig = instrument_x,
      factor_id_x_orig = factor_id_x,
      factor_label_x_orig = factor_label_x,
      instrument_y_orig = instrument_y,
      factor_id_y_orig = factor_id_y,
      factor_label_y_orig = factor_label_y
    ) |>
    transmute(
      factor_x = factor_y_orig,
      factor_y = factor_x_orig,
      rho = .data$rho,
      p = .data$p,
      n = .data$n,
      note = .data$note,
      p_bonferroni = .data$p_bonferroni,
      p_bh = .data$p_bh,
      abs_r = .data$abs_r,
      instrument_x = instrument_y_orig,
      factor_id_x = factor_id_y_orig,
      factor_label_x = factor_label_y_orig,
      instrument_y = instrument_x_orig,
      factor_id_y = factor_id_x_orig,
      factor_label_y = factor_label_x_orig,
      pair_type = .data$pair_type,
      survives_bonferroni = .data$survives_bonferroni,
      survives_bh = .data$survives_bh
    ),
  factor_correlations_diagonal
)

write_csv(
  factor_correlations_unique,
  file.path(csv_dir, "Other_Instrument_Factor_Correlations.csv")
)
```

```{r}
factor_correlation_summary <- tibble(
  metric = c(
    "Factor columns",
    "Unique factor pairs",
    "Within-instrument pairs",
    "Across-instrument pairs"
  ),
  value = c(
    length(factor_cols),
    nrow(factor_correlations_unique),
    sum(factor_correlations_unique$pair_type == "Within instrument"),
    sum(factor_correlations_unique$pair_type == "Across instrument")
  )
)

kable(factor_correlation_summary)
```

## Strongest Factor-Factor Signals

```{r}
factor_correlations_unique |>
  select(
    instrument_x, factor_label_x, instrument_y, factor_label_y,
    pair_type, rho, p_bh, p_bonferroni, n
  ) |>
  mutate(
    rho = round(rho, 3),
    p_bh = round(p_bh, 4),
    p_bonferroni = round(p_bonferroni, 4)
  ) |>
  slice_head(n = 20) |>
  kable()
```

## Factor Map Heatmap

```{r}
factor_heat_df <- factor_correlations_heat |>
  left_join(
    factor_label_lookup |>
      rename(
        factor_x = factor,
        plot_factor_x = plot_factor_label
      ),
    by = "factor_x"
  ) |>
  left_join(
    factor_label_lookup |>
      rename(
        factor_y = factor,
        plot_factor_y = plot_factor_label
      ),
    by = "factor_y"
  ) |>
  mutate(
    plot_factor_x = factor(
      plot_factor_x,
      levels = factor_label_lookup$plot_factor_label[match(factor_levels, factor_label_lookup$factor)]
    ),
    plot_factor_y = factor(
      plot_factor_y,
      levels = rev(factor_label_lookup$plot_factor_label[match(factor_levels, factor_label_lookup$factor)])
    ),
    sig_label = case_when(
      factor_x == factor_y ~ "",
      survives_bonferroni ~ "**",
      survives_bh ~ "*",
      TRUE ~ ""
    ),
    cell_label = if_else(is.na(rho), "", paste0(formatC(rho, format = "f", digits = 2), sig_label))
  )
```

```{r, fig.width=10, fig.height=8.5}
factor_map_plot <- ggplot(factor_heat_df, aes(x = plot_factor_x, y = plot_factor_y, fill = rho)) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = cell_label), size = 2.8) +
  scale_fill_gradient2(
    low = "#c73e3a",
    mid = "#f7f7f7",
    high = "#4f79b7",
    midpoint = 0,
    limits = c(-1, 1),
    name = "Spearman rho"
  ) +
  labs(
    title = "Factor Map Across IMI, WritingEfficacy, and AIReflection",
    subtitle = "* BH < .05   ** Bonferroni < .05",
    x = NULL,
    y = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid = element_blank(),
    axis.text.x = element_text(size = 10, lineheight = 0.9, angle = 0),
    axis.text.y = element_text(size = 10),
    plot.margin = margin(10, 20, 10, 10)
  )

ggsave(
  filename = file.path(plot_dir, "Other_Instrument_Factor_Correlation_Heatmap.png"),
  plot = factor_map_plot,
  width = 12,
  height = 10,
  units = "in",
  dpi = 300,
  bg = "white"
)

ggsave(
  filename = file.path(plot_dir, "Other_Instrument_Factor_Correlation_Heatmap.pdf"),
  plot = factor_map_plot,
  width = 12,
  height = 10,
  units = "in",
  bg = "white"
)

factor_map_plot
```

## Correlate Beliefs Items with Other Instrument Factors

```{r}
combined <- beliefs_wide |>
  inner_join(all_factor_scores, by = "participant_id")

belief_items <- names(beliefs_wide) |> setdiff("participant_id")

correlation_results <- expand_grid(
  belief_item = belief_items,
  factor = factor_cols
) |>
  mutate(result = map2(belief_item, factor, ~ safe_spearman(combined, .x, .y))) |>
  pull(result) |>
  bind_rows() |>
  mutate(
    p_bonferroni = p.adjust(p, method = "bonferroni"),
    p_bh = p.adjust(p, method = "BH"),
    abs_r = abs(rho),
    survives_bonferroni = p_bonferroni < 0.05,
    survives_bh = p_bh < 0.05
  ) |>
  left_join(
    belief_item_lookup |>
      mutate(belief_item = paste0("Beliefs_", item_id)) |>
      select(belief_item, item_id, item_text),
    by = "belief_item"
  ) |>
  left_join(factor_lookup, by = "factor") |>
  mutate(
    session_relation = case_when(
      instrument %in% traditional_session_instruments ~ "Cross-session Traditional_vs_AI",
      instrument %in% ai_session_instruments ~ "Within AI session",
      TRUE ~ "Unknown session relation"
    )
  ) |>
  arrange(p_bh, p_bonferroni, desc(abs_r))

write_csv(
  correlation_results,
  file.path(csv_dir, "Beliefs_Item_vs_Other_Instrument_Factors_Correlations.csv")
)
```

```{r}
beliefs_overlap_summary <- factor_lookup |>
  group_by(instrument) |>
  summarise(
    factors = list(factor),
    factor_score_participants = map_int(
      factors,
      ~ all_factor_scores_raw |>
        select(participant_id, all_of(.x)) |>
        filter(if_any(all_of(.x), ~ !is.na(.x))) |>
        nrow()
    ),
    beliefs_overlap_n = map_int(
      factors,
      ~ all_factor_scores |>
        select(participant_id, all_of(.x)) |>
        filter(if_any(all_of(.x), ~ !is.na(.x))) |>
        nrow()
    ),
    .groups = "drop"
  ) |>
  select(-factors)

summary_table <- tibble(
  metric = c(
    "Beliefs participants",
    "Order-effects overlap (analysis sample)",
    "Participants with at least one non-missing factor score",
    "Beliefs items",
    "Factor columns",
    "Total tests"
  ),
  value = c(
    nrow(beliefs_wide),
    nrow(analysis_participants),
    combined |> filter(if_any(all_of(factor_cols), ~ !is.na(.x))) |> nrow(),
    length(belief_items),
    length(factor_cols),
    nrow(correlation_results)
  )
)

kable(summary_table)
```

```{r}
beliefs_overlap_summary |>
  kable()
```

## Top Item-Factor Associations

```{r}
correlation_results |>
  select(item_id, item_text, instrument, factor, rho, p, p_bh, p_bonferroni, survives_bh, survives_bonferroni, n) |>
  mutate(
    rho = round(rho, 3),
    p = round(p, 4),
    p_bh = round(p_bh, 4),
    p_bonferroni = round(p_bonferroni, 4)
  ) |>
  slice_head(n = 30) |>
  kable()
```

## Strongest Signals by Factor

```{r}
correlation_results |>
  filter(!is.na(rho)) |>
  group_by(factor) |>
  slice_max(order_by = abs_r, n = 3, with_ties = FALSE) |>
  ungroup() |>
  select(instrument, factor, item_id, item_text, rho, p_bh, p_bonferroni, n) |>
  mutate(
    rho = round(rho, 3),
    p_bh = round(p_bh, 4),
    p_bonferroni = round(p_bonferroni, 4)
  ) |>
  kable()
```

## Heatmap

```{r}
heat_df <- correlation_results |>
  left_join(factor_label_lookup, by = "factor") |>
  mutate(
    item_label = str_wrap(item_text, width = 62),
    item_label = factor(item_label, levels = rev(unique(item_label[order(item_id)]))),
    plot_factor_label = base::factor(
      plot_factor_label,
      levels = factor_label_lookup$plot_factor_label[match(factor_levels, factor_label_lookup$factor)]
    ),
    sig_label = case_when(
      survives_bonferroni ~ "**",
      survives_bh ~ "*",
      TRUE ~ ""
    ),
    cell_label = if_else(is.na(rho), "", paste0(formatC(rho, format = "f", digits = 2), sig_label))
  )
```

```{r, fig.width=12, fig.height=11}
heatmap_plot <- ggplot(heat_df, aes(x = plot_factor_label, y = item_label, fill = rho)) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = cell_label), size = 2.8) +
  scale_fill_gradient2(
    low = "#c73e3a",
    mid = "#f7f7f7",
    high = "#4f79b7",
    midpoint = 0,
    limits = c(-1, 1),
    name = "Spearman rho"
  ) +
  labs(
    title = "Beliefs Items vs Other Instrument Factor Scores",
    subtitle = "* BH < .05   ** Bonferroni < .05",
    x = NULL,
    y = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid = element_blank(),
    axis.text.x = element_text(size = 10, lineheight = 0.9),
    axis.text.y = element_text(size = 10)
  )

ggsave(
  filename = file.path(plot_dir, "Beliefs_Items_vs_Other_Instrument_Factors_Heatmap.png"),
  plot = heatmap_plot,
  width = 16,
  height = 18,
  units = "in",
  dpi = 300,
  bg = "white"
)

ggsave(
  filename = file.path(plot_dir, "Beliefs_Items_vs_Other_Instrument_Factors_Heatmap.pdf"),
  plot = heatmap_plot,
  width = 16,
  height = 18,
  units = "in",
  bg = "white"
)

heatmap_plot
```

## Notes

-   This is an exploratory fallback because `BeliefsAboutAI` itself did not support a stable factor solution in the main EFA workflow.
-   The new factor map section is a **factor-to-factor** view across the three instruments that did support factor solutions.
-   The factor-score side uses the **current recommended primary models**, not locked final models. If you later lock different `k` values in the main EFA script, this report should be re-rendered.
-   `WritingEfficacy` is rescaled from `0/25/50/75/100` to ordered `1:5` **for factor modeling only**, to match the ordinal EFA treatment used elsewhere.
-   These are **item-to-factor** relationships, not proof that the Beliefs items define their own valid latent structure.
-   Pairwise `n` can differ across factors because the RW-side factor models have fewer overlapping participants with the Beliefs sample than the AI-side factor model does.

## Output Manifest

```{r beliefs-manifest}
beliefs_manifest <- tibble(
  output_type = c(
    "other_instrument_factor_scores",
    "other_instrument_factor_model_summary",
    "other_instrument_factor_correlations",
    "beliefs_wide",
    "beliefs_item_factor_correlations"
  ),
  file = c(
    "Other_Instrument_Factor_Scores.csv",
    "Other_Instrument_Factor_Model_Summary.csv",
    "Other_Instrument_Factor_Correlations.csv",
    "BeliefsAboutAI_Wide.csv",
    "Beliefs_Item_vs_Other_Instrument_Factors_Correlations.csv"
  ),
  description = c(
    "Factor scores for IMI, WritingEfficacy, and AIReflection (primary EFA samples)",
    "EFA model diagnostics per instrument (k, polychoric repair, participant N)",
    "Unique Spearman correlations across factors (BH and Bonferroni corrected)",
    "BeliefsAboutAI item responses in wide format (participant × item)",
    "Spearman correlations: each Beliefs item vs each other-instrument factor score"
  )
)

write_csv(beliefs_manifest, file.path(csv_dir, "Beliefs_Export_Manifest.csv"))
kable(beliefs_manifest, caption = "05_beliefs_item_analysis.qmd — Output Manifest")
```
