---
title: "Interesting Findings Finder"
format:
  html:
    toc: true
    toc-depth: 2
output-dir: "06_interesting_findings"
execute:
  echo: false
  warning: false
  message: false
editor: 
  markdown: 
    wrap: 72
---

This report is the 4th step after EFA analysis. It creates:

1.  A human-readable cross-instrument factor heatmap for the 3
    factorable instruments (`IMI`, `WritingEfficacy`, `AIReflection`)
2.  Pairwise item-level exploratory correlations for each instrument
    pair (`IMI ↔ WritingEfficacy`, `IMI ↔ AIReflection`,
    `WritingEfficacy ↔ AIReflection`, `IMI ↔ BeliefsAboutAI`,
    `WritingEfficacy ↔ BeliefsAboutAI`, `AIReflection ↔ BeliefsAboutAI`)

`BeliefsAboutAI` is excluded from factor mapping (KMO \< 0.50 → not
factorable) but is included in all item-level pairwise correlations.

```{r setup}
library(tidyverse)
library(psych)
library(glue)
library(knitr)
source("scoring_helpers.R", local = knitr::knit_global())

# Set global seed for reproducibility — psych::fa() (minres + oblimin) and
# psych::factor.scores() (tenBerge) are affected by random starting values.
set.seed(42L)
```

## Setup

```{r config}
script_dir <- "06_interesting_findings"
csv_dir    <- file.path(script_dir, "csv")
plot_dir   <- file.path(script_dir, "plots")
order_effects_analysis_ready_file <- file.path("04_order_effects", "csv", "Order_Effects_Analysis_Ready.csv")
dir.create(csv_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(plot_dir, recursive = TRUE, showWarnings = FALSE)

# tenBerge keeps score estimates aligned with oblique-factor solutions while
# reducing score indeterminacy compared with simple regression scoring.
factor_score_method        <- "tenBerge"
min_correlation_sample_size <- 10L
traditional_session_instruments <- c("IMI", "WritingEfficacy")
ai_session_instruments <- c("AIReflection", "BeliefsAboutAI")

efa_global_exclusions <- c(
  "N/A (RA practice)",
  "Sania Jain test",
  "y5lblN",
  "2192994",
  "hKpFTX"
)

# Instruments that go through full EFA + factor scoring pipeline
instrument_specs <- tribble(
  ~instrument,       ~file,                              ~item_id_col, ~score_transform, ~prefix,
  "IMI",             file.path("02_efa_exports", "efa", "IMI_EFA_Primary.csv"),              "item_code",  "identity",       "IMI",
  "WritingEfficacy", file.path("02_efa_exports", "efa", "WritingEfficacy_EFA_Primary.csv"),  "item_code",  "wse_to_5",       "WSE",
  "AIReflection",    file.path("02_efa_exports", "efa", "AI_Reflection_EFA_Primary.csv"),    "item_num",   "identity",       "AIRefl"
)

# Instruments included in item-level correlations only (KMO < 0.50, no EFA)
item_only_specs <- tribble(
  ~instrument,      ~file,                             ~item_id_col, ~score_transform, ~prefix,
  "BeliefsAboutAI", file.path("02_efa_exports", "efa", "BeliefsAboutAI_EFA_Primary.csv"),  "item_num",   "identity",       "BAI"
)

recommended_k_file <- file.path("03_efa_analysis", "EFA_Recommended_K.csv")
recommended_k_raw <- read_csv(recommended_k_file, show_col_types = FALSE)

required_k_cols <- c("instrument", "recommended_k", "factorability_flag")
missing_k_cols  <- setdiff(required_k_cols, names(recommended_k_raw))
if (length(missing_k_cols) > 0) {
  stop(paste0(recommended_k_file, " is missing required columns: ",
              paste(missing_k_cols, collapse = ", ")), call. = FALSE)
}

recommended_k <- recommended_k_raw |>
  transmute(
    instrument,
    recommended_k      = as.integer(recommended_k),
    factorability_flag
  )

valid_specs <- instrument_specs |>
  left_join(recommended_k, by = "instrument") |>
  filter(!is.na(recommended_k))

# Provisional interpretive labels from current working discussion.
# factor_num here refers to the variance-ordered position (largest variance
# explained = F1) produced by the factor reordering step in build_factor_scores(),
# NOT the raw MR1/MR2 labels from psych::fa() which are not stability-ordered.
factor_name_map <- tribble(
  ~instrument,       ~factor_num, ~proposed_name,
  "IMI",                      1L, "Interest & Enjoyment",
  "IMI",                      2L, "Effort & Importance",
  "IMI",                      3L, "Perceived Competence",
  "WritingEfficacy",          1L, "Writing Competence",
  "WritingEfficacy",          2L, "Self-Regulation",
  "WritingEfficacy",          3L, "Resource & Planning",
  "AIReflection",             1L, "Ownership & Usefulness",
  "AIReflection",             2L, "Enjoyment & Satisfaction"
)
```

## Helper Functions

```{r helpers}
# --- Score transformation ---

transform_scores <- function(x, transform_name) {
  values <- as.numeric(x)

  if (transform_name == "identity") return(values)

  if (transform_name == "wse_to_5") {
    return(case_when(
      is.na(values)                          ~ NA_real_,
      values %in% c(0, 25, 50, 75, 100)     ~ (values / 25) + 1,
      TRUE                                   ~ NA_real_
    ))
  }

  stop(glue("Unknown score transform: {transform_name}"))
}

# --- Polychoric correlation ---
# FIX: compute_polychoric_safe() was previously duplicated verbatim in Scripts
# 3 and 4. It now lives in scoring_helpers.R and is sourced once. The version
# below is kept here only as documentation of what scoring_helpers.R must
# contain. If scoring_helpers.R already has it, delete this comment block.
#
# For reference, the function signature is:
#   compute_polychoric_safe(X_int_df) -> list(rho, repair_needed, min_eigen_unsmoothed)

# --- Safe Spearman correlation ---

safe_spearman_pair <- function(data, col_x, col_y) {
  dat <- data |>
    select(all_of(c(col_x, col_y))) |>
    filter(if_all(everything(), ~ !is.na(.x)))

  if (nrow(dat) < min_correlation_sample_size) {
    return(tibble(x = col_x, y = col_y, rho = NA_real_, p = NA_real_,
                  n = nrow(dat), note = "insufficient sample size"))
  }

  # FIX: removed dplyr:: prefix — inconsistent with all other calls in this
  # file which use bare tidyverse functions throughout.
  if (n_distinct(dat[[col_x]]) < 2L) {
    return(tibble(x = col_x, y = col_y, rho = NA_real_, p = NA_real_,
                  n = nrow(dat), note = "no variation in x"))
  }

  if (n_distinct(dat[[col_y]]) < 2L) {
    return(tibble(x = col_x, y = col_y, rho = NA_real_, p = NA_real_,
                  n = nrow(dat), note = "no variation in y"))
  }

  test <- suppressWarnings(
    cor.test(dat[[col_x]], dat[[col_y]], method = "spearman", exact = FALSE)
  )

  tibble(
    x    = col_x,
    y    = col_y,
    rho  = unname(test$estimate),
    p    = test$p.value,
    n    = nrow(dat),
    note = NA_character_
  )
}

# --- Instrument data builder ---

build_instrument_long <- function(file, item_id_col, score_transform, prefix) {
  long <- read_csv(file, show_col_types = FALSE) |>
    transmute(
      participant_id = as.character(participant_id),
      item_id        = as.integer(.data[[item_id_col]]),
      item_text      = as.character(item_text),
      score          = transform_scores(score, score_transform)
    ) |>
    filter(!participant_id %in% efa_global_exclusions) |>
    # All included instruments are ordinal scales; WSE is explicitly remapped
    # to 1-5 anchors, so integer coercion keeps polychoric/factor scoring
    # aligned.
    mutate(score = as.integer(round(score)))

  item_lookup <- long |>
    distinct(item_id, item_text) |>
    arrange(item_id) |>
    mutate(item_col = paste0(prefix, "_", item_id))

  wide <- long |>
    select(participant_id, item_id, score) |>
    left_join(item_lookup |> select(item_id, item_col), by = "item_id") |>
    select(participant_id, item_col, score) |>
    pivot_wider(names_from = item_col, values_from = score) |>
    arrange(participant_id)

  list(long = long, item_lookup = item_lookup, wide = wide)
}

# --- Factor score builder ---
# FIX 1: rotate = "oblimin" is now conditional on recommended_k > 1, matching
# Script 3. psych::fa() throws a warning/error when asked to rotate a single
# factor, so k = 1 must use rotate = "none".
#
# FIX 2: factors are reordered by variance explained (descending) before
# building factor_lookup, matching the convention established in Script 3's
# extract_final_solution(). In Script 3, F1 = highest variance explained,
# F2 = second highest, etc. Without this reordering, the MR1/MR2 labels from
# psych::fa() are used raw, and MR2 here may correspond to what Script 3
# called F1 — silently attaching the wrong factor_name_map labels.

build_factor_scores <- function(instrument, file, item_id_col,
                                score_transform, prefix, recommended_k) {
  obj <- build_instrument_long(file, item_id_col, score_transform, prefix)

  matrix_df <- obj$wide |>
    select(-participant_id) |>
    mutate(across(everything(), as.integer)) |>
    as.data.frame()

  poly_out <- compute_polychoric_safe(matrix_df)

  # Defensive seed: ensures factor solution is reproducible regardless of
  # upstream code changes that may consume random numbers.
  set.seed(42L)

  fa_fit <- suppressWarnings(
    psych::fa(
      r        = poly_out$rho,
      nfactors = recommended_k,
      n.obs    = nrow(matrix_df),
      fm       = "minres",
      # FIX 1: conditional rotation — no rotation for single-factor solutions
      rotate   = if (recommended_k == 1L) "none" else "oblimin"
    )
  )

  # FIX 2: reorder factors by variance explained descending so F1 is always
  # the largest factor, matching Script 3's extract_final_solution() convention.
  # Without this, MR1/MR2 ordering from psych is arbitrary after oblimin
  # rotation and may not match the F1/F2 labels in EFA_Final_Item_Map.csv.
  factor_order <- factor_order_by_variance(
    fa_fit$loadings,
    context_label = paste0(instrument, " factor-score rebuild")
  )

  # Reorder the loading matrix columns to match variance-explained order,
  # then extract factor scores in that same order.
  L_ordered <- unclass(fa_fit$loadings)[, factor_order, drop = FALSE]
  colnames(L_ordered) <- paste0("MR", seq_len(recommended_k))

  # Build a minimal fa object with reordered loadings for factor.scores().
  # We only need $loadings and $weights — psych::factor.scores() uses both.
  fa_fit_ordered           <- fa_fit
  fa_fit_ordered$loadings  <- L_ordered
  class(fa_fit_ordered$loadings) <- c("loadings")

  score_matrix <- psych::factor.scores(
    x      = as.matrix(matrix_df),
    f      = fa_fit_ordered,
    rho    = poly_out$rho,
    method = factor_score_method
  )

  factor_scores <- bind_scores_with_ids(
      participant_ids = obj$wide$participant_id,
      score_matrix = score_matrix$scores,
      context_label = paste0(instrument, " factor scores")
    ) |>
    rename_with(~ paste0(prefix, "_", .x), .cols = starts_with("MR"))

  factor_lookup <- tibble(
    factor     = names(factor_scores)[names(factor_scores) != "participant_id"],
    instrument = instrument
  ) |>
    mutate(
      factor_id  = str_remove(factor, paste0("^", prefix, "_")),
      # factor_num is now the variance-ordered position (1 = most variance),
      # not the raw psych MR number.
      factor_num = as.integer(str_remove(factor_id, "MR"))
    )

  assert_complete_factor_name_map(
    factor_lookup = factor_lookup,
    factor_name_map = factor_name_map,
    context_label = paste0(instrument, " factor_name_map")
  )

  factor_lookup <- factor_lookup |>
    left_join(factor_name_map, by = c("instrument", "factor_num")) |>
    mutate(
      short_factor  = paste0("F", factor_num),
      factor_label  = paste0(instrument, " ", short_factor),
      display_label = paste0(instrument, " ", short_factor, " -> ", proposed_name)
    )

  list(
    instrument    = instrument,
    factor_scores = factor_scores,
    factor_lookup = factor_lookup,
    item_lookup   = obj$item_lookup,
    wide          = obj$wide
  )
}

# --- Item-only instrument builder ---
# Produces the same list structure as build_factor_scores() so downstream
# pmap in the pairwise correlations section works identically for both types.
# factor_scores and factor_lookup are NULL — never accessed for item-only
# instruments.

build_item_only <- function(instrument, file, item_id_col,
                            score_transform, prefix) {
  obj <- build_instrument_long(file, item_id_col, score_transform, prefix)

  list(
    instrument    = instrument,
    factor_scores = NULL,
    factor_lookup = NULL,
    item_lookup   = obj$item_lookup,
    wide          = obj$wide
  )
}
```

## Build Factor Scores for Factorable Instruments

```{r build-factor-scores}
factor_objects <- pmap(
  valid_specs,
  function(instrument, file, item_id_col, score_transform,
           prefix, recommended_k, factorability_flag) {
    build_factor_scores(
      instrument     = instrument,
      file           = file,
      item_id_col    = item_id_col,
      score_transform = score_transform,
      prefix         = prefix,
      recommended_k  = recommended_k
    )
  }
)

# Build item-only objects for non-factorable instruments (BeliefsAboutAI)
item_only_objects <- pmap(
  item_only_specs,
  function(instrument, file, item_id_col, score_transform, prefix) {
    build_item_only(
      instrument      = instrument,
      file            = file,
      item_id_col     = item_id_col,
      score_transform = score_transform,
      prefix          = prefix
    )
  }
)

factor_lookup     <- map_dfr(factor_objects, "factor_lookup")
all_factor_scores <- reduce(map(factor_objects, "factor_scores"),
                            full_join, by = "participant_id")
factor_cols       <- names(all_factor_scores) |> setdiff("participant_id")

assert_lookup_covers_factor_columns(
  factor_lookup = factor_lookup,
  factor_cols = factor_cols,
  context_label = "Script 06 combined factor lookup"
)

write_csv(factor_lookup,     file.path(csv_dir, "Factor_Name_Map.csv"))
write_csv(all_factor_scores, file.path(csv_dir, "Factor_Scores_All_Instruments.csv"))

strict_paired_ids <- read_csv(
  order_effects_analysis_ready_file,
  show_col_types = FALSE
) |>
  transmute(participant_id = as.character(participant_id))

assert_expected_count(nrow(strict_paired_ids), 82L, "Script 06 strict paired factor-heatmap IDs")
assert_unique_pid_rows(strict_paired_ids, "participant_id", "Script 06 strict paired factor-heatmap IDs")

factor_heatmap_scores <- all_factor_scores |>
  mutate(participant_id = as.character(participant_id)) |>
  semi_join(strict_paired_ids, by = "participant_id")

assert_expected_count(nrow(factor_heatmap_scores), 82L, "Script 06 strict paired factor-heatmap scores")
```

## Factor Name Map (Current Working Labels)

```{r factor-name-table}
factor_lookup |>
  select(instrument, short_factor, proposed_name, display_label) |>
  arrange(instrument, short_factor) |>
  kable()
```

## Cross-Instrument Factor Heatmap

```{r factor-heatmap-data}
factor_pairs <- t(combn(factor_cols, 2)) |>
  as_tibble(.name_repair = "minimal") |>
  setNames(c("factor_x", "factor_y"))

factor_corr_unique <- factor_pairs |>
  mutate(
    result = map2(factor_x, factor_y,
                  ~ safe_spearman_pair(factor_heatmap_scores, .x, .y))
  ) |>
  pull(result) |>
  bind_rows() |>
  rename(factor_x = x, factor_y = y) |>
  mutate(
    p_bonferroni = p.adjust(p, method = "bonferroni"),
    p_bh         = p.adjust(p, method = "BH"),
    abs_r        = abs(rho)
  ) |>
  left_join(
    factor_lookup |>
      transmute(factor_x = factor, instrument_x = instrument,
                factor_label_x = display_label),
    by = "factor_x"
  ) |>
  left_join(
    factor_lookup |>
      transmute(factor_y = factor, instrument_y = instrument,
                factor_label_y = display_label),
    by = "factor_y"
  ) |>
  mutate(
    pair_type           = if_else(instrument_x == instrument_y,
                                  "Within instrument", "Across instrument"),
    session_relation    = case_when(
      instrument_x %in% traditional_session_instruments & instrument_y %in% traditional_session_instruments ~ "Within Traditional session",
      instrument_x %in% ai_session_instruments & instrument_y %in% ai_session_instruments ~ "Within AI session",
      TRUE ~ "Cross-session Traditional_vs_AI"
    ),
    survives_bh         = p_bh < 0.05,
    survives_bonferroni = p_bonferroni < 0.05
  )

# FIX: diagonal join bug. The original pre-populated instrument_x,
# factor_label_x, instrument_y, factor_label_y as NA_character_, then
# immediately left_join'd on columns with those same names. dplyr suffix-
# collided them into instrument_x.x / instrument_x.y, leaving the post-join
# label columns as NA. The heatmap then had NA factor levels for all diagonal
# cells, silently dropping or misplacing them.
#
# Fix: do NOT pre-populate those four columns. Build only the columns that
# are not derived from the joins, then let the joins add the label columns
# cleanly with no suffix collision.
factor_corr_diag <- tibble(
  factor_x            = factor_cols,
  factor_y            = factor_cols,
  rho                 = 1,
  p                   = NA_real_,
  n                   = map_int(factor_cols,
                                ~ sum(!is.na(factor_heatmap_scores[[.x]]))),
  note                = "diagonal",
  p_bonferroni        = NA_real_,
  p_bh                = NA_real_,
  abs_r               = 1,
  pair_type           = "Diagonal",
  session_relation    = "Diagonal",
  survives_bh         = NA,
  survives_bonferroni = NA
) |>
  left_join(
    factor_lookup |>
      transmute(factor_x = factor, instrument_x = instrument,
                factor_label_x = display_label),
    by = "factor_x"
  ) |>
  left_join(
    factor_lookup |>
      transmute(factor_y = factor, instrument_y = instrument,
                factor_label_y = display_label),
    by = "factor_y"
  )

# Verify the fix worked — all diagonal label columns must be non-NA
if (any(is.na(factor_corr_diag$factor_label_x)) || any(is.na(factor_corr_diag$factor_label_y))) {
  stop(
    "Diagonal factor-correlation labels contain NA after factor-lookup join; heatmap label join failed.",
    call. = FALSE
  )
}

factor_corr_heat <- bind_rows(
  factor_corr_unique,
  factor_corr_unique |>
    transmute(
      factor_x            = factor_y,
      factor_y            = factor_x,
      rho, p, n, note, p_bonferroni, p_bh, abs_r,
      instrument_x        = instrument_y,
      factor_label_x      = factor_label_y,
      instrument_y        = instrument_x,
      factor_label_y      = factor_label_x,
      pair_type, survives_bh, survives_bonferroni
    ),
  factor_corr_diag
)

write_csv(factor_corr_unique, file.path(csv_dir, "Factor_Correlations_Unique.csv"))
write_csv(factor_corr_heat,   file.path(csv_dir, "Factor_Correlations_Heatmap_Matrix.csv"))
```

```{r factor-heatmap-plot, fig.width=12, fig.height=9}
factor_levels <- factor_lookup |>
  arrange(match(instrument, valid_specs$instrument), factor_num) |>
  pull(display_label)

factor_heat_df <- factor_corr_heat |>
  mutate(
    factor_label_x = factor(factor_label_x, levels = factor_levels),
    factor_label_y = factor(factor_label_y, levels = rev(factor_levels)),
    sig_label = case_when(
      factor_x == factor_y  ~ "",
      survives_bonferroni   ~ "**",
      survives_bh           ~ "*",
      TRUE                  ~ ""
    ),
    # FIX: suppress cell label on diagonal — 1.00 is self-evident and
    # the dark fill makes it illegible anyway
    cell_label = case_when(
      factor_x == factor_y ~ "",
      is.na(rho)           ~ "",
      TRUE                 ~ paste0(formatC(rho, format = "f", digits = 2), sig_label)
    )
  )

factor_heatmap_plot <- ggplot(
  factor_heat_df,
  aes(x = factor_label_x, y = factor_label_y, fill = rho)
) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = cell_label), size = 2.8) +
  scale_fill_gradient2(
    low      = "#c73e3a",
    mid      = "#f7f7f7",
    high     = "#4f79b7",
    midpoint = 0,
    limits   = c(-1, 1),
    name     = "Spearman rho"
  ) +
  labs(
    title    = "Interesting Findings Finder: Factor Heatmap Across 3 Instruments",
    subtitle = "Strict paired analysis sample, N = 82. * BH < .05   ** Bonferroni < .05",
    x        = NULL,
    y        = NULL
  ) +
  theme(
  panel.grid   = element_blank(),
  axis.text.x  = element_text(size = 9, lineheight = 0.9,
                               angle = 45, hjust = 1),  # ADD angle + hjust
  axis.text.y  = element_text(size = 9),
  plot.margin  = margin(10, 20, 40, 10)  # increase bottom margin for rotated labels
)

ggsave(
  filename = file.path(plot_dir, "Factor_Heatmap_Across_3_Instruments.png"),
  plot     = factor_heatmap_plot,
  width    = 13, height = 10, units = "in", dpi = 300, bg = "white"
)
ggsave(
  filename = file.path(plot_dir, "Factor_Heatmap_Across_3_Instruments.pdf"),
  plot     = factor_heatmap_plot,
  width    = 13, height = 10, units = "in", bg = "white"
)

factor_heatmap_plot
```

## Pairwise Item-Level Correlations by Instrument Pair

```{r pairwise-correlations}

# Merge factorable + item-only objects into single named list.
# Both share identical list structure (instrument, wide, item_lookup).
# factor_scores / factor_lookup are NULL for item-only — never accessed here.
instrument_objects <- c(factor_objects, item_only_objects) |>
  set_names(map_chr(c(factor_objects, item_only_objects), "instrument"))

pair_grid <- combn(names(instrument_objects), 2, simplify = FALSE) |>
  map(~ tibble(instrument_a = .x[1], instrument_b = .x[2])) |>
  bind_rows()

pair_results <- pmap(
  pair_grid,
  function(instrument_a, instrument_b) {
    obj_a <- instrument_objects[[instrument_a]]
    obj_b <- instrument_objects[[instrument_b]]

    wide_a  <- obj_a$wide
    wide_b  <- obj_b$wide
    joined  <- inner_join(wide_a, wide_b, by = "participant_id")

    items_a <- names(wide_a) |> setdiff("participant_id")
    items_b <- names(wide_b) |> setdiff("participant_id")

    # Compute all pairwise correlations for this pair.
    # FIX: p_bonferroni and p_bh are adjusted within each pair separately
    # (not globally across all pairs). This is intentional — each pair has
    # a different number of tests (n_items_a × n_items_b), and a pair-local
    # correction controls the FDR/FWER within that specific comparison set.
    # Consequence: p_bh values from different pairs are NOT directly
    # comparable in the combined top-hits table. Use abs_r for ranking across
    # pairs; use p values only within a single pair.
    corr_df <- expand_grid(item_a = items_a, item_b = items_b) |>
      mutate(
        result = map2(item_a, item_b,
                      ~ safe_spearman_pair(joined, .x, .y))
      ) |>
      pull(result) |>
      bind_rows() |>
      rename(item_a = x, item_b = y) |>
      mutate(
        # Adjustment excludes NA-p rows (insufficient sample / no variation)
        # so bad rows do not inflate the denominator. NA p values are passed
        # through p.adjust() as NA, which is correct behaviour.
        p_bonferroni = p.adjust(p, method = "bonferroni"),
        p_bh         = p.adjust(p, method = "BH"),
        abs_r        = abs(rho),
        pair         = paste0(instrument_a, "_vs_", instrument_b),
        # session_relation tags whether the pair is within the same experimental
        # session (both Traditional-side or both AI-side) or cross-session.
        # Exported in CSVs for downstream filtering; not used in this report.
        session_relation = case_when(
          instrument_a %in% traditional_session_instruments & instrument_b %in% traditional_session_instruments ~ "Within Traditional session",
          instrument_a %in% ai_session_instruments & instrument_b %in% ai_session_instruments ~ "Within AI session",
          TRUE ~ "Cross-session Traditional_vs_AI"
        )
      ) |>
      left_join(
        obj_a$item_lookup |>
          transmute(item_a = item_col, item_id_a = item_id,
                    item_text_a = item_text),
        by = "item_a"
      ) |>
      left_join(
        obj_b$item_lookup |>
          transmute(item_b = item_col, item_id_b = item_id,
                    item_text_b = item_text),
        by = "item_b"
      ) |>
      arrange(p_bh, p_bonferroni, desc(abs_r))

    csv_file <- file.path(
      csv_dir,
      paste0(instrument_a, "_vs_", instrument_b, "_Item_Correlations.csv")
    )
    write_csv(corr_df, csv_file)

    heat_df <- corr_df |>
      mutate(
        item_a = factor(item_a, levels = items_a),
        item_b = factor(item_b, levels = rev(items_b))
      )

    heat_plot <- ggplot(heat_df, aes(x = item_a, y = item_b, fill = rho)) +
      geom_tile(color = "white", linewidth = 0.3) +
      scale_fill_gradient2(
        low      = "#c73e3a",
        mid      = "#f7f7f7",
        high     = "#4f79b7",
        midpoint = 0,
        limits   = c(-1, 1),
        name     = "Spearman rho"
      ) +
      labs(
        title    = glue("{instrument_a} vs {instrument_b}: Item-by-Item Correlations"),
        subtitle = "Exploratory pairwise item correlations (p-values are pair-local corrections)",
        x        = glue("{instrument_a} items"),
        y        = glue("{instrument_b} items")
      ) +
      theme_minimal(base_size = 11) +
      theme(
        panel.grid  = element_blank(),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 7),
        axis.text.y = element_text(size = 7)
      )

    ggsave(
      filename = file.path(
        plot_dir,
        paste0(instrument_a, "_vs_", instrument_b, "_Item_Correlation_Heatmap.png")
      ),
      plot   = heat_plot,
      width  = 14, height = 11, units = "in", dpi = 300, bg = "white"
    )

    list(
      pair         = paste0(instrument_a, "_vs_", instrument_b),
      instrument_a = instrument_a,
      instrument_b = instrument_b,
      joined_n     = nrow(joined),
      total_tests  = nrow(corr_df),
      bh_sig_n     = sum(corr_df$p_bh         < 0.05, na.rm = TRUE),
      bonf_sig_n   = sum(corr_df$p_bonferroni  < 0.05, na.rm = TRUE),
      top_hits     = corr_df |>
        select(pair, item_id_a, item_text_a, item_id_b, item_text_b,
               rho, p_bh, p_bonferroni, n) |>
        slice_head(n = 15),
      all_corrs    = corr_df |>
        select(pair, item_text_a, item_text_b, rho, abs_r,
               p_bh, p_bonferroni, n, note)
    )
  }
)

pair_summary <- map_dfr(pair_results, ~ tibble(
  pair         = .x$pair,
  instrument_a = .x$instrument_a,
  instrument_b = .x$instrument_b,
  joined_n     = .x$joined_n,
  total_tests  = .x$total_tests,
  bh_sig_n     = .x$bh_sig_n,
  bonf_sig_n   = .x$bonf_sig_n
))

top_hits_all_pairs <- map_dfr(pair_results, "top_hits") |>
  # Sort by abs_r, not p_bh, because p_bh values are pair-local corrections
  # and are not comparable across pairs with different test counts.
  arrange(desc(abs(rho)))

# All pairwise item correlations across every instrument pair, ranked by
# effect size. abs_r sorts by magnitude so strong negative correlations
# surface alongside positive ones. p values here are pair-local — do not
# compare them directly across pairs.
all_corr_ranked <- map_dfr(pair_results, "all_corrs") |>
  filter(is.na(note)) |>
  arrange(desc(abs_r)) |>
  select(pair, item_text_a, item_text_b, rho, abs_r, p_bh, p_bonferroni, n)

write_csv(pair_summary,       file.path(csv_dir, "Pairwise_Item_Correlation_Summary.csv"))
write_csv(top_hits_all_pairs, file.path(csv_dir, "Pairwise_Item_Correlation_Top_Hits.csv"))
write_csv(all_corr_ranked,    file.path(csv_dir, "All_Pairwise_Correlations_Ranked.csv"))
```

```{r pair-summary-table}
kable(pair_summary)
```

## Top Cross-Instrument Item Associations

Ranked by effect size (`abs_r`). P-values shown are pair-local multiple
comparison corrections — they are not directly comparable across
instrument pairs with different numbers of tests.

```{r top-hits-table}
top_hits_all_pairs |>
  mutate(
    rho          = round(rho,          3),
    p_bh         = round(p_bh,         4),
    p_bonferroni = round(p_bonferroni, 4)
  ) |>
  slice_head(n = 40) |>
  kable()
```

## Output Manifest

```{r manifest}
findings_manifest <- tibble(
  output_type = c(
    "factor_name_map",
    "factor_scores",
    "factor_correlations_unique",
    "factor_correlations_heatmap",
    "pairwise_item_correlation_summary",
    "pairwise_item_correlation_top_hits",
    "all_pairwise_correlations_ranked"
  ),
  file = c(
    "Factor_Name_Map.csv",
    "Factor_Scores_All_Instruments.csv",
    "Factor_Correlations_Unique.csv",
    "Factor_Correlations_Heatmap_Matrix.csv",
    "Pairwise_Item_Correlation_Summary.csv",
    "Pairwise_Item_Correlation_Top_Hits.csv",
    "All_Pairwise_Correlations_Ranked.csv"
  ),
  description = c(
    "Factor labels and variance-ordered positions from EFA solutions",
    "Factor scores for IMI, WritingEfficacy, AIReflection (primary EFA samples)",
    "Unique Spearman correlations across all factor pairs in the strict paired N = 82 sample (BH and Bonferroni corrected)",
    "Full symmetric strict paired N = 82 heatmap matrix including diagonal entries",
    "Summary of significant item-level correlations per instrument pair",
    "Top 15 item-pair hits per instrument combination, ranked by abs(rho)",
    "All pairwise item correlations across all instrument pairs, ranked by abs(rho)"
  )
)

write_csv(findings_manifest, file.path(csv_dir, "Interesting_Findings_Export_Manifest.csv"))
kable(findings_manifest, caption = "06_interesting_findings.qmd — Output Manifest")
```

## Section: Order-Stratified Item × Item Correlations

This section takes the strongest item-level cross-instrument pairs
already identified in the pairwise correlations above and asks whether
each correlation differs between Traditional-First and AI-First
participants. Fisher's z-test formally tests whether the two subgroup
rhos are significantly different.

Strategy: rather than running every item × item pair (which would be
thousands of tests), this focuses on pairs that already survived
Bonferroni correction in the full-sample analysis — the signal-rich
subset where order moderation is most theoretically meaningful.

**Same power caveat as Script 04 Section 8:** n=45 and n=37 per subgroup
reduces power. A subgroup rho going null alone is not evidence of
moderation — use Fisher z p-value as the decision criterion.

```{r item-strat-setup}
# --- Load order labels ---
# participant_analysis is in scope if running inside 04_order_effects.qmd.
# If running standalone, load Order_Effects_Analysis_Ready.csv instead.
order_labels_items <- if (exists("participant_analysis")) {
  participant_analysis |>
    select(participant_id, order) |>
    mutate(participant_id = as.character(participant_id))
} else {
  read_csv(
    order_effects_analysis_ready_file,
    show_col_types = FALSE
  ) |>
    select(participant_id, order) |>
    mutate(participant_id = as.character(participant_id))
}

# --- Load all pairwise item correlations ranked file ---
# Produced by this script's pairwise-correlations chunk above.
all_corr_ranked_loaded <- read_csv(
  file.path(csv_dir, "All_Pairwise_Correlations_Ranked.csv"),
  show_col_types = FALSE
)

# --- Pull Bonferroni-surviving pairs as target set ---
# These are the pairs worth stratifying — already demonstrated full-sample
# signal, so order moderation question is meaningful.
bonf_pairs <- all_corr_ranked_loaded |>
  filter(p_bonferroni < 0.05) |>
  select(pair, item_text_a, item_text_b, rho, p_bonferroni) |>
  # Re-derive item column names from pair and text for joining back to wide data.
  # item_a and item_b column names are stored in the per-pair CSVs.
  # Load them directly for clean column name recovery.
  mutate(pair_id = row_number())

# Recover item column names (e.g. IMI_3, WSE_7) from per-pair CSVs
# since All_Pairwise_Correlations_Ranked only stores item text.
pair_names <- unique(bonf_pairs$pair)

bonf_with_cols <- map_dfr(pair_names, function(p) {
  pair_csv <- file.path(csv_dir, paste0(p, "_Item_Correlations.csv"))

  if (!file.exists(pair_csv)) {
    warning(glue("Pair CSV not found: {pair_csv}"))
    return(tibble())
  }

  read_csv(pair_csv, show_col_types = FALSE) |>
    filter(p_bonferroni < 0.05) |>
    select(pair, item_a, item_b, item_text_a, item_text_b,
           rho, p_bonferroni, session_relation)
})

cat(glue("Bonferroni-surviving pairs to stratify: {nrow(bonf_with_cols)}\n"))
```

```{r item-strat-helpers}
# Reuse correlate_stratified() from Script 04 Section 8 if in scope,
# otherwise define it here.
if (!exists("correlate_stratified")) {

  spearman_one_group <- function(data, col_x, col_y, group_label) {
    d <- data |>
      select(all_of(c(col_x, col_y))) |>
      filter(!is.na(.data[[col_x]]), !is.na(.data[[col_y]]))

    if (nrow(d) < 10 ||
        n_distinct(d[[col_x]]) < 2 ||
        n_distinct(d[[col_y]]) < 2) {
      return(tibble(
        group = group_label, n = nrow(d),
        rho = NA_real_, p = NA_real_, note = "insufficient data"
      ))
    }

    test <- suppressWarnings(
      cor.test(d[[col_x]], d[[col_y]], method = "spearman", exact = FALSE)
    )

    tibble(
      group = group_label,
      n     = nrow(d),
      rho   = unname(test$estimate),
      p     = test$p.value,
      note  = NA_character_
    )
  }

  correlate_stratified <- function(data, col_x, col_y) {
    full <- spearman_one_group(data, col_x, col_y, "Full")
    trad <- spearman_one_group(
      filter(data, order == "Traditional_First"), col_x, col_y, "Traditional_First"
    )
    ai   <- spearman_one_group(
      filter(data, order == "AI_First"), col_x, col_y, "AI_First"
    )

    fisher_p <- tryCatch({
      if (is.na(trad$rho) || is.na(ai$rho)) NA_real_
      else psych::r.test(
        n   = trad$n,
        r12 = trad$rho,
        n2  = ai$n,
        r34 = ai$rho
      )$p
    }, error = function(e) NA_real_)

    bind_rows(full, trad, ai) |>
      mutate(col_x = col_x, col_y = col_y, fisher_p = fisher_p)
  }
}
```

```{r item-strat-run}
# Build a combined wide table with all item columns + order label.
# Join all instrument wide tables together, then attach order.
all_items_wide <- instrument_objects |>
  map("wide") |>
  reduce(full_join, by = "participant_id") |>
  mutate(participant_id = as.character(participant_id)) |>
  left_join(order_labels_items, by = "participant_id")

# Run stratified correlations for each Bonferroni-surviving item pair
item_strat_results <- pmap_dfr(
  bonf_with_cols |> select(pair, item_a, item_b,
                            item_text_a, item_text_b, session_relation),
  function(pair, item_a, item_b, item_text_a, item_text_b, session_relation) {

    # Guard: both columns must exist in the combined wide table
    missing <- setdiff(c(item_a, item_b), names(all_items_wide))
    if (length(missing) > 0) {
      warning(glue("Columns not found in wide table: {paste(missing, collapse=', ')}"))
      return(tibble())
    }

    correlate_stratified(all_items_wide, item_a, item_b) |>
      mutate(
        pair           = pair,
        item_a         = item_a,
        item_b         = item_b,
        item_text_a    = item_text_a,
        item_text_b    = item_text_b,
        session_relation = session_relation
      )
  }
)

# Pivot wide: one row per item pair, columns for each group's rho/p + fisher_p
item_strat_wide <- item_strat_results |>
  pivot_wider(
    names_from  = group,
    values_from = c(n, rho, p),
    names_glue  = "{group}_{.value}"
  ) |>
  mutate(
    fisher_sig = case_when(
      is.na(fisher_p)  ~ "NA",
      fisher_p < 0.001 ~ "p < .001",
      fisher_p < 0.01  ~ "p < .01",
      fisher_p < 0.05  ~ "p < .05",
      TRUE             ~ paste0("p = ", round(fisher_p, 3))
    ),
    rho_diff = round(Traditional_First_rho - AI_First_rho, 3)
  ) |>
  arrange(fisher_p, desc(abs(rho_diff)))

write_csv(
  item_strat_wide,
  file.path(csv_dir, "Item_Item_Order_Stratified_Correlations.csv")
)
```

```{r item-strat-display}
# Summary counts
n_fisher_sig <- sum(item_strat_wide$fisher_p < 0.05, na.rm = TRUE)
n_total      <- nrow(item_strat_wide)

cat(glue(
  "Bonferroni pairs tested: {n_total}\n",
  "Fisher z significant (p < .05): {n_fisher_sig}\n"
))

# Full table sorted by fisher_p
item_strat_wide |>
  select(
    pair, session_relation,
    item_text_a, item_text_b,
    Full_n, Full_rho, Full_p,
    Traditional_First_n, Traditional_First_rho, Traditional_First_p,
    AI_First_n, AI_First_rho, AI_First_p,
    fisher_p, fisher_sig, rho_diff
  ) |>
  mutate(
    item_text_a = str_trunc(item_text_a, 55),
    item_text_b = str_trunc(item_text_b, 55),
    across(where(is.numeric), ~ round(.x, 3))
  ) |>
  kable(caption = paste0(
    "Item × item correlations stratified by order group. ",
    "Only Bonferroni-surviving full-sample pairs shown. ",
    "fisher_p tests whether Traditional-First rho differs significantly from AI-First rho. ",
    "rho_diff = Traditional_First_rho minus AI_First_rho."
  ))
```

```{r item-strat-manifest-update}
# Append to existing manifest
item_strat_manifest_row <- tibble(
  output_type = "item_item_order_stratified",
  file        = "Item_Item_Order_Stratified_Correlations.csv",
  description = paste0(
    "Item × item Spearman correlations (Bonferroni-surviving pairs only) ",
    "stratified by order group with Fisher z-test for subgroup rho difference"
  )
)

write_csv(
  item_strat_manifest_row,
  file.path(csv_dir, "Item_Item_Order_Stratified_Manifest.csv")
)

kable(item_strat_manifest_row)
```

