---
title: "Cowriters Survey Order Effects Analysis"
format:
  html:
    toc: true
    toc-depth: 2
output-dir: "06_order_effects"
execute:
  echo: false
  warning: false
  message: false
editor:
  markdown:
    wrap: 72
---

# Order Effects Analysis

This script is a downstream inferential step after the EFA
export/analysis pipeline. It builds composite scores from the locked EFA
item map, compares Traditional-First versus AI-First participants, and
tests Tool × Order interactions with a secondary topic-controlled model.

```{r setup}

library(tidyverse)
library(knitr)
if (!file.exists("scoring_helpers.R")) {
  stop("Required file scoring_helpers.R not found.", call. = FALSE)
}
source("scoring_helpers.R", local = knitr::knit_global())
set.seed(42L)
```

## Section 1: Paths and Input Data

```{r load-data}
order_levels <- c("Traditional_First", "AI_First")
topic_levels <- c("Metaphor", "Category")
adjustment_methods <- c("BH", "bonferroni")

script_dir <- "06_order_effects"
csv_dir <- file.path(script_dir, "csv")
plot_dir <- file.path(script_dir, "plots")
master_wide_file <- file.path("02_efa_exports", "Final_Master_Wide.csv")
final_item_map_file <- file.path("03_efa_analysis", "EFA_Final_Item_Map.csv")
factor_scores_all_file <- file.path("05_interesting_findings", "csv", "Factor_Scores_All_Instruments.csv")
beliefs_wide_file <- file.path("04_beliefs_item_analysis", "csv", "BeliefsAboutAI_Wide.csv")
factor_name_map_file <- file.path("05_interesting_findings", "csv", "Factor_Name_Map.csv")
beliefs_long_file <- file.path("02_efa_exports", "efa", "BeliefsAboutAI_EFA_Primary.csv")
schedule_lab_files <- tribble(
  ~lab_source,   ~path,
  "SS2",         "Scheduling Tracking - SS2.csv",
  "Stevenson",   "Scheduling Tracking - Stevenson.csv"
)
dir.create(csv_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(plot_dir, recursive = TRUE, showWarnings = FALSE)

master_wide <- read_csv(master_wide_file, show_col_types = FALSE)
tracking <- read_csv(
  "Participant Tracking - IDs and Conditions Table.csv",
  show_col_types = FALSE
)
final_item_map <- read_csv(final_item_map_file, show_col_types = FALSE)

required_master_cols <- c("participant_id", "order", "condition_1", "condition_2")
missing_master_cols <- setdiff(required_master_cols, names(master_wide))
if (length(missing_master_cols) > 0) {
  stop(
    paste0(
      basename(master_wide_file), " is missing required columns: ",
      paste(missing_master_cols, collapse = ", ")
    ),
    call. = FALSE
  )
}

required_tracking_cols <- c("ParticipantID", "Topic 1", "Topic 2", "Condition 1", "Condition 2")
missing_tracking_cols <- setdiff(required_tracking_cols, names(tracking))
if (length(missing_tracking_cols) > 0) {
  stop(
    paste0(
      "Participant tracking file is missing required columns: ",
      paste(missing_tracking_cols, collapse = ", ")
    ),
    call. = FALSE
  )
}

assert_required_columns(final_item_map, c("instrument", "factor_id", "item_id"), "EFA_Final_Item_Map")
assert_factor_id_format(final_item_map$factor_id, "EFA_Final_Item_Map factor_id")
```

## Section 2: Build Analysis-Ready Participant Table (Order + Topic)

```{r build-participant-table}

tracking_topics <- tracking |>
  transmute(
    participant_id = as.character(ParticipantID),
    topic_1 = as.character(`Topic 1`),
    topic_2 = as.character(`Topic 2`),
    condition_1_track = as.character(`Condition 1`),
    condition_2_track = as.character(`Condition 2`)
  ) |>
  filter(!is.na(participant_id))

assert_unique_pid_rows(
  tracking_topics,
  pid_col = "participant_id",
  context_label = "tracking_topics"
)

participant_analysis <- master_wide |>
  mutate(participant_id = as.character(participant_id)) |>
  inner_join(tracking_topics, by = "participant_id") |>
  mutate(
    order = factor(order, levels = order_levels),
    traditional_topic = case_when(
      condition_1 == "Alone" ~ topic_1,
      condition_2 == "Alone" ~ topic_2,
      TRUE ~ NA_character_
    ),
    ai_topic = case_when(
      condition_1 == "LLM" ~ topic_1,
      condition_2 == "LLM" ~ topic_2,
      TRUE ~ NA_character_
    ),
    traditional_topic = factor(traditional_topic, levels = topic_levels),
    ai_topic          = factor(ai_topic,          levels = topic_levels),
    # first_topic = the article type in session 1 (between-subjects covariate).
    # Because design is fully counterbalanced, first_topic = traditional_topic
    # for Traditional-First participants and = ai_topic for AI-First participants.
    # It is constant per participant and goes outside Error() in the ANOVA.
    first_topic = factor(
      case_when(
        order == "Traditional_First" ~ as.character(traditional_topic),
        order == "AI_First"          ~ as.character(ai_topic),
        TRUE                         ~ NA_character_
      ),
      levels = topic_levels
    )
  )

assert_expected_count(nrow(participant_analysis), 82L, "participant_analysis row count")
assert_unique_pid_rows(participant_analysis, "participant_id", "participant_analysis")
assert_no_missing_values(
  participant_analysis,
  c("participant_id", "order", "condition_1", "condition_2", "topic_1", "topic_2", "first_topic"),
  "participant_analysis"
)

order_mismatch <- participant_analysis |>
  filter(
    !is.na(order),
    !is.na(condition_1),
    !is.na(condition_2),
    (
      order == "Traditional_First" & !(condition_1 == "Alone" & condition_2 == "LLM")
    ) |
      (
        order == "AI_First" & !(condition_1 == "LLM" & condition_2 == "Alone")
      )
  )

if (nrow(order_mismatch) > 0) {
  stop(
    paste0(
      "Order/condition mismatch detected for participants: ",
      paste(order_mismatch$participant_id, collapse = ", ")
    ),
    call. = FALSE
  )
}

participant_topic_summary <- participant_analysis |>
  summarise(
    n_participants = n(),
    traditional_topic_missing = sum(is.na(traditional_topic)),
    ai_topic_missing = sum(is.na(ai_topic)),
    order_missing = sum(is.na(order))
  )

write_csv(participant_topic_summary, file.path(csv_dir, "Participant_Topic_Summary.csv"))
```

## Section 3: Build Unit-Weighted Composite Scores from Locked Item Map

```{r build-composites}

instrument_prefix_map <- tribble(
  ~instrument,       ~item_prefix,
  "IMI",            "IMI_",
  "WritingEfficacy", "Efficacy_",
  "AIReflection",   "Refl_",
  "BeliefsAboutAI", "Beliefs_"
)

locked_item_map <- if ("efa_sample" %in% names(final_item_map)) {
  final_item_map |>
    filter(efa_sample == "primary")
} else {
  final_item_map
}

if ("clean_item" %in% names(locked_item_map)) {
  locked_item_map <- locked_item_map |> filter(clean_item)
}

locked_item_map <- locked_item_map |>
  filter(!is.na(instrument), !is.na(factor_id), !is.na(item_id)) |>
  distinct(instrument, factor_id, item_id)

if (nrow(locked_item_map) == 0) {
  stop(paste0("No locked clean items found in ", final_item_map_file, "."), call. = FALSE)
}

print(unique(locked_item_map$instrument))
print(filter(locked_item_map, grepl("rit", instrument, ignore.case = TRUE)))

composite_membership <- locked_item_map |>
  left_join(instrument_prefix_map, by = "instrument") |>
  mutate(
    item_col = paste0(item_prefix, item_id),
    composite = paste0(instrument, "_", factor_id)
  )

if (any(is.na(composite_membership$item_prefix))) {
  bad_instruments <- composite_membership |>
    filter(is.na(item_prefix)) |>
    distinct(instrument) |>
    pull(instrument)

  stop(
    paste0(
      "Instrument-to-prefix mapping missing for: ",
      paste(bad_instruments, collapse = ", ")
    ),
    call. = FALSE
  )
}

missing_item_cols <- setdiff(unique(composite_membership$item_col), names(participant_analysis))
if (length(missing_item_cols) > 0) {
  stop(
    paste0(
      "Composite item columns missing from Final_Master_Wide: ",
      paste(missing_item_cols, collapse = ", ")
    ),
    call. = FALSE
  )
}

composite_specs <- composite_membership |>
  group_by(instrument, factor_id, composite) |>
  summarise(
    item_cols = list(sort(unique(item_col))),
    n_items = n(),
    composite_meaning = paste0(
      first(instrument),
      " ",
      first(factor_id),
      " unit-weighted mean of clean items"
    ),
    rowmeans_na_rm = FALSE,
    .groups = "drop"
  )

assert_nonempty_df(composite_specs, "composite_specs")

participant_with_composites <- participant_analysis

for (i in seq_len(nrow(composite_specs))) {
  comp_name <- composite_specs$composite[[i]]
  item_cols <- composite_specs$item_cols[[i]]

  participant_with_composites[[comp_name]] <- rowMeans(
    participant_with_composites[, item_cols, drop = FALSE],
    # Hard stop on partial composites: because these are unit-weighted means of
    # locked EFA item sets, every contributing item must be present.
    na.rm = FALSE
  )
}

composite_cols <- composite_specs$composite

composite_score_summary <- participant_with_composites |>
  summarise(
    across(
      all_of(composite_cols),
      list(
        mean = ~ mean(.x, na.rm = TRUE),
        sd = ~ sd(.x, na.rm = TRUE),
        n_nonmissing = ~ sum(!is.na(.x))
      ),
      .names = "{.col}__{.fn}"
    )
  )

write_csv(composite_membership, file.path(csv_dir, "Composite_Item_Membership.csv"))
write_csv(composite_specs, file.path(csv_dir, "Composite_Specs.csv"))
write_csv(composite_score_summary, file.path(csv_dir, "Composite_Score_Summary.csv"))
```

## Section 4: Long Composite Table + Descriptives by Order

```{r descriptives}

composite_long <- participant_with_composites |>
  select(
    participant_id,
    order,
    traditional_topic,
    ai_topic,
    all_of(composite_cols)
  ) |>
  pivot_longer(
    cols = all_of(composite_cols),
    names_to = "composite",
    values_to = "score"
  )

order_descriptives <- composite_long |>
  group_by(composite, order) |>
  summarise(
    n = sum(!is.na(score)),
    mean = mean(score, na.rm = TRUE),
    sd = sd(score, na.rm = TRUE),
    median = median(score, na.rm = TRUE),
    iqr = IQR(score, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(composite, order)

write_csv(composite_long, file.path(csv_dir, "Composite_Long.csv"))
write_csv(order_descriptives, file.path(csv_dir, "Order_Descriptives_By_Composite.csv"))
```

```{r descriptive-plots, fig.width=10, fig.height=6}

make_filename_safe <- function(x) {
  stringr::str_replace_all(x, "[^A-Za-z0-9_\\-]+", "_")
}

for (comp in composite_cols) {
  p <- composite_long |>
    filter(composite == comp) |>
    ggplot(aes(x = order, y = score, fill = order)) +
    geom_violin(alpha = 0.35, width = 0.9, color = NA, na.rm = TRUE) +
    geom_boxplot(width = 0.18, outlier.alpha = 0.6, na.rm = TRUE) +
    scale_fill_manual(values = c(
      "Traditional_First" = "#4f79b7",
      "AI_First" = "#c96b3b"
    )) +
    labs(
      title = paste0("Order Split: ", comp),
      x = "Order Group",
      y = "Composite Score",
      fill = NULL
    ) +
    theme_minimal(base_size = 12)

  file_stub <- make_filename_safe(comp)

  ggsave(
    filename = file.path(plot_dir, paste0(file_stub, "_order_violin_box.png")),
    plot = p,
    width = 10,
    height = 6,
    units = "in",
    dpi = 300,
    bg = "white"
  )

  ggsave(
    filename = file.path(plot_dir, paste0(file_stub, "_order_violin_box.pdf")),
    plot = p,
    width = 10,
    height = 6,
    units = "in",
    bg = "white"
  )
}
```

## Section 5: Mann-Whitney U Tests by Order

**Multiple-comparison correction strategy:** Composite-level tests
(Section 5) form one correction family — all EFA-derived composites
tested for order effects. Item-level tests (Section 5b) use a two-tier
strategy: BH correction within each instrument (controls FDR per
instrument) and Bonferroni correction globally across all items. Mixed
ANOVA interaction p-values (Section 6) are corrected within each model
type (primary, topic-controlled) separately.

```{r mann-whitney}

# Two-vector wilcox: x = Trad-First scores, y = AI-First scores.
# wilcox.test() returns the rank-sum W statistic for x, not U directly.
# Convert W -> U before computing rank-biserial effect size.
#
# Sign convention: positive rb -> Traditional-First tends higher.
# This depends on W being the rank-sum for the Traditional-First group,
# which requires trad_vec to always be passed as x (first argument).
# The formula interface (used in the item-level section below) also produces
# W for the first factor level of `order`, which is "Traditional_First"
# because order_levels is defined with that level first.
rank_biserial_from_u <- function(u_stat, n1, n2) {
  (2 * as.numeric(u_stat) / (n1 * n2)) - 1
}

mann_whitney_results <- map_dfr(composite_cols, function(comp) {
  dat <- participant_with_composites |>
    select(order, all_of(comp)) |>
    rename(score = all_of(comp)) |>
    filter(!is.na(order), !is.na(score))

  trad_vec <- dat |> filter(order == "Traditional_First") |> pull(score)
  ai_vec   <- dat |> filter(order == "AI_First")          |> pull(score)

  n_trad <- length(trad_vec)
  n_ai   <- length(ai_vec)

  med_trad <- median(trad_vec)
  med_ai   <- median(ai_vec)

  if (n_trad < 2 || n_ai < 2) {
    return(tibble(
      composite = comp,
      n_traditional_first = n_trad,
      n_ai_first = n_ai,
      median_traditional_first = med_trad,
      median_ai_first = med_ai,
      w_stat = NA_real_,
      u_stat = NA_real_,
      p_value = NA_real_,
      estimate_hl = NA_real_,
      conf_low = NA_real_,
      conf_high = NA_real_,
      rank_biserial = NA_real_,
      note = "insufficient sample size"
    ))
  }

  test <- suppressWarnings(
    wilcox.test(
      x         = trad_vec,
      y         = ai_vec,
      exact     = FALSE,
      conf.int  = TRUE,
      conf.level = 0.95
    )
  )

  w <- as.numeric(unname(test$statistic))


  tibble(
    composite = comp,
    n_traditional_first = n_trad,
    n_ai_first = n_ai,
    median_traditional_first = med_trad,
    median_ai_first = med_ai,
    w_stat = w,
    u_stat = as.numeric(w),
    p_value = test$p.value,
    estimate_hl = if (!is.null(test$estimate)) as.numeric(test$estimate) else NA_real_,
    conf_low  = if (!is.null(test$conf.int)) as.numeric(test$conf.int[[1]]) else NA_real_,
    conf_high = if (!is.null(test$conf.int)) as.numeric(test$conf.int[[2]]) else NA_real_,
    rank_biserial = rank_biserial_from_u(w, n_trad, n_ai),
    note = NA_character_
  )
}) |>
  left_join(
    composite_specs |>
      select(composite, instrument, factor_id, n_items, composite_meaning, rowmeans_na_rm),
    by = "composite"
  ) |>
  mutate(
    p_bh = p.adjust(p_value, method = adjustment_methods[[1]]),
    p_bonferroni = p.adjust(p_value, method = adjustment_methods[[2]]),
    effect_size = rank_biserial
  ) |>
  select(
    composite, instrument, factor_id, n_items, composite_meaning, rowmeans_na_rm,
    n_traditional_first, n_ai_first, median_traditional_first, median_ai_first,
    w_stat, u_stat, p_value, p_bh, p_bonferroni, estimate_hl, conf_low, conf_high,
    effect_size, note
  ) |>
  arrange(p_bh, p_value)

write_csv(mann_whitney_results, file.path(csv_dir, "Mann_Whitney_Order_Comparisons.csv"))
```

```{r}
# ============================================================
# S5b: Item-Level Order Effects (Mann-Whitney per item)
# ============================================================

# Prefix map: instrument name → column prefix in master data
item_prefix_map <- tribble(
  ~instrument,       ~prefix,    ~n_items,
  "IMI",             "IMI_",         18,
  "WritingEfficacy", "Efficacy_",    20,
  "AIReflection",    "Refl_",        12,
  "BeliefsAboutAI",  "Beliefs_",     22
)

# Build long item-level dataframe
item_long <- item_prefix_map |>
  pmap_dfr(function(instrument, prefix, n_items) {
    cols <- paste0(prefix, seq_len(n_items))
    missing <- setdiff(cols, names(participant_with_composites))
    if (length(missing) > 0) {
      stop(
        paste0(
          "Item-level order effects are missing required columns for ",
          instrument, ": ", paste(missing, collapse = ", ")
        ),
        call. = FALSE
      )
    }
    participant_with_composites |>
      select(participant_id, order, all_of(cols)) |>
      pivot_longer(
        cols = all_of(cols),
        names_to  = "column",
        values_to = "score"
      ) |>
      mutate(
        instrument = instrument,
        item_num   = as.integer(str_extract(column, "\\d+$")),
        item_label = paste0(instrument, "_item", item_num)
      )
  })

# Mann-Whitney per item
item_mw_results <- item_long |>
  group_by(instrument, item_label, item_num) |>
  group_modify(function(df, keys) {
    trad <- df |> filter(order == "Traditional_First") |> pull(score)
    ai   <- df |> filter(order == "AI_First")          |> pull(score)
    
    if (length(trad) < 3 || length(ai) < 3) {
      return(tibble(
        n_traditional_first = length(trad),
        n_ai_first          = length(ai),
        w_stat = NA_real_, u_stat = NA_real_, p_value = NA_real_,
        estimate_hl = NA_real_, conf_low = NA_real_, conf_high = NA_real_,
        rank_biserial = NA_real_, note = "Insufficient data"
      ))
    }
    
    test <- wilcox.test(trad, ai, exact = FALSE, conf.int = TRUE)
    w    <- as.numeric(unname(test$statistic))
    r_rb <- rank_biserial_from_u(w, length(trad), length(ai))
    
    tibble(
      n_traditional_first = length(trad),
      n_ai_first          = length(ai),
      w_stat        = w,
      u_stat        = w,
      p_value       = test$p.value,
      estimate_hl   = test$estimate,
      conf_low      = test$conf.int[[1]],
      conf_high     = test$conf.int[[2]],
      rank_biserial = as.numeric(r_rb),
      note          = NA_character_
    )
  }) |>
  ungroup()

# BH correction within each instrument, Bonferroni global
item_mw_results <- item_mw_results |>
  group_by(instrument) |>
  mutate(p_bh_within = p.adjust(p_value, method = "BH")) |>
  ungroup() |>
  mutate(p_bonferroni_global = p.adjust(p_value, method = "bonferroni")) |>
  arrange(instrument, item_num)

# Flag significant items
item_mw_results <- item_mw_results |>
  mutate(
    sig_within_instrument = p_bh_within       < 0.05,
    sig_global            = p_bonferroni_global < 0.05
  )

# Export
write_csv(
  item_mw_results,
  file.path(csv_dir, "Item_Level_Order_Comparisons.csv")
)

# Summary table — significant items only
sig_items <- item_mw_results |>
  filter(sig_within_instrument) |>
  select(instrument, item_label, n_traditional_first, n_ai_first,
         w_stat, p_value, p_bh_within, p_bonferroni_global, rank_biserial)

cat("\n--- Significant items (BH within instrument) ---\n")
if (nrow(sig_items) == 0) {
  cat("None.\n")
} else {
  print(kable(sig_items))
}
```

## Section 6a: Approved Two-Way ANOVA Order Effects (One-Time Surveys)

```{r approved-lm-order-effects}

# ── Helper: run lm, extract terms, compute partial eta-sq ──────────────────
run_two_way_lm <- function(data, dv, formula_chr, survey_label) {
  dat <- data |> filter(!is.na(.data[[dv]]))
  
  if (nrow(dat) < 10) {
    warning(paste0("Skipping ", survey_label, "/", dv, ": n = ", nrow(dat)))
    return(NULL)
  }
  
  fit <- lm(as.formula(paste(dv, formula_chr)), data = dat)
  av  <- anova(fit)
  
  tibble(
    survey    = survey_label,
    composite = dv,
    term      = rownames(av),
    df        = av$Df,
    ss        = av$`Sum Sq`,
    ms        = av$`Mean Sq`,
    f_value   = av$`F value`,
    p_value   = av$`Pr(>F)`,
    partial_eta_sq = av$`Sum Sq` / (av$`Sum Sq` + av[nrow(av), "Sum Sq"])
  ) |>
    filter(term != "Residuals")
}

# ── Identify composites per survey ─────────────────────────────────────────
imi_composites <- composite_specs |>
  filter(instrument == "IMI") |>
  pull(composite)

wse_composites <- composite_specs |>
  filter(instrument == "WritingEfficacy") |>
  pull(composite)

air_composites <- composite_specs |>
  filter(instrument == "AIReflection") |>
  pull(composite)

beliefs_cols_present <- names(participant_with_composites)[
  str_starts(names(participant_with_composites), "Beliefs_") &
  !str_detect(names(participant_with_composites), "_F")
]

beliefs_efa_composites <- composite_specs |>
  filter(instrument == "BeliefsAboutAI") |>
  pull(composite)

if (length(beliefs_efa_composites) > 0) {
  beliefs_dvs <- beliefs_efa_composites
} else if (length(beliefs_cols_present) > 0) {
  participant_with_composites <- participant_with_composites |>
    mutate(BeliefsAboutAI_mean = rowMeans(
      pick(all_of(beliefs_cols_present)), na.rm = FALSE
    ))
  beliefs_dvs <- "BeliefsAboutAI_mean"
  message("BeliefsAboutAI: no EFA composites found, using item mean.")
} else {
  beliefs_dvs <- character(0)
  warning("BeliefsAboutAI: no item columns or composites found.")
}

# ── Run models ──────────────────────────────────────────────────────────────

# Model 1: IMI — score ~ Order * traditional_topic (Traditional session instrument)
imi_results <- map_dfr(
  imi_composites,
  ~ run_two_way_lm(
      participant_with_composites,
      dv = .x,
      formula_chr = "~ order * traditional_topic",
      survey_label = "IMI"
    )
)

# Model 2: WritingEfficacy — score ~ Order * traditional_topic (Traditional session instrument)
wse_results <- map_dfr(
  wse_composites,
  ~ run_two_way_lm(
      participant_with_composites,
      dv = .x,
      formula_chr = "~ order * traditional_topic",
      survey_label = "WritingEfficacy"
    )
)

# Model 3: AIReflection — score ~ Order * ai_topic (AI session instrument)
air_results <- map_dfr(
  air_composites,
  ~ run_two_way_lm(
      participant_with_composites,
      dv = .x,
      formula_chr = "~ order * ai_topic",
      survey_label = "AIReflection"
    )
)

# Model 4: BeliefsAboutAI — score ~ Order * ai_topic (AI session instrument)
beliefs_results <- map_dfr(
  beliefs_dvs,
  ~ run_two_way_lm(
      participant_with_composites,
      dv = .x,
      formula_chr = "~ order * ai_topic",
      survey_label = "BeliefsAboutAI"
    )
)

all_lm_results <- bind_rows(imi_results, wse_results, air_results, beliefs_results)

# ── BH correction — three separate families ─────────────────────────────────
term_family <- function(term_chr) {
  case_when(
    str_detect(term_chr, ":") ~ "interaction",
    str_detect(term_chr, "order") & !str_detect(term_chr, "topic") ~ "order_main",
    str_detect(term_chr, "topic") & !str_detect(term_chr, "order") ~ "topic_main",
    TRUE ~ "other"
  )
}

all_lm_corrected <- all_lm_results |>
  mutate(
    term_clean  = str_trim(term),
    term_family = term_family(term_clean)
  ) |>
  group_by(term_family) |>
  mutate(p_bh = p.adjust(p_value, method = "BH")) |>
  ungroup() |>
  arrange(survey, composite, term_clean)

write_csv(all_lm_corrected, file.path(csv_dir, "TwoWay_ANOVA_Order_Effects.csv"))

all_lm_corrected |>
  mutate(across(c(f_value, p_value, p_bh, partial_eta_sq), ~ round(.x, 4))) |>
  kable(caption = "Two-way ANOVA order effects. p_bh = BH-corrected within term family.")
```

```{r cell-means-tables}

make_cell_means <- function(data, dv, order_var, topic_var, label) {
  data |>
    filter(!is.na(.data[[dv]]), !is.na(.data[[order_var]]), !is.na(.data[[topic_var]])) |>
    group_by(.data[[order_var]], .data[[topic_var]]) |>
    summarise(
      n    = n(),
      mean = round(mean(.data[[dv]], na.rm = TRUE), 3),
      sd   = round(sd(.data[[dv]], na.rm = TRUE), 3),
      .groups = "drop"
    ) |>
    rename(Order = 1, Topic = 2) |>
    mutate(composite = dv, survey = label)
}

# IMI + WSE: topic = traditional_topic
trad_cell_means <- map_dfr(
  c(imi_composites, wse_composites),
  ~ make_cell_means(
      participant_with_composites,
      dv = .x,
      order_var = "order",
      topic_var = "traditional_topic",
      label = if (.x %in% imi_composites) "IMI" else "WritingEfficacy"
    )
)

# AIReflection + BeliefsAboutAI: topic = ai_topic
ai_session_cell_means <- map_dfr(
  c(air_composites, beliefs_dvs),
  ~ make_cell_means(
      participant_with_composites,
      dv = .x,
      order_var = "order",
      topic_var = "ai_topic",
      label = if (.x %in% air_composites) "AIReflection" else "BeliefsAboutAI"
    )
)

all_cell_means <- bind_rows(trad_cell_means, ai_session_cell_means)

write_csv(all_cell_means, file.path(csv_dir, "TwoWay_ANOVA_Cell_Means.csv"))

for (comp in unique(all_cell_means$composite)) {
  cat("\n\n###", comp, "\n")
  all_cell_means |>
    filter(composite == comp) |>
    select(survey, Order, Topic, n, mean, sd) |>
    kable(caption = paste("Cell means:", comp)) |>
    print()
}
```

## Section 6: Predeclared Tool-Comparable Pairs and 2×2 Mixed ANOVAs

```{r mixed-anovas}

extract_aov_table <- function(aov_fit) {
  # Flattens a nested summary(aov(..., Error(...))) object into one tidy table
  # with term-level statistics and the originating error stratum label.
  summary_obj <- summary(aov_fit)

  map2_dfr(summary_obj, names(summary_obj), function(stratum_obj, stratum_name) {
    if (!is.list(stratum_obj) || length(stratum_obj) == 0) {
      return(tibble())
    }

    tab <- stratum_obj[[1]]

    if (!is.data.frame(tab)) {
      return(tibble())
    }

    tab |>
      as.data.frame() |>
      tibble::rownames_to_column("term") |>
      as_tibble() |>
      mutate(stratum = stratum_name)
  })
}

extract_term <- function(aov_fit, term_name) {
  tbl <- extract_aov_table(aov_fit)

  if (nrow(tbl) == 0) {
    return(tibble(
      term = term_name,
      stratum = NA_character_,
      df = NA_real_,
      sum_sq = NA_real_,
      mean_sq = NA_real_,
      f_value = NA_real_,
      p_value = NA_real_
    ))
  }

  p_col <- names(tbl)[str_detect(names(tbl), "Pr\\(>F\\)")]
  f_col <- names(tbl)[str_detect(names(tbl), "F value")]

  if (length(p_col) > 1 || length(f_col) > 1) {
    stop(
      paste0(
        "ANOVA term extraction found ambiguous statistic columns. ",
        "Detected p columns: ", paste(p_col, collapse = ", "),
        " | F columns: ", paste(f_col, collapse = ", ")
      ),
      call. = FALSE
    )
  }

  row <- tbl |>
    filter(term == term_name) |>
    slice(1)

  if (nrow(row) == 0) {
    return(tibble(
      term = term_name,
      stratum = NA_character_,
      df = NA_real_,
      sum_sq = NA_real_,
      mean_sq = NA_real_,
      f_value = NA_real_,
      p_value = NA_real_
    ))
  }

  tibble(
    term = term_name,
    stratum = row$stratum,
    df = if ("Df" %in% names(row)) as.numeric(row$Df) else NA_real_,
    sum_sq = if ("Sum Sq" %in% names(row)) as.numeric(row$`Sum Sq`) else NA_real_,
    mean_sq = if ("Mean Sq" %in% names(row)) as.numeric(row$`Mean Sq`) else NA_real_,
    f_value = if (length(f_col) == 1) as.numeric(row[[f_col]]) else NA_real_,
    p_value = if (length(p_col) == 1) as.numeric(row[[p_col]]) else NA_real_
  )
}

# Predeclared tool-comparable pairs: each row declares one Traditional-side
# instrument and one AI-side instrument to compare at matched factor IDs (F1,
# F2, ...). This is intentionally explicit so the pairing logic can be edited
# without changing model code.
pairing_map <- tribble(
  ~traditional_instrument, ~ai_instrument,
  "IMI", "AIReflection",
  "WritingEfficacy", "BeliefsAboutAI"
)

composite_lookup <- composite_specs |>
  select(instrument, factor_id, composite) |>
  distinct()

pair_specs <- pairing_map |>
  left_join(
    composite_lookup |>
      rename(
        traditional_instrument = instrument,
        traditional_composite = composite
      ),
    by = "traditional_instrument"
  ) |>
  left_join(
    composite_lookup |>
      rename(
        ai_instrument = instrument,
        ai_composite = composite
      ),
    by = c("ai_instrument", "factor_id")
  ) |>
  filter(!is.na(traditional_composite), !is.na(ai_composite)) |>
  mutate(
    pair_id = paste0(traditional_instrument, "_", factor_id, "__vs__", ai_instrument, "_", factor_id),
    construct = factor_id
  ) |>
  distinct(pair_id, construct, traditional_instrument, ai_instrument, traditional_composite, ai_composite)

# Check if any declared pairs were dropped (e.g. BeliefsAboutAI has no locked
# EFA factors because KMO < 0.50 — its composite rows will be absent).
# This is expected for BeliefsAboutAI; a hard stop fires for anything else.
declared_instruments <- unique(c(pairing_map$traditional_instrument, pairing_map$ai_instrument))
available_locked_instruments <- unique(composite_lookup$instrument)
dropped_instruments   <- setdiff(declared_instruments, available_locked_instruments)
if (length(dropped_instruments) > 0) {
  expected_drops <- c("BeliefsAboutAI")
  unexpected_drops <- setdiff(dropped_instruments, expected_drops)

  cat(
    "NOTE: The following instruments were declared in pairing_map but have no ",
    "locked EFA composites and were dropped before pair_specs was built: ",
    paste(dropped_instruments, collapse = ", "), "\n"
  )

  if (length(unexpected_drops) > 0) {
    stop(
      paste0(
        "Unexpected instrument(s) dropped from pair_specs: ",
        paste(unexpected_drops, collapse = ", "),
        ". Check that locked_k is set for these instruments in 03_efa_analysis.qmd."
      ),
      call. = FALSE
    )
  }

  cat("BeliefsAboutAI drop is expected (KMO < 0.50, not factorable).\n")
}

write_csv(pair_specs, file.path(csv_dir, "Tool_Comparable_Pair_Specs.csv"))

tool_factor_levels <- c("Traditional", "AI")
traditional_score_col <- "traditional_score"
ai_score_col <- "ai_score"

mixed_anova_rows <- if (nrow(pair_specs) == 0) {
  tibble(
    pair_id = character(),
    construct = character(),
    traditional_composite = character(),
    ai_composite = character(),
    n_participants = integer(),
    model = character(),
    tool_order_f = numeric(),
    tool_order_p = numeric(),
    note = character()
  )
} else {
  map_dfr(seq_len(nrow(pair_specs)), function(i) {
    spec <- pair_specs[i, ]

   long_dat <- participant_with_composites |>
  transmute(
    participant_id,
    order,
    first_topic,           # ADD THIS
    traditional_topic,
    ai_topic,
    traditional_score = .data[[spec$traditional_composite[[1]]]],
    ai_score = .data[[spec$ai_composite[[1]]]]
  ) |>
      pivot_longer(
        cols = all_of(c(traditional_score_col, ai_score_col)),
        names_to = "tool_row",
        values_to = "score"
      ) |>
      mutate(
        Tool = factor(if_else(tool_row == traditional_score_col, tool_factor_levels[[1]], tool_factor_levels[[2]]),
                      levels = tool_factor_levels),
        # Topic intentionally omitted here — first_topic (between-subjects)
        # is carried from participant_with_composites and used in the ANOVA directly.
        Order = factor(order, levels = order_levels)
      ) |>
      filter(!is.na(score), !is.na(Order), !is.na(Tool))

    if (n_distinct(long_dat$participant_id) < 4) {
      return(bind_rows(
        tibble(
          pair_id = spec$pair_id,
          construct = spec$construct,
          traditional_composite = spec$traditional_composite,
          ai_composite = spec$ai_composite,
          n_participants = n_distinct(long_dat$participant_id),
          model = "primary",
          tool_order_f = NA_real_,
          tool_order_p = NA_real_,
          note = "insufficient overlap for mixed ANOVA"
        ),
        tibble(
          pair_id = spec$pair_id,
          construct = spec$construct,
          traditional_composite = spec$traditional_composite,
          ai_composite = spec$ai_composite,
          n_participants = n_distinct(long_dat$participant_id),
          model = "topic_controlled",
          tool_order_f = NA_real_,
          tool_order_p = NA_real_,
          note = "insufficient overlap for mixed ANOVA"
        )
      ))
    }

    fit_primary <- suppressWarnings(
      aov(score ~ Tool * Order + Error(participant_id / Tool), data = long_dat)
    )

    fit_topic <- suppressWarnings(
      # first_topic is between-subjects (constant per participant) so it goes
      # outside Error(). This controls for article-type assignment without
      # conflating topic with the within-subjects Tool factor.
      # Sphericity note: the within-subjects Tool factor has only two levels,
      # so the sphericity assumption is satisfied by definition.
      aov(score ~ Tool * Order + first_topic + Error(participant_id / Tool), data = long_dat)
    )

    primary_interaction <- extract_term(fit_primary, "Tool:Order")
    topic_interaction <- extract_term(fit_topic, "Tool:Order")

    bind_rows(
      tibble(
        pair_id = spec$pair_id,
        construct = spec$construct,
        traditional_composite = spec$traditional_composite,
        ai_composite = spec$ai_composite,
        n_participants = n_distinct(long_dat$participant_id),
        model = "primary",
        tool_order_f = primary_interaction$f_value,
        tool_order_p = primary_interaction$p_value,
        note = NA_character_
      ),
      tibble(
        pair_id = spec$pair_id,
        construct = spec$construct,
        traditional_composite = spec$traditional_composite,
        ai_composite = spec$ai_composite,
        n_participants = n_distinct(long_dat$participant_id),
        model = "topic_controlled",
        tool_order_f = topic_interaction$f_value,
        tool_order_p = topic_interaction$p_value,
        note = NA_character_
      )
    )
  })
}

mixed_anova_results <- mixed_anova_rows |>
  group_by(model) |>
  mutate(
    p_bh = p.adjust(tool_order_p, method = adjustment_methods[[1]]),
    p_bonferroni = p.adjust(tool_order_p, method = adjustment_methods[[2]])
  ) |>
  ungroup() |>
  mutate(
    sphericity_note = "Within-subject Tool factor has 2 levels; sphericity is met by definition."
  ) |>
  arrange(model, p_bh, tool_order_p)

interaction_summary <- mixed_anova_results |>
  select(
    pair_id, construct, model, n_participants,
    traditional_composite, ai_composite,
    tool_order_f, tool_order_p, p_bh, p_bonferroni
  ) |>
  mutate(model = factor(model, levels = c("primary", "topic_controlled"))) |>
  pivot_wider(
    names_from = model,
    values_from = c(tool_order_f, tool_order_p, p_bh, p_bonferroni),
    names_expand = TRUE
  ) |>
  mutate(
    persists_after_topic_control = case_when(
      is.na(p_bh_primary) | is.na(p_bh_topic_controlled) ~ NA_character_,
      p_bh_primary < 0.05 & p_bh_topic_controlled < 0.05 ~ "Yes (BH-adjusted)",
      p_bh_primary < 0.05 & p_bh_topic_controlled >= 0.05 ~ "No (drops after topic control)",
      TRUE ~ "Not significant in primary model (BH-adjusted)"
    )
  )

write_csv(mixed_anova_results, file.path(csv_dir, "Mixed_ANOVA_Tool_Order_Results.csv"))
write_csv(interaction_summary, file.path(csv_dir, "Tool_Order_Interaction_Summary.csv"))
```

## Section 6b: Lab / Recording-Method Sensitivity Analysis

This exploratory section asks whether participants in SS2 versus
Stevenson differed on the locked EFA-derived composite scores. Lab
assignment comes from the sanitized scheduling-tracking CSVs. Because each file
nominally corresponds to one lab, file membership is the default rule;
explicit cross-lab note conflicts or cross-file duplicate schedule keys are
treated as ambiguous and excluded from the lab comparison.

Poor-quality paired data are already screened out upstream: this section
starts from `participant_with_composites`, which inherits the strict
`clean_pids` gate from `01_audit_cleaning.qmd`.

```{r lab-sensitivity-setup}
missing_schedule_files <- schedule_lab_files |>
  filter(!file.exists(path))

if (nrow(missing_schedule_files) > 0) {
  stop(
    paste0(
      "Missing lab scheduling file(s): ",
      paste(missing_schedule_files$path, collapse = ", ")
    ),
    call. = FALSE
  )
}

lab_factor_labels <- tribble(
  ~composite,            ~instrument,         ~factor_name,                ~plot_label,
  "IMI_F1",              "IMI",               "Interest & Enjoyment",      "IMI\nInterest & Enjoyment",
  "IMI_F2",              "IMI",               "Effort & Importance",       "IMI\nEffort & Importance",
  "IMI_F3",              "IMI",               "Perceived Competence",      "IMI\nPerceived Competence",
  "WritingEfficacy_F1",  "WritingEfficacy",   "Writing Competence",        "WritingEfficacy\nWriting Competence",
  "WritingEfficacy_F2",  "WritingEfficacy",   "Self-Regulation",           "WritingEfficacy\nSelf-Regulation",
  "WritingEfficacy_F3",  "WritingEfficacy",   "Resource & Planning",       "WritingEfficacy\nResource & Planning",
  "AIReflection_F1",     "AIReflection",      "Ownership & Usefulness",    "AIReflection\nOwnership & Usefulness",
  "AIReflection_F2",     "AIReflection",      "Enjoyment & Satisfaction",  "AIReflection\nEnjoyment & Satisfaction"
)

normalize_schedule_text <- function(x) {
  x |>
    as.character() |>
    stringr::str_replace_all("\\u00A0", " ") |>
    stringr::str_squish() |>
    na_if("")
}

first_nonmissing_chr <- function(x) {
  x <- x[!is.na(x) & x != ""]
  if (length(x) == 0) NA_character_ else x[[1]]
}

schedule_tracking <- purrr::pmap_dfr(
  schedule_lab_files,
  function(lab_source, path) {
    read_csv(path, show_col_types = FALSE) |>
      mutate(lab_source = lab_source, source_path = path)
  }
)

required_schedule_cols <- c(
  "x", "Participant", "Session 1 Status", "Session 2 Status", "Notes",
  "lab_source", "source_path"
)
assert_required_columns(
  schedule_tracking,
  required_schedule_cols,
  "schedule_tracking"
)

schedule_tracking_clean <- schedule_tracking |>
  transmute(
    lab_source,
    source_path,
    participant_id = normalize_schedule_text(x),
    participant_id_lower = str_to_lower(participant_id),
    participant_schedule_key = str_to_lower(normalize_schedule_text(Participant)),
    session_1_status = normalize_schedule_text(`Session 1 Status`),
    session_2_status = normalize_schedule_text(`Session 2 Status`),
    notes = normalize_schedule_text(Notes)
  ) |>
  mutate(
    cross_lab_note = case_when(
      lab_source == "SS2" ~ str_detect(
        coalesce(notes, ""),
        regex(
          "session\\s*[12].*stevenson|taken in stevenson|scheduled\\s*s?[12]?.*stevenson|completed\\s*s[12].*stevenson",
          ignore_case = TRUE
        )
      ),
      lab_source == "Stevenson" ~ str_detect(
        coalesce(notes, ""),
        regex("\\bss2\\b", ignore_case = TRUE)
      ),
      TRUE ~ FALSE
    )
  )

schedule_key_lab_counts <- schedule_tracking_clean |>
  filter(!is.na(participant_schedule_key)) |>
  distinct(participant_schedule_key, lab_source) |>
  count(participant_schedule_key, name = "schedule_key_lab_count")

schedule_id_summary <- schedule_tracking_clean |>
  filter(!is.na(participant_id_lower)) |>
  group_by(participant_id_lower) |>
  summarise(
    participant_id_schedule = first_nonmissing_chr(participant_id),
    participant_schedule_key = first_nonmissing_chr(participant_schedule_key),
    n_schedule_labs = n_distinct(lab_source),
    schedule_labs = str_c(sort(unique(lab_source)), collapse = "; "),
    assigned_lab = if_else(
      n_schedule_labs == 1L,
      first(lab_source),
      NA_character_
    ),
    session_1_status = str_c(
      sort(unique(na.omit(session_1_status))),
      collapse = "; "
    ),
    session_2_status = str_c(
      sort(unique(na.omit(session_2_status))),
      collapse = "; "
    ),
    any_cross_lab_note = any(cross_lab_note, na.rm = TRUE),
    note_excerpt = str_trunc(
      str_squish(str_c(unique(na.omit(notes)), collapse = " | ")),
      width = 260
    ),
    .groups = "drop"
  ) |>
  left_join(schedule_key_lab_counts, by = "participant_schedule_key") |>
  mutate(
    schedule_key_lab_count = replace_na(schedule_key_lab_count, 0L),
    assignment_status = case_when(
      n_schedule_labs > 1L ~ "ambiguous_id_in_both_lab_files",
      any_cross_lab_note   ~ "ambiguous_cross_lab_note",
      schedule_key_lab_count > 1L  ~ "ambiguous_key_in_both_lab_files",
      n_schedule_labs == 1L ~ "assigned",
      TRUE                 ~ "no_schedule_lab_match"
    ),
    exclusion_reason = case_when(
      assignment_status == "ambiguous_id_in_both_lab_files" ~
        "participant ID appears in both lab scheduling files",
      assignment_status == "ambiguous_cross_lab_note" ~
        "notes explicitly place at least one session in the other lab",
      assignment_status == "ambiguous_key_in_both_lab_files" ~
        "anonymized schedule key appears across both lab scheduling files",
      assignment_status == "no_schedule_lab_match" ~
        "no scheduling-file lab match found",
      TRUE ~ NA_character_
    )
  )

lab_assignment <- participant_with_composites |>
  select(participant_id) |>
  distinct() |>
  mutate(participant_id_lower = str_to_lower(as.character(participant_id))) |>
  left_join(schedule_id_summary, by = "participant_id_lower") |>
  mutate(
    assignment_status = coalesce(assignment_status, "no_schedule_lab_match"),
    exclusion_reason = case_when(
      assignment_status == "no_schedule_lab_match" & is.na(exclusion_reason) ~
        "no scheduling-file lab match found",
      TRUE ~ exclusion_reason
    ),
    lab = if_else(assignment_status == "assigned", assigned_lab, NA_character_)
  ) |>
  select(
    participant_id,
    lab,
    assignment_status,
    exclusion_reason,
    participant_schedule_key,
    schedule_labs,
    session_1_status,
    session_2_status,
    any_cross_lab_note,
    note_excerpt
  )

write_csv(
  lab_assignment,
  file.path(csv_dir, "Lab_Assignment_Analysis_Ready.csv")
)

lab_assignment_summary <- lab_assignment |>
  count(assignment_status, lab, name = "n") |>
  arrange(assignment_status, lab)

kable(
  lab_assignment_summary,
  caption = "Lab assignment summary for analysis-ready participants. Only rows with assignment_status = assigned enter the lab sensitivity analysis."
)

participant_with_lab <- participant_with_composites |>
  inner_join(
    lab_assignment |>
      filter(assignment_status == "assigned") |>
      select(participant_id, lab),
    by = "participant_id"
  ) |>
  mutate(lab = factor(lab, levels = c("SS2", "Stevenson")))

lab_composite_long <- participant_with_lab |>
  select(participant_id, lab, all_of(composite_cols)) |>
  pivot_longer(
    cols = all_of(composite_cols),
    names_to = "composite",
    values_to = "score"
  ) |>
  left_join(lab_factor_labels, by = "composite") |>
  mutate(
    plot_label = factor(plot_label, levels = lab_factor_labels$plot_label)
  )

lab_descriptives <- lab_composite_long |>
  group_by(composite, instrument, factor_name, lab) |>
  summarise(
    n = sum(!is.na(score)),
    mean = mean(score, na.rm = TRUE),
    sd = sd(score, na.rm = TRUE),
    median = median(score, na.rm = TRUE),
    iqr = IQR(score, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(instrument, composite, lab)

write_csv(
  lab_descriptives,
  file.path(csv_dir, "Lab_Descriptives_By_Composite.csv")
)
```

```{r lab-mann-whitney}
lab_mann_whitney_results <- map_dfr(composite_cols, function(comp) {
  dat <- participant_with_lab |>
    select(lab, all_of(comp)) |>
    rename(score = all_of(comp)) |>
    filter(!is.na(score))

  ss2_vec <- dat |>
    filter(lab == "SS2") |>
    pull(score)

  stevenson_vec <- dat |>
    filter(lab == "Stevenson") |>
    pull(score)

  n_ss2 <- length(ss2_vec)
  n_stevenson <- length(stevenson_vec)

  wt <- suppressWarnings(
    wilcox.test(
      ss2_vec,
      stevenson_vec,
      exact = FALSE,
      conf.int = TRUE
    )
  )

  w_stat <- unname(wt$statistic)
  u_stat <- w_stat
  rb <- rank_biserial_from_u(w_stat, n_ss2, n_stevenson)

  tibble(
    composite = comp,
    n_ss2 = n_ss2,
    n_stevenson = n_stevenson,
    median_ss2 = median(ss2_vec, na.rm = TRUE),
    median_stevenson = median(stevenson_vec, na.rm = TRUE),
    mean_ss2 = mean(ss2_vec, na.rm = TRUE),
    mean_stevenson = mean(stevenson_vec, na.rm = TRUE),
    w_stat = w_stat,
    u_stat = u_stat,
    p_value = wt$p.value,
    estimate_hl = unname(wt$estimate),
    conf_low = wt$conf.int[[1]],
    conf_high = wt$conf.int[[2]],
    effect_size = rb
  )
})

lab_mann_whitney_results <- lab_mann_whitney_results |>
  mutate(
    p_bh = p.adjust(p_value, method = "BH"),
    p_bonferroni = p.adjust(p_value, method = "bonferroni")
  ) |>
  left_join(lab_factor_labels, by = "composite") |>
  relocate(instrument, factor_name, plot_label, .after = composite)

write_csv(
  lab_mann_whitney_results,
  file.path(csv_dir, "Mann_Whitney_Lab_Comparisons.csv")
)

lab_mann_whitney_results |>
  mutate(
    across(
      c(
        mean_ss2, mean_stevenson, median_ss2, median_stevenson,
        p_value, p_bh, p_bonferroni, estimate_hl, conf_low,
        conf_high, effect_size
      ),
      ~ round(.x, 3)
    )
  ) |>
  select(
    instrument, factor_name, n_ss2, n_stevenson,
    mean_ss2, mean_stevenson,
    median_ss2, median_stevenson,
    p_value, p_bh, effect_size
  ) |>
  kable(
    caption = "SS2 versus Stevenson composite comparisons. Positive rank-biserial effect sizes indicate higher scores in SS2."
  )
```

```{r lab-plots, fig.width=14, fig.height=10}
lab_palette <- c(
  "SS2" = "#2E6F95",
  "Stevenson" = "#C97A3D"
)

instrument_palette <- c(
  "IMI" = "#2A9D8F",
  "WritingEfficacy" = "#E07A5F",
  "AIReflection" = "#6D597A"
)

lab_violin_plot <- lab_composite_long |>
  ggplot(aes(x = lab, y = score, fill = lab)) +
  geom_violin(alpha = 0.35, width = 0.95, color = NA, trim = FALSE, na.rm = TRUE) +
  geom_boxplot(width = 0.18, outlier.alpha = 0.55, na.rm = TRUE) +
  facet_wrap(~ plot_label, scales = "free_y", ncol = 3) +
  scale_fill_manual(values = lab_palette) +
  labs(
    title = "EFA composite scores by lab",
    subtitle = "Exploratory SS2 vs Stevenson comparison on clean paired participants",
    x = "Lab",
    y = "Composite score",
    fill = NULL,
    caption = "Lab assignment comes from sanitized scheduling tracking CSVs. Explicit cross-lab note conflicts and cross-file duplicate schedule keys are excluded."
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "none",
    panel.grid.minor = element_blank(),
    strip.text = element_text(face = "bold", size = 10),
    axis.text.x = element_text(size = 10)
  )

ggsave(
  filename = file.path(plot_dir, "lab_composite_violin_box.png"),
  plot = lab_violin_plot,
  width = 14,
  height = 10,
  units = "in",
  dpi = 300,
  bg = "white"
)

ggsave(
  filename = file.path(plot_dir, "lab_composite_violin_box.pdf"),
  plot = lab_violin_plot,
  width = 14,
  height = 10,
  units = "in",
  bg = "white"
)

lab_effect_plot_data <- lab_mann_whitney_results |>
  mutate(
    plot_label = factor(plot_label, levels = rev(lab_factor_labels$plot_label)),
    p_bh_label = paste0("BH p = ", scales::number(p_bh, accuracy = 0.001))
  )

lab_effect_plot <- lab_effect_plot_data |>
  ggplot(aes(x = effect_size, y = plot_label, color = instrument)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_segment(
    aes(x = 0, xend = effect_size, yend = plot_label),
    linewidth = 1.1,
    alpha = 0.45
  ) +
  geom_point(size = 3.4) +
  geom_text(
    aes(x = 0.92, y = plot_label, label = p_bh_label),
    inherit.aes = FALSE,
    color = "grey35",
    hjust = 1,
    size = 3.2
  ) +
  scale_color_manual(values = instrument_palette) +
  scale_x_continuous(
    limits = c(-1, 1),
    breaks = seq(-1, 1, by = 0.25),
    labels = scales::number_format(accuracy = 0.01)
  ) +
  labs(
    title = "Lab sensitivity effect sizes across EFA composites",
    subtitle = "Positive values indicate higher scores in SS2; points show rank-biserial effect sizes",
    x = "Rank-biserial effect size (SS2 higher \u2192)",
    y = NULL,
    color = "Instrument",
    caption = "Mann-Whitney comparisons with BH correction across the 8 composite tests."
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.minor = element_blank(),
    legend.position = "bottom",
    axis.text.y = element_text(size = 10)
  )

ggsave(
  filename = file.path(plot_dir, "lab_effect_size_summary.png"),
  plot = lab_effect_plot,
  width = 13,
  height = 7,
  units = "in",
  dpi = 300,
  bg = "white"
)

ggsave(
  filename = file.path(plot_dir, "lab_effect_size_summary.pdf"),
  plot = lab_effect_plot,
  width = 13,
  height = 7,
  units = "in",
  bg = "white"
)
```

## Section 7: Export Ready Tables

```{r final-exports}

analysis_ready <- participant_with_composites |>
  select(
    participant_id,
    order,
    condition_1,
    condition_2,
    traditional_topic,
    ai_topic,
    first_topic,
    ends_with("_F1"),
    ends_with("_F2"),
    ends_with("_F3")
  )


write_csv(analysis_ready, file.path(csv_dir, "Order_Effects_Analysis_Ready.csv"))

export_manifest <- tibble(
  output_type = c(
    "analysis_ready",
    "composite_membership",
    "composite_specs",
    "order_descriptives",
    "mann_whitney",
    "item_level_mann_whitney",
    "pair_specs",
    "mixed_anova",
    "interaction_summary",
    "lab_assignment",
    "lab_descriptives",
    "lab_mann_whitney"
  ),
  file = c(
    "Order_Effects_Analysis_Ready.csv",
    "Composite_Item_Membership.csv",
    "Composite_Specs.csv",
    "Order_Descriptives_By_Composite.csv",
    "Mann_Whitney_Order_Comparisons.csv",
    "Item_Level_Order_Comparisons.csv",
    "Tool_Comparable_Pair_Specs.csv",
    "Mixed_ANOVA_Tool_Order_Results.csv",
    "Tool_Order_Interaction_Summary.csv",
    "Lab_Assignment_Analysis_Ready.csv",
    "Lab_Descriptives_By_Composite.csv",
    "Mann_Whitney_Lab_Comparisons.csv"
  )
)

write_csv(export_manifest, file.path(csv_dir, "Order_Effects_Export_Manifest.csv"))

kable(export_manifest)
```

Then we need to come up with a quick way to understand what we like. All of this should be one or two sentences describing what we did for the script and then one or two graphs. Ideally just one graph for these early scripts.

For script 6 we should say, "This builds the composite scores from locked EFA item map, compares traditional first versus AI first participants, and tests tool times ordered interactions with a secondary topic controlled model." We should show some table or graph that shows the results of that.## Section 8: Order-Stratified Correlation Analysis

This section asks whether key cross-instrument factor correlations and
Beliefs item correlations differ depending on which session participants
completed first. Each correlation is computed three ways: full sample,
Traditional-First only, AI-First only. Fisher's z-test formally tests
whether the two subgroup correlations differ significantly.

**Interpretation note:** Splitting N = 82 into \~45 and \~37 reduces
power substantially. A subgroup correlation going null does not
necessarily mean the effect changed — it may simply reflect reduced
sample size. Use Fisher's z p-value, not subgroup nullity alone, to
judge differences.

```{r order-strat-setup}
library(psych)  # for paired.r()

# --- Load inputs ---
# Factor scores: use the file produced by Script 05.
factor_scores_all <- read_csv(
  factor_scores_all_file,
  show_col_types = FALSE
) |>
  mutate(participant_id = as.character(participant_id))

# Beliefs item wide: produced by Script 04.
beliefs_wide <- read_csv(
  beliefs_wide_file,
  show_col_types = FALSE
) |>
  mutate(participant_id = as.character(participant_id))

# Order labels: already built in Section 2 of this script as participant_analysis
# Pull just what we need
order_labels <- participant_analysis |>
  select(participant_id, order) |>
  mutate(participant_id = as.character(participant_id))

# --- Join everything ---
strat_base <- order_labels |>
  left_join(factor_scores_all, by = "participant_id") |>
  left_join(beliefs_wide,      by = "participant_id")

factor_cols_strat <- names(factor_scores_all) |> setdiff("participant_id")
belief_cols_strat <- names(beliefs_wide)       |> setdiff("participant_id")
```

```{r order-strat-helpers}

# Compute Spearman rho for one group subset
spearman_one_group <- function(data, col_x, col_y, group_label) {
  d <- data |>
    select(all_of(c(col_x, col_y))) |>
    filter(!is.na(.data[[col_x]]), !is.na(.data[[col_y]]))

  if (nrow(d) < 10 || n_distinct(d[[col_x]]) < 2 || n_distinct(d[[col_y]]) < 2) {
    return(tibble(
      group = group_label, n = nrow(d),
      rho = NA_real_, p = NA_real_, note = "insufficient data"
    ))
  }

  test <- suppressWarnings(
    cor.test(d[[col_x]], d[[col_y]], method = "spearman", exact = FALSE)
  )

  tibble(
    group = group_label,
    n     = nrow(d),
    rho   = unname(test$estimate),
    p     = test$p.value,
    note  = NA_character_
  )
}

# Compute full + stratified correlations + Fisher z-test for one pair
correlate_stratified <- function(data, col_x, col_y) {
  full  <- spearman_one_group(data,                              col_x, col_y, "Full")
  trad  <- spearman_one_group(filter(data, order == "Traditional_First"), col_x, col_y, "Traditional_First")
  ai    <- spearman_one_group(filter(data, order == "AI_First"),          col_x, col_y, "AI_First")

  # Fisher z-test comparing the two subgroup correlations
  fisher_p <- tryCatch({
    if (is.na(trad$rho) || is.na(ai$rho)) {
      NA_real_
    } else {
      psych::r.test(
      n   = trad$n,
      r12 = trad$rho,
      n2  = ai$n,
      r34 = ai$rho
    )$p 
    }
  }, error = function(e) NA_real_)

  bind_rows(full, trad, ai) |>
    mutate(
      col_x    = col_x,
      col_y    = col_y,
      fisher_p = fisher_p
    )
}
```

```{r factor-factor-stratified}
# --- Factor × Factor stratified correlations ---
# All unique factor pairs (same pairs as Section 6 factor map)

factor_pairs_strat <- t(combn(factor_cols_strat, 2)) |>
  as_tibble(.name_repair = "minimal") |>
  setNames(c("col_x", "col_y"))

factor_strat_results <- pmap_dfr(
  factor_pairs_strat,
  function(col_x, col_y) correlate_stratified(strat_base, col_x, col_y)
)

# Load factor name map for readable labels
factor_name_map_loaded <- read_csv(
  factor_name_map_file,
  show_col_types = FALSE
)

assert_lookup_covers_factor_columns(
  factor_lookup = factor_name_map_loaded,
  factor_cols = factor_cols_strat,
  context_label = "Script 06 factor-name-map handoff"
)

factor_label_lookup_strat <- factor_name_map_loaded |>
  transmute(factor = factor, display_label)

factor_strat_wide <- factor_strat_results |>
  pivot_wider(
    names_from  = group,
    values_from = c(n, rho, p),
    names_glue  = "{group}_{.value}"
  ) |>
  left_join(factor_label_lookup_strat |> rename(col_x = factor, label_x = display_label), by = "col_x") |>
  left_join(factor_label_lookup_strat |> rename(col_y = factor, label_y = display_label), by = "col_y") |>
  mutate(
    fisher_sig = case_when(
      is.na(fisher_p)  ~ "NA",
      fisher_p < 0.001 ~ "p < .001",
      fisher_p < 0.01  ~ "p < .01",
      fisher_p < 0.05  ~ "p < .05",
      TRUE             ~ paste0("p = ", round(fisher_p, 3))
    ),
    rho_diff = round(Traditional_First_rho - AI_First_rho, 3)
  ) |>
  arrange(fisher_p, desc(abs(rho_diff)))

write_csv(
  factor_strat_wide,
  file.path(csv_dir, "Factor_Factor_Order_Stratified_Correlations.csv")
)

# Display top pairs sorted by largest rho difference between order groups
factor_strat_wide |>
  select(
    label_x, label_y,
    Full_n, Full_rho, Full_p,
    Traditional_First_n, Traditional_First_rho, Traditional_First_p,
    AI_First_n, AI_First_rho, AI_First_p,
    fisher_p, fisher_sig, rho_diff
  ) |>
  mutate(across(where(is.numeric), ~ round(.x, 3))) |>
  kable(caption = "Factor × Factor correlations stratified by order group. fisher_p tests whether Traditional-First rho differs significantly from AI-First rho.")
```

```{r beliefs-factor-stratified}
# --- Beliefs Item × Factor stratified correlations ---
# Focus on items that survived BH correction in Script 04 full-sample analysis.
# Defined here explicitly so this section is self-contained.
# Update this vector if your significant item list changes.

sig_belief_items <- paste0("Beliefs_", c(1, 4, 8, 9, 10, 11, 12, 14, 15, 17, 19, 21, 22))
sig_belief_items <- intersect(sig_belief_items, belief_cols_strat)  # guard against missing cols

# Pairs to test: sig belief items × all factor cols
belief_factor_pairs <- expand_grid(
  col_x = sig_belief_items,
  col_y = factor_cols_strat
)

belief_strat_results <- pmap_dfr(
  belief_factor_pairs,
  function(col_x, col_y) correlate_stratified(strat_base, col_x, col_y)
)

# Belief item text lookup
belief_item_text <- beliefs_wide |>
  select(starts_with("Beliefs_")) |>
  names() |>
  tibble(belief_col = _) |>
  mutate(item_num = as.integer(str_extract(belief_col, "\\d+"))) |>
  arrange(item_num)

# Note: item text comes from the long file — load it here for labeling
beliefs_long_text <- read_csv(
  beliefs_long_file,
  show_col_types = FALSE
) |>
  distinct(item_num = as.integer(item_num), item_text) |>
  mutate(belief_col = paste0("Beliefs_", item_num))

belief_strat_wide <- belief_strat_results |>
  pivot_wider(
    names_from  = group,
    values_from = c(n, rho, p),
    names_glue  = "{group}_{.value}"
  ) |>
  left_join(beliefs_long_text |> select(belief_col, item_text) |> rename(col_x = belief_col), by = "col_x") |>
  left_join(factor_label_lookup_strat |> rename(col_y = factor, label_y = display_label), by = "col_y") |>
  mutate(
    fisher_sig = case_when(
      is.na(fisher_p)  ~ "NA",
      fisher_p < 0.001 ~ "p < .001",
      fisher_p < 0.01  ~ "p < .01",
      fisher_p < 0.05  ~ "p < .05",
      TRUE             ~ paste0("p = ", round(fisher_p, 3))
    ),
    rho_diff = round(Traditional_First_rho - AI_First_rho, 3)
  ) |>
  arrange(fisher_p, desc(abs(rho_diff)))

belief_factor_levels <- factor_label_lookup_strat$display_label[
  match(factor_cols_strat, factor_label_lookup_strat$factor)
]

if (any(is.na(belief_factor_levels))) {
  stop("Belief-item order plots: missing factor display labels for one or more factor columns.", call. = FALSE)
}

belief_plot_long <- belief_strat_results |>
  left_join(
    beliefs_long_text |>
      select(belief_col, item_text) |>
      rename(col_x = belief_col),
    by = "col_x"
  ) |>
  left_join(
    factor_label_lookup_strat |>
      rename(col_y = factor, label_y = display_label),
    by = "col_y"
  ) |>
  mutate(
    label_y = factor(label_y, levels = belief_factor_levels),
    group = factor(group, levels = c("Full", "Traditional_First", "AI_First"))
  )

belief_plot_annotations <- belief_strat_wide |>
  select(col_x, col_y, label_y, fisher_sig) |>
  mutate(label_y = factor(label_y, levels = belief_factor_levels))

for (belief_col in sig_belief_items) {
  plot_df <- belief_plot_long |>
    filter(col_x == belief_col)

  ann_df <- belief_plot_annotations |>
    filter(col_x == belief_col)

  if (nrow(plot_df) == 0 || all(is.na(plot_df$rho))) {
    next
  }

  item_title <- plot_df |>
    distinct(item_text) |>
    pull(item_text) |>
    first()

  belief_order_plot <- ggplot(
    plot_df,
    aes(x = label_y, y = rho, group = group, color = group, linetype = group, shape = group)
  ) +
    geom_hline(yintercept = 0, color = "#c7c7c7", linewidth = 0.8) +
    geom_hline(yintercept = c(-0.30, 0.30), color = "#bdbdbd", linewidth = 0.7, linetype = "dotted") +
    geom_line(linewidth = 1.2, alpha = 0.95) +
    geom_point(size = 3.7, alpha = 0.95) +
    geom_text(
      data = ann_df,
      aes(x = label_y, y = -1.07, label = fisher_sig),
      inherit.aes = FALSE,
      color = "#5a5a5a",
      size = 4.0
    ) +
    scale_color_manual(
      values = c(
        "Full" = "#7a7a7a",
        "Traditional_First" = "#c93e2c",
        "AI_First" = "#3a88bf"
      ),
      labels = c(
        "Full" = "Full sample",
        "Traditional_First" = "Traditional-First",
        "AI_First" = "AI-First"
      )
    ) +
    scale_linetype_manual(
      values = c(
        "Full" = "22",
        "Traditional_First" = "solid",
        "AI_First" = "solid"
      ),
      labels = c(
        "Full" = "Full sample",
        "Traditional_First" = "Traditional-First",
        "AI_First" = "AI-First"
      )
    ) +
    scale_shape_manual(
      values = c(
        "Full" = 16,
        "Traditional_First" = 17,
        "AI_First" = 15
      ),
      labels = c(
        "Full" = "Full sample",
        "Traditional_First" = "Traditional-First",
        "AI_First" = "AI-First"
      )
    ) +
    scale_y_continuous(
      limits = c(-1.1, 1.0),
      breaks = seq(-1, 1, by = 0.25),
      labels = scales::number_format(accuracy = 0.01)
    ) +
    labs(
      title = item_title,
      subtitle = "Spearman rho with each factor — Full sample (gray dashed), Traditional-First (red), AI-First (blue)",
      x = NULL,
      y = "Spearman rho",
      caption = "Fisher's z p-value shown below each factor label. Dotted lines at rho = +/-0.30."
    ) +
    theme_minimal(base_size = 14) +
    theme(
      legend.position = "none",
      panel.grid.minor = element_blank(),
      axis.text.x = element_text(angle = 35, hjust = 1, size = 10),
      axis.text.y = element_text(size = 11),
      plot.title = element_text(face = "bold", size = 17),
      plot.subtitle = element_text(size = 11, color = "#666666"),
      plot.caption = element_text(size = 10, color = "#7a7a7a"),
      plot.margin = margin(15, 20, 20, 15)
    )

  ggsave(
    filename = file.path(plot_dir, paste0("belief_", belief_col, "_order_corr.png")),
    plot = belief_order_plot,
    width = 16,
    height = 10,
    units = "in",
    dpi = 160,
    bg = "white"
  )
}

write_csv(
  belief_strat_wide,
  file.path(csv_dir, "Beliefs_Factor_Order_Stratified_Correlations.csv")
)

# Display: focus on Item 1 x WritingEfficacy F1 first (your key finding),
# then top hits by rho difference
belief_strat_wide |>
  select(
    item_text, label_y,
    Full_n, Full_rho, Full_p,
    Traditional_First_n, Traditional_First_rho, Traditional_First_p,
    AI_First_n, AI_First_rho, AI_First_p,
    fisher_p, fisher_sig, rho_diff
  ) |>
  mutate(
    item_text = str_trunc(item_text, 60),
    across(where(is.numeric), ~ round(.x, 3))
  ) |>
  kable(caption = "Beliefs item × Factor correlations stratified by order group. fisher_p tests subgroup rho difference.")
```

## Section 9: Exploratory Beliefs 6-22 Order-Stratified Addendum

This addendum treats the secondary BeliefsAboutAI items 6-22 factors from
Script 16 as exploratory factor scores. These are not the locked
production Beliefs factors; they come from a narrower post hoc model and
are used here only for hypothesis-generating order checks. The existing
Section 8 outputs remain unchanged.

```{r exploratory-beliefs-order-levels}
exploratory_beliefs_factor_file <- file.path(
  "16_exploratory_beliefs",
  "csv",
  "Beliefs_Exploratory_Factor_Scores.csv"
)
exploratory_beliefs_lookup_file <- file.path(
  "16_exploratory_beliefs",
  "csv",
  "Beliefs_Exploratory_Factor_Lookup.csv"
)

run_exploratory_beliefs_order <- file.exists(exploratory_beliefs_factor_file) &&
  file.exists(exploratory_beliefs_lookup_file)

if (!run_exploratory_beliefs_order) {
  cat(
    "Skipping exploratory Beliefs 6-22 order addendum because script 16 outputs are not present yet. ",
    "Render 16_exploratory_beliefs.qmd and rerender this script to refresh that optional addendum.\n",
    sep = ""
  )
}

if (run_exploratory_beliefs_order) {
new_beliefs_factor_cols <- c(
  "Beliefs_UtilityComfort",
  "Beliefs_FutureAIIntent",
  "Beliefs_ConcernHarms"
)

exploratory_beliefs_scores <- read_csv(
  exploratory_beliefs_factor_file,
  show_col_types = FALSE
) |>
  mutate(participant_id = as.character(participant_id)) |>
  select(participant_id, all_of(new_beliefs_factor_cols))

exploratory_beliefs_lookup <- read_csv(
  exploratory_beliefs_lookup_file,
  show_col_types = FALSE
) |>
  filter(factor %in% new_beliefs_factor_cols) |>
  mutate(
    factor = as.character(factor),
    display_label = paste0(display_label, " (exploratory 6-22)")
  )

assert_lookup_covers_factor_columns(
  factor_lookup = exploratory_beliefs_lookup,
  factor_cols = new_beliefs_factor_cols,
  context_label = "Script 16 exploratory Beliefs factor lookup"
)

exploratory_beliefs_with_order <- order_labels |>
  inner_join(exploratory_beliefs_scores, by = "participant_id")

if (nrow(exploratory_beliefs_with_order) != nrow(order_labels)) {
  warning(
    paste0(
      "Exploratory Beliefs order join returned ",
      nrow(exploratory_beliefs_with_order),
      " rows for ",
      nrow(order_labels),
      " strict-paired participants."
    ),
    call. = FALSE
  )
}

missing_exploratory_scores <- exploratory_beliefs_with_order |>
  summarise(across(all_of(new_beliefs_factor_cols), ~ sum(is.na(.x)))) |>
  pivot_longer(everything(), names_to = "factor", values_to = "n_missing")

if (any(missing_exploratory_scores$n_missing > 0)) {
  warning(
    paste0(
      "Some strict-paired participants have missing exploratory Beliefs factor scores: ",
      paste(
        paste0(missing_exploratory_scores$factor, "=", missing_exploratory_scores$n_missing),
        collapse = ", "
      )
    ),
    call. = FALSE
  )
}

exploratory_beliefs_mw <- map_dfr(new_beliefs_factor_cols, function(comp) {
  dat <- exploratory_beliefs_with_order |>
    select(order, all_of(comp)) |>
    rename(score = all_of(comp)) |>
    filter(!is.na(order), !is.na(score))

  trad_vec <- dat |> filter(order == "Traditional_First") |> pull(score)
  ai_vec   <- dat |> filter(order == "AI_First")          |> pull(score)

  n_trad <- length(trad_vec)
  n_ai   <- length(ai_vec)

  med_trad <- median(trad_vec)
  med_ai   <- median(ai_vec)

  if (n_trad < 2 || n_ai < 2) {
    return(tibble(
      composite = comp,
      n_traditional_first = n_trad,
      n_ai_first = n_ai,
      median_traditional_first = med_trad,
      median_ai_first = med_ai,
      w_stat = NA_real_,
      u_stat = NA_real_,
      p_value = NA_real_,
      estimate_hl = NA_real_,
      conf_low = NA_real_,
      conf_high = NA_real_,
      rank_biserial = NA_real_,
      note = "insufficient sample size"
    ))
  }

  test <- suppressWarnings(
    wilcox.test(
      x = trad_vec,
      y = ai_vec,
      exact = FALSE,
      conf.int = TRUE,
      conf.level = 0.95
    )
  )

  w <- as.numeric(unname(test$statistic))

  tibble(
    composite = comp,
    n_traditional_first = n_trad,
    n_ai_first = n_ai,
    median_traditional_first = med_trad,
    median_ai_first = med_ai,
    w_stat = w,
    u_stat = as.numeric(w),
    p_value = test$p.value,
    estimate_hl = if (!is.null(test$estimate)) as.numeric(test$estimate) else NA_real_,
    conf_low  = if (!is.null(test$conf.int)) as.numeric(test$conf.int[[1]]) else NA_real_,
    conf_high = if (!is.null(test$conf.int)) as.numeric(test$conf.int[[2]]) else NA_real_,
    rank_biserial = rank_biserial_from_u(w, n_trad, n_ai),
    note = NA_character_
  )
}) |>
  left_join(
    exploratory_beliefs_lookup |>
      select(composite = factor, display_label),
    by = "composite"
  ) |>
  mutate(
    instrument = "BeliefsAboutAI items 6-22 exploratory factors",
    p_bh = p.adjust(p_value, method = adjustment_methods[[1]]),
    p_bonferroni = p.adjust(p_value, method = adjustment_methods[[2]]),
    effect_size = rank_biserial
  ) |>
  select(
    composite, display_label, instrument,
    n_traditional_first, n_ai_first,
    median_traditional_first, median_ai_first,
    w_stat, u_stat, p_value, p_bh, p_bonferroni,
    estimate_hl, conf_low, conf_high, effect_size, note
  ) |>
  arrange(p_bh, p_value)

write_csv(
  exploratory_beliefs_mw,
  file.path(csv_dir, "Exploratory_Beliefs_Mann_Whitney_Order_Comparisons.csv")
)

exploratory_beliefs_mw |>
  mutate(across(where(is.numeric), ~ round(.x, 3))) |>
  kable(caption = "Exploratory Beliefs 6-22 factor scores compared by order group. Positive rank-biserial means Traditional-First tends higher.")
}
```

```{r exploratory-beliefs-factor-stratified, eval=run_exploratory_beliefs_order}
strat_base_ext <- strat_base |>
  left_join(exploratory_beliefs_scores, by = "participant_id")

strict_missing_exploratory <- strat_base_ext |>
  summarise(across(all_of(new_beliefs_factor_cols), ~ sum(is.na(.x)))) |>
  pivot_longer(everything(), names_to = "factor", values_to = "n_missing")

if (any(strict_missing_exploratory$n_missing > 0)) {
  warning(
    paste0(
      "Exploratory Beliefs factor scores are missing after joining to strat_base: ",
      paste(
        paste0(strict_missing_exploratory$factor, "=", strict_missing_exploratory$n_missing),
        collapse = ", "
      )
    ),
    call. = FALSE
  )
}

exploratory_beliefs_existing_pairs <- expand_grid(
  col_x = new_beliefs_factor_cols,
  col_y = factor_cols_strat
)

exploratory_beliefs_internal_pairs <- t(combn(new_beliefs_factor_cols, 2)) |>
  as_tibble(.name_repair = "minimal") |>
  setNames(c("col_x", "col_y"))

exploratory_beliefs_factor_pairs <- bind_rows(
  exploratory_beliefs_existing_pairs,
  exploratory_beliefs_internal_pairs
)

exploratory_beliefs_strat_results <- pmap_dfr(
  exploratory_beliefs_factor_pairs,
  function(col_x, col_y) correlate_stratified(strat_base_ext, col_x, col_y)
)

exploratory_factor_label_lookup <- bind_rows(
  factor_label_lookup_strat,
  exploratory_beliefs_lookup |>
    select(factor, display_label)
)

assert_lookup_covers_factor_columns(
  factor_lookup = exploratory_factor_label_lookup,
  factor_cols = c(factor_cols_strat, new_beliefs_factor_cols),
  context_label = "Exploratory Beliefs order-stratified label lookup"
)

exploratory_beliefs_strat_wide <- exploratory_beliefs_strat_results |>
  pivot_wider(
    names_from  = group,
    values_from = c(n, rho, p),
    names_glue  = "{group}_{.value}"
  ) |>
  left_join(
    exploratory_factor_label_lookup |>
      rename(col_x = factor, label_x = display_label),
    by = "col_x"
  ) |>
  left_join(
    exploratory_factor_label_lookup |>
      rename(col_y = factor, label_y = display_label),
    by = "col_y"
  ) |>
  mutate(
    fisher_p_bh = p.adjust(fisher_p, method = adjustment_methods[[1]]),
    fisher_p_bonferroni = p.adjust(fisher_p, method = adjustment_methods[[2]]),
    fisher_sig = case_when(
      is.na(fisher_p)  ~ "NA",
      fisher_p < 0.001 ~ "p < .001",
      fisher_p < 0.01  ~ "p < .01",
      fisher_p < 0.05  ~ "p < .05",
      TRUE             ~ paste0("p = ", round(fisher_p, 3))
    ),
    fisher_sig_bh = case_when(
      is.na(fisher_p_bh)  ~ "NA",
      fisher_p_bh < 0.001 ~ "BH p < .001",
      fisher_p_bh < 0.01  ~ "BH p < .01",
      fisher_p_bh < 0.05  ~ "BH p < .05",
      TRUE                ~ paste0("BH p = ", round(fisher_p_bh, 3))
    ),
    fisher_sig_bonferroni = case_when(
      is.na(fisher_p_bonferroni)  ~ "NA",
      fisher_p_bonferroni < 0.001 ~ "Bonf p < .001",
      fisher_p_bonferroni < 0.01  ~ "Bonf p < .01",
      fisher_p_bonferroni < 0.05  ~ "Bonf p < .05",
      TRUE                        ~ paste0("Bonf p = ", round(fisher_p_bonferroni, 3))
    ),
    rho_diff = round(Traditional_First_rho - AI_First_rho, 3),
    comparison_family = case_when(
      col_x %in% new_beliefs_factor_cols & col_y %in% factor_cols_strat ~
        "Exploratory Beliefs 6-22 factor x locked IMI/WritingEfficacy/AIReflection factor",
      col_x %in% new_beliefs_factor_cols & col_y %in% new_beliefs_factor_cols ~
        "Within exploratory Beliefs 6-22 factors",
      TRUE ~ "Exploratory Beliefs 6-22 factor pair"
    )
  ) |>
  arrange(fisher_p_bh, fisher_p, desc(abs(rho_diff)))

write_csv(
  exploratory_beliefs_strat_wide,
  file.path(csv_dir, "Exploratory_Beliefs_Factor_Order_Stratified_Correlations.csv")
)

exploratory_factor_levels <- factor_label_lookup_strat$display_label[
  match(factor_cols_strat, factor_label_lookup_strat$factor)
]

if (any(is.na(exploratory_factor_levels))) {
  stop("Exploratory Beliefs order plots: missing display labels for one or more locked factor columns.", call. = FALSE)
}

exploratory_beliefs_plot_long <- exploratory_beliefs_strat_results |>
  filter(col_x %in% new_beliefs_factor_cols, col_y %in% factor_cols_strat) |>
  left_join(
    exploratory_beliefs_lookup |>
      select(col_x = factor, belief_factor_label = display_label),
    by = "col_x"
  ) |>
  left_join(
    factor_label_lookup_strat |>
      rename(col_y = factor, factor_label = display_label),
    by = "col_y"
  ) |>
  mutate(
    factor_label = factor(factor_label, levels = exploratory_factor_levels),
    group = factor(group, levels = c("Full", "Traditional_First", "AI_First"))
  )

exploratory_beliefs_plot_annotations <- exploratory_beliefs_strat_wide |>
  filter(col_x %in% new_beliefs_factor_cols, col_y %in% factor_cols_strat) |>
  select(col_x, col_y, label_y, fisher_sig_bh) |>
  mutate(label_y = factor(label_y, levels = exploratory_factor_levels))

for (belief_factor_col in new_beliefs_factor_cols) {
  plot_df <- exploratory_beliefs_plot_long |>
    filter(col_x == belief_factor_col)

  ann_df <- exploratory_beliefs_plot_annotations |>
    filter(col_x == belief_factor_col)

  if (nrow(plot_df) == 0 || all(is.na(plot_df$rho))) {
    next
  }

  belief_factor_title <- plot_df |>
    distinct(belief_factor_label) |>
    pull(belief_factor_label) |>
    first()

  exploratory_beliefs_order_plot <- ggplot(
    plot_df,
    aes(x = factor_label, y = rho, group = group, color = group, linetype = group, shape = group)
  ) +
    geom_hline(yintercept = 0, color = "#c7c7c7", linewidth = 0.8) +
    geom_hline(yintercept = c(-0.30, 0.30), color = "#bdbdbd", linewidth = 0.7, linetype = "dotted") +
    geom_line(linewidth = 1.2, alpha = 0.95) +
    geom_point(size = 3.7, alpha = 0.95) +
    geom_text(
      data = ann_df,
      aes(x = label_y, y = -1.07, label = fisher_sig_bh),
      inherit.aes = FALSE,
      color = "#5a5a5a",
      size = 4.0
    ) +
    scale_color_manual(
      values = c(
        "Full" = "#7a7a7a",
        "Traditional_First" = "#c93e2c",
        "AI_First" = "#3a88bf"
      ),
      labels = c(
        "Full" = "Full sample",
        "Traditional_First" = "Traditional-First",
        "AI_First" = "AI-First"
      )
    ) +
    scale_linetype_manual(
      values = c(
        "Full" = "22",
        "Traditional_First" = "solid",
        "AI_First" = "solid"
      ),
      labels = c(
        "Full" = "Full sample",
        "Traditional_First" = "Traditional-First",
        "AI_First" = "AI-First"
      )
    ) +
    scale_shape_manual(
      values = c(
        "Full" = 16,
        "Traditional_First" = 17,
        "AI_First" = 15
      ),
      labels = c(
        "Full" = "Full sample",
        "Traditional_First" = "Traditional-First",
        "AI_First" = "AI-First"
      )
    ) +
    scale_y_continuous(
      limits = c(-1.1, 1.0),
      breaks = seq(-1, 1, by = 0.25),
      labels = scales::number_format(accuracy = 0.01)
    ) +
    labs(
      title = belief_factor_title,
      subtitle = "Spearman rho with locked factors by order group; exploratory Beliefs model uses items 6-22",
      x = NULL,
      y = "Spearman rho",
      caption = "BH-adjusted Fisher's z p-value shown below each factor label. Dotted lines at rho = +/-0.30."
    ) +
    theme_minimal(base_size = 14) +
    theme(
      legend.position = "none",
      panel.grid.minor = element_blank(),
      axis.text.x = element_text(angle = 35, hjust = 1, size = 10),
      axis.text.y = element_text(size = 11),
      plot.title = element_text(face = "bold", size = 17),
      plot.subtitle = element_text(size = 11, color = "#666666"),
      plot.caption = element_text(size = 10, color = "#7a7a7a"),
      plot.margin = margin(15, 20, 20, 15)
    )

  ggsave(
    filename = file.path(plot_dir, paste0("exploratory_", belief_factor_col, "_order_corr.png")),
    plot = exploratory_beliefs_order_plot,
    width = 16,
    height = 10,
    units = "in",
    dpi = 160,
    bg = "white"
  )
}

combined_all_factor_strat_results <- bind_rows(
  factor_strat_results,
  exploratory_beliefs_strat_results
)

combined_all_factor_strat_wide <- combined_all_factor_strat_results |>
  pivot_wider(
    names_from  = group,
    values_from = c(n, rho, p),
    names_glue  = "{group}_{.value}"
  ) |>
  left_join(
    exploratory_factor_label_lookup |>
      rename(col_x = factor, label_x = display_label),
    by = "col_x"
  ) |>
  left_join(
    exploratory_factor_label_lookup |>
      rename(col_y = factor, label_y = display_label),
    by = "col_y"
  ) |>
  mutate(
    fisher_p_bh = p.adjust(fisher_p, method = adjustment_methods[[1]]),
    fisher_p_bonferroni = p.adjust(fisher_p, method = adjustment_methods[[2]]),
    fisher_sig = case_when(
      is.na(fisher_p)  ~ "NA",
      fisher_p < 0.001 ~ "p < .001",
      fisher_p < 0.01  ~ "p < .01",
      fisher_p < 0.05  ~ "p < .05",
      TRUE             ~ paste0("p = ", round(fisher_p, 3))
    ),
    fisher_sig_bh = case_when(
      is.na(fisher_p_bh)  ~ "NA",
      fisher_p_bh < 0.001 ~ "BH p < .001",
      fisher_p_bh < 0.01  ~ "BH p < .01",
      fisher_p_bh < 0.05  ~ "BH p < .05",
      TRUE                ~ paste0("BH p = ", round(fisher_p_bh, 3))
    ),
    fisher_sig_bonferroni = case_when(
      is.na(fisher_p_bonferroni)  ~ "NA",
      fisher_p_bonferroni < 0.001 ~ "Bonf p < .001",
      fisher_p_bonferroni < 0.01  ~ "Bonf p < .01",
      fisher_p_bonferroni < 0.05  ~ "Bonf p < .05",
      TRUE                        ~ paste0("Bonf p = ", round(fisher_p_bonferroni, 3))
    ),
    plot_sig = case_when(
      !is.na(fisher_p_bonferroni) & fisher_p_bonferroni < 0.05 ~ fisher_sig_bonferroni,
      !is.na(fisher_p_bh) & fisher_p_bh < 0.05 ~ fisher_sig_bh,
      TRUE ~ fisher_sig
    ),
    rho_diff = round(Traditional_First_rho - AI_First_rho, 3),
    comparison_family = case_when(
      col_x %in% factor_cols_strat & col_y %in% factor_cols_strat ~
        "Locked IMI/WritingEfficacy/AIReflection factors",
      col_x %in% new_beliefs_factor_cols & col_y %in% factor_cols_strat ~
        "Exploratory Beliefs 6-22 factor x locked IMI/WritingEfficacy/AIReflection factor",
      col_x %in% new_beliefs_factor_cols & col_y %in% new_beliefs_factor_cols ~
        "Within exploratory Beliefs 6-22 factors",
      TRUE ~ "All-factor pair"
    )
  ) |>
  arrange(fisher_p_bh, fisher_p, desc(abs(rho_diff)))

write_csv(
  combined_all_factor_strat_wide,
  file.path(csv_dir, "All_Factors_With_Exploratory_Beliefs_Order_Stratified_Correlations.csv")
)

all_factor_cols_order <- c(factor_cols_strat, new_beliefs_factor_cols)
all_factor_label_levels <- exploratory_factor_label_lookup$display_label[
  match(all_factor_cols_order, exploratory_factor_label_lookup$factor)
]

if (any(is.na(all_factor_label_levels))) {
  stop("All-factor order plots: missing display labels for one or more factor columns.", call. = FALSE)
}

combined_all_factor_plot_long <- bind_rows(
  combined_all_factor_strat_results |>
    transmute(
      focal_factor = col_x,
      comparison_factor = col_y,
      group, n, rho, p, note, fisher_p
    ),
  combined_all_factor_strat_results |>
    transmute(
      focal_factor = col_y,
      comparison_factor = col_x,
      group, n, rho, p, note, fisher_p
    )
) |>
  left_join(
    exploratory_factor_label_lookup |>
      rename(focal_factor = factor, focal_label = display_label),
    by = "focal_factor"
  ) |>
  left_join(
    exploratory_factor_label_lookup |>
      rename(comparison_factor = factor, comparison_label = display_label),
    by = "comparison_factor"
  ) |>
  mutate(group = factor(group, levels = c("Full", "Traditional_First", "AI_First")))

combined_all_factor_plot_annotations <- bind_rows(
  combined_all_factor_strat_wide |>
    transmute(
      focal_factor = col_x,
      comparison_factor = col_y,
      comparison_label = label_y,
      plot_sig
    ),
  combined_all_factor_strat_wide |>
    transmute(
      focal_factor = col_y,
      comparison_factor = col_x,
      comparison_label = label_x,
      plot_sig
    )
)

for (focal_col in all_factor_cols_order) {
  comparison_levels <- all_factor_label_levels[all_factor_cols_order != focal_col]

  plot_df <- combined_all_factor_plot_long |>
    filter(focal_factor == focal_col) |>
    mutate(comparison_label = factor(comparison_label, levels = comparison_levels))

  ann_df <- combined_all_factor_plot_annotations |>
    filter(focal_factor == focal_col) |>
    mutate(comparison_label = factor(comparison_label, levels = comparison_levels))

  if (nrow(plot_df) == 0 || all(is.na(plot_df$rho))) {
    next
  }

  focal_title <- plot_df |>
    distinct(focal_label) |>
    pull(focal_label) |>
    first()

  all_factor_order_plot <- ggplot(
    plot_df,
    aes(x = comparison_label, y = rho, group = group, color = group, linetype = group, shape = group)
  ) +
    geom_hline(yintercept = 0, color = "#c7c7c7", linewidth = 0.8) +
    geom_hline(yintercept = c(-0.30, 0.30), color = "#bdbdbd", linewidth = 0.7, linetype = "dotted") +
    geom_line(linewidth = 1.2, alpha = 0.95) +
    geom_point(size = 3.7, alpha = 0.95) +
    geom_text(
      data = ann_df,
      aes(x = comparison_label, y = -1.07, label = plot_sig),
      inherit.aes = FALSE,
      color = "#5a5a5a",
      size = 3.7
    ) +
    scale_color_manual(
      values = c(
        "Full" = "#7a7a7a",
        "Traditional_First" = "#c93e2c",
        "AI_First" = "#3a88bf"
      ),
      labels = c(
        "Full" = "Full sample",
        "Traditional_First" = "Traditional-First",
        "AI_First" = "AI-First"
      )
    ) +
    scale_linetype_manual(
      values = c(
        "Full" = "22",
        "Traditional_First" = "solid",
        "AI_First" = "solid"
      ),
      labels = c(
        "Full" = "Full sample",
        "Traditional_First" = "Traditional-First",
        "AI_First" = "AI-First"
      )
    ) +
    scale_shape_manual(
      values = c(
        "Full" = 16,
        "Traditional_First" = 17,
        "AI_First" = 15
      ),
      labels = c(
        "Full" = "Full sample",
        "Traditional_First" = "Traditional-First",
        "AI_First" = "AI-First"
      )
    ) +
    scale_y_continuous(
      limits = c(-1.1, 1.0),
      breaks = seq(-1, 1, by = 0.25),
      labels = scales::number_format(accuracy = 0.01)
    ) +
    labs(
      title = focal_title,
      subtitle = "Spearman rho with each other factor — Full sample (gray dashed), Traditional-First (red), AI-First (blue)",
      x = NULL,
      y = "Spearman rho",
      caption = "Fisher's z p-value shown below each factor label; corrected labels shown when BH/Bonferroni survive. Dotted lines at rho = +/-0.30."
    ) +
    theme_minimal(base_size = 14) +
    theme(
      legend.position = "none",
      panel.grid.minor = element_blank(),
      axis.text.x = element_text(angle = 35, hjust = 1, size = 9.2),
      axis.text.y = element_text(size = 11),
      plot.title = element_text(face = "bold", size = 17),
      plot.subtitle = element_text(size = 11, color = "#666666"),
      plot.caption = element_text(size = 10, color = "#7a7a7a"),
      plot.margin = margin(15, 20, 20, 15)
    )

  ggsave(
    filename = file.path(
      plot_dir,
      paste0(
        "factor_all_",
        str_replace_all(focal_col, "[^A-Za-z0-9]+", "_"),
        "_order_corr.png"
      )
    ),
    plot = all_factor_order_plot,
    width = 17,
    height = 10,
    units = "in",
    dpi = 160,
    bg = "white"
  )
}

exploratory_beliefs_diff_plot_data <- exploratory_beliefs_strat_wide |>
  mutate(
    pair_label = paste0(label_x, "\n× ", label_y),
    significance = case_when(
      !is.na(fisher_p_bonferroni) & fisher_p_bonferroni < 0.05 ~ "Bonferroni < .05",
      !is.na(fisher_p_bh) & fisher_p_bh < 0.05 ~ "BH < .05",
      !is.na(fisher_p) & fisher_p < 0.05 ~ "Nominal < .05",
      TRUE ~ "Not significant"
    ),
    significance = factor(
      significance,
      levels = c("Bonferroni < .05", "BH < .05", "Nominal < .05", "Not significant")
    ),
    p_label = case_when(
      significance == "Bonferroni < .05" ~ fisher_sig_bonferroni,
      significance == "BH < .05" ~ fisher_sig_bh,
      significance == "Nominal < .05" ~ fisher_sig,
      TRUE ~ ""
    ),
    pair_label = fct_reorder(pair_label, rho_diff)
  )

exploratory_beliefs_diff_plot <- ggplot(
  exploratory_beliefs_diff_plot_data,
  aes(x = rho_diff, y = pair_label, fill = significance)
) +
  geom_vline(xintercept = 0, color = "#bdbdbd", linewidth = 0.8) +
  geom_col(width = 0.72, alpha = 0.95) +
  geom_text(
    aes(
      label = p_label,
      hjust = if_else(rho_diff >= 0, -0.08, 1.08)
    ),
    size = 3.4,
    color = "#3f3f3f"
  ) +
  scale_fill_manual(
    values = c(
      "Bonferroni < .05" = "#7b2cbf",
      "BH < .05" = "#1b9e77",
      "Nominal < .05" = "#e69500",
      "Not significant" = "#b8b8b8"
    ),
    drop = FALSE
  ) +
  scale_x_continuous(
    limits = c(-0.9, 0.55),
    breaks = seq(-0.8, 0.4, by = 0.2),
    labels = scales::number_format(accuracy = 0.01)
  ) +
  labs(
    title = "Order-group rho differences involving exploratory Beliefs factors",
    subtitle = "Bars show Traditional-First rho minus AI-First rho; color marks Fisher z multiplicity status",
    x = "rho difference",
    y = NULL,
    fill = NULL,
    caption = "Exploratory Beliefs factors use the Script 16 items 6-22 model. Bonferroni and BH corrections are across this 27-pair addendum family."
  ) +
  theme_minimal(base_size = 13) +
  theme(
    legend.position = "top",
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.y = element_text(size = 8.4),
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(size = 11, color = "#666666"),
    plot.caption = element_text(size = 9.5, color = "#7a7a7a"),
    plot.margin = margin(12, 50, 12, 12)
  )

ggsave(
  filename = file.path(plot_dir, "exploratory_beliefs_order_rho_diff_ranked.png"),
  plot = exploratory_beliefs_diff_plot,
  width = 14,
  height = 10,
  units = "in",
  dpi = 180,
  bg = "white"
)

exploratory_beliefs_strat_wide |>
  select(
    label_x, label_y, comparison_family,
    Full_n, Full_rho, Full_p,
    Traditional_First_n, Traditional_First_rho, Traditional_First_p,
    AI_First_n, AI_First_rho, AI_First_p,
    fisher_p, fisher_p_bh, fisher_p_bonferroni, fisher_sig_bh,
    fisher_sig_bonferroni, rho_diff
  ) |>
  mutate(across(where(is.numeric), ~ round(.x, 3))) |>
  kable(caption = "Exploratory Beliefs 6-22 factor correlations stratified by order group. fisher_p tests whether Traditional-First rho differs from AI-First rho.")
```

```{r order-strat-exports, eval=run_exploratory_beliefs_order}
strat_export_manifest <- tibble(
  file = c(
    "Factor_Factor_Order_Stratified_Correlations.csv",
    "Beliefs_Factor_Order_Stratified_Correlations.csv",
    "Exploratory_Beliefs_Mann_Whitney_Order_Comparisons.csv",
    "Exploratory_Beliefs_Factor_Order_Stratified_Correlations.csv",
    "All_Factors_With_Exploratory_Beliefs_Order_Stratified_Correlations.csv",
    "plots/factor_all_*_order_corr.png",
    "plots/exploratory_beliefs_order_rho_diff_ranked.png"
  ),
  description = c(
    "Factor × factor Spearman correlations split by order group with Fisher z-test",
    "Beliefs item × factor Spearman correlations split by order group with Fisher z-test",
    "Exploratory BeliefsAboutAI items 6-22 factor scores compared by order group with Mann-Whitney tests",
    "Exploratory BeliefsAboutAI items 6-22 factor correlations split by order group with Fisher z-test and multiplicity correction",
    "Combined 11-factor order-stratified correlations including locked factors and exploratory Beliefs 6-22 factors",
    "One plot per focal factor showing order-stratified rho with every other factor",
    "Ranked plot of Traditional-First minus AI-First rho differences for exploratory Beliefs factor pairs"
  )
)

write_csv(strat_export_manifest, file.path(csv_dir, "Order_Stratified_Export_Manifest.csv"))
kable(strat_export_manifest)
```
