---
title: "Q17 AI Tool Use vs Author Recognition"
format:
  html:
    toc: true
    toc-depth: 2
output-dir: "07_q17_ai_usePART2"
execute:
  echo: false
  warning: false
  message: false
---

This is a quick exploratory side analysis of `Q17` from the AI survey against `ART` (Author Recognition Test) as a proxy for reading exposure/reading ability. It is useful for pattern-finding, but it is not a direct comprehension or retention outcome.

```{r}
library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(purrr)
library(ggplot2)
library(forcats)
library(scales)
library(knitr)
library(glue)
source("scoring_helpers.R", local = knitr::knit_global())
```

## Setup

```{r}
script_dir <- "07_q17_ai_usePART2"
csv_dir <- file.path(script_dir, "csv")
art_clean_file <- file.path("01_audit_cleaning", "cleaned", "AuthorRecognition_cleaned.csv")
dir.create(csv_dir, recursive = TRUE, showWarnings = FALSE)

normalize_text <- function(x) {
  x |>
    str_replace_all("[\u2018\u2019]", "'") |>
    str_replace_all("[\u201C\u201D]", "\"") |>
    str_squish()
}

status_priority <- c(
  "unique" = 4L,
  "second-dup" = 3L,
  "first-dup" = 2L,
  "incomplete" = 1L
)

q17_response_map <- c(
  "I have never heard of this tool." = 1L,
  "I have heard of this tool but never used it." = 2L,
  "I rarely use this tool." = 3L,
  "I sometimes use this tool." = 4L,
  "I often use this tool." = 5L
)

safe_spearman <- function(data, predictor, outcome = "art_net_real_minus_fake") {
  cols <- c(predictor, outcome)
  dat <- data |>
    select(all_of(cols)) |>
    filter(if_all(everything(), ~ !is.na(.x)))

  if (nrow(dat) < 10 || dplyr::n_distinct(dat[[predictor]]) < 2 || dplyr::n_distinct(dat[[outcome]]) < 2) {
    return(tibble(
      predictor = predictor,
      outcome = outcome,
      n = nrow(dat),
      rho = NA_real_,
      p_value = NA_real_,
      note = "insufficient variation or sample size"
    ))
  }

  test <- suppressWarnings(
    cor.test(dat[[predictor]], dat[[outcome]], method = "spearman", exact = FALSE)
  )

  tibble(
    predictor = predictor,
    outcome = outcome,
    n = nrow(dat),
    rho = unname(test$estimate),
    p_value = test$p.value,
    note = NA_character_
  )
}

safe_lm <- function(data, predictor, outcome = "art_net_real_minus_fake") {
  dat <- data |>
    select(all_of(c(outcome, predictor))) |>
    filter(if_all(everything(), ~ !is.na(.x)))

  if (nrow(dat) < 10 || dplyr::n_distinct(dat[[predictor]]) < 2) {
    return(tibble(
      predictor = predictor,
      outcome = outcome,
      n = nrow(dat),
      intercept = NA_real_,
      slope = NA_real_,
      slope_p_value = NA_real_,
      r_squared = NA_real_,
      note = "insufficient variation or sample size"
    ))
  }

  fit <- lm(stats::as.formula(paste(outcome, "~", predictor)), data = dat)
  coef_table <- summary(fit)$coefficients

  tibble(
    predictor = predictor,
    outcome = outcome,
    n = nrow(dat),
    intercept = unname(coef(fit)[1]),
    slope = unname(coef(fit)[2]),
    slope_p_value = coef_table[2, 4],
    r_squared = summary(fit)$r.squared,
    note = NA_character_
  )
}

summarize_tool_relationship <- function(df, art_col = "art_net_real_minus_fake") {
  dat <- df |>
    filter(!is.na(use_score), !is.na(.data[[art_col]])) |>
    mutate(regular_use = use_score >= 4L)

  n_total <- nrow(dat)
  n_regular <- sum(dat$regular_use, na.rm = TRUE)
  n_non_regular <- sum(!dat$regular_use, na.rm = TRUE)

  spearman_result <- safe_spearman(dat, "use_score", art_col)

  wilcox_p <- NA_real_
  if (n_regular >= 3 && n_non_regular >= 3 && dplyr::n_distinct(dat[[art_col]]) > 1) {
    wilcox_p <- suppressWarnings(
      wilcox.test(dat[[art_col]] ~ dat$regular_use, exact = FALSE)$p.value
    )
  }

  tibble(
    n_total = n_total,
    n_regular = n_regular,
    n_non_regular = n_non_regular,
    regular_use_pct = mean(dat$regular_use, na.rm = TRUE),
    mean_use_score = mean(dat$use_score, na.rm = TRUE),
    mean_art_regular = if (n_regular > 0) mean(dat[[art_col]][dat$regular_use], na.rm = TRUE) else NA_real_,
    mean_art_non_regular = if (n_non_regular > 0) mean(dat[[art_col]][!dat$regular_use], na.rm = TRUE) else NA_real_,
    median_art_regular = if (n_regular > 0) median(dat[[art_col]][dat$regular_use], na.rm = TRUE) else NA_real_,
    median_art_non_regular = if (n_non_regular > 0) median(dat[[art_col]][!dat$regular_use], na.rm = TRUE) else NA_real_,
    art_diff_regular_minus_non = mean_art_regular - mean_art_non_regular,
    use_score_rho = spearman_result$rho[[1]],
    use_score_p_value = spearman_result$p_value[[1]],
    wilcox_p_value = wilcox_p
  )
}

model_focus <- c(
  "ChatGPT (including DALL-E) by OpenAI",
  "Claude by Anthropic",
  "Gemini (formerly Bard) by Google",
  "Perplexity AI",
  "Copilot (Bing Chat) by Microsoft",
  "DeepSeek",
  "Duck Duck Go AI Chat",
  "GitHub Copilot",
  "Grammarly"
)
```

## Read and Score ART

```{r}
art_raw <- read_csv(art_clean_file, show_col_types = FALSE)

required_art_cols <- c("participant_id", "order", "response_raw")
missing_art_cols  <- setdiff(required_art_cols, names(art_raw))
if (length(missing_art_cols) > 0) {
  stop(paste0("AuthorRecognition_cleaned.csv is missing required columns: ",
              paste(missing_art_cols, collapse = ", ")), call. = FALSE)
}
if (anyNA(art_raw$participant_id)) {
  stop("AuthorRecognition_cleaned.csv has NA values in participant_id.", call. = FALSE)
}
art_dup_pids <- art_raw |> count(participant_id, name = "n") |> filter(n > 1L)
if (nrow(art_dup_pids) > 0) {
  stop(paste0("AuthorRecognition_cleaned.csv has duplicate participant_id rows: ",
              paste(art_dup_pids$participant_id, collapse = ", ")), call. = FALSE)
}

authorkey <- read_csv("authorkey.csv", show_col_types = FALSE) |>
  mutate(
    author_clean = normalize_text(author),
    validity = tolower(validity)
  )

required_ak_cols <- c("author", "validity")
missing_ak_cols  <- setdiff(required_ak_cols, names(authorkey))
if (length(missing_ak_cols) > 0) {
  stop(paste0("authorkey.csv is missing required columns: ",
              paste(missing_ak_cols, collapse = ", ")), call. = FALSE)
}

n_real_items <- sum(authorkey$validity == "real", na.rm = TRUE)
n_fake_items <- sum(authorkey$validity == "fake", na.rm = TRUE)

art_long <- art_raw |>
  transmute(
    participant_id,
    order,
    response_raw = coalesce(response_raw, "")
  ) |>
  separate_rows(response_raw, sep = ",") |>
  mutate(author_selected = normalize_text(response_raw)) |>
  filter(
    author_selected != "",
    !tolower(author_selected) %in% c("none", "na", "n/a")
  )

art_scored_long <- art_long |>
  left_join(
    authorkey |> select(author_clean, validity),
    by = c("author_selected" = "author_clean")
  )

art_unmatched <- art_scored_long |>
  filter(is.na(validity)) |>
  distinct(participant_id, author_selected) |>
  arrange(participant_id, author_selected)

art_score_counts <- art_scored_long |>
  group_by(participant_id, order) |>
  summarise(
    art_total_selected = n(),
    art_real_hits = sum(validity == "real", na.rm = TRUE),
    art_fake_false_alarms = sum(validity == "fake", na.rm = TRUE),
    art_neutral_selected = sum(validity == "neutral", na.rm = TRUE),
    art_unknown_selected = sum(is.na(validity)),
    art_net_real_minus_fake = art_real_hits - art_fake_false_alarms,
    art_hit_rate = art_real_hits / n_real_items,
    art_false_alarm_rate = art_fake_false_alarms / n_fake_items,
    art_adjusted_rate = art_hit_rate - art_false_alarm_rate,
    .groups = "drop"
  )

art_scores <- art_raw |>
  distinct(participant_id, order) |>
  left_join(art_score_counts, by = c("participant_id", "order")) |>
  mutate(
    across(
      c(
        art_total_selected,
        art_real_hits,
        art_fake_false_alarms,
        art_neutral_selected,
        art_unknown_selected,
        art_net_real_minus_fake,
        art_hit_rate,
        art_false_alarm_rate,
        art_adjusted_rate
      ),
      ~ coalesce(.x, 0)
    )
  )

write_csv(art_scores, file.path(csv_dir, "ART_Scored.csv"))
write_csv(art_unmatched, file.path(csv_dir, "ART_Unmatched_Names.csv"))
```

```{r}
art_summary <- tibble(
  metric = c(
    "ART participants",
    "Real author targets",
    "Fake foils",
    "Unmatched names after scoring"
  ),
  value = c(
    nrow(art_scores),
    n_real_items,
    n_fake_items,
    nrow(art_unmatched)
  )
)

kable(art_summary)
```

## Resolve Q17 AI Tool Use

```{r}
# Use named columns matching Scripts 01/02 rather than positional X_ references.
llm_col_names <- c(
  "participant_number_order", "pid", "topic", "item_code", "score_raw",
  "qualtrics_qid", "item_subnum", "question_stem",
  "input_type", "input_subtype", "answer_type",
  "question_block", "item_num", "item_text",
  "item_text_full", "response_labeled", "response_label_short",
  "score_numeric", "response_label2", "response_html",
  "question_stem2", "item_text2", "submission_status"
)

llm_raw <- read_csv(
  "llm-survey-long-040726.csv",
  skip = 9, col_names = llm_col_names, show_col_types = FALSE,
  col_types = cols(
    pid = col_character(),
    question_block = col_character(),
    item_num = col_character(),
    score_raw = col_character(),
    submission_status = col_character()
  )
)

q17_raw <- llm_raw |>
  filter(question_block == "Q17", !is.na(pid), pid != "") |>
  transmute(
    participant_id = pid,
    item_num = as.integer(item_num),
    tool = normalize_text(coalesce(item_text, item_text2)),
    response_raw = normalize_text(coalesce(response_labeled, score_raw, response_label_short, response_label2, response_html)),
    submission_status = submission_status,
    use_score = unname(q17_response_map[normalize_text(coalesce(response_labeled, score_raw, response_label_short, response_label2, response_html))])
  )

q17_submission_audit <- q17_raw |>
  group_by(participant_id, submission_status) |>
  summarise(
    n_answered = sum(!is.na(use_score)),
    total_use_score = sum(use_score, na.rm = TRUE),
    distinct_response_levels = n_distinct(use_score[!is.na(use_score)]),
    status_rank = dplyr::first(coalesce(unname(status_priority[submission_status]), 0L)),
    .groups = "drop"
  ) |>
  arrange(
    participant_id,
    desc(n_answered),
    desc(distinct_response_levels), # straight-liners (1 distinct level) lose to any varied submission
    desc(total_use_score),
    desc(status_rank),
    submission_status
  )

q17_best_submission <- q17_submission_audit |>
  group_by(participant_id) |>
  slice(1) |>
  ungroup()

assert_unique_pid_rows(q17_best_submission, "participant_id", "q17_best_submission")

q17_clean <- q17_raw |>
  inner_join(
    q17_best_submission |> select(participant_id, submission_status),
    by = c("participant_id", "submission_status")
  )

assert_nonempty_df(q17_clean, "q17_clean")

# Participants excluded from Q17 analysis regardless of data quality.
# 9g0fXm: straight-line first-dup (all 5s) inflates ai_tools_regular_n to 28;
# dedup ordering fix above should already prefer the varied second-dup, but
# we exclude explicitly as a belt-and-suspenders guard for this known outlier.
q17_analysis_exclusions <- c("9g0fXm")

q17_clean <- q17_clean |>
  filter(!participant_id %in% q17_analysis_exclusions)

q17_tool_popularity <- q17_clean |>
  group_by(tool) |>
  summarise(
    n_participants = sum(!is.na(use_score)),
    never_heard_n = sum(use_score == 1L, na.rm = TRUE),
    heard_never_used_n = sum(use_score == 2L, na.rm = TRUE),
    rarely_n = sum(use_score == 3L, na.rm = TRUE),
    sometimes_n = sum(use_score == 4L, na.rm = TRUE),
    often_n = sum(use_score == 5L, na.rm = TRUE),
    heard_pct = mean(use_score >= 2L, na.rm = TRUE),
    ever_used_pct = mean(use_score >= 3L, na.rm = TRUE),
    regular_use_pct = mean(use_score >= 4L, na.rm = TRUE),
    mean_use = mean(use_score, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(ever_used_pct), desc(mean_use), tool)

q17_participant_indices <- q17_clean |>
  group_by(participant_id) |>
  summarise(
    ai_tools_answered = sum(!is.na(use_score)),
    ai_tools_heard_n = sum(use_score >= 2L, na.rm = TRUE),
    ai_tools_used_n = sum(use_score >= 3L, na.rm = TRUE),
    ai_tools_regular_n = sum(use_score >= 4L, na.rm = TRUE),
    ai_tools_often_n = sum(use_score == 5L, na.rm = TRUE),
    ai_use_mean = mean(use_score, na.rm = TRUE),
    ai_use_mean_heard_only = mean(use_score[use_score >= 2L], na.rm = TRUE),
    .groups = "drop"
  )

write_csv(q17_submission_audit, file.path(csv_dir, "Q17_Submission_Resolution.csv"))
write_csv(q17_tool_popularity, file.path(csv_dir, "Q17_Tool_Popularity.csv"))
write_csv(q17_participant_indices, file.path(csv_dir, "Q17_Participant_AI_Use_Index.csv"))
```

```{r, fig.height=6, fig.width=10}
q17_tool_popularity |>
  slice_head(n = 12) |>
  select(tool, ever_used_pct, regular_use_pct) |>
  pivot_longer(cols = c(ever_used_pct, regular_use_pct), names_to = "metric", values_to = "pct") |>
  mutate(
    tool = fct_reorder(tool, pct, .fun = max),
    metric = recode(metric, ever_used_pct = "Ever used", regular_use_pct = "Regular use")
  ) |>
  ggplot(aes(x = pct, y = tool, fill = metric)) +
  geom_col(position = "dodge") +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  scale_fill_manual(values = c("Ever used" = "#c96b3b", "Regular use" = "#4f7c5f")) +
  labs(
    title = "Q17 Tool Popularity",
    subtitle = "Top 12 tools by ever-used rate",
    x = "Share of participants",
    y = NULL,
    fill = NULL
  ) +
  theme_minimal(base_size = 12)
```

```{r}
q17_tool_popularity |>
  select(tool, ever_used_pct, regular_use_pct, mean_use) |>
  slice_head(n = 12) |>
  mutate(
    ever_used_pct = percent(ever_used_pct, accuracy = 0.1),
    regular_use_pct = percent(regular_use_pct, accuracy = 0.1),
    mean_use = round(mean_use, 2)
  ) |>
  kable()
```

## Merge Q17 with ART

```{r}
q17_focus_wide <- q17_clean |>
  filter(tool %in% model_focus) |>
  transmute(
    participant_id,
    tool,
    use_score,
    regular_use = use_score >= 4L
  )

analysis_df <- art_scores |>
  inner_join(q17_participant_indices, by = "participant_id")

# N is not hardcoded to 82: ART gate = RW completers, Q17 gate = LLM completers.
# Single-source participants (RW-only or LLM-only) appear in one but not both,
# so the inner_join naturally produces the paired overlap without requiring
# strict paired clean_pids. Log actual N for provenance.
cat("Q17 x ART overlap N:", nrow(analysis_df), "\n")
assert_unique_pid_rows(analysis_df, "participant_id", "Q17 x ART merged")

write_csv(analysis_df, file.path(csv_dir, "Q17_AI_Use_vs_ART_Merged.csv"))
```

```{r}
summary_table <- tibble(
  metric = c(
    "ART participants",
    "Q17 participants after duplicate resolution",
    "Q17 x ART overlap",
    "Top tool by ever-used rate",
    "Top tool ever-used rate"
  ),
  value = c(
    nrow(art_scores),
    n_distinct(q17_clean$participant_id),
    nrow(analysis_df),
    q17_tool_popularity$tool[[1]],
    percent(q17_tool_popularity$ever_used_pct[[1]], accuracy = 0.1)
  )
)

write_csv(summary_table, file.path(csv_dir, "Q17_AI_Use_vs_ART_Summary.csv"))

kable(summary_table)
```

## Overall AI Use vs ART

```{r}
correlation_predictors <- c(
  "ai_use_mean",
  "ai_tools_heard_n",
  "ai_tools_used_n",
  "ai_tools_regular_n",
  "ai_tools_often_n"
)

analysis_outcomes <- c(
  "art_net_real_minus_fake",
  "art_real_hits",
  "art_fake_false_alarms",
  "art_adjusted_rate"
)

q17_art_correlations <- crossing(
  predictor = correlation_predictors,
  outcome = analysis_outcomes
) |>
  mutate(result = map2(predictor, outcome, ~ safe_spearman(analysis_df, .x, .y))) |>
  pull(result) |>
  bind_rows() |>
  mutate(
    p_bh = p.adjust(p_value, method = "BH"),
    p_bonferroni = p.adjust(p_value, method = "bonferroni")
  ) |>
  arrange(outcome, p_value, desc(abs(rho)))

q17_art_regressions <- crossing(
  predictor = correlation_predictors,
  outcome = analysis_outcomes
) |>
  mutate(result = map2(predictor, outcome, ~ safe_lm(analysis_df, .x, .y))) |>
  pull(result) |>
  bind_rows() |>
  mutate(
    p_bh = p.adjust(slope_p_value, method = "BH"),
    p_bonferroni = p.adjust(slope_p_value, method = "bonferroni")
  ) |>
  arrange(outcome, slope_p_value, desc(abs(slope)))

write_csv(q17_art_correlations, file.path(csv_dir, "Q17_AI_Use_vs_ART_Correlations.csv"))
write_csv(q17_art_regressions, file.path(csv_dir, "Q17_AI_Use_vs_ART_Regressions.csv"))
```

```{r}
q17_art_correlations |>
  filter(outcome == "art_net_real_minus_fake") |>
  mutate(
    rho = round(rho, 3),
    p_value = round(p_value, 4),
    p_bh = round(p_bh, 4),
    p_bonferroni = round(p_bonferroni, 4)
  ) |>
  kable()
```

Participants with 20+ regular tools excluded (outlier; n_excluded = `r sum(analysis_df$ai_tools_regular_n > 10)`).

```{r, fig.height=5, fig.width=8}
scatter_df <- analysis_df |> filter(ai_tools_regular_n <= 10)

scatter_cor <- suppressWarnings(
  cor.test(scatter_df$ai_tools_regular_n, scatter_df$art_net_real_minus_fake,
           method = "spearman", exact = FALSE)
)
scatter_label <- glue(
  "\u03c1 = {round(scatter_cor$estimate, 2)}, p = {round(scatter_cor$p.value, 3)} (n = {nrow(scatter_df)})"
)

ggplot(scatter_df, aes(x = ai_tools_regular_n, y = art_net_real_minus_fake)) +
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.7, color = "#3b6a8f") +
  geom_smooth(method = "lm", se = FALSE, color = "#c96b3b", linewidth = 1) +
  annotate("text", x = Inf, y = Inf, label = scatter_label,
           hjust = 1.05, vjust = 1.5, size = 3.5, color = "gray30") +
  labs(
    title = "Broader Regular AI Use vs ART Net Score",
    subtitle = "Higher ART net means more real-author hits minus fake-author false alarms",
    x = "Number of tools used regularly or often",
    y = "ART net score"
  ) +
  theme_minimal(base_size = 12)
```

## Tool-Specific Regular Use vs ART

```{r}
tool_specific_art <- q17_clean |>
  inner_join(
    art_scores |>
      select(participant_id, art_net_real_minus_fake, art_real_hits, art_fake_false_alarms, art_adjusted_rate),
    by = "participant_id"
  )

tool_regular_use_summary <- tool_specific_art |>
  group_by(tool) |>
  group_modify(~ summarize_tool_relationship(.x, "art_net_real_minus_fake")) |>
  ungroup() |>
  mutate(
    use_score_p_bh = p.adjust(use_score_p_value, method = "BH"),
    use_score_p_bonferroni = p.adjust(use_score_p_value, method = "bonferroni"),
    wilcox_p_bh = p.adjust(wilcox_p_value, method = "BH"),
    wilcox_p_bonferroni = p.adjust(wilcox_p_value, method = "bonferroni")
  ) |>
  arrange(desc(n_regular), desc(art_diff_regular_minus_non))

tool_score_vs_art_summary <- tool_specific_art |>
  group_by(tool) |>
  group_modify(~ summarize_tool_relationship(.x, "art_adjusted_rate")) |>
  ungroup() |>
  mutate(
    use_score_p_bh = p.adjust(use_score_p_value, method = "BH"),
    use_score_p_bonferroni = p.adjust(use_score_p_value, method = "bonferroni"),
    wilcox_p_bh = p.adjust(wilcox_p_value, method = "BH"),
    wilcox_p_bonferroni = p.adjust(wilcox_p_value, method = "bonferroni")
  ) |>
  arrange(desc(n_regular), desc(art_diff_regular_minus_non))

write_csv(tool_regular_use_summary, file.path(csv_dir, "Q17_Tool_RegularUse_vs_ART.csv"))
write_csv(tool_score_vs_art_summary, file.path(csv_dir, "Q17_Tool_RegularUse_vs_AdjustedART.csv"))
```

This section focuses on whether people who use a specific tool **regularly** (`sometimes` or `often`) tend to have higher or lower ART scores than everyone else. For these comparisons, lower values mean a weaker ART reading-exposure proxy, not "dumber" in any absolute sense.

```{r}
tool_regular_use_summary |>
  filter(tool %in% model_focus) |>
  select(
    tool,
    n_regular,
    regular_use_pct,
    mean_art_regular,
    mean_art_non_regular,
    art_diff_regular_minus_non,
    use_score_rho,
    use_score_p_value,
    use_score_p_bh,
    wilcox_p_value,
    wilcox_p_bh
  ) |>
  mutate(
    regular_use_pct = percent(regular_use_pct, accuracy = 0.1),
    across(
      c(mean_art_regular, mean_art_non_regular, art_diff_regular_minus_non, use_score_rho),
      ~ round(.x, 2)
    ),
    across(c(use_score_p_value, use_score_p_bh, wilcox_p_value, wilcox_p_bh), ~ round(.x, 4))
  ) |>
  kable()
```

```{r, fig.height=6.5, fig.width=9.5}
bar_data <- tool_regular_use_summary |>
  filter(n_regular >= 5) |>
  slice_max(order_by = n_regular, n = 10, with_ties = FALSE) |>
  mutate(
    tool = fct_reorder(tool, art_diff_regular_minus_non),
    stat_label = glue("\u03c1={round(use_score_rho, 2)}, p={round(use_score_p_value, 3)}")
  )

ggplot(bar_data, aes(x = art_diff_regular_minus_non, y = tool, fill = art_diff_regular_minus_non > 0)) +
  geom_col() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  geom_text(
    aes(
      x = if_else(art_diff_regular_minus_non >= 0,
                  art_diff_regular_minus_non + 0.05,
                  art_diff_regular_minus_non - 0.05),
      label = stat_label,
      hjust = if_else(art_diff_regular_minus_non >= 0, 0, 1)
    ),
    size = 3, color = "gray25"
  ) +
  scale_fill_manual(values = c("TRUE" = "#4f7c5f", "FALSE" = "#c96b3b"), guide = "none") +
  labs(
    title = "ART Difference for Regular Users of Each Tool",
    subtitle = "Mean ART net score among regular users minus mean ART net score among everyone else",
    x = "ART net difference",
    y = NULL
  ) +
  theme_minimal(base_size = 12)
```

```{r, fig.height=8, fig.width=10}
# Pull rho/p for focus tools to use as facet annotations
facet_stats <- tool_regular_use_summary |>
  filter(tool %in% model_focus) |>
  transmute(
    tool,
    facet_label = glue("{tool}\n\u03c1={round(use_score_rho, 2)}, p={round(use_score_p_value, 3)}")
  )

tool_specific_art |>
  filter(tool %in% model_focus) |>
  left_join(facet_stats, by = "tool") |>
  mutate(
    regular_use = if_else(use_score >= 4L, "Regular user", "Not regular"),
    facet_label = fct_relevel(facet_label, facet_stats$facet_label[match(model_focus, facet_stats$tool)])
  ) |>
  ggplot(aes(x = regular_use, y = art_net_real_minus_fake, fill = regular_use)) +
  geom_boxplot(alpha = 0.7, outlier.shape = NA) +
  geom_jitter(width = 0.15, alpha = 0.6, size = 1.6) +
  facet_wrap(~ facet_label, scales = "free_x") +
  scale_fill_manual(values = c("Regular user" = "#c96b3b", "Not regular" = "#d7ddd3")) +
  labs(
    title = "ART Net Score by Regular Use of Specific Tools",
    subtitle = "Facet headers show Spearman \u03c1 (use_score vs ART net) and p-value",
    x = NULL,
    y = "ART net score",
    fill = NULL
  ) +
  theme_minimal(base_size = 11) +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

## Quick Read

```{r}
top_net_patterns <- tool_regular_use_summary |>
  filter(tool %in% model_focus) |>
  arrange(art_diff_regular_minus_non) |>
  select(tool, n_regular, art_diff_regular_minus_non, wilcox_p_value, wilcox_p_bh) |>
  slice_head(n = 5)

top_net_patterns |>
  mutate(
    art_diff_regular_minus_non = round(art_diff_regular_minus_non, 2),
    wilcox_p_value = round(wilcox_p_value, 4),
    wilcox_p_bh = round(wilcox_p_bh, 4)
  ) |>
  kable()
```

The clearest overall pattern here is that **broader regular AI use** tends to line up with somewhat lower `ART` proxy scores. Tool-by-tool results should be interpreted more cautiously because some tools have small regular-user counts, but the regular-use tables and plots above make those cases easy to inspect directly.

## Output Files

```{r q17-manifest}
q17_manifest <- tibble(
  output_type = c(
    "art_scored",
    "art_unmatched",
    "q17_submission_resolution",
    "q17_tool_popularity",
    "q17_participant_ai_use_index",
    "q17_art_merged",
    "q17_summary",
    "q17_art_correlations",
    "q17_art_regressions",
    "q17_tool_regular_use_vs_art",
    "q17_tool_regular_use_vs_adjusted_art"
  ),
  file = c(
    "ART_Scored.csv",
    "ART_Unmatched_Names.csv",
    "Q17_Submission_Resolution.csv",
    "Q17_Tool_Popularity.csv",
    "Q17_Participant_AI_Use_Index.csv",
    "Q17_AI_Use_vs_ART_Merged.csv",
    "Q17_AI_Use_vs_ART_Summary.csv",
    "Q17_AI_Use_vs_ART_Correlations.csv",
    "Q17_AI_Use_vs_ART_Regressions.csv",
    "Q17_Tool_RegularUse_vs_ART.csv",
    "Q17_Tool_RegularUse_vs_AdjustedART.csv"
  ),
  description = c(
    "ART net scores, hit rates, and false-alarm rates per participant",
    "ART author selections that could not be matched to the answer key",
    "Q17 duplicate-submission resolution: best submission per participant",
    "Q17 AI tool popularity summary (ever-used and regular-use rates)",
    "Per-participant AI use indices (number of tools heard/used/regularly used)",
    "Merged Q17 AI use indices and ART scores (analysis-ready)",
    "Summary table: sample sizes and top-tool statistics",
    "Spearman correlations: AI use predictors vs ART outcomes",
    "OLS regressions: AI use predictors vs ART outcomes",
    "Tool-specific regular-use group vs ART net score comparison",
    "Tool-specific regular-use group vs adjusted ART rate comparison"
  )
)

write_csv(q17_manifest, file.path(csv_dir, "Q17_Export_Manifest.csv"))
kable(q17_manifest, caption = "Q17 AI Use Analysis — Output Manifest")
```
