---
title: "AI Beliefs Item-Level Order Effects Analysis"
format:
  html:
    toc: true
    toc-depth: 2
output-dir: "08_ai_beliefs_items"
execute:
  echo: false
  warning: false
  message: false
editor:
  markdown:
    wrap: 72
---

# AI Beliefs Item-Level Analysis

This script performs exploratory item-level analysis on the
BeliefsAboutAI instrument (22 items, 1–5 Likert scale). The instrument
had a KMO of \~0.26 and was not factorable as a whole. Rather than
forcing a composite score, this script analyzes each item individually,
organized by thematic grouping, and compares Traditional-First vs
AI-First participants.

Note: Item 1 ("I have used generative AI technologies like ChatGPT") is
a screening/categorical item and is excluded from inferential tests but
retained for descriptive reference.

```{r setup}
library(tidyverse)
library(knitr)
library(ggplot2)
source("scoring_helpers.R", local = knitr::knit_global())

# ── Output directories ────────────────────────────────────────────────────────
script_dir <- "08_ai_beliefs_items"
csv_dir    <- file.path(script_dir, "csv")
plot_dir   <- file.path(script_dir, "plots")
master_wide_file <- file.path("02_efa_exports", "Final_Master_Wide.csv")
dir.create(csv_dir,  recursive = TRUE, showWarnings = FALSE)
dir.create(plot_dir, recursive = TRUE, showWarnings = FALSE)

# ── Constants ─────────────────────────────────────────────────────────────────
order_levels   <- c("Traditional_First", "AI_First")
likert_levels  <- 1:5
likert_labels  <- c(
  "1" = "Strongly Disagree",
  "2" = "Disagree",
  "3" = "Neutral",
  "4" = "Agree",
  "5" = "Strongly Agree"
)

# Analysis-column indices of reverse-scored items (Beliefs_16 through Beliefs_19).
# These correspond to Qualtrics items 17-20; the screening item was excluded
# upstream, shifting the numbering by one. Reverse-scoring is already applied
# by score_beliefs_items() in scoring_helpers.R (which uses original Qualtrics
# numbers 17-20). Do NOT call score_beliefs_items() with these column indices.
beliefs_reversed_analysis_cols <- c(16L, 17L, 18L, 19L)

# Screening item ("I have used generative AI...") was excluded upstream by
# score_beliefs_items() — it does not appear in master_wide. All 22 Beliefs_
# columns are inferential. No screening_item exclusion needed here.

# Total number of Beliefs items
n_beliefs_items <- 22L
```

## Section 1: Item Metadata and Thematic Groupings

```{r item-metadata}
# ── Item text ─────────────────────────────────────────────────────────────────
# Beliefs_1 = Qualtrics Q2: screening item ("I have used generative AI...")
# was excluded upstream by score_beliefs_items(). item_text starts at Q3 = Beliefs_1.
item_text <- c(
  "I understand generative AI technologies like ChatGPT have limitations in their ability to handle complex tasks",
  "I understand generative AI technologies like ChatGPT can generate output that is factually inaccurate",
  "I understand generative AI technologies like ChatGPT can generate output that is out of context or inappropriate",
  "I understand generative AI technologies like ChatGPT can exhibit biases and unfairness in their output",
  "I understand generative AI technologies like ChatGPT have limited emotional intelligence and empathy, which can lead to output that is insensitive or inappropriate",
  "Students must learn how to use generative AI technologies well for their career",
  "I believe generative AI technologies such as ChatGPT can improve my digital competence",
  "I believe generative AI technologies such as ChatGPT can improve my overall academic performance",
  "I think generative AI technologies such as ChatGPT can help me become a better writer",
  "I can ask questions to generative AI technologies such as ChatGPT that I would otherwise not voice out to my teacher",
  "Generative AI technologies such as ChatGPT will not judge me, so I feel comfortable with it",
  "I think AI technologies such as ChatGPT is a great tool for student support services due to anonymity",
  "I believe generative AI technologies such as ChatGPT can help me save time",
  "I believe AI technologies such as ChatGPT can provide me with unique insights and perspectives that I may not have thought of myself",
  "I think AI technologies such as ChatGPT can provide me with personalized and immediate feedback and suggestions for my assignments",
  "I think AI technologies such as ChatGPT is a great tool as it is available 24/7",
  "Using generative AI technologies such as ChatGPT to complete assignments undermines the value of a university education",
  "Generative AI technologies such as ChatGPT will limit my opportunities to interact with others and socialize while completing coursework",
  "Generative AI technologies such as ChatGPT will hinder my development of generic or transferable skills such as teamwork, problem-solving, and leadership skills",
  "I can become over-reliant on generative AI technologies",
  "The integration of generative AI technologies like ChatGPT in higher education will have a positive impact on teaching and learning in the long run",
  "I envision integrating generative AI technologies like ChatGPT into my teaching and learning practices in the future"
)

stopifnot(
  "item_text length must equal n_beliefs_items" = length(item_text) == n_beliefs_items
)

# ── Thematic groupings ────────────────────────────────────────────────────────
# item_num = Beliefs_ column index (1–22). No screening item — excluded upstream.
# item_num here = Beliefs_ column index (1-22), not Qualtrics question number.
# Screening item excluded upstream; themes shifted accordingly.
item_themes <- tribble(
  ~item_num, ~theme,
  1L,  "AI Literacy and Limitations",
  2L,  "AI Literacy and Limitations",
  3L,  "AI Literacy and Limitations",
  4L,  "AI Literacy and Limitations",
  5L,  "AI Literacy and Limitations",
  6L,  "Academic Utility",
  7L,  "Academic Utility",
  8L,  "Academic Utility",
  9L,  "Academic Utility",
  10L, "Psychological Comfort and Anonymity",
  11L, "Psychological Comfort and Anonymity",
  12L, "Psychological Comfort and Anonymity",
  13L, "Practical Convenience",
  14L, "Practical Convenience",
  15L, "Practical Convenience",
  16L, "Practical Convenience",
  17L, "Risks and Concerns",
  18L, "Risks and Concerns",
  19L, "Risks and Concerns",
  20L, "Risks and Concerns",
  21L, "Future Integration",
  22L, "Future Integration"
)

# Build full item metadata table
item_metadata <- tibble(
  item_num  = seq_len(n_beliefs_items),
  item_col  = paste0("Beliefs_", seq_len(n_beliefs_items)),
  item_text = item_text,
  reversed  = item_num %in% beliefs_reversed_analysis_cols,
  inferential = TRUE  # screening item excluded upstream; all 22 cols are inferential
) |>
  left_join(item_themes, by = "item_num") |>
  mutate(
    theme = factor(theme, levels = c(
      "AI Literacy and Limitations",
      "Academic Utility",
      "Psychological Comfort and Anonymity",
      "Practical Convenience",
      "Risks and Concerns",
      "Future Integration"
    )),
    item_label = paste0("Item ", item_num, ": ", item_text)
  )

write_csv(item_metadata, file.path(csv_dir, "AIBeliefs_Item_Metadata.csv"))
kable(item_metadata |> select(item_num, theme, reversed, inferential, item_text),
      caption = "AIBeliefs Item Metadata")
```

## Section 2: Load and Prepare Data

```{r load-data}
master_wide <- read_csv(master_wide_file, show_col_types = FALSE)

# ── Validate required columns ─────────────────────────────────────────────────
# master_wide carries order, condition_1, condition_2 from the imi_wide pivot
# in 02_efa_exports.qmd — no need to re-derive from the tracking file.
required_master <- c("participant_id", "order", "condition_1", "condition_2")
missing_master  <- setdiff(required_master, names(master_wide))
if (length(missing_master) > 0) {
  stop(paste0(master_wide_file, " missing columns: ",
              paste(missing_master, collapse = ", ")), call. = FALSE)
}

beliefs_cols <- paste0("Beliefs_", seq_len(n_beliefs_items))
missing_beliefs <- setdiff(beliefs_cols, names(master_wide))
if (length(missing_beliefs) > 0) {
  stop(paste0(master_wide_file, " missing Beliefs item columns: ",
              paste(missing_beliefs, collapse = ", ")), call. = FALSE)
}

# ── Filter to participants with a valid order assignment ─────────────────────
# Reverse scoring for items 17-20 is already applied by score_beliefs_items()
# in scoring_helpers.R upstream. Do NOT re-reverse here.
analysis_data <- master_wide |>
  mutate(
    participant_id = as.character(participant_id),
    order          = factor(order, levels = order_levels)
  ) |>
  filter(!is.na(order))

assert_expected_count(nrow(analysis_data), 82L, "AIBeliefs analysis participant count")
assert_unique_pid_rows(analysis_data, "participant_id", "AIBeliefs analysis_data")
assert_allowed_values(analysis_data$order, order_levels, "AIBeliefs order")

n_participants <- nrow(analysis_data)
n_trad_first   <- sum(analysis_data$order == "Traditional_First", na.rm = TRUE)
n_ai_first     <- sum(analysis_data$order == "AI_First",          na.rm = TRUE)

cat(glue::glue(
  "Participants retained: {n_participants}  ",
  "(Traditional-First: {n_trad_first}, AI-First: {n_ai_first})\n"
))
```

## Section 3: Long Format for Item-Level Analysis

```{r pivot-long}
beliefs_long <- analysis_data |>
  select(participant_id, order, all_of(beliefs_cols)) |>
  pivot_longer(
    cols      = all_of(beliefs_cols),
    names_to  = "item_col",
    values_to = "response"
  ) |>
  mutate(
    item_num  = as.integer(str_remove(item_col, "Beliefs_")),
    response  = as.integer(response)
  ) |>
  left_join(item_metadata |> select(item_num, item_text, theme, reversed,
                                     inferential, item_label),
            by = "item_num") |>
  filter(!is.na(response))

write_csv(beliefs_long, file.path(csv_dir, "AIBeliefs_Long.csv"))
```

## Section 4: Descriptives by Order Group

```{r descriptives}

item_descriptives <- beliefs_long |>
  filter(inferential) |>
  group_by(theme, item_num, item_col, item_text, order) |>
  summarise(
    n      = sum(!is.na(response)),
    mean   = round(mean(response, na.rm = TRUE), 2),
    sd     = round(sd(response,   na.rm = TRUE), 2),
    median = median(response,     na.rm = TRUE),
    iqr    = IQR(response,        na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(theme, item_num, order)

write_csv(item_descriptives, file.path(csv_dir, "AIBeliefs_Item_Descriptives.csv"))
kable(item_descriptives, caption = "Item-Level Descriptives by Order Group")
```

## Section 5: Diverging Stacked Bar Charts by Theme

```{r diverging-bar-charts, fig.width=12, fig.height=7}

# ── Helper: build diverging stacked bar data ──────────────────────────────────
make_diverging_data <- function(long_data) {
  long_data |>
    filter(!is.na(response)) |>
    mutate(
      response_label = factor(
        likert_labels[as.character(response)],
        levels = rev(unname(likert_labels))
      ),
      # Disagree responses are negative, Agree responses are positive
      direction = case_when(
        response %in% c(1, 2) ~ "disagree",
        response == 3         ~ "neutral",
        response %in% c(4, 5) ~ "agree"
      )
    ) |>
    count(item_num, item_label, order, response, response_label, direction) |>
    group_by(item_num, order) |>
    mutate(pct = n / sum(n) * 100) |>
    ungroup() |>
    mutate(
      pct_diverging = case_when(
        response %in% c(1, 2) ~ -pct,
        response == 3         ~ pct * 0.5,  # neutrals split at center
        response %in% c(4, 5) ~ pct
      )
    )
}

diverging_colors <- c(
  "Strongly Disagree" = "#d73027",
  "Disagree"          = "#f46d43",
  "Neutral"           = "#ffffbf",
  "Agree"             = "#74add1",
  "Strongly Agree"    = "#313695"
)

theme_list <- item_metadata |>
  filter(inferential) |>
  pull(theme) |>
  unique() |>
  as.character()

# Build all theme plots and collect them, then write a single combined PDF.
# str_wrap on item_label keeps long Likert statements readable on the y-axis.
all_theme_plots <- list()

for (thm in theme_list) {
  theme_items <- item_metadata |>
    filter(theme == thm, inferential) |>
    pull(item_num)

  plot_data <- beliefs_long |>
    filter(item_num %in% theme_items, inferential) |>
    make_diverging_data() |>
    mutate(item_label = str_wrap(item_label, width = 55))

  if (nrow(plot_data) == 0) next

  # item_label factor levels must be rebuilt after str_wrap so reorder() works
  label_order <- plot_data |>
    distinct(item_num, item_label) |>
    arrange(item_num) |>
    pull(item_label)

  plot_data <- plot_data |>
    mutate(item_label = factor(item_label, levels = rev(label_order)))

  p <- ggplot(plot_data, aes(
      x    = item_label,
      y    = pct_diverging,
      fill = response_label
    )) +
    geom_col(position = "stack", width = 0.7) +
    geom_hline(yintercept = 0, color = "grey30", linewidth = 0.4) +
    coord_flip() +
    facet_wrap(~ order, ncol = 2) +
    scale_fill_manual(
      values = diverging_colors,
      breaks = names(diverging_colors),
      name   = NULL
    ) +
    scale_y_continuous(
      labels = function(x) paste0(abs(x), "%"),
      limits = c(-100, 100)
    ) +
    labs(
      title    = paste0("AI Beliefs — ", thm),
      subtitle = "Traditional-First vs AI-First  |  Reversed items rescored",
      x        = NULL,
      y        = "← Disagree   |   Agree →",
      caption  = "Note: Neutral responses (3) split at center"
    ) +
    theme_minimal(base_size = 11) +
    theme(
      legend.position  = "bottom",
      strip.text       = element_text(face = "bold"),
      panel.grid.minor = element_blank(),
      plot.title       = element_text(face = "bold"),
      axis.text.y      = element_text(lineheight = 0.85)
    )

  all_theme_plots[[thm]] <- list(plot = p, n_items = length(theme_items))
  print(p)
}

# Single combined PDF — one page per theme.
# cairo_pdf supports Unicode and embeds fonts cleanly.
# Height is fixed at 9in which comfortably fits up to 6 items with wrapped labels.
pdf_path <- file.path(plot_dir, "AIBeliefs_Diverging_Bar_All_Themes.pdf")
grDevices::cairo_pdf(pdf_path, width = 14, height = 9, onefile = TRUE)
for (obj in all_theme_plots) {
  print(obj$plot)
}
dev.off()
cat("Exported: AIBeliefs_Diverging_Bar_All_Themes.pdf\n")
```

Secret section:

```{r}
if (requireNamespace("ggridges", quietly = TRUE)) {
  library(ggridges)

  all_theme_plots <- list()

  for (thm in theme_list) {
    theme_items <- item_metadata |>
      filter(theme == thm, inferential) |>
      pull(item_num)

    plot_data <- beliefs_long |>
      filter(item_num %in% theme_items, inferential, !is.na(response)) |>
      mutate(
        item_label = str_wrap(item_label, width = 55),
        item_label = factor(item_label,
          levels = rev(
            beliefs_long |>
              filter(item_num %in% theme_items) |>
              distinct(item_num, item_label) |>
              mutate(item_label = str_wrap(item_label, width = 55)) |>
              arrange(item_num) |>
              pull(item_label)
          )
        ),
        response = as.numeric(response)
      )

    if (nrow(plot_data) == 0) next

    n_items <- length(theme_items)

    p <- ggplot(plot_data, aes(
        x     = response,
        y     = item_label,
        fill  = order,
        color = order
      )) +
      geom_density_ridges(
        aes(height = after_stat(density)),
        stat           = "density",
        alpha          = 0.45,
        scale          = min(0.85, 0.5 + 0.07 * n_items),
        bandwidth      = 0.6,
        rel_min_height = 0.01
      ) +
      scale_x_continuous(
        breaks = 1:5,
        labels = unname(likert_labels[as.character(1:5)]),
        limits = c(0.5, 5.5)
      ) +
      scale_fill_manual(values  = c("Traditional_First" = "#4f7c5f", "AI_First" = "#c96b3b")) +
      scale_color_manual(values = c("Traditional_First" = "#4f7c5f", "AI_First" = "#c96b3b")) +
      labs(
        title    = paste0("AI Beliefs — ", thm),
        subtitle = "Response distributions by condition  |  Reversed items rescored",
        x        = NULL,
        y        = NULL,
        fill     = NULL,
        color    = NULL,
        caption  = "Bandwidth = 0.6 on 1–5 ordinal scale. Bimodal ridges = polarized item."
      ) +
      theme_minimal(base_size = 11) +
      theme(
        legend.position  = "bottom",
        panel.grid.minor = element_blank(),
        plot.title       = element_text(face = "bold"),
        axis.text.y      = element_text(lineheight = 0.85),
        axis.text.x      = element_text(size = 8)
      )

    all_theme_plots[[thm]] <- list(plot = p, n_items = n_items)
    print(p)
  }

  pdf_path <- file.path(plot_dir, "AIBeliefs_Ridgeline_All_Themes.pdf")
  grDevices::cairo_pdf(pdf_path, width = 12, height = 11, onefile = TRUE)
  for (obj in all_theme_plots) print(obj$plot)
  dev.off()
  cat("Exported: AIBeliefs_Ridgeline_All_Themes.pdf\n")
} else {
  cat("Skipping AIBeliefs ridgeline export because ggridges is not installed.\n")
}
```

## Section 6: Mann-Whitney U Tests Per Item

**Multiple-comparison correction strategy:** All 22 inferential Beliefs
items form a single correction family. BH controls the false discovery
rate across items; Bonferroni controls the family-wise error rate. Both
are reported to let the reader choose the appropriate threshold for
their interpretive goals.

```{r mann-whitney}

# Sign convention: positive rb -> group 1 (Traditional-First) tends higher.
# wilcox.test(response ~ order) returns W for the first factor level of
# order, which is "Traditional_First" (set by order_levels on line 43).
# If order_levels changes, this convention flips silently.
rank_biserial_from_w <- function(w_stat, n1, n2) {
  u_stat <- as.numeric(w_stat) - (n1 * (n1 + 1) / 2)
  (2 * u_stat / (n1 * n2)) - 1
}

mw_results <- map_dfr(
  item_metadata |> filter(inferential) |> pull(item_num),
  function(inum) {
    col <- paste0("Beliefs_", inum)

    dat <- beliefs_long |>
      filter(item_num == inum, !is.na(response), !is.na(order)) |>
      mutate(order = factor(order, levels = order_levels))

    grp_counts <- dat |> count(order, name = "n")
    n_trad <- grp_counts |> filter(order == "Traditional_First") |> pull(n)
    n_ai   <- grp_counts |> filter(order == "AI_First")          |> pull(n)
    n_trad <- if (length(n_trad) == 0) 0L else n_trad
    n_ai   <- if (length(n_ai)   == 0) 0L else n_ai

    med_trad <- dat |> filter(order == "Traditional_First") |>
      summarise(v = median(response, na.rm = TRUE)) |> pull(v)
    med_ai <- dat |> filter(order == "AI_First") |>
      summarise(v = median(response, na.rm = TRUE)) |> pull(v)

    theme_val <- item_metadata |>
      filter(item_num == inum) |>
      pull(theme) |>
      as.character()

    if (n_trad < 2 || n_ai < 2) {
      return(tibble(
        item_num                 = inum,
        item_col                 = col,
        theme                    = theme_val,
        n_traditional_first      = n_trad,
        n_ai_first               = n_ai,
        median_traditional_first = med_trad,
        median_ai_first          = med_ai,
        w_stat                   = NA_real_,
        u_stat                   = NA_real_,
        p_value                  = NA_real_,
        rank_biserial            = NA_real_,
        note                     = "insufficient sample size"
      ))
    }

    test <- suppressWarnings(
      wilcox.test(
        response ~ order,
        data      = dat,
        exact     = FALSE,
        conf.int  = FALSE
      )
    )

    w  <- unname(test$statistic)
    u  <- as.numeric(w) - (n_trad * (n_trad + 1) / 2)
    rb <- rank_biserial_from_w(w, n_trad, n_ai)

    tibble(
      item_num                 = inum,
      item_col                 = col,
      theme                    = theme_val,
      n_traditional_first      = n_trad,
      n_ai_first               = n_ai,
      median_traditional_first = med_trad,
      median_ai_first          = med_ai,
      w_stat                   = as.numeric(w),
      u_stat                   = as.numeric(u),
      p_value                  = test$p.value,
      rank_biserial            = rb,
      note                     = NA_character_
    )
  }
) |>
  mutate(
    p_bh         = p.adjust(p_value, method = "BH"),
    p_bonferroni = p.adjust(p_value, method = "bonferroni")
  ) |>
  left_join(
    item_metadata |> select(item_num, item_text, reversed),
    by = "item_num"
  ) |>
  arrange(theme, p_bh, p_value)

write_csv(mw_results, file.path(csv_dir, "AIBeliefs_MannWhitney_Results.csv"))

kable(
  mw_results |>
    select(item_num, theme, item_text, median_traditional_first,
           median_ai_first, w_stat, p_value, p_bh, rank_biserial, note),
  digits  = 3,
  caption = "Mann-Whitney U Results by Item (BH-corrected), organized by theme"
)
```

## Section 7: Effect Size Summary

```{r effect-size-summary}

# Flag items with meaningful effect sizes regardless of p-value
# At small N, rank-biserial |r| >= 0.3 is worth noting
effect_summary <- mw_results |>
  filter(!is.na(rank_biserial)) |>
  mutate(
    effect_magnitude = case_when(
      abs(rank_biserial) >= 0.5 ~ "Large",
      abs(rank_biserial) >= 0.3 ~ "Medium",
      abs(rank_biserial) >= 0.1 ~ "Small",
      TRUE                      ~ "Negligible"
    ),
    direction = case_when(
      rank_biserial > 0  ~ "Traditional-First scored higher",
      rank_biserial < 0  ~ "AI-First scored higher",
      rank_biserial == 0 ~ "No difference"
    ),
    contrast_hypothesis_relevant = item_num %in% c(8L, 9L, 10L, 16L, 18L, 19L, 21L)
  ) |>
  select(theme, item_num, item_text, rank_biserial,
         effect_magnitude, direction,
         p_bh, contrast_hypothesis_relevant) |>
  arrange(desc(abs(rank_biserial)))

write_csv(effect_summary, file.path(csv_dir, "AIBeliefs_Effect_Size_Summary.csv"))

kable(
  effect_summary,
  digits  = 3,
  caption = "Effect Size Summary — items flagged for contrast hypothesis relevance"
)
```

## Section 8: Consolidated Item Summary Table

```{r consolidated-summary}


# One-stop table: every item, all key stats, sorted by theme then effect size.
# median_diff = median_traditional_first - median_ai_first (positive = Trad higher)
# mw_results already carries theme from its own left_join in Section 6.
# A second join here would collide into theme.x/theme.y — drop it.
consolidated_summary <- mw_results |>
  mutate(
    median_diff      = median_traditional_first - median_ai_first,
    effect_magnitude = case_when(
      is.na(rank_biserial)           ~ NA_character_,
      abs(rank_biserial) >= 0.5      ~ "Large",
      abs(rank_biserial) >= 0.3      ~ "Medium",
      abs(rank_biserial) >= 0.1      ~ "Small",
      TRUE                           ~ "Negligible"
    ),
    sig_bh = case_when(
      is.na(p_bh)  ~ "",
      p_bh < 0.001 ~ "***",
      p_bh < 0.01  ~ "**",
      p_bh < 0.05  ~ "*",
      TRUE         ~ ""
    )
  ) |>
  select(
    theme, item_num, item_text,
    median_traditional_first, median_ai_first, median_diff,
    rank_biserial, effect_magnitude,
    p_value, p_bh, sig_bh
  ) |>
  arrange(theme, item_num)

write_csv(consolidated_summary, file.path(csv_dir, "AIBeliefs_Consolidated_Summary.csv"))

kable(
  consolidated_summary |>
    transmute(
      Theme    = theme,
      Item     = item_num,
      Text     = str_trunc(item_text, 70),
      `Mdn Trad` = median_traditional_first,
      `Mdn AI`   = median_ai_first,
      `Δ Mdn`    = median_diff,
      `r_rb`     = round(rank_biserial, 3),
      Magnitude  = effect_magnitude,
      `p (raw)`  = round(p_value, 3),
      `p (BH)`   = round(p_bh, 3),
      Sig        = sig_bh
    ),
  caption = "Consolidated Item Summary — sorted by theme and item number"
)
```

## Section 9: Export Manifest

```{r manifest}

manifest <- tibble(
  output_type = c(
    "item_metadata",
    "long_format",
    "descriptives",
    "mann_whitney",
    "effect_summary",
    "consolidated_summary"
  ),
  file = c(
    "AIBeliefs_Item_Metadata.csv",
    "AIBeliefs_Long.csv",
    "AIBeliefs_Item_Descriptives.csv",
    "AIBeliefs_MannWhitney_Results.csv",
    "AIBeliefs_Effect_Size_Summary.csv",
    "AIBeliefs_Consolidated_Summary.csv"
  )
)

write_csv(manifest, file.path(csv_dir, "AIBeliefs_Export_Manifest.csv"))
kable(manifest)
```
