---
title: "ART vs All Factors and Item Statements"
format:
  html:
    toc: true
    toc-depth: 2
output-dir: "09_art_vs_all_factors_items"
execute:
  echo: false
  warning: false
  message: false
editor: 
  markdown: 
    wrap: 72
---

This report extends the `Q17` side-analysis by using `ART` (Author
Recognition Test) as the anchor variable across the rest of the survey.
It does two things:

1.  correlates ART outcomes with factor scores from the three
    instruments that supported factor models (`IMI`, `WritingEfficacy`,
    `AIReflection`)
2.  correlates ART outcomes with all individual item statements across
    the four cleaned survey instruments (`IMI`, `WritingEfficacy`,
    `AIReflection`, `BeliefsAboutAI`)

`BeliefsAboutAI` remains item-only here because it did not support a
clean factor solution in the main EFA workflow.

```{r setup}
library(tidyverse)
library(psych)
library(glue)
library(knitr)
library(forcats)
source("scoring_helpers.R", local = knitr::knit_global())

set.seed(42L)
```

## Setup

```{r config}
script_dir <- "09_art_vs_all_factors_items"
csv_dir <- file.path(script_dir, "csv")
plot_dir <- file.path(script_dir, "plots")
recommended_k_file <- file.path("03_efa_analysis", "EFA_Recommended_K.csv")
art_clean_file <- file.path("01_audit_cleaning", "cleaned", "AuthorRecognition_cleaned.csv")
dir.create(csv_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(plot_dir, recursive = TRUE, showWarnings = FALSE)

factor_score_method <- "tenBerge"
min_correlation_sample_size <- 10L

art_metric_lookup <- tribble(
  ~art_metric, ~art_label, ~metric_role,
  "art_net_real_minus_fake", "ART net real minus fake", "Primary",
  "art_adjusted_rate", "ART adjusted rate", "Secondary",
  "art_real_hits", "ART real hits", "Component",
  "art_fake_false_alarms", "ART fake false alarms", "Component"
)

factor_name_map <- tribble(
  ~instrument, ~factor_num, ~proposed_name,
  "IMI", 1L, "Interest & Enjoyment",
  "IMI", 2L, "Effort & Importance",
  "IMI", 3L, "Perceived Competence",
  "WritingEfficacy", 1L, "Writing Competence",
  "WritingEfficacy", 2L, "Self-Regulation",
  "WritingEfficacy", 3L, "Resource & Planning",
  "AIReflection", 1L, "Ownership & Usefulness",
  "AIReflection", 2L, "Enjoyment & Satisfaction"
)

factor_instrument_specs <- tribble(
  ~instrument, ~file, ~item_id_col, ~score_transform, ~prefix,
  "IMI", file.path("02_efa_exports", "efa", "IMI_EFA_Primary.csv"), "item_code", "identity", "IMI",
  "WritingEfficacy", file.path("02_efa_exports", "efa", "WritingEfficacy_EFA_Primary.csv"), "item_code", "wse_to_5", "WSE",
  "AIReflection", file.path("02_efa_exports", "efa", "AI_Reflection_EFA_Primary.csv"), "item_num", "identity", "AIRefl"
)

item_instrument_specs <- tribble(
  ~instrument, ~file, ~item_id_col, ~score_transform, ~prefix,
  "IMI", file.path("01_audit_cleaning", "cleaned", "IMI_cleaned.csv"), "item_code", "identity", "IMI",
  "WritingEfficacy", file.path("01_audit_cleaning", "cleaned", "WritingEfficacy_cleaned.csv"), "item_code", "wse_to_5", "Efficacy",
  "AIReflection", file.path("01_audit_cleaning", "cleaned", "AI_Reflection_cleaned.csv"), "item_num", "identity", "Refl",
  "BeliefsAboutAI", file.path("01_audit_cleaning", "cleaned", "BeliefsAboutAI_cleaned.csv"), "item_num", "identity", "Beliefs"
)

recommended_k_raw <- read_csv(recommended_k_file, show_col_types = FALSE)

required_k_cols <- c("instrument", "recommended_k", "factorability_flag")
missing_k_cols <- setdiff(required_k_cols, names(recommended_k_raw))
if (length(missing_k_cols) > 0) {
  stop(
    paste0(
      recommended_k_file, " is missing required columns: ",
      paste(missing_k_cols, collapse = ", ")
    ),
    call. = FALSE
  )
}

valid_factor_specs <- factor_instrument_specs |>
  left_join(
    recommended_k_raw |>
      transmute(
        instrument,
        recommended_k = as.integer(recommended_k),
        factorability_flag = as.character(factorability_flag)
      ),
    by = "instrument"
  ) |>
  filter(!is.na(recommended_k))
```

## Helper Functions

```{r helpers}
normalize_text <- function(x) {
  x |>
    str_replace_all("[\u2018\u2019]", "'") |>
    str_replace_all("[\u201C\u201D]", "\"") |>
    str_squish()
}

transform_scores <- function(x, transform_name) {
  values <- as.numeric(x)

  if (transform_name == "identity") {
    return(values)
  }

  if (transform_name == "wse_to_5") {
    return(case_when(
      is.na(values) ~ NA_real_,
      values %in% c(0, 25, 50, 75, 100) ~ (values / 25) + 1,
      TRUE ~ NA_real_
    ))
  }

  stop(glue("Unknown score transform: {transform_name}"))
}

safe_spearman <- function(data, predictor, outcome) {
  dat <- data |>
    select(all_of(c(predictor, outcome))) |>
    filter(if_all(everything(), ~ !is.na(.x)))

  if (nrow(dat) < min_correlation_sample_size ||
      dplyr::n_distinct(dat[[predictor]]) < 2L ||
      dplyr::n_distinct(dat[[outcome]]) < 2L) {
    return(tibble(
      predictor = predictor,
      outcome = outcome,
      n = nrow(dat),
      rho = NA_real_,
      p_value = NA_real_,
      note = "insufficient variation or sample size"
    ))
  }

  test <- suppressWarnings(
    cor.test(dat[[predictor]], dat[[outcome]], method = "spearman", exact = FALSE)
  )

  tibble(
    predictor = predictor,
    outcome = outcome,
    n = nrow(dat),
    rho = unname(test$estimate),
    p_value = test$p.value,
    note = NA_character_
  )
}

build_factor_scores <- function(instrument, file, item_id_col, score_transform, prefix, recommended_k) {
  long <- read_csv(file, show_col_types = FALSE) |>
    transmute(
      participant_id = as.character(participant_id),
      item_id = as.integer(.data[[item_id_col]]),
      item_text = as.character(item_text),
      score = transform_scores(score, score_transform)
    )

  assert_nonempty_df(long, paste0(instrument, " factor input"))

  wide <- long |>
    select(participant_id, item_id, score) |>
    mutate(item_id = as.character(item_id)) |>
    pivot_wider(names_from = item_id, values_from = score) |>
    arrange(participant_id)

  matrix_df <- wide |>
    select(-participant_id) |>
    mutate(across(everything(), ~ as.integer(round(.x)))) |>
    as.data.frame()

  poly_out <- compute_polychoric_safe(matrix_df)

  set.seed(42L)

  fa_fit <- suppressWarnings(
    psych::fa(
      r = poly_out$rho,
      nfactors = recommended_k,
      n.obs = nrow(matrix_df),
      fm = "minres",
      rotate = if (recommended_k == 1L) "none" else "oblimin"
    )
  )

  if (!is.null(fa_fit$Vaccounted) && recommended_k > 1L) {
    prop_var <- fa_fit$Vaccounted["Proportion Var", ]
    factor_order <- order(prop_var, decreasing = TRUE)
  } else {
    factor_order <- seq_len(recommended_k)
  }

  ordered_loadings <- unclass(fa_fit$loadings)[, factor_order, drop = FALSE]
  colnames(ordered_loadings) <- paste0("MR", seq_len(recommended_k))

  fa_fit_ordered <- fa_fit
  fa_fit_ordered$loadings <- ordered_loadings
  class(fa_fit_ordered$loadings) <- c("loadings")

  score_matrix <- psych::factor.scores(
    x = as.matrix(matrix_df),
    f = fa_fit_ordered,
    rho = poly_out$rho,
    method = factor_score_method
  )

  factor_scores <- bind_scores_with_ids(
    participant_ids = wide$participant_id,
    score_matrix = score_matrix$scores,
    context_label = paste0(instrument, " factor scores")
  ) |>
    rename_with(~ paste0(prefix, "_", .x), .cols = starts_with("MR"))

  factor_lookup <- tibble(
    factor = names(factor_scores)[names(factor_scores) != "participant_id"],
    instrument = instrument
  ) |>
    mutate(
      factor_id = str_remove(factor, paste0("^", prefix, "_")),
      factor_num = as.integer(str_remove(factor_id, "MR"))
    ) |>
    left_join(factor_name_map, by = c("instrument", "factor_num")) |>
    mutate(
      proposed_name = coalesce(proposed_name, paste0("Factor ", factor_num)),
      short_factor = paste0("F", factor_num),
      factor_label = paste0(instrument, " ", short_factor),
      display_label = paste0(instrument, " ", short_factor, " - ", proposed_name)
    )

  list(
    instrument = instrument,
    factor_scores = factor_scores,
    factor_lookup = factor_lookup
  )
}

build_item_matrix <- function(instrument, file, item_id_col, score_transform, prefix) {
  long <- read_csv(file, show_col_types = FALSE) |>
    transmute(
      participant_id = as.character(participant_id),
      item_id = as.integer(.data[[item_id_col]]),
      item_text = as.character(item_text),
      score = transform_scores(score, score_transform)
    )

  assert_nonempty_df(long, paste0(instrument, " cleaned item input"))

  item_lookup <- long |>
    distinct(item_id, item_text) |>
    arrange(item_id) |>
    mutate(
      instrument = instrument,
      item_col = paste0(prefix, "_", item_id),
      item_label = paste0(instrument, " Item ", item_id),
      display_label = paste0(instrument, " ", item_id, ": ", item_text)
    )

  wide <- long |>
    left_join(item_lookup |> select(item_id, item_col), by = "item_id") |>
    select(participant_id, item_col, score) |>
    pivot_wider(names_from = item_col, values_from = score) |>
    arrange(participant_id)

  list(
    instrument = instrument,
    item_lookup = item_lookup,
    wide = wide
  )
}
```

## Read and Score ART

```{r art-scoring}
art_raw <- read_csv(art_clean_file, show_col_types = FALSE)

required_art_cols <- c("participant_id", "order", "response_raw")
missing_art_cols <- setdiff(required_art_cols, names(art_raw))
if (length(missing_art_cols) > 0) {
  stop(
    paste0(
      "AuthorRecognition_cleaned.csv is missing required columns: ",
      paste(missing_art_cols, collapse = ", ")
    ),
    call. = FALSE
  )
}

if (anyNA(art_raw$participant_id)) {
  stop("AuthorRecognition_cleaned.csv has NA values in participant_id.", call. = FALSE)
}

art_dup_pids <- art_raw |>
  count(participant_id, name = "n") |>
  filter(n > 1L)

if (nrow(art_dup_pids) > 0) {
  stop(
    paste0(
      "AuthorRecognition_cleaned.csv has duplicate participant_id rows: ",
      paste(art_dup_pids$participant_id, collapse = ", ")
    ),
    call. = FALSE
  )
}

authorkey <- read_csv("authorkey.csv", show_col_types = FALSE) |>
  mutate(
    author_clean = normalize_text(author),
    validity = tolower(validity)
  )

required_ak_cols <- c("author", "validity")
missing_ak_cols <- setdiff(required_ak_cols, names(authorkey))
if (length(missing_ak_cols) > 0) {
  stop(
    paste0(
      "authorkey.csv is missing required columns: ",
      paste(missing_ak_cols, collapse = ", ")
    ),
    call. = FALSE
  )
}

n_real_items <- sum(authorkey$validity == "real", na.rm = TRUE)
n_fake_items <- sum(authorkey$validity == "fake", na.rm = TRUE)

art_long <- art_raw |>
  transmute(
    participant_id = as.character(participant_id),
    order = as.character(order),
    response_raw = coalesce(response_raw, "")
  ) |>
  separate_rows(response_raw, sep = ",") |>
  mutate(author_selected = normalize_text(response_raw)) |>
  filter(
    author_selected != "",
    !tolower(author_selected) %in% c("none", "na", "n/a")
  )

art_scored_long <- art_long |>
  left_join(
    authorkey |> select(author_clean, validity),
    by = c("author_selected" = "author_clean")
  )

art_unmatched <- art_scored_long |>
  filter(is.na(validity)) |>
  distinct(participant_id, author_selected) |>
  arrange(participant_id, author_selected)

art_score_counts <- art_scored_long |>
  group_by(participant_id, order) |>
  summarise(
    art_total_selected = n(),
    art_real_hits = sum(validity == "real", na.rm = TRUE),
    art_fake_false_alarms = sum(validity == "fake", na.rm = TRUE),
    art_neutral_selected = sum(validity == "neutral", na.rm = TRUE),
    art_unknown_selected = sum(is.na(validity)),
    art_net_real_minus_fake = art_real_hits - art_fake_false_alarms,
    art_hit_rate = art_real_hits / n_real_items,
    art_false_alarm_rate = art_fake_false_alarms / n_fake_items,
    art_adjusted_rate = art_hit_rate - art_false_alarm_rate,
    .groups = "drop"
  )

art_scores <- art_raw |>
  distinct(participant_id, order) |>
  mutate(participant_id = as.character(participant_id)) |>
  left_join(art_score_counts, by = c("participant_id", "order")) |>
  mutate(
    across(
      c(
        art_total_selected,
        art_real_hits,
        art_fake_false_alarms,
        art_neutral_selected,
        art_unknown_selected,
        art_net_real_minus_fake,
        art_hit_rate,
        art_false_alarm_rate,
        art_adjusted_rate
      ),
      ~ coalesce(.x, 0)
    )
  ) |>
  arrange(participant_id)

assert_expected_count(nrow(art_scores), 82L, "ART scored participant count")
assert_unique_pid_rows(art_scores, "participant_id", "ART scored participants")

write_csv(art_scores, file.path(csv_dir, "ART_Scored.csv"))
write_csv(art_unmatched, file.path(csv_dir, "ART_Unmatched_Names.csv"))
```

```{r art-summary}
art_summary <- tibble(
  metric = c(
    "ART participants",
    "Real author targets",
    "Fake foils",
    "Unmatched names after scoring"
  ),
  value = c(
    nrow(art_scores),
    n_real_items,
    n_fake_items,
    nrow(art_unmatched)
  )
)

knitr::kable(art_summary)
```

## Build Factor Scores

```{r factor-scores}
factor_objects <- pmap(
  valid_factor_specs,
  function(instrument, file, item_id_col, score_transform, prefix, recommended_k, factorability_flag) {
    build_factor_scores(
      instrument = instrument,
      file = file,
      item_id_col = item_id_col,
      score_transform = score_transform,
      prefix = prefix,
      recommended_k = recommended_k
    )
  }
)

factor_score_tables <- map(factor_objects, "factor_scores")
factor_lookup <- map_dfr(factor_objects, "factor_lookup")
all_factor_scores <- reduce(factor_score_tables, full_join, by = "participant_id")
factor_cols <- factor_lookup$factor

factor_overlap_summary <- map_dfr(factor_objects, function(obj) {
  tibble(
    instrument = obj$instrument,
    factor_score_participants = nrow(obj$factor_scores),
    art_overlap_n = nrow(
      inner_join(
        art_scores |> select(participant_id),
        obj$factor_scores |> select(participant_id),
        by = "participant_id"
      )
    )
  )
})

art_factor_df <- art_scores |>
  inner_join(all_factor_scores, by = "participant_id")

assert_expected_count(nrow(art_factor_df), 82L, "ART x factor overlap participant count")
assert_unique_pid_rows(art_factor_df, "participant_id", "ART x factor merged")

write_csv(all_factor_scores, file.path(csv_dir, "Other_Instrument_Factor_Scores.csv"))
write_csv(factor_lookup, file.path(csv_dir, "Factor_Lookup.csv"))
write_csv(factor_overlap_summary, file.path(csv_dir, "ART_Factor_Overlap_Summary.csv"))
write_csv(art_factor_df, file.path(csv_dir, "ART_Factor_Merged.csv"))
```

```{r factor-overlap}
knitr::kable(factor_overlap_summary)
```

## Build All Item Statements Matrix

```{r item-matrix}
item_objects <- pmap(
  item_instrument_specs,
  function(instrument, file, item_id_col, score_transform, prefix) {
    build_item_matrix(
      instrument = instrument,
      file = file,
      item_id_col = item_id_col,
      score_transform = score_transform,
      prefix = prefix
    )
  }
)

item_pid_sets <- setNames(map(item_objects, ~ .x$wide$participant_id), map_chr(item_objects, "instrument"))
assert_identical_pid_sets(c(list(ART = art_scores$participant_id), item_pid_sets), "ART and cleaned item PID consistency")

item_lookup <- map_dfr(item_objects, "item_lookup")
all_item_wide <- reduce(map(item_objects, "wide"), full_join, by = "participant_id")
item_cols <- item_lookup$item_col

art_item_df <- art_scores |>
  inner_join(all_item_wide, by = "participant_id")

assert_expected_count(nrow(art_item_df), 82L, "ART x item overlap participant count")
assert_unique_pid_rows(art_item_df, "participant_id", "ART x item merged")

write_csv(item_lookup, file.path(csv_dir, "All_Item_Lookup.csv"))
write_csv(all_item_wide, file.path(csv_dir, "All_Items_Wide.csv"))
write_csv(art_item_df, file.path(csv_dir, "ART_Item_Merged.csv"))
```

```{r item-summary}
item_summary <- tibble(
  metric = c(
    "Participants in ART x item merge",
    "All item columns",
    "IMI items",
    "WritingEfficacy items",
    "AIReflection items",
    "BeliefsAboutAI items"
  ),
  value = c(
    nrow(art_item_df),
    length(item_cols),
    sum(item_lookup$instrument == "IMI"),
    sum(item_lookup$instrument == "WritingEfficacy"),
    sum(item_lookup$instrument == "AIReflection"),
    sum(item_lookup$instrument == "BeliefsAboutAI")
  )
)

knitr::kable(item_summary)
```

## ART vs Factor Scores

```{r factor-correlations}
factor_correlations <- crossing(
  factor = factor_cols,
  art_metric = art_metric_lookup$art_metric
) |>
  mutate(
    result = map2(factor, art_metric, ~ safe_spearman(art_factor_df, .x, .y))
  ) |>
  pull(result) |>
  bind_rows() |>
  rename(
    factor = predictor,
    art_metric = outcome
  ) |>
  mutate(
    abs_r = abs(rho),
    p_bh = p.adjust(p_value, method = "BH"),
    p_bonferroni = p.adjust(p_value, method = "bonferroni"),
    survives_bh = p_bh < 0.05,
    survives_bonferroni = p_bonferroni < 0.05
  ) |>
  left_join(factor_lookup, by = "factor") |>
  left_join(art_metric_lookup, by = "art_metric") |>
  arrange(p_bh, p_bonferroni, desc(abs_r))

factor_ranking_primary <- factor_correlations |>
  filter(art_metric == "art_net_real_minus_fake") |>
  arrange(desc(abs_r), p_bh, p_bonferroni)

write_csv(factor_correlations, file.path(csv_dir, "ART_vs_Factors_Correlations.csv"))
write_csv(factor_ranking_primary, file.path(csv_dir, "ART_Net_vs_Factors_Ranked.csv"))
```

```{r factor-top-table}
factor_correlations |>
  select(
    art_label, instrument, display_label, rho, p_value, p_bh, p_bonferroni, n
  ) |>
  mutate(
    rho = round(rho, 3),
    p_value = round(p_value, 4),
    p_bh = round(p_bh, 4),
    p_bonferroni = round(p_bonferroni, 4)
  ) |>
  slice_head(n = 20) |>
  knitr::kable()
```

## ART vs All Item Statements

```{r item-correlations}
item_correlations <- crossing(
  item_col = item_cols,
  art_metric = art_metric_lookup$art_metric
) |>
  mutate(
    result = map2(item_col, art_metric, ~ safe_spearman(art_item_df, .x, .y))
  ) |>
  pull(result) |>
  bind_rows() |>
  rename(
    item_col = predictor,
    art_metric = outcome
  ) |>
  mutate(
    abs_r = abs(rho),
    p_bh = p.adjust(p_value, method = "BH"),
    p_bonferroni = p.adjust(p_value, method = "bonferroni"),
    survives_bh = p_bh < 0.05,
    survives_bonferroni = p_bonferroni < 0.05
  ) |>
  left_join(item_lookup, by = "item_col") |>
  left_join(art_metric_lookup, by = "art_metric") |>
  arrange(p_bh, p_bonferroni, desc(abs_r))

item_ranking_primary <- item_correlations |>
  filter(art_metric == "art_net_real_minus_fake") |>
  arrange(desc(abs_r), p_bh, p_bonferroni)

write_csv(item_correlations, file.path(csv_dir, "ART_vs_All_Items_Correlations.csv"))
write_csv(item_ranking_primary, file.path(csv_dir, "ART_Net_vs_All_Items_Ranked.csv"))
```

```{r item-top-table}
item_correlations |>
  select(
    art_label, instrument, item_id, item_text, rho, p_value, p_bh, p_bonferroni, n
  ) |>
  mutate(
    rho = round(rho, 3),
    p_value = round(p_value, 4),
    p_bh = round(p_bh, 4),
    p_bonferroni = round(p_bonferroni, 4)
  ) |>
  slice_head(n = 25) |>
  knitr::kable()
```

## Factor Heatmap

```{r factor-heatmap-data}
factor_heat_df <- factor_correlations |>
  mutate(
    display_label = factor(
      display_label,
      levels = factor_lookup |>
        arrange(match(instrument, valid_factor_specs$instrument), factor_num) |>
        pull(display_label)
    ),
    art_label = factor(
      art_label,
      levels = art_metric_lookup$art_label
    ),
    sig_label = case_when(
      survives_bonferroni ~ "**",
      survives_bh ~ "*",
      TRUE ~ ""
    ),
    cell_label = if_else(
      is.na(rho),
      "",
      paste0(formatC(rho, format = "f", digits = 2), sig_label)
    )
  )
```

```{r factor-heatmap, fig.width=9, fig.height=6.5}
factor_heatmap_plot <- ggplot(factor_heat_df, aes(x = art_label, y = display_label, fill = rho)) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = cell_label), size = 3) +
  scale_fill_gradient2(
    low = "#c73e3a",
    mid = "#f7f7f7",
    high = "#4f79b7",
    midpoint = 0,
    limits = c(-1, 1),
    name = "Spearman rho"
  ) +
  labs(
    title = "ART vs Factor Scores",
    subtitle = "* BH < .05   ** Bonferroni < .05",
    x = NULL,
    y = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid = element_blank(),
    axis.text.x = element_text(angle = 15, hjust = 1),
    plot.margin = margin(10, 15, 10, 10)
  )

ggsave(
  filename = file.path(plot_dir, "ART_vs_Factors_Heatmap.png"),
  plot = factor_heatmap_plot,
  width = 10,
  height = 7,
  units = "in",
  dpi = 300,
  bg = "white"
)

ggsave(
  filename = file.path(plot_dir, "ART_vs_Factors_Heatmap.pdf"),
  plot = factor_heatmap_plot,
  width = 10,
  height = 7,
  units = "in",
  bg = "white"
)

factor_heatmap_plot
```

## Ranked All-Statement Signals for ART Net Score

```{r primary-item-plot-data}
top_item_signals_primary <- item_ranking_primary |>
  filter(!is.na(rho)) |>
  slice_head(n = 30) |>
  mutate(
    plot_label = paste0(instrument, " ", item_id, ": ", str_trunc(item_text, 80)),
    plot_label = fct_reorder(plot_label, rho)
  )
```

```{r primary-item-plot, fig.width=11, fig.height=10}
top_item_plot <- ggplot(top_item_signals_primary, aes(x = rho, y = plot_label, fill = instrument)) +
  geom_col(width = 0.75) +
  geom_vline(xintercept = 0, color = "gray50", linewidth = 0.5) +
  scale_fill_manual(values = c(
    "IMI" = "#4f79b7",
    "WritingEfficacy" = "#c96b3b",
    "AIReflection" = "#5a9367",
    "BeliefsAboutAI" = "#8c6bb1"
  )) +
  labs(
    title = "Top ART Net Score Correlates Across All Item Statements",
    subtitle = "Top 30 items by absolute Spearman correlation with ART net real minus fake",
    x = "Spearman rho",
    y = NULL,
    fill = NULL
  ) +
  theme_minimal(base_size = 11) +
  theme(
    panel.grid.minor = element_blank(),
    axis.text.y = element_text(size = 9, lineheight = 0.9),
    legend.position = "bottom"
  )

ggsave(
  filename = file.path(plot_dir, "ART_Net_vs_All_Items_Top30.png"),
  plot = top_item_plot,
  width = 12,
  height = 10.5,
  units = "in",
  dpi = 300,
  bg = "white"
)

ggsave(
  filename = file.path(plot_dir, "ART_Net_vs_All_Items_Top30.pdf"),
  plot = top_item_plot,
  width = 12,
  height = 10.5,
  units = "in",
  bg = "white"
)

top_item_plot
```

## Strongest Signals by ART Metric

```{r strongest-by-metric}
top_by_metric <- item_correlations |>
  filter(!is.na(rho)) |>
  group_by(art_label) |>
  slice_max(order_by = abs_r, n = 8, with_ties = FALSE) |>
  ungroup() |>
  select(art_label, instrument, item_id, item_text, rho, p_bh, p_bonferroni, n) |>
  mutate(
    rho = round(rho, 3),
    p_bh = round(p_bh, 4),
    p_bonferroni = round(p_bonferroni, 4)
  )

write_csv(top_by_metric, file.path(csv_dir, "ART_Top_Item_Signals_By_Metric.csv"))

knitr::kable(top_by_metric)
```

## Summary

```{r summary}
analysis_summary <- tibble(
  metric = c(
    "ART participants",
    "Factor columns",
    "Item columns",
    "ART x factor tests",
    "ART x item tests",
    "Top ART net factor signal",
    "Top ART net item signal"
  ),
  value = c(
    nrow(art_scores),
    length(factor_cols),
    length(item_cols),
    nrow(factor_correlations),
    nrow(item_correlations),
    paste0(
      factor_ranking_primary$display_label[[1]],
      " (rho = ",
      round(factor_ranking_primary$rho[[1]], 3),
      ")"
    ),
    paste0(
      item_ranking_primary$instrument[[1]],
      " Item ",
      item_ranking_primary$item_id[[1]],
      " (rho = ",
      round(item_ranking_primary$rho[[1]], 3),
      ")"
    )
  )
)

knitr::kable(analysis_summary)
```

## Output Manifest

```{r manifest}
manifest <- tibble(
  object = c(
    "art_scored",
    "art_unmatched",
    "factor_scores",
    "factor_lookup",
    "art_factor_overlap",
    "art_factor_correlations",
    "art_net_factor_ranking",
    "item_lookup",
    "all_items_wide",
    "art_item_correlations",
    "art_net_item_ranking",
    "top_item_signals_by_metric"
  ),
  file = c(
    "ART_Scored.csv",
    "ART_Unmatched_Names.csv",
    "Other_Instrument_Factor_Scores.csv",
    "Factor_Lookup.csv",
    "ART_Factor_Overlap_Summary.csv",
    "ART_vs_Factors_Correlations.csv",
    "ART_Net_vs_Factors_Ranked.csv",
    "All_Item_Lookup.csv",
    "All_Items_Wide.csv",
    "ART_vs_All_Items_Correlations.csv",
    "ART_Net_vs_All_Items_Ranked.csv",
    "ART_Top_Item_Signals_By_Metric.csv"
  )
)

write_csv(manifest, file.path(csv_dir, "ART_Analysis_Manifest.csv"))

knitr::kable(manifest)
```
