---
title: "Profile Comparisons on ART, AI Use, and AI Beliefs"
format:
  html:
    toc: true
    toc-depth: 2
output-dir: "11_profile_external_comparisons"
execute:
  echo: false
  warning: false
  message: false
---

This report compares the named participant profiles against external variables that were not used to define the clusters.

Profiles were defined in [10_participant_profiles.qmd](10_participant_profiles.qmd) using only validated factor scores from `IMI`, `WritingEfficacy`, and `AIReflection`.

Comparison families in this script:

- `ART` metrics
- `Q17` AI-use indices
- Beliefs theme averages
- all `22` individual `BeliefsAboutAI` items

Inference strategy:

- omnibus `Kruskal-Wallis` tests for each variable
- `BH` correction within each variable family
- pairwise `Wilcoxon` follow-up tests only for variables that survive the omnibus family correction
- `BH` correction across the three pairwise tests within each variable

```{r setup}
library(tidyverse)
library(glue)
library(knitr)
source("scoring_helpers.R", local = knitr::knit_global())
```

## Setup

```{r config}
script_dir <- "11_profile_external_comparisons"
csv_dir <- file.path(script_dir, "csv")
plot_dir <- file.path(script_dir, "plots")
dir.create(csv_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(plot_dir, recursive = TRUE, showWarnings = FALSE)

profile_assignments_file <- file.path(
  "10_participant_profiles", "csv", "Participant_Profile_Assignments.csv"
)
profile_signatures_file <- file.path(
  "10_participant_profiles", "csv", "Profile_Signatures.csv"
)
q17_index_file <- file.path("09_q17_ai_use", "csv", "Q17_Participant_AI_Use_Index.csv")
beliefs_metadata_file <- file.path(
  "08_ai_beliefs_items", "csv", "AIBeliefs_Item_Metadata.csv"
)
master_wide_file <- file.path("02_efa_exports", "Final_Master_Wide.csv")

required_files <- c(
  profile_assignments_file,
  profile_signatures_file,
  q17_index_file,
  beliefs_metadata_file,
  master_wide_file
)

missing_files <- required_files[!file.exists(required_files)]
if (length(missing_files) > 0) {
  stop(
    paste0(
      "Profile external comparisons are missing required inputs: ",
      paste(missing_files, collapse = ", ")
    ),
    call. = FALSE
  )
}

theme_order <- c(
  "AI Literacy and Limitations",
  "Academic Utility",
  "Psychological Comfort and Anonymity",
  "Practical Convenience",
  "Risks and Concerns",
  "Future Integration"
)

# Participants intentionally excluded from the Q17 index in script 07.
# 9g0fXm: straight-line first-dup (all 5s) — excluded in 09_q17_ai_use
# to avoid inflating ai_tools_regular_n. They remain in all non-Q17 comparisons.
known_q17_exclusions <- c("9g0fXm")
```

## Load Data

```{r load-data}
profile_assignments <- read_csv(profile_assignments_file, show_col_types = FALSE) |>
  mutate(participant_id = as.character(participant_id))

profile_signatures <- read_csv(profile_signatures_file, show_col_types = FALSE)
cluster_levels <- profile_signatures$cluster

q17_index <- read_csv(q17_index_file, show_col_types = FALSE) |>
  mutate(participant_id = as.character(participant_id))

beliefs_metadata <- read_csv(beliefs_metadata_file, show_col_types = FALSE) |>
  mutate(theme = factor(theme, levels = theme_order))

master_wide <- read_csv(master_wide_file, show_col_types = FALSE) |>
  mutate(participant_id = as.character(participant_id))

profile_assignments <- profile_assignments |>
  mutate(cluster = factor(cluster, levels = cluster_levels))

assert_expected_count(nrow(profile_assignments), 82L, "profile assignments row count")
assert_unique_pid_rows(profile_assignments, "participant_id", "profile assignments")
assert_unique_pid_rows(q17_index, "participant_id", "Q17 profile comparison")
assert_expected_count(nrow(master_wide), 82L, "Final_Master_Wide profile comparison row count")
assert_unique_pid_rows(master_wide, "participant_id", "Final_Master_Wide profile comparison")

# Check for unexpected Q17 gaps (i.e. anyone missing who is NOT a known exclusion).
q17_missing_from_profiles <- setdiff(profile_assignments$participant_id, q17_index$participant_id)
unexpected_q17_missing <- setdiff(q17_missing_from_profiles, known_q17_exclusions)

if (length(unexpected_q17_missing) > 0L) {
  stop(
    paste0(
      "Q17 profile comparison: clustered participants missing from Q17 index: ",
      paste(head(unexpected_q17_missing, 20), collapse = ", ")
    ),
    call. = FALSE
  )
}

if (length(q17_missing_from_profiles) > 0L) {
  message(
    "Dropping ", length(q17_missing_from_profiles),
    " participant(s) from Q17 comparisons (known Q17 exclusions): ",
    paste(q17_missing_from_profiles, collapse = ", ")
  )
}

# profile_assignments_q17 excludes known Q17 exclusions.
# profile_assignments (full) is kept intact for ART and beliefs comparisons.
profile_assignments_q17 <- profile_assignments |>
  filter(!participant_id %in% known_q17_exclusions)

assert_identical_pid_sets(
  list(
    profile_assignments = profile_assignments$participant_id,
    master_wide = master_wide$participant_id
  ),
  "profile comparison participant set"
)
```

## Profile Overview

```{r profile-overview}
knitr::kable(profile_signatures)
```

## Build Analysis Frames

```{r analysis-frames}
# art_theme_df uses profile_assignments_q17 so the Q17 left_join has no gaps.
# ART and beliefs columns for 9g0fXm are still present; only Q17 cols will be NA.
art_theme_df <- profile_assignments_q17 |>
  select(
    participant_id,
    cluster,
    art_net_real_minus_fake,
    art_adjusted_rate,
    art_real_hits,
    art_fake_false_alarms,
    starts_with("BeliefsTheme_")
  ) |>
  left_join(
    q17_index |>
      select(
        participant_id,
        ai_tools_heard_n,
        ai_tools_used_n,
        ai_tools_regular_n,
        ai_tools_often_n,
        ai_use_mean,
        ai_use_mean_heard_only
      ),
    by = "participant_id"
  )

assert_expected_count(nrow(art_theme_df), 82L - length(known_q17_exclusions), "profile comparison analysis rows")
assert_unique_pid_rows(art_theme_df, "participant_id", "profile comparison analysis rows")

beliefs_item_cols <- beliefs_metadata$item_col
assert_required_columns(master_wide, beliefs_item_cols, "Final_Master_Wide beliefs item columns")

# beliefs_item_df uses the full profile_assignments so 9g0fXm is included.
beliefs_item_df <- profile_assignments |>
  select(participant_id, cluster) |>
  left_join(
    master_wide |>
      select(participant_id, all_of(beliefs_item_cols)),
    by = "participant_id"
  )

assert_expected_count(nrow(beliefs_item_df), 82L, "beliefs item profile comparison rows")
assert_unique_pid_rows(beliefs_item_df, "participant_id", "beliefs item profile comparison rows")
```

## Variable Families

```{r variable-families}
art_vars <- tribble(
  ~variable, ~variable_label,
  "art_net_real_minus_fake", "ART net (real - fake)",
  "art_adjusted_rate", "ART adjusted rate",
  "art_real_hits", "ART real hits",
  "art_fake_false_alarms", "ART false alarms"
)

q17_vars <- tribble(
  ~variable, ~variable_label,
  "ai_tools_heard_n", "AI tools heard of",
  "ai_tools_used_n", "AI tools used",
  "ai_tools_regular_n", "AI tools used regularly",
  "ai_tools_often_n", "AI tools used often",
  "ai_use_mean", "Q17 average use",
  "ai_use_mean_heard_only", "Q17 average use among heard-of tools"
)

theme_vars <- tibble(
  variable = names(art_theme_df)[str_detect(names(art_theme_df), "^BeliefsTheme_")]
) |>
  mutate(
    variable_label = variable |>
      str_remove("^BeliefsTheme_") |>
      str_replace_all("_", " "),
    theme = factor(variable_label, levels = theme_order)
  ) |>
  arrange(theme) |>
  select(-theme)

beliefs_item_vars <- beliefs_metadata |>
  filter(inferential) |>
  transmute(
    variable = item_col,
    variable_label = item_label,
    item_num,
    item_text,
    theme = as.character(theme)
  )
```

## Statistical Helpers

```{r helpers}
build_family_descriptives <- function(df, var_tbl, family) {
  long <- df |>
    select(cluster, all_of(var_tbl$variable)) |>
    pivot_longer(
      cols = all_of(var_tbl$variable),
      names_to = "variable",
      values_to = "value"
    ) |>
    mutate(value = as.numeric(value)) |>
    left_join(var_tbl, by = "variable") |>
    group_by(family = family, variable, variable_label, cluster) |>
    summarise(
      n = sum(!is.na(value)),
      mean = mean(value, na.rm = TRUE),
      median = median(value, na.rm = TRUE),
      sd = sd(value, na.rm = TRUE),
      .groups = "drop"
    )

  extra_cols <- setdiff(names(var_tbl), c("variable", "variable_label"))
  if (length(extra_cols) > 0) {
    long <- long |>
      left_join(var_tbl |> distinct(variable, across(all_of(extra_cols))), by = "variable")
  }

  long
}

run_kruskal_one <- function(df, variable, variable_label, family, extra = NULL) {
  dat <- df |>
    select(cluster, value = all_of(variable)) |>
    mutate(
      cluster = factor(cluster, levels = cluster_levels),
      value = as.numeric(value)
    ) |>
    filter(!is.na(cluster), !is.na(value))

  base_out <- tibble(
    family = family,
    variable = variable,
    variable_label = variable_label,
    n_total = nrow(dat),
    groups_observed = n_distinct(dat$cluster),
    kw_statistic = NA_real_,
    kw_df = NA_real_,
    p_value = NA_real_,
    epsilon_sq = NA_real_,
    note = NA_character_
  )

  if (!is.null(extra)) {
    base_out <- bind_cols(base_out, extra)
  }

  if (nrow(dat) == 0L) {
    return(base_out |> mutate(note = "No non-missing observations"))
  }

  if (n_distinct(dat$cluster) < 2L) {
    return(base_out |> mutate(note = "Fewer than 2 observed profile groups"))
  }

  kw <- tryCatch(
    kruskal.test(value ~ cluster, data = dat),
    error = function(e) e
  )

  if (inherits(kw, "error")) {
    return(base_out |> mutate(note = conditionMessage(kw)))
  }

  n_obs <- nrow(dat)
  k_obs <- n_distinct(dat$cluster)
  kw_stat <- unname(as.numeric(kw$statistic))
  epsilon_sq_val <- if (n_obs > k_obs) {
    max((kw_stat - k_obs + 1) / (n_obs - k_obs), 0)
  } else {
    NA_real_
  }

  base_out |>
    mutate(
      kw_statistic = kw_stat,
      kw_df = unname(as.numeric(kw$parameter)),
      p_value = unname(as.numeric(kw$p.value)),
      epsilon_sq = epsilon_sq_val
    )
}

run_kruskal_family <- function(df, var_tbl, family) {
  extra_cols <- setdiff(names(var_tbl), c("variable", "variable_label"))

  out <- map_dfr(seq_len(nrow(var_tbl)), function(i) {
    extra_tbl <- if (length(extra_cols) > 0L) {
      var_tbl[i, extra_cols, drop = FALSE]
    } else {
      NULL
    }

    run_kruskal_one(
      df = df,
      variable = var_tbl$variable[[i]],
      variable_label = var_tbl$variable_label[[i]],
      family = family,
      extra = extra_tbl
    )
  })

  out |>
    mutate(
      p_bh = p.adjust(p_value, method = "BH"),
      sig_bh = !is.na(p_bh) & p_bh < 0.05
    ) |>
    arrange(p_bh, p_value, variable)
}

run_pairwise_one <- function(df, variable, variable_label, family, extra = NULL) {
  dat <- df |>
    select(cluster, value = all_of(variable)) |>
    mutate(
      cluster = factor(cluster, levels = cluster_levels),
      value = as.numeric(value)
    ) |>
    filter(!is.na(cluster), !is.na(value))

  observed_clusters <- dat |>
    count(cluster, name = "n_group") |>
    filter(n_group > 0) |>
    pull(cluster) |>
    as.character()

  base_cols <- tibble(
    family = family,
    variable = variable,
    variable_label = variable_label,
    cluster_a = character(),
    cluster_b = character(),
    n_a = integer(),
    n_b = integer(),
    median_a = double(),
    median_b = double(),
    median_diff = double(),
    p_value = double(),
    note = character()
  )

  if (!is.null(extra)) {
    base_cols <- bind_cols(base_cols, extra[rep(1, 0), , drop = FALSE])
  }

  if (length(observed_clusters) < 2L) {
    return(base_cols)
  }

  pair_list <- combn(observed_clusters, 2, simplify = FALSE)

  out <- map_dfr(pair_list, function(pair) {
    sub <- dat |>
      filter(as.character(cluster) %in% pair)

    counts <- sub |>
      count(cluster, name = "n_group") |>
      mutate(cluster = as.character(cluster))

    medians <- sub |>
      group_by(cluster) |>
      summarise(median_value = median(value, na.rm = TRUE), .groups = "drop") |>
      mutate(cluster = as.character(cluster))

    n_a <- counts$n_group[counts$cluster == pair[[1]]]
    n_b <- counts$n_group[counts$cluster == pair[[2]]]
    median_a <- medians$median_value[medians$cluster == pair[[1]]]
    median_b <- medians$median_value[medians$cluster == pair[[2]]]

    base_row <- tibble(
      family = family,
      variable = variable,
      variable_label = variable_label,
      cluster_a = pair[[1]],
      cluster_b = pair[[2]],
      n_a = n_a,
      n_b = n_b,
      median_a = median_a,
      median_b = median_b,
      median_diff = median_a - median_b,
      p_value = NA_real_,
      note = NA_character_
    )

    if (!is.null(extra)) {
      base_row <- bind_cols(base_row, extra)
    }

    if (n_a < 2L || n_b < 2L) {
      return(base_row |> mutate(note = "Insufficient observations for pairwise test"))
    }

    wt <- tryCatch(
      wilcox.test(value ~ cluster, data = sub, exact = FALSE),
      error = function(e) e
    )

    if (inherits(wt, "error")) {
      return(base_row |> mutate(note = conditionMessage(wt)))
    }

    base_row |> mutate(p_value = unname(as.numeric(wt$p.value)))
  })

  out |>
    mutate(
      p_bh = p.adjust(p_value, method = "BH"),
      sig_bh = !is.na(p_bh) & p_bh < 0.05,
      direction = case_when(
        is.na(median_diff) | median_diff == 0 ~ "No median difference",
        median_diff > 0 ~ paste0(cluster_a, " > ", cluster_b),
        TRUE ~ paste0(cluster_b, " > ", cluster_a)
      )
    ) |>
    arrange(p_bh, p_value, cluster_a, cluster_b)
}

run_pairwise_for_significant <- function(df, sig_results) {
  if (nrow(sig_results) == 0L) {
    return(tibble(
      family = character(),
      variable = character(),
      variable_label = character(),
      cluster_a = character(),
      cluster_b = character(),
      n_a = integer(),
      n_b = integer(),
      median_a = double(),
      median_b = double(),
      median_diff = double(),
      p_value = double(),
      note = character(),
      p_bh = double(),
      sig_bh = logical(),
      direction = character()
    ))
  }

  extra_cols <- setdiff(names(sig_results), c(
    "family", "variable", "variable_label", "n_total", "groups_observed",
    "kw_statistic", "kw_df", "p_value", "epsilon_sq", "note", "p_bh", "sig_bh"
  ))

  map_dfr(seq_len(nrow(sig_results)), function(i) {
    extra_tbl <- if (length(extra_cols) > 0L) {
      sig_results[i, extra_cols, drop = FALSE]
    } else {
      NULL
    }

    run_pairwise_one(
      df = df,
      variable = sig_results$variable[[i]],
      variable_label = sig_results$variable_label[[i]],
      family = sig_results$family[[i]],
      extra = extra_tbl
    )
  })
}

scale_or_zero <- function(x) {
  if (all(is.na(x))) {
    return(rep(NA_real_, length(x)))
  }

  if (sd(x, na.rm = TRUE) == 0) {
    return(rep(0, length(x)))
  }

  as.numeric(scale(x))
}
```

## Family Descriptives

```{r descriptives}
art_desc <- build_family_descriptives(art_theme_df, art_vars, "ART")
q17_desc <- build_family_descriptives(art_theme_df, q17_vars, "Q17")
theme_desc <- build_family_descriptives(art_theme_df, theme_vars, "Beliefs themes")
beliefs_item_desc <- build_family_descriptives(beliefs_item_df, beliefs_item_vars, "Beliefs items")

write_csv(art_desc, file.path(csv_dir, "ART_Profile_Descriptives.csv"))
write_csv(q17_desc, file.path(csv_dir, "Q17_Profile_Descriptives.csv"))
write_csv(theme_desc, file.path(csv_dir, "Beliefs_Theme_Profile_Descriptives.csv"))
write_csv(beliefs_item_desc, file.path(csv_dir, "Beliefs_Item_Profile_Descriptives.csv"))
```

## Omnibus Tests

```{r omnibus-tests}
art_results <- run_kruskal_family(art_theme_df, art_vars, "ART")
q17_results <- run_kruskal_family(art_theme_df, q17_vars, "Q17")
theme_results <- run_kruskal_family(art_theme_df, theme_vars, "Beliefs themes")
beliefs_item_results <- run_kruskal_family(beliefs_item_df, beliefs_item_vars, "Beliefs items") |>
  arrange(theme, p_bh, p_value, item_num)

omnibus_summary <- bind_rows(
  art_results,
  q17_results,
  theme_results,
  beliefs_item_results
) |>
  group_by(family) |>
  summarise(
    n_tests = n(),
    n_sig_bh = sum(sig_bh, na.rm = TRUE),
    top_signal = variable_label[which.min(coalesce(p_bh, Inf))],
    best_p_bh = min(p_bh, na.rm = TRUE),
    .groups = "drop"
  ) |>
  mutate(best_p_bh = if_else(is.infinite(best_p_bh), NA_real_, best_p_bh))

write_csv(art_results, file.path(csv_dir, "ART_Profile_Kruskal_Results.csv"))
write_csv(q17_results, file.path(csv_dir, "Q17_Profile_Kruskal_Results.csv"))
write_csv(theme_results, file.path(csv_dir, "Beliefs_Theme_Profile_Kruskal_Results.csv"))
write_csv(beliefs_item_results, file.path(csv_dir, "Beliefs_Item_Profile_Kruskal_Results.csv"))
write_csv(omnibus_summary, file.path(csv_dir, "Profile_Comparison_Omnibus_Summary.csv"))
```

```{r omnibus-summary-table}
knitr::kable(omnibus_summary)
```

```{r art-q17-theme-table}
art_q17_theme_table <- bind_rows(art_results, q17_results, theme_results) |>
  select(family, variable_label, kw_statistic, kw_df, epsilon_sq, p_value, p_bh, sig_bh) |>
  mutate(
    kw_statistic = round(kw_statistic, 3),
    epsilon_sq = round(epsilon_sq, 3),
    p_value = signif(p_value, 3),
    p_bh = signif(p_bh, 3)
  )

knitr::kable(art_q17_theme_table)
```

```{r beliefs-item-top-table}
beliefs_item_top <- beliefs_item_results |>
  select(theme, item_num, item_text, kw_statistic, epsilon_sq, p_value, p_bh, sig_bh) |>
  arrange(p_bh, p_value, item_num) |>
  slice_head(n = 12) |>
  mutate(
    kw_statistic = round(kw_statistic, 3),
    epsilon_sq = round(epsilon_sq, 3),
    p_value = signif(p_value, 3),
    p_bh = signif(p_bh, 3),
    item_text = str_trunc(item_text, width = 90)
  )

knitr::kable(beliefs_item_top)
```

## Pairwise Follow-Up Tests

```{r pairwise-tests}
art_pairwise <- run_pairwise_for_significant(art_theme_df, art_results |> filter(sig_bh))
q17_pairwise <- run_pairwise_for_significant(art_theme_df, q17_results |> filter(sig_bh))
theme_pairwise <- run_pairwise_for_significant(art_theme_df, theme_results |> filter(sig_bh))
beliefs_item_pairwise <- run_pairwise_for_significant(
  beliefs_item_df,
  beliefs_item_results |> filter(sig_bh)
) |>
  arrange(theme, p_bh, p_value, item_num, cluster_a, cluster_b)

write_csv(art_pairwise, file.path(csv_dir, "ART_Profile_Pairwise_Wilcoxon_Results.csv"))
write_csv(q17_pairwise, file.path(csv_dir, "Q17_Profile_Pairwise_Wilcoxon_Results.csv"))
write_csv(theme_pairwise, file.path(csv_dir, "Beliefs_Theme_Profile_Pairwise_Wilcoxon_Results.csv"))
write_csv(
  beliefs_item_pairwise,
  file.path(csv_dir, "Beliefs_Item_Profile_Pairwise_Wilcoxon_Results.csv")
)
```

```{r pairwise-summary-table}
pairwise_summary <- bind_rows(
  art_pairwise,
  q17_pairwise,
  theme_pairwise,
  beliefs_item_pairwise
) |>
  group_by(family) |>
  summarise(
    n_pairwise_tests = n(),
    n_sig_bh = sum(sig_bh, na.rm = TRUE),
    .groups = "drop"
  )

knitr::kable(pairwise_summary)
```

```{r beliefs-item-pairwise-top}
beliefs_item_pairwise_top <- beliefs_item_pairwise |>
  select(theme, item_num, item_text, cluster_a, cluster_b, median_a, median_b,
         median_diff, p_value, p_bh, sig_bh, direction) |>
  arrange(p_bh, p_value, item_num, cluster_a, cluster_b) |>
  slice_head(n = 18) |>
  mutate(
    item_text = str_trunc(item_text, width = 80),
    median_a = round(median_a, 2),
    median_b = round(median_b, 2),
    median_diff = round(median_diff, 2),
    p_value = signif(p_value, 3),
    p_bh = signif(p_bh, 3)
  )

knitr::kable(beliefs_item_pairwise_top)
```

## Heatmaps

```{r heatmap-data}
external_heatmap_df <- bind_rows(art_desc, q17_desc, theme_desc) |>
  mutate(
    family = factor(family, levels = c("ART", "Q17", "Beliefs themes")),
    profile_z = ave(median, variable, FUN = scale_or_zero),
    cell_label = formatC(median, format = "f", digits = 2),
    cluster = factor(cluster, levels = cluster_levels),
    variable_label = factor(variable_label, levels = rev(unique(variable_label)))
  )

top_beliefs_item_levels <- beliefs_item_results |>
  arrange(p_bh, p_value, item_num) |>
  slice_head(n = 12) |>
  pull(variable)

beliefs_item_heatmap_df <- beliefs_item_desc |>
  filter(variable %in% top_beliefs_item_levels) |>
  mutate(
    item_label_wrapped = beliefs_item_vars$variable_label[
      match(variable, beliefs_item_vars$variable)
    ] |>
      str_remove("^Item \\d+: ") |>
      str_wrap(width = 52),
    cluster = factor(cluster, levels = cluster_levels),
    profile_z = ave(median, variable, FUN = scale_or_zero),
    cell_label = formatC(median, format = "f", digits = 2)
  )

beliefs_item_levels <- beliefs_item_results |>
  filter(variable %in% top_beliefs_item_levels) |>
  arrange(p_bh, p_value, item_num) |>
  pull(variable_label) |>
  str_remove("^Item \\d+: ") |>
  str_wrap(width = 52)

beliefs_item_heatmap_df <- beliefs_item_heatmap_df |>
  mutate(item_label_wrapped = factor(item_label_wrapped, levels = rev(beliefs_item_levels)))
```

```{r external-heatmap-plot, fig.width=11, fig.height=8}
external_heatmap_plot <- ggplot(
  external_heatmap_df,
  aes(x = cluster, y = variable_label, fill = profile_z)
) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = cell_label), size = 3) +
  facet_wrap(~ family, scales = "free_y", ncol = 1) +
  scale_fill_gradient2(
    low = "#c73e3a",
    mid = "#f7f7f7",
    high = "#4f79b7",
    midpoint = 0,
    name = "Profile z"
  ) +
  labs(
    title = "Profile Differences Across ART, Q17, and Beliefs Themes",
    subtitle = "Cells show profile medians; fill is standardized within variable across profiles",
    x = NULL,
    y = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid = element_blank(),
    axis.text.x = element_text(face = "bold"),
    strip.text = element_text(face = "bold")
  )

ggsave(
  filename = file.path(plot_dir, "Profile_External_Medians_Heatmap.png"),
  plot = external_heatmap_plot,
  width = 11,
  height = 8,
  units = "in",
  dpi = 300,
  bg = "white"
)

ggsave(
  filename = file.path(plot_dir, "Profile_External_Medians_Heatmap.pdf"),
  plot = external_heatmap_plot,
  width = 11,
  height = 8,
  units = "in",
  bg = "white"
)

external_heatmap_plot
```

```{r beliefs-item-heatmap-plot, fig.width=11, fig.height=8.5}
beliefs_item_heatmap_plot <- ggplot(
  beliefs_item_heatmap_df,
  aes(x = cluster, y = item_label_wrapped, fill = profile_z)
) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = cell_label), size = 2.9) +
  scale_fill_gradient2(
    low = "#c73e3a",
    mid = "#f7f7f7",
    high = "#4f79b7",
    midpoint = 0,
    name = "Profile z"
  ) +
  labs(
    title = "Top Beliefs Items by Profile",
    subtitle = "Top 12 item-level omnibus signals; cells show profile medians",
    x = NULL,
    y = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid = element_blank(),
    axis.text.x = element_text(face = "bold")
  )

ggsave(
  filename = file.path(plot_dir, "Profile_Beliefs_Items_Top12_Heatmap.png"),
  plot = beliefs_item_heatmap_plot,
  width = 11,
  height = 8.5,
  units = "in",
  dpi = 300,
  bg = "white"
)

ggsave(
  filename = file.path(plot_dir, "Profile_Beliefs_Items_Top12_Heatmap.pdf"),
  plot = beliefs_item_heatmap_plot,
  width = 11,
  height = 8.5,
  units = "in",
  bg = "white"
)

beliefs_item_heatmap_plot
```

## Output Manifest

```{r manifest}
manifest <- tibble(
  object = c(
    "art_descriptives",
    "q17_descriptives",
    "beliefs_theme_descriptives",
    "beliefs_item_descriptives",
    "art_kruskal_results",
    "q17_kruskal_results",
    "beliefs_theme_kruskal_results",
    "beliefs_item_kruskal_results",
    "omnibus_summary",
    "art_pairwise_results",
    "q17_pairwise_results",
    "beliefs_theme_pairwise_results",
    "beliefs_item_pairwise_results"
  ),
  file = c(
    "ART_Profile_Descriptives.csv",
    "Q17_Profile_Descriptives.csv",
    "Beliefs_Theme_Profile_Descriptives.csv",
    "Beliefs_Item_Profile_Descriptives.csv",
    "ART_Profile_Kruskal_Results.csv",
    "Q17_Profile_Kruskal_Results.csv",
    "Beliefs_Theme_Profile_Kruskal_Results.csv",
    "Beliefs_Item_Profile_Kruskal_Results.csv",
    "Profile_Comparison_Omnibus_Summary.csv",
    "ART_Profile_Pairwise_Wilcoxon_Results.csv",
    "Q17_Profile_Pairwise_Wilcoxon_Results.csv",
    "Beliefs_Theme_Profile_Pairwise_Wilcoxon_Results.csv",
    "Beliefs_Item_Profile_Pairwise_Wilcoxon_Results.csv"
  )
)

write_csv(manifest, file.path(csv_dir, "Profile_External_Comparison_Manifest.csv"))
knitr::kable(manifest)
```
