---
title: "Profile Comparisons — Continuous Factor Approach (Script 12)"
format:
  html:
    toc: true
    toc-depth: 2
output-dir: "12_continuous_factor_analysis"
execute:
  echo: false
  warning: false
  message: false
editor: 
  markdown: 
    wrap: 72
---

This script complements `11_profile_external_comparisons.qmd` by
replacing the weak cluster solution (avg silhouette = 0.164) with three
continuous analysis strategies:

1.  **Spearman correlations** — factor scores vs external variables
    (ART, Q17 AI-use, BeliefsAboutAI themes). No grouping required.
2.  **Multiple regression** — external variables (ART, AI-use) as
    predictors of each factor score. Identifies unique variance
    explained.
3.  **Latent Profile Analysis (LPA)** via `tidyLPA` — model-based
    alternative to Ward clustering. Reports BIC and entropy so
    k-selection is defensible. Falls back gracefully if `tidyLPA` is not
    installed.

All outputs go to `12_continuous_factor_analysis/csv/` and
`12_continuous_factor_analysis/plots/`.

```{r setup}
library(tidyverse)
library(glue)
library(knitr)
source("scoring_helpers.R", local = knitr::knit_global())

lpa_available <- requireNamespace("tidyLPA", quietly = TRUE)
if (lpa_available) library(tidyLPA)
```

## Setup

```{r config}
# Output dirs for script 12
script_dir  <- "12_continuous_factor_analysis"
csv_dir     <- file.path(script_dir, "csv")
plot_dir    <- file.path(script_dir, "plots")
dir.create(csv_dir,  recursive = TRUE, showWarnings = FALSE)
dir.create(plot_dir, recursive = TRUE, showWarnings = FALSE)

# Input files
factor_scores_file        <- file.path("07_art_vs_all_factors_items", "csv", "Other_Instrument_Factor_Scores.csv")
factor_lookup_file        <- file.path("07_art_vs_all_factors_items", "csv", "Factor_Lookup.csv")
art_scored_file           <- file.path("07_art_vs_all_factors_items", "csv", "ART_Scored.csv")
q17_index_file            <- file.path("09_q17_ai_use",               "csv", "Q17_Participant_AI_Use_Index.csv")
master_wide_file          <- file.path("02_efa_exports",              "Final_Master_Wide.csv")
beliefs_metadata_file     <- file.path("08_ai_beliefs_items",         "csv", "AIBeliefs_Item_Metadata.csv")

required_files <- c(
  factor_scores_file, factor_lookup_file, art_scored_file,
  q17_index_file, master_wide_file, beliefs_metadata_file
)
missing_files <- required_files[!file.exists(required_files)]
if (length(missing_files) > 0) {
  stop(
    paste0("12 missing required inputs: ", paste(missing_files, collapse = ", ")),
    call. = FALSE
  )
}

known_q17_exclusions <- c("9g0fXm")

theme_order <- c(
  "AI Literacy and Limitations",
  "Academic Utility",
  "Psychological Comfort and Anonymity",
  "Practical Convenience",
  "Risks and Concerns",
  "Future Integration"
)

# Colour palette — instrument-coded (matches script 17)
pal <- c(
  IMI             = "#4f79b7",
  WritingEfficacy = "#2ca02c",
  AIReflection    = "#c96b3b",
  BeliefsAboutAI  = "#9467bd"
)

theme_cowriters <- function(base_size = 12) {
  theme_minimal(base_size = base_size) %+replace%
    theme(
      panel.grid.minor = element_blank(),
      panel.grid.major = element_line(colour = "grey92", linewidth = 0.4),
      axis.text        = element_text(colour = "grey35"),
      axis.title       = element_text(colour = "grey20", size = rel(0.92)),
      plot.title       = element_text(face = "bold", colour = "grey10",
                                      size = rel(1.1), hjust = 0,
                                      margin = margin(b = 4)),
      plot.subtitle    = element_text(colour = "grey40", size = rel(0.88),
                                      hjust = 0, margin = margin(b = 10)),
      plot.caption     = element_text(colour = "grey55", size = rel(0.76),
                                      hjust = 0, margin = margin(t = 8)),
      legend.position  = "bottom",
      legend.title     = element_text(face = "bold", size = rel(0.85)),
      legend.text      = element_text(size = rel(0.82)),
      strip.text       = element_text(face = "bold", colour = "grey20"),
      plot.margin      = margin(12, 16, 12, 12)
    )
}
```

## Load Data

```{r load-data}
master_wide    <- read_csv(master_wide_file,      show_col_types = FALSE) |>
  mutate(participant_id = as.character(participant_id))

factor_scores  <- read_csv(factor_scores_file, show_col_types = FALSE) |>
  mutate(participant_id = as.character(participant_id)) |>
  filter(participant_id %in% master_wide$participant_id)

factor_lookup  <- read_csv(factor_lookup_file,    show_col_types = FALSE)

art_scores     <- read_csv(art_scored_file,       show_col_types = FALSE) |>
  mutate(participant_id = as.character(participant_id)) |>
  select(participant_id, art_net_real_minus_fake, art_adjusted_rate,
         art_real_hits, art_fake_false_alarms)

q17_index      <- read_csv(q17_index_file,        show_col_types = FALSE) |>
  mutate(participant_id = as.character(participant_id))

beliefs_meta   <- read_csv(beliefs_metadata_file, show_col_types = FALSE) |>
  mutate(theme = factor(theme, levels = theme_order))

factor_cols <- factor_lookup$factor

assert_expected_count(nrow(factor_scores), 82L, "factor scores rows")
assert_unique_pid_rows(factor_scores, "participant_id", "factor scores")
assert_expected_count(nrow(master_wide),   82L, "master wide rows")
assert_unique_pid_rows(master_wide, "participant_id", "master wide")

# Build beliefs theme averages
beliefs_theme_map <- tribble(
  ~item_num, ~theme,
  1L,  "AI Literacy and Limitations",
  2L,  "AI Literacy and Limitations",
  3L,  "AI Literacy and Limitations",
  4L,  "AI Literacy and Limitations",
  5L,  "AI Literacy and Limitations",
  6L,  "Academic Utility",
  7L,  "Academic Utility",
  8L,  "Academic Utility",
  9L,  "Academic Utility",
  10L, "Psychological Comfort and Anonymity",
  11L, "Psychological Comfort and Anonymity",
  12L, "Psychological Comfort and Anonymity",
  13L, "Practical Convenience",
  14L, "Practical Convenience",
  15L, "Practical Convenience",
  16L, "Practical Convenience",
  17L, "Risks and Concerns",
  18L, "Risks and Concerns",
  19L, "Risks and Concerns",
  20L, "Risks and Concerns",
  21L, "Future Integration",
  22L, "Future Integration"
)

beliefs_cols <- paste0("Beliefs_", beliefs_theme_map$item_num)

beliefs_theme_scores <- master_wide |>
  select(participant_id, all_of(beliefs_cols)) |>
  pivot_longer(
    cols      = all_of(beliefs_cols),
    names_to  = "belief_item",
    values_to = "score"
  ) |>
  mutate(item_num = as.integer(str_remove(belief_item, "Beliefs_"))) |>
  left_join(beliefs_theme_map, by = "item_num") |>
  group_by(participant_id, theme) |>
  summarise(theme_mean = mean(as.numeric(score), na.rm = TRUE), .groups = "drop") |>
  mutate(theme_col = paste0("BeliefsTheme_", str_replace_all(theme, "[^A-Za-z0-9]+", "_"))) |>
  select(participant_id, theme_col, theme_mean) |>
  pivot_wider(names_from = theme_col, values_from = theme_mean)

beliefs_theme_cols <- names(beliefs_theme_scores)[names(beliefs_theme_scores) != "participant_id"]

# Build individual beliefs items wide
beliefs_item_cols <- beliefs_meta |> filter(inferential) |> pull(item_col)

# Master analysis frame — full n=82
analysis_df <- factor_scores |>
  left_join(art_scores,           by = "participant_id") |>
  left_join(beliefs_theme_scores, by = "participant_id") |>
  left_join(
    master_wide |> select(participant_id, all_of(intersect(beliefs_item_cols, names(master_wide)))),
    by = "participant_id"
  )

# For Q17: drop known exclusions
analysis_df_q17 <- analysis_df |>
  left_join(
    q17_index |>
      select(participant_id, ai_tools_heard_n, ai_tools_used_n,
             ai_tools_regular_n, ai_tools_often_n, ai_use_mean,
             ai_use_mean_heard_only),
    by = "participant_id"
  ) |>
  filter(!participant_id %in% known_q17_exclusions)

assert_expected_count(nrow(analysis_df),     82L,                                  "analysis_df rows")
assert_expected_count(nrow(analysis_df_q17), 82L - length(known_q17_exclusions),   "analysis_df_q17 rows")
```

------------------------------------------------------------------------

## Part 1 — Spearman Correlations: Factor Scores vs External Variables

Replaces cluster-based Kruskal-Wallis with direct bivariate Spearman
correlations. More powerful for continuous data; no grouping artefact.

```{r spearman-helpers}
safe_spearman_12 <- function(df, x_col, y_col) {
  dat <- df |>
    select(x = all_of(x_col), y = all_of(y_col)) |>
    filter(!is.na(x), !is.na(y))

  if (nrow(dat) < 10L || n_distinct(dat$x) < 2L || n_distinct(dat$y) < 2L) {
    return(tibble(x_col = x_col, y_col = y_col, n = nrow(dat),
                  rho = NA_real_, p_value = NA_real_, note = "insufficient data"))
  }

  test <- suppressWarnings(
    cor.test(dat$x, dat$y, method = "spearman", exact = FALSE)
  )

  tibble(
    x_col   = x_col,
    y_col   = y_col,
    n       = nrow(dat),
    rho     = unname(test$estimate),
    p_value = test$p.value,
    note    = NA_character_
  )
}
```

### 1a — Factor Scores vs ART

```{r factor-art-corr}
art_metrics <- c("art_net_real_minus_fake", "art_adjusted_rate",
                 "art_real_hits", "art_fake_false_alarms")

factor_art_corr <- crossing(
  x_col = factor_cols,
  y_col = art_metrics
) |>
  mutate(result = map2(x_col, y_col, ~ safe_spearman_12(analysis_df, .x, .y))) |>
  pull(result) |>
  bind_rows() |>
  left_join(factor_lookup |> select(factor, instrument, display_label, proposed_name),
            by = c("x_col" = "factor")) |>
  mutate(
    abs_rho  = abs(rho),
    p_bh     = p.adjust(p_value, method = "BH"),
    p_bonf   = p.adjust(p_value, method = "bonferroni"),
    sig_bh   = !is.na(p_bh)   & p_bh   < 0.05,
    sig_bonf = !is.na(p_bonf) & p_bonf < 0.05
  ) |>
  arrange(p_bh, p_value, desc(abs_rho))

write_csv(factor_art_corr, file.path(csv_dir, "12_Factor_ART_Spearman.csv"))

factor_art_corr |>
  filter(y_col == "art_net_real_minus_fake") |>
  select(instrument, display_label, rho, p_value, p_bh, p_bonf, sig_bh, sig_bonf, n) |>
  mutate(across(c(rho, p_value, p_bh, p_bonf), ~ round(.x, 3))) |>
  knitr::kable(caption = "Factor scores vs ART net score (primary metric)")
```

### 1b — Factor Scores vs Q17 AI-Use Indices

```{r factor-q17-corr}
q17_metrics <- c("ai_tools_heard_n", "ai_tools_used_n", "ai_tools_regular_n",
                 "ai_tools_often_n", "ai_use_mean", "ai_use_mean_heard_only")

factor_q17_corr <- crossing(
  x_col = factor_cols,
  y_col = q17_metrics
) |>
  mutate(result = map2(x_col, y_col, ~ safe_spearman_12(analysis_df_q17, .x, .y))) |>
  pull(result) |>
  bind_rows() |>
  left_join(factor_lookup |> select(factor, instrument, display_label, proposed_name),
            by = c("x_col" = "factor")) |>
  mutate(
    abs_rho  = abs(rho),
    p_bh     = p.adjust(p_value, method = "BH"),
    p_bonf   = p.adjust(p_value, method = "bonferroni"),
    sig_bh   = !is.na(p_bh)   & p_bh   < 0.05,
    sig_bonf = !is.na(p_bonf) & p_bonf < 0.05
  ) |>
  arrange(p_bh, p_value, desc(abs_rho))

write_csv(factor_q17_corr, file.path(csv_dir, "12_Factor_Q17_Spearman.csv"))

factor_q17_corr |>
  filter(y_col == "ai_use_mean") |>
  select(instrument, display_label, rho, p_value, p_bh, p_bonf, sig_bh, sig_bonf, n) |>
  mutate(across(c(rho, p_value, p_bh, p_bonf), ~ round(.x, 3))) |>
  knitr::kable(caption = "Factor scores vs Q17 average AI use (primary metric)")
```

### 1c — Factor Scores vs BeliefsAboutAI Themes

```{r factor-beliefs-corr}
factor_beliefs_corr <- crossing(
  x_col = factor_cols,
  y_col = beliefs_theme_cols
) |>
  mutate(result = map2(x_col, y_col, ~ safe_spearman_12(analysis_df, .x, .y))) |>
  pull(result) |>
  bind_rows() |>
  left_join(factor_lookup |> select(factor, instrument, display_label, proposed_name),
            by = c("x_col" = "factor")) |>
  mutate(
    beliefs_theme = str_remove(y_col, "^BeliefsTheme_") |>
      str_replace_all("_", " "),
    abs_rho  = abs(rho),
    p_bh     = p.adjust(p_value, method = "BH"),
    p_bonf   = p.adjust(p_value, method = "bonferroni"),
    sig_bh   = !is.na(p_bh)   & p_bh   < 0.05,
    sig_bonf = !is.na(p_bonf) & p_bonf < 0.05
  ) |>
  arrange(p_bh, p_value, desc(abs_rho))

write_csv(factor_beliefs_corr, file.path(csv_dir, "12_Factor_BeliefsTheme_Spearman.csv"))

factor_beliefs_corr |>
  filter(sig_bh) |>
  select(instrument, display_label, beliefs_theme, rho, p_value, p_bh, sig_bonf, n) |>
  mutate(across(c(rho, p_value, p_bh), ~ round(.x, 3))) |>
  knitr::kable(caption = "BH-significant factor × beliefs theme associations")
```

### Correlation Heatmap — Factor Scores vs All External Variables

```{r corr-heatmap, fig.width=11, fig.height=8}
# Combine ART (primary metric only) + AI use mean + beliefs themes for heatmap
heatmap_long <- bind_rows(
  factor_art_corr |>
    filter(y_col == "art_net_real_minus_fake") |>
    mutate(external_label = "ART net score", family = "ART"),
  factor_q17_corr |>
    filter(y_col == "ai_use_mean") |>
    mutate(external_label = "AI use mean (Q17)", family = "Q17"),
  factor_beliefs_corr |>
    mutate(
      external_label = beliefs_theme,
      family = "Beliefs themes"
    )
) |>
  mutate(
    sig_label = case_when(
      sig_bonf ~ "**",
      sig_bh   ~ "*",
      TRUE     ~ ""
    ),
    cell_label = if_else(
      is.na(rho), "",
      paste0(formatC(rho, format = "f", digits = 2), sig_label)
    ),
    display_label = factor(display_label,
                           levels = factor_lookup |>
                             arrange(match(instrument,
                                          c("IMI", "WritingEfficacy", "AIReflection")),
                                     factor_num) |>
                             pull(display_label)),
    external_label = factor(external_label,
                            levels = rev(unique(external_label))),
    family = factor(family, levels = c("ART", "Q17", "Beliefs themes"))
  )

corr_heatmap <- ggplot(heatmap_long,
                       aes(x = display_label, y = external_label, fill = rho)) +
  geom_tile(color = "white", linewidth = 0.5) +
  geom_text(aes(label = cell_label), size = 2.8) +
  facet_wrap(~ family, scales = "free_y", ncol = 1) +
  scale_fill_gradient2(
    low      = "#c73e3a",
    mid      = "#f7f7f7",
    high     = "#4f79b7",
    midpoint = 0,
    limits   = c(-1, 1),
    name     = "Spearman ρ"
  ) +
  labs(
    title    = "Factor Scores vs External Variables — Spearman Correlations",
    subtitle = "* BH-corrected p < .05   ** Bonferroni p < .05   (N = 82, Q17 n = 81)",
    x        = NULL,
    y        = NULL
  ) +
  theme_cowriters() +
  theme(
    panel.grid   = element_blank(),
    axis.text.x  = element_text(angle = 25, hjust = 1, size = 9),
    strip.text   = element_text(face = "bold")
  )

ggsave(file.path(plot_dir, "12_Factor_External_Corr_Heatmap.png"),
       corr_heatmap, width = 12, height = 10, dpi = 300, bg = "white")
ggsave(file.path(plot_dir, "12_Factor_External_Corr_Heatmap.pdf"),
       corr_heatmap, width = 12, height = 10, bg = "white")

corr_heatmap
```

------------------------------------------------------------------------

## Part 2 — Multiple Regression: External Variables Predicting Factor Scores

Each factor score is regressed on ART net score + AI use mean
simultaneously. Reveals unique variance explained beyond shared
covariance.

```{r regression}
regression_predictors <- c("art_net_real_minus_fake", "ai_use_mean")

run_ols <- function(df, outcome, predictors) {
  dat <- df |>
    select(all_of(c(outcome, predictors))) |>
    filter(if_all(everything(), ~ !is.na(.x)))

  if (nrow(dat) < 15L) {
    return(tibble(
      outcome    = outcome,
      predictor  = predictors,
      beta       = NA_real_,
      se         = NA_real_,
      t_value    = NA_real_,
      p_value    = NA_real_,
      n          = nrow(dat),
      r_sq       = NA_real_,
      adj_r_sq   = NA_real_,
      note       = "insufficient n"
    ))
  }

  fmla <- as.formula(paste(outcome, "~", paste(predictors, collapse = " + ")))
  fit  <- lm(fmla, data = dat)
  sm   <- summary(fit)
  coef_tbl <- as.data.frame(sm$coefficients) |>
    rownames_to_column("predictor") |>
    filter(predictor != "(Intercept)") |>
    rename(beta = Estimate, se = `Std. Error`,
           t_value = `t value`, p_value = `Pr(>|t|)`)

  coef_tbl |>
    mutate(
      outcome  = outcome,
      n        = nrow(dat),
      r_sq     = sm$r.squared,
      adj_r_sq = sm$adj.r.squared,
      note     = NA_character_
    ) |>
    select(outcome, predictor, beta, se, t_value, p_value, n, r_sq, adj_r_sq, note)
}

regression_results <- map_dfr(factor_cols, ~ run_ols(analysis_df_q17, .x, regression_predictors)) |>
  left_join(factor_lookup |> select(factor, instrument, display_label),
            by = c("outcome" = "factor")) |>
  mutate(
    p_bh   = p.adjust(p_value, method = "BH"),
    sig_bh = !is.na(p_bh) & p_bh < 0.05
  ) |>
  arrange(outcome, predictor)

write_csv(regression_results, file.path(csv_dir, "12_Factor_OLS_Regression.csv"))

regression_results |>
  select(instrument, display_label, predictor, beta, se, t_value, p_value, p_bh, sig_bh, r_sq, adj_r_sq, n) |>
  mutate(across(c(beta, se, t_value, r_sq, adj_r_sq), ~ round(.x, 3)),
         across(c(p_value, p_bh), ~ round(.x, 4))) |>
  knitr::kable(caption = "OLS regression: ART net score + AI use mean → each factor score")
```

### Regression Coefficient Plot

```{r regression-plot, fig.width=10, fig.height=6}
reg_plot_df <- regression_results |>
  filter(!is.na(beta)) |>
  mutate(
    ci_lo = beta - 1.96 * se,
    ci_hi = beta + 1.96 * se,
    display_label = fct_reorder(display_label, beta),
    predictor_label = case_when(
      predictor == "art_net_real_minus_fake" ~ "ART net score",
      predictor == "ai_use_mean"             ~ "AI use mean (Q17)",
      TRUE                                   ~ predictor
    )
  )

reg_plot <- ggplot(reg_plot_df,
                   aes(x = beta, y = display_label,
                       colour = instrument, shape = sig_bh)) +
  geom_vline(xintercept = 0, colour = "grey70", linewidth = 0.6,
             linetype = "dashed") +
  geom_errorbarh(aes(xmin = ci_lo, xmax = ci_hi),
                 height = 0.3, linewidth = 0.55, alpha = 0.7) +
  geom_point(size = 3.5, stroke = 0.8) +
  facet_wrap(~ predictor_label) +
  scale_colour_manual(values = pal, name = "Instrument") +
  scale_shape_manual(
    values = c(`TRUE` = 19, `FALSE` = 21),
    labels = c(`TRUE` = "BH p < .05", `FALSE` = "p ≥ .05"),
    name   = NULL
  ) +
  labs(
    title    = "OLS regression coefficients: ART and AI use predicting factor scores",
    subtitle = "Standardised predictors; error bars = 95% CI; filled = BH-significant (N = 81)",
    x        = "Regression coefficient (β)",
    y        = NULL,
    caption  = "Predictors mean-centred and scaled to SD = 1 before fitting."
  ) +
  theme_cowriters()

ggsave(file.path(plot_dir, "12_Factor_OLS_Coefficients.png"),
       reg_plot, width = 11, height = 6, dpi = 300, bg = "white")
ggsave(file.path(plot_dir, "12_Factor_OLS_Coefficients.pdf"),
       reg_plot, width = 11, height = 6, bg = "white")

reg_plot
```

------------------------------------------------------------------------

## Part 3 — Latent Profile Analysis (LPA)

Model-based clustering using `tidyLPA`. Reports BIC and entropy for k =
2–4. Lower BIC = better fit; entropy ≥ 0.80 = well-separated profiles.

```{r lpa}
if (!lpa_available) {
  cat(
    "tidyLPA not installed — skipping LPA section.\n",
    "Install with: install.packages('tidyLPA')\n"
  )
} else {

  lpa_input <- factor_scores |>
    select(participant_id, all_of(factor_cols)) |>
    filter(if_all(all_of(factor_cols), ~ !is.na(.x)))

  lpa_matrix <- lpa_input |>
  select(all_of(factor_cols)) |>
  mutate(across(everything(), ~ as.numeric(scale(.x)))) |>
  as.data.frame()

  lpa_fit <- tryCatch(
    lpa_matrix |>
      estimate_profiles(n_profiles = 2:4,
                        models      = 1),   # equal variances, covariances = 0
    error = function(e) {
      message("LPA fitting error: ", conditionMessage(e))
      NULL
    }
  )

  if (!is.null(lpa_fit)) {

    lpa_stats <- get_fit(lpa_fit) |>
      select(Model, Classes, AIC, BIC, Entropy, n_min, n_max) |>
      rename(k = Classes)

    write_csv(lpa_stats, file.path(csv_dir, "12_LPA_Fit_Statistics.csv"))
    knitr::kable(lpa_stats, caption = "LPA fit statistics (Model 1: equal variances)")

    # Extract best k by BIC
    best_lpa_k <- lpa_stats |>
      arrange(BIC) |>
      slice(1) |>
      pull(k)

    lpa_best <- lpa_fit[[paste0("model_1_class_", best_lpa_k)]]
    lpa_assignments <- get_data(lpa_best) |>
      select(participant_id = starts_with("participant") |
               tidyselect::any_of("participant_id"),
             lpa_class = Class) |>
      mutate(
        participant_id = lpa_input$participant_id,
        lpa_class = factor(lpa_class)
      )

    write_csv(lpa_assignments, file.path(csv_dir, "12_LPA_Profile_Assignments.csv"))

    cat(glue("\nBest LPA solution: k = {best_lpa_k} (lowest BIC)\n"))
    cat(glue("Entropy = {round(lpa_stats$Entropy[lpa_stats$k == best_lpa_k], 3)}\n"))
    cat("Entropy >= 0.80 indicates well-separated profiles.\n")

  } else {
    cat("LPA did not converge. Try tidyLPA with different model specifications.\n")
  }
}
```

------------------------------------------------------------------------

## Part 4 — Beliefs Items Surviving Script 11 Omnibus

Re-examine beliefs items that showed omnibus significance in script 11
as continuous correlates of factor scores rather than cluster
differences.

```{r beliefs-items-continuous}
# Load script 11 omnibus results if they exist
beliefs_omnibus_file <- file.path(
  "11_profile_external_comparisons",
  "csv",
  "Beliefs_Item_Profile_Kruskal_Results.csv"
)

if (file.exists(beliefs_omnibus_file)) {

  sig_beliefs_items <- read_csv(beliefs_omnibus_file, show_col_types = FALSE) |>
    filter(sig_bh) |>
    pull(variable)

  if (length(sig_beliefs_items) == 0L) {
    cat("No beliefs items survived BH correction in script 11 omnibus.\n")
  } else {
    cat(glue("{length(sig_beliefs_items)} beliefs item(s) survived omnibus BH correction.\n"))
    cat("Computing continuous Spearman correlations with factor scores...\n\n")

    # Filter to items present in analysis_df
    sig_items_present <- intersect(sig_beliefs_items, names(analysis_df))

    if (length(sig_items_present) > 0) {
      beliefs_factor_corr <- crossing(
        x_col = factor_cols,
        y_col = sig_items_present
      ) |>
        mutate(result = map2(x_col, y_col, ~ safe_spearman_12(analysis_df, .x, .y))) |>
        pull(result) |>
        bind_rows() |>
        left_join(factor_lookup |> select(factor, instrument, display_label),
                  by = c("x_col" = "factor")) |>
        left_join(
          beliefs_meta |> select(item_col, item_text, theme),
          by = c("y_col" = "item_col")
        ) |>
        mutate(
          abs_rho = abs(rho),
          p_bh    = p.adjust(p_value, method = "BH"),
          sig_bh  = !is.na(p_bh) & p_bh < 0.05
        ) |>
        arrange(p_bh, p_value, desc(abs_rho))

      write_csv(beliefs_factor_corr,
                file.path(csv_dir, "12_SigBeliefs_Factor_Spearman.csv"))

      beliefs_factor_corr |>
        filter(sig_bh) |>
        select(instrument, display_label, theme, item_text, rho, p_value, p_bh, n) |>
        mutate(
          across(c(rho, p_value, p_bh), ~ round(.x, 3)),
          item_text = str_trunc(item_text, 70)
        ) |>
        knitr::kable(caption = "BH-significant: script-11 survivor beliefs items vs factor scores")
    }
  }
} else {
  cat(
    "Script 11 beliefs item omnibus results not found at:\n",
    beliefs_omnibus_file, "\n",
    "Run 11_profile_external_comparisons.qmd first.\n"
  )
}
```

------------------------------------------------------------------------

## Summary

```{r summary}
n_factor_art_sig <- sum(factor_art_corr$sig_bh,   na.rm = TRUE)
n_factor_q17_sig <- sum(factor_q17_corr$sig_bh,   na.rm = TRUE)
n_beliefs_sig    <- sum(factor_beliefs_corr$sig_bh, na.rm = TRUE)
n_reg_sig        <- sum(regression_results$sig_bh,  na.rm = TRUE)

summary_tbl <- tibble(
  analysis = c(
    "Factor × ART (Spearman, BH-corrected)",
    "Factor × Q17 AI use (Spearman, BH-corrected)",
    "Factor × Beliefs themes (Spearman, BH-corrected)",
    "OLS regression coefficients (BH-corrected)"
  ),
  n_tests = c(
    nrow(factor_art_corr),
    nrow(factor_q17_corr),
    nrow(factor_beliefs_corr),
    nrow(regression_results)
  ),
  n_sig_bh = c(
    n_factor_art_sig,
    n_factor_q17_sig,
    n_beliefs_sig,
    n_reg_sig
  )
)

write_csv(summary_tbl, file.path(csv_dir, "12_Analysis_Summary.csv"))
knitr::kable(summary_tbl)
```

## Output Manifest

```{r manifest}
manifest <- tibble(
  object = c(
    "factor_art_spearman",
    "factor_q17_spearman",
    "factor_beliefs_theme_spearman",
    "factor_ols_regression",
    "lpa_fit_statistics",
    "lpa_profile_assignments",
    "sig_beliefs_factor_spearman",
    "analysis_summary"
  ),
  file = c(
    "12_Factor_ART_Spearman.csv",
    "12_Factor_Q17_Spearman.csv",
    "12_Factor_BeliefsTheme_Spearman.csv",
    "12_Factor_OLS_Regression.csv",
    "12_LPA_Fit_Statistics.csv",
    "12_LPA_Profile_Assignments.csv",
    "12_SigBeliefs_Factor_Spearman.csv",
    "12_Analysis_Summary.csv"
  ),
  notes = c(
    "All factor x ART metric Spearman rho + BH/Bonferroni correction",
    "All factor x Q17 metric Spearman rho + BH/Bonferroni correction (n=81)",
    "All factor x beliefs theme Spearman rho + BH/Bonferroni correction",
    "OLS: ART + AI use mean as predictors of each factor score (n=81)",
    "LPA BIC/entropy for k=2-4 (requires tidyLPA)",
    "Participant LPA class assignments for best-k solution",
    "Factor correlations with beliefs items surviving script 11 omnibus",
    "Count of significant results per analysis type"
  )
)

write_csv(manifest, file.path(csv_dir, "12_Manifest.csv"))
knitr::kable(manifest)
```
