---
title: "AI Model Use vs Factor Scores and Item Statements"
format:
  html:
    toc: true
    toc-depth: 3
output-dir: "12_model_use_vs_factors_items"
execute:
  echo: false
  warning: false
  message: false
editor: 
  markdown: 
    wrap: 72
---

This report examines whether the specific AI tool a participant uses
most is associated with their psychological factor scores (IMI,
WritingEfficacy, AIReflection) and individual item-level responses
across all four instruments.

Two complementary analyses:

1.  **Per-model continuous correlations** — Spearman rho between each
    model's use score (1–5) and each factor/item, across all
    participants with valid data for that model. Mirrors the approach in
    `07` and `09`.
2.  **Primary-model group comparisons** — classify each participant by
    their dominant model (highest use score among the four focus
    models), then run Kruskal-Wallis + pairwise Wilcoxon on factor
    scores.

Focus models: ChatGPT, Claude, Gemini, Copilot.

```{r setup}
library(tidyverse)
library(psych)
library(glue)
library(knitr)
library(forcats)
library(scales)
source("scoring_helpers.R", local = knitr::knit_global())

set.seed(42L)
```

## Configuration

```{r config}
script_dir    <- "12_model_use_vs_factors_items"
csv_dir       <- file.path(script_dir, "csv")
plot_dir      <- file.path(script_dir, "plots")
q17_csv_dir   <- file.path("07_q17_ai_usePART2", "csv")

recommended_k_file <- file.path("03_efa_analysis", "EFA_Recommended_K.csv")
dir.create(csv_dir,  recursive = TRUE, showWarnings = FALSE)
dir.create(plot_dir, recursive = TRUE, showWarnings = FALSE)

factor_score_method    <- "tenBerge"
min_corr_n             <- 10L
min_group_n_kw         <- 5L   # minimum per group for KW
min_group_n_pairwise   <- 4L   # minimum per pair for Wilcoxon

# Focus models only (sufficient N expected)
focus_models <- c(
  "ChatGPT (including DALL-E) by OpenAI",
  "Claude by Anthropic",
  "Gemini (formerly Bard) by Google",
  "Copilot (Bing Chat) by Microsoft"
)

focus_model_labels <- c(
  "ChatGPT (including DALL-E) by OpenAI" = "ChatGPT",
  "Claude by Anthropic"                  = "Claude",
  "Gemini (formerly Bard) by Google"     = "Gemini",
  "Copilot (Bing Chat) by Microsoft"     = "Copilot"
)

q17_response_map <- c(
  "I have never heard of this tool."         = 1L,
  "I have heard of this tool but never used it." = 2L,
  "I rarely use this tool."                  = 3L,
  "I sometimes use this tool."               = 4L,
  "I often use this tool."                   = 5L
)

factor_name_map <- tribble(
  ~instrument,       ~factor_num, ~proposed_name,
  "IMI",              1L,          "Interest & Enjoyment",
  "IMI",              2L,          "Effort & Importance",
  "IMI",              3L,          "Perceived Competence",
  "WritingEfficacy",  1L,          "Writing Competence",
  "WritingEfficacy",  2L,          "Self-Regulation",
  "WritingEfficacy",  3L,          "Resource & Planning",
  "AIReflection",     1L,          "Ownership & Usefulness",
  "AIReflection",     2L,          "Enjoyment & Satisfaction"
)

factor_instrument_specs <- tribble(
  ~instrument,       ~file,                                                             ~item_id_col, ~score_transform, ~prefix,
  "IMI",             file.path("02_efa_exports", "efa", "IMI_EFA_Primary.csv"),         "item_code",  "identity",       "IMI",
  "WritingEfficacy", file.path("02_efa_exports", "efa", "WritingEfficacy_EFA_Primary.csv"), "item_code", "wse_to_5",   "WSE",
  "AIReflection",    file.path("02_efa_exports", "efa", "AI_Reflection_EFA_Primary.csv"), "item_num",  "identity",      "AIRefl"
)

item_instrument_specs <- tribble(
  ~instrument,       ~file,                                                                         ~item_id_col, ~score_transform, ~prefix,
  "IMI",             file.path("01_audit_cleaning", "cleaned", "IMI_cleaned.csv"),                  "item_code",  "identity",       "IMI",
  "WritingEfficacy", file.path("01_audit_cleaning", "cleaned", "WritingEfficacy_cleaned.csv"),       "item_code",  "wse_to_5",       "Efficacy",
  "AIReflection",    file.path("01_audit_cleaning", "cleaned", "AI_Reflection_cleaned.csv"),         "item_num",   "identity",       "Refl",
  "BeliefsAboutAI",  file.path("01_audit_cleaning", "cleaned", "BeliefsAboutAI_cleaned.csv"),        "item_num",   "identity",       "Beliefs"
)

recommended_k_raw <- read_csv(recommended_k_file, show_col_types = FALSE)
valid_factor_specs <- factor_instrument_specs |>
  left_join(
    recommended_k_raw |>
      transmute(instrument, recommended_k = as.integer(recommended_k),
                factorability_flag = as.character(factorability_flag)),
    by = "instrument"
  ) |>
  filter(!is.na(recommended_k))
```

## Helper Functions

```{r helpers}
normalize_text <- function(x) {
  x |>
    str_replace_all("[\u2018\u2019]", "'") |>
    str_replace_all("[\u201C\u201D]", "\"") |>
    str_squish()
}

transform_scores <- function(x, transform_name) {
  values <- as.numeric(x)
  if (transform_name == "identity") return(values)
  if (transform_name == "wse_to_5") {
    return(case_when(
      is.na(values)              ~ NA_real_,
      values %in% c(0,25,50,75,100) ~ (values / 25) + 1,
      TRUE                       ~ NA_real_
    ))
  }
  stop(glue("Unknown score transform: {transform_name}"))
}

safe_spearman <- function(data, predictor, outcome) {
  dat <- data |>
    select(all_of(c(predictor, outcome))) |>
    filter(if_all(everything(), ~ !is.na(.x)))

  if (nrow(dat) < min_corr_n ||
      dplyr::n_distinct(dat[[predictor]]) < 2L ||
      dplyr::n_distinct(dat[[outcome]])   < 2L) {
    return(tibble(predictor = predictor, outcome = outcome,
                  n = nrow(dat), rho = NA_real_, p_value = NA_real_,
                  note = "insufficient variation or sample size"))
  }

  test <- suppressWarnings(
    cor.test(dat[[predictor]], dat[[outcome]], method = "spearman", exact = FALSE)
  )
  tibble(predictor = predictor, outcome = outcome,
         n = nrow(dat), rho = unname(test$estimate), p_value = test$p.value,
         note = NA_character_)
}

build_factor_scores <- function(instrument, file, item_id_col, score_transform, prefix, recommended_k) {
  long <- read_csv(file, show_col_types = FALSE) |>
    transmute(
      participant_id = as.character(participant_id),
      item_id        = as.integer(.data[[item_id_col]]),
      score          = transform_scores(score, score_transform)
    )

  wide <- long |>
    mutate(item_id = as.character(item_id)) |>
    pivot_wider(names_from = item_id, values_from = score) |>
    arrange(participant_id)

  matrix_df <- wide |>
    select(-participant_id) |>
    mutate(across(everything(), ~ as.integer(round(.x)))) |>
    as.data.frame()

  poly_out <- compute_polychoric_safe(matrix_df)

  set.seed(42L)
  fa_fit <- suppressWarnings(
    psych::fa(
      r         = poly_out$rho,
      nfactors  = recommended_k,
      n.obs     = nrow(matrix_df),
      fm        = "minres",
      rotate    = if (recommended_k == 1L) "none" else "oblimin"
    )
  )

  if (!is.null(fa_fit$Vaccounted) && recommended_k > 1L) {
    prop_var     <- fa_fit$Vaccounted["Proportion Var", ]
    factor_order <- order(prop_var, decreasing = TRUE)
  } else {
    factor_order <- seq_len(recommended_k)
  }

  ordered_loadings <- unclass(fa_fit$loadings)[, factor_order, drop = FALSE]
  colnames(ordered_loadings) <- paste0("MR", seq_len(recommended_k))
  fa_fit_ordered <- fa_fit
  fa_fit_ordered$loadings <- ordered_loadings
  class(fa_fit_ordered$loadings) <- c("loadings")

  score_matrix <- psych::factor.scores(
    x      = as.matrix(matrix_df),
    f      = fa_fit_ordered,
    rho    = poly_out$rho,
    method = factor_score_method
  )

  factor_scores <- bind_scores_with_ids(
    participant_ids = wide$participant_id,
    score_matrix    = score_matrix$scores,
    context_label   = paste0(instrument, " factor scores")
  ) |>
    rename_with(~ paste0(prefix, "_", .x), .cols = starts_with("MR"))

  factor_lookup <- tibble(
    factor = names(factor_scores)[names(factor_scores) != "participant_id"],
    instrument = instrument
  ) |>
    mutate(
      factor_id  = str_remove(factor, paste0("^", prefix, "_")),
      factor_num = as.integer(str_remove(factor_id, "MR"))
    ) |>
    left_join(factor_name_map, by = c("instrument", "factor_num")) |>
    mutate(
      proposed_name = coalesce(proposed_name, paste0("Factor ", factor_num)),
      short_factor  = paste0("F", factor_num),
      factor_label  = paste0(instrument, " ", short_factor),
      display_label = paste0(instrument, " ", short_factor, " - ", proposed_name)
    )

  list(instrument = instrument, factor_scores = factor_scores, factor_lookup = factor_lookup)
}

build_item_matrix <- function(instrument, file, item_id_col, score_transform, prefix) {
  long <- read_csv(file, show_col_types = FALSE) |>
    transmute(
      participant_id = as.character(participant_id),
      item_id        = as.integer(.data[[item_id_col]]),
      item_text      = as.character(item_text),
      score          = transform_scores(score, score_transform)
    )

  item_lookup <- long |>
    distinct(item_id, item_text) |>
    arrange(item_id) |>
    mutate(
      instrument    = instrument,
      item_col      = paste0(prefix, "_", item_id),
      item_label    = paste0(instrument, " Item ", item_id),
      display_label = paste0(instrument, " ", item_id, ": ", item_text)
    )

  wide <- long |>
    left_join(item_lookup |> select(item_id, item_col), by = "item_id") |>
    select(participant_id, item_col, score) |>
    pivot_wider(names_from = item_col, values_from = score) |>
    arrange(participant_id)

  list(instrument = instrument, item_lookup = item_lookup, wide = wide)
}
```

## Load Q17 Use Scores

```{r q17-load}
# Read the resolved Q17 CSV from script 07 outputs.
# Fallback: re-read from raw cleaned file if 07 output missing.
# ---------------------------------------------------------------------------
# Load long-format Q17 responses written by 07_q17_ai_usePART2:
# Q17_Responses_Long.csv — one row per participant x tool, columns:
#   participant_id | tool | response_text | use_score
# ---------------------------------------------------------------------------
q17_resolution_file <- file.path(q17_csv_dir, "Q17_Responses_Long.csv")

if (!file.exists(q17_resolution_file)) {
  stop(glue(
    "Cannot find {q17_resolution_file}.\n",
    "Re-run 07_q17_ai_usePART2 to regenerate it.\n",
    "Note: Q17_Submission_Resolution.csv is a per-participant summary and ",
    "cannot be used here — the long-format file is required."
  ), call. = FALSE)
}

q17_resolved_raw <- read_csv(q17_resolution_file, show_col_types = FALSE)

# Score responses and filter to focus models only
q17_focus <- q17_resolved_raw |>
  filter(tool %in% focus_models) |>
  mutate(
    participant_id = as.character(participant_id),
    use_score      = q17_response_map[normalize_text(response_text)],
    model_label    = focus_model_labels[tool]
  ) |>
  filter(!is.na(use_score))

# Participant × model use-score wide table
q17_wide <- q17_focus |>
  select(participant_id, model_label, use_score) |>
  pivot_wider(names_from = model_label, values_from = use_score) |>
  arrange(participant_id)

# Report coverage
q17_coverage <- q17_focus |>
  group_by(model_label) |>
  summarise(
    n_participants  = n_distinct(participant_id),
    n_regular       = sum(use_score >= 4L, na.rm = TRUE),
    pct_regular     = mean(use_score >= 4L, na.rm = TRUE),
    mean_use_score  = round(mean(use_score, na.rm = TRUE), 2),
    .groups = "drop"
  )

kable(q17_coverage, caption = "Q17 focus-model coverage")
```

## Assign Primary Model

A participant's primary model is the focus model with the highest use
score. Ties broken by first match in `focus_model_labels` order.
Participants with all-NA focus-model scores excluded.

```{r primary-model}


# Cleaner: non-rowwise approach
primary_model_df <- q17_wide |>
  pivot_longer(
    cols      = all_of(unname(focus_model_labels)),
    names_to  = "model_label",
    values_to = "use_score"
  ) |>
  filter(!is.na(use_score)) |>
  group_by(participant_id) |>
  slice_max(order_by = use_score, n = 1, with_ties = FALSE) |>
  ungroup() |>
  select(participant_id, primary_model = model_label)

primary_model_counts <- primary_model_df |>
  count(primary_model, name = "n") |>
  arrange(desc(n))

kable(primary_model_counts, caption = "Primary model group sizes")
```

## Build Factor Scores

```{r factor-scores}
factor_objects <- pmap(
  valid_factor_specs,
  function(instrument, file, item_id_col, score_transform, prefix, recommended_k, factorability_flag) {
    build_factor_scores(
      instrument       = instrument,
      file             = file,
      item_id_col      = item_id_col,
      score_transform  = score_transform,
      prefix           = prefix,
      recommended_k    = recommended_k
    )
  }
)

factor_score_tables <- map(factor_objects, "factor_scores")
factor_lookup       <- map_dfr(factor_objects, "factor_lookup")
all_factor_scores   <- reduce(factor_score_tables, full_join, by = "participant_id")
factor_cols         <- factor_lookup$factor
```

## Build Item Matrix

```{r item-matrix}
item_objects  <- pmap(
  item_instrument_specs,
  function(instrument, file, item_id_col, score_transform, prefix) {
    build_item_matrix(
      instrument      = instrument,
      file            = file,
      item_id_col     = item_id_col,
      score_transform = score_transform,
      prefix          = prefix
    )
  }
)

item_lookup    <- map_dfr(item_objects, "item_lookup")
all_item_wide  <- reduce(map(item_objects, "wide"), full_join, by = "participant_id")
item_cols      <- item_lookup$item_col
```

## Merge Analysis Dataset

```{r merge}
# Master df: participant_id | model use scores | factor scores | item scores | primary model
analysis_df <- q17_wide |>
  full_join(all_factor_scores, by = "participant_id") |>
  full_join(all_item_wide,     by = "participant_id") |>
  left_join(primary_model_df,  by = "participant_id")

assert_unique_pid_rows(analysis_df, "participant_id", "merged analysis df")

write_csv(analysis_df, file.path(csv_dir, "Model_Use_Factor_Item_Merged.csv"))
```

------------------------------------------------------------------------

```{r}
# Quick Verification: AI Sample Sizes and Breakdown
library(dplyr)
library(tidyr)

usage_verification <- analysis_df |>
  # Select the participant ID and the 4 focus models
  select(participant_id, ChatGPT, Claude, Gemini, Copilot) |>
  # Filter for participants who have valid scores for all 4 models
  filter(!is.na(ChatGPT) & !is.na(Claude) & !is.na(Gemini) & !is.na(Copilot)) |>
  rowwise() |>
  mutate(
    # Check if they used ChatGPT (score 3, 4, or 5)
    used_chatgpt = ChatGPT >= 3,
    # Count how many total focus models they used (score 3, 4, or 5)
    num_models_used = sum(c_across(c(ChatGPT, Claude, Gemini, Copilot)) >= 3)
  ) |>
  ungroup() |>
  # Summarize the exact breakdown
  summarise(
    `01. Total Valid Q17 Sample`                 = n(),
    `02. Total ChatGPT Users (score >= 3)`       = sum(used_chatgpt),
    `03. Zero Models Used`                       = sum(num_models_used == 0),
    `04. Exclusive ChatGPT Users (Only 1 model)` = sum(used_chatgpt & num_models_used == 1),
    `05. Exclusive Gemini Users (Only 1 model)`  = sum(Gemini >= 3 & num_models_used == 1),
    `06. Used exactly 2 models`                  = sum(num_models_used == 2),
    `07. Used exactly 3 models`                  = sum(num_models_used == 3),
    `08. Used all 4 models`                      = sum(num_models_used == 4)
  ) |>
  # Pivot so it prints as a clean vertical list instead of a wide table
  pivot_longer(everything(), names_to = "Metric", values_to = "Count")

# Print the results
print(usage_verification, n = 20)
```

# Part A — Per-Model Continuous Correlations

For each focus model, Spearman rho between use score (1–5) and each
factor / item. Uses all participants who have valid data for that model,
not just regular users.

BH correction applied within each model × outcome-type block (factors
block, items block).

## A1 — Use Score vs Factor Scores

```{r corr-factor}
model_factor_corrs <- crossing(
  model_label = unname(focus_model_labels),
  factor      = factor_cols
) |>
  mutate(
    result = map2(model_label, factor, ~ safe_spearman(analysis_df, .x, .y))
  ) |>
  pull(result) |>
  bind_rows() |>
  rename(model_label = predictor, factor = outcome) |>
  left_join(factor_lookup |> select(factor, instrument, display_label, proposed_name, short_factor),
            by = "factor") |>
  group_by(model_label) |>
  mutate(
    p_bh         = p.adjust(p_value, method = "BH"),
    p_bonferroni = p.adjust(p_value, method = "bonferroni")
  ) |>
  ungroup() |>
  mutate(
    abs_r              = abs(rho),
    survives_bh        = !is.na(p_bh) & p_bh < 0.05,
    survives_bonferroni= !is.na(p_bonferroni) & p_bonferroni < 0.05
  ) |>
  arrange(model_label, p_bh, desc(abs_r))

write_csv(model_factor_corrs, file.path(csv_dir, "Model_Use_vs_Factors_Correlations.csv"))

model_factor_corrs |>
  select(model_label, instrument, display_label, n, rho, p_value, p_bh, p_bonferroni) |>
  mutate(across(c(rho), ~ round(.x, 3)),
         across(c(p_value, p_bh, p_bonferroni), ~ round(.x, 4))) |>
  kable(caption = "Spearman rho: model use score vs factor scores (BH within model)")
```

### Heatmap — Use Score vs Factors

```{r factor-heatmap, fig.width=10, fig.height=5.5}
factor_heat_df <- model_factor_corrs |>
  filter(!is.na(rho)) |>
  mutate(
    sig_label  = case_when(survives_bonferroni ~ "**", survives_bh ~ "*", TRUE ~ ""),
    cell_label = paste0(formatC(rho, format = "f", digits = 2), sig_label),
    display_label = factor(
      display_label,
      levels = factor_lookup |>
        arrange(match(instrument, valid_factor_specs$instrument), factor_num) |>
        pull(display_label)
    ),
    model_label = factor(model_label, levels = unname(focus_model_labels))
  )

p_factor_heat <- ggplot(factor_heat_df,
                        aes(x = model_label, y = display_label, fill = rho)) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = cell_label), size = 3) +
  scale_fill_gradient2(
    low = "#c73e3a", mid = "#f7f7f7", high = "#4f79b7",
    midpoint = 0, limits = c(-1, 1), name = "Spearman \u03c1"
  ) +
  labs(
    title    = "Model Use Score vs Factor Scores",
    subtitle = "* BH < .05   ** Bonferroni < .05  |  BH corrected within each model",
    x = "Primary AI model use score predictor",
    y = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid    = element_blank(),
    axis.text.x   = element_text(angle = 15, hjust = 1),
    plot.margin   = margin(10, 15, 10, 10)
  )

ggsave(file.path(plot_dir, "Model_Use_vs_Factors_Heatmap.png"),
       p_factor_heat, width = 10, height = 5.5, dpi = 300, bg = "white")
p_factor_heat
```

## A2 — Use Score vs Item Scores

```{r corr-items}
# Run all model × item correlations
model_item_corrs <- crossing(
  model_label = unname(focus_model_labels),
  item_col    = item_cols
) |>
  mutate(
    result = map2(model_label, item_col, ~ safe_spearman(analysis_df, .x, .y))
  ) |>
  pull(result) |>
  bind_rows() |>
  rename(model_label = predictor, item_col = outcome) |>
  left_join(item_lookup |> select(item_col, instrument, item_id, item_text, display_label),
            by = "item_col") |>
  group_by(model_label) |>
  mutate(
    p_bh         = p.adjust(p_value, method = "BH"),
    p_bonferroni = p.adjust(p_value, method = "bonferroni")
  ) |>
  ungroup() |>
  mutate(
    abs_r               = abs(rho),
    survives_bh         = !is.na(p_bh) & p_bh < 0.05,
    survives_bonferroni = !is.na(p_bonferroni) & p_bonferroni < 0.05
  ) |>
  arrange(model_label, p_bh, desc(abs_r))

write_csv(model_item_corrs, file.path(csv_dir, "Model_Use_vs_Items_Correlations.csv"))

# Top 10 per model by abs rho
top_items_per_model <- model_item_corrs |>
  filter(!is.na(rho)) |>
  group_by(model_label) |>
  slice_max(order_by = abs_r, n = 10, with_ties = FALSE) |>
  ungroup() |>
  select(model_label, instrument, item_id, item_text, n, rho, p_value, p_bh, p_bonferroni) |>
  mutate(across(c(rho), ~ round(.x, 3)),
         across(c(p_value, p_bh, p_bonferroni), ~ round(.x, 4)))

write_csv(top_items_per_model, file.path(csv_dir, "Model_Use_vs_Items_Top10_Per_Model.csv"))

top_items_per_model |>
  kable(caption = "Top 10 item correlates per model (by |rho|, BH within model)")
```

### Cross-Model Item Signal Plot

```{r item-signal-plot, fig.width=12, fig.height=8}
# Items that survive BH in at least one model
sig_items <- model_item_corrs |>
  filter(survives_bh) |>
  pull(item_col) |>
  unique()

item_signal_df <- model_item_corrs |>
  filter(item_col %in% sig_items, !is.na(rho)) |>
  mutate(
    short_label = paste0(instrument, " ", item_id, ": ",
                         str_trunc(item_text, 60)),
    short_label = fct_reorder(short_label, abs_r, .fun = max),
    model_label = factor(model_label, levels = unname(focus_model_labels))
  )

p_item_signal <- ggplot(item_signal_df,
                        aes(x = rho, y = short_label, fill = model_label)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6) +
  geom_vline(xintercept = 0, color = "gray50", linewidth = 0.4) +
  scale_fill_manual(
    values = c(
      "ChatGPT" = "#4f79b7",
      "Claude"  = "#c96b3b",
      "Gemini"  = "#5a9367",
      "Copilot" = "#8c6bb1"
    )
  ) +
  labs(
    title    = "Items with BH-Significant Correlation to Any Model Use Score",
    subtitle = "Bars grouped by model; only items surviving BH < .05 in \u2265 1 model shown",
    x        = "Spearman \u03c1",
    y        = NULL,
    fill     = NULL
  ) +
  theme_minimal(base_size = 11) +
  theme(
    axis.text.y  = element_text(size = 8.5, lineheight = 0.9),
    legend.position = "bottom",
    panel.grid.minor = element_blank()
  )

ggsave(file.path(plot_dir, "Model_Use_vs_Items_BH_Signal.png"),
       p_item_signal, width = 12, height = 8, dpi = 300, bg = "white")

if (nrow(item_signal_df) == 0) {
  cat("No items survive BH correction in any model. See full CSV for raw rho rankings.")
} else {
  p_item_signal
}
```

------------------------------------------------------------------------

# Part B — Primary-Model Group Comparisons

Each participant assigned to their highest-use focus model.
Kruskal-Wallis across groups; pairwise Wilcoxon (BH-adjusted) for
factors where KW p \< .10. Groups with n \< `r min_group_n_kw` excluded
from KW; pairs with either side \< `r min_group_n_pairwise` excluded
from pairwise tests.

Item-level group tests omitted (too many comparisons; see Part A for
item-level continuous analysis).

## B1 — Group Sizes and Factor Score Distributions

```{r group-factor-merge}
group_factor_df <- analysis_df |>
  filter(!is.na(primary_model)) |>
  select(participant_id, primary_model, all_of(factor_cols))

eligible_groups <- group_factor_df |>
  count(primary_model) |>
  filter(n >= min_group_n_kw) |>
  pull(primary_model)

group_factor_eligible <- group_factor_df |>
  filter(primary_model %in% eligible_groups) |>
  mutate(primary_model = factor(primary_model, levels = intersect(unname(focus_model_labels), eligible_groups)))

kable(
  group_factor_eligible |> count(primary_model),
  caption = glue("Primary-model group sizes (groups with n \u2265 {min_group_n_kw} shown)")
)
```

## B2 — Kruskal-Wallis Tests

```{r kw-tests}
kw_results <- factor_cols |>
  map_dfr(function(fc) {
    dat <- group_factor_eligible |>
      select(primary_model, score = all_of(fc)) |>
      filter(!is.na(score))

    groups_present <- dat |> count(primary_model) |> filter(n >= min_group_n_kw)
    dat_filtered   <- dat |> filter(primary_model %in% groups_present$primary_model)

    if (nrow(dat_filtered) < 10 || dplyr::n_distinct(dat_filtered$primary_model) < 2) {
      return(tibble(factor = fc, kw_statistic = NA_real_, df = NA_integer_,
                    p_value = NA_real_, note = "insufficient data"))
    }

    test <- kruskal.test(score ~ primary_model, data = dat_filtered)
    tibble(
      factor       = fc,
      kw_statistic = unname(test$statistic),
      df           = as.integer(test$parameter),
      p_value      = test$p.value,
      note         = NA_character_
    )
  }) |>
  mutate(p_bh = p.adjust(p_value, method = "BH")) |>
  left_join(factor_lookup |> select(factor, instrument, display_label), by = "factor") |>
  arrange(p_bh, p_value)

write_csv(kw_results, file.path(csv_dir, "PrimaryModel_KW_Factors.csv"))

kw_results |>
  select(instrument, display_label, kw_statistic, df, p_value, p_bh, note) |>
  mutate(across(c(kw_statistic), ~ round(.x, 3)),
         across(c(p_value, p_bh),   ~ round(.x, 4))) |>
  kable(caption = "Kruskal-Wallis: primary model group vs factor scores")
```

## B3 — Pairwise Wilcoxon (Factors with KW p \< .10)

```{r pairwise-wilcox}
follow_up_factors <- kw_results |>
  filter(!is.na(p_value), p_value < 0.10) |>
  pull(factor)

if (length(follow_up_factors) == 0) {
  cat("No factors with KW p < .10; no pairwise tests run.")
} else {
  pairwise_results <- follow_up_factors |>
    map_dfr(function(fc) {
      dat <- group_factor_eligible |>
        select(primary_model, score = all_of(fc)) |>
        filter(!is.na(score))

      group_ns <- dat |> count(primary_model)
      eligible_pairs <- combn(group_ns$primary_model[group_ns$n >= min_group_n_pairwise], 2,
                              simplify = FALSE)

      eligible_pairs |>
        map_dfr(function(pair) {
          g1 <- dat |> filter(primary_model == pair[1]) |> pull(score)
          g2 <- dat |> filter(primary_model == pair[2]) |> pull(score)

          if (length(g1) < min_group_n_pairwise || length(g2) < min_group_n_pairwise) {
            return(tibble(factor = fc, group_a = pair[1], group_b = pair[2],
                          n_a = length(g1), n_b = length(g2),
                          w_statistic = NA_real_, p_value = NA_real_,
                          r_rb = NA_real_, note = "n too small"))
          }

          test <- suppressWarnings(
            wilcox.test(g1, g2, exact = FALSE)
          )

          # Rank-biserial effect size: r = 1 - (2W)/(n1*n2)
          r_rb <- 1 - (2 * test$statistic) / (length(g1) * length(g2))

          tibble(
            factor      = fc,
            group_a     = pair[1],
            group_b     = pair[2],
            n_a         = length(g1),
            n_b         = length(g2),
            w_statistic = unname(test$statistic),
            p_value     = test$p.value,
            r_rb        = unname(r_rb),
            note        = NA_character_
          )
        })
    }) |>
    mutate(p_bh = p.adjust(p_value, method = "BH")) |>
    left_join(factor_lookup |> select(factor, instrument, display_label), by = "factor") |>
    arrange(p_bh, p_value)

  write_csv(pairwise_results, file.path(csv_dir, "PrimaryModel_Pairwise_Wilcox_Factors.csv"))

  pairwise_results |>
    select(instrument, display_label, group_a, group_b, n_a, n_b,
           w_statistic, p_value, p_bh, r_rb, note) |>
    mutate(across(c(w_statistic, r_rb), ~ round(.x, 3)),
           across(c(p_value, p_bh),     ~ round(.x, 4))) |>
    kable(caption = "Pairwise Wilcoxon (BH-adjusted): factors with KW p < .10")
}
```

## B4 — Factor Score Distributions by Primary Model

```{r group-boxplots, fig.width=11, fig.height=7}
plot_long <- group_factor_eligible |>
  pivot_longer(cols = all_of(factor_cols), names_to = "factor", values_to = "score") |>
  filter(!is.na(score)) |>
  left_join(factor_lookup |> select(factor, display_label), by = "factor") |>
  mutate(
    display_label = factor(
      display_label,
      levels = factor_lookup |>
        arrange(match(instrument, valid_factor_specs$instrument), factor_num) |>
        pull(display_label)
    ),
    primary_model = factor(primary_model, levels = intersect(unname(focus_model_labels), eligible_groups))
  )

p_group_box <- ggplot(plot_long,
                      aes(x = primary_model, y = score, fill = primary_model)) +
  geom_boxplot(alpha = 0.7, outlier.shape = NA) +
  geom_jitter(width = 0.15, alpha = 0.55, size = 1.4) +
  facet_wrap(~ display_label, scales = "free_y", ncol = 4) +
  scale_fill_manual(
    values = c(
      "ChatGPT" = "#4f79b7",
      "Claude"  = "#c96b3b",
      "Gemini"  = "#5a9367",
      "Copilot" = "#8c6bb1"
    ),
    guide = "none"
  ) +
  labs(
    title    = "Factor Score Distributions by Primary AI Model",
    subtitle = "Primary model = focus model with highest Q17 use score",
    x        = NULL,
    y        = "Factor score"
  ) +
  theme_minimal(base_size = 11) +
  theme(
    axis.text.x      = element_text(angle = 25, hjust = 1),
    strip.text       = element_text(size = 8.5, lineheight = 0.9),
    panel.grid.minor = element_blank()
  )

ggsave(file.path(plot_dir, "PrimaryModel_Factor_Distributions.png"),
       p_group_box, width = 12, height = 7.5, dpi = 300, bg = "white")
p_group_box
```

------------------------------------------------------------------------

## Output Manifest

```{r manifest}
manifest <- tribble(
  ~file,                                        ~description,
  "Model_Use_Factor_Item_Merged.csv",           "Master merged df: Q17 use scores, factor scores, item scores, primary model",
  "Model_Use_vs_Factors_Correlations.csv",      "Part A: Spearman rho — model use score vs all factor scores",
  "Model_Use_vs_Items_Correlations.csv",        "Part A: Spearman rho — model use score vs all item scores",
  "Model_Use_vs_Items_Top10_Per_Model.csv",     "Part A: Top 10 item correlates per model by |rho|",
  "PrimaryModel_KW_Factors.csv",                "Part B: Kruskal-Wallis — primary model group vs factor scores",
  "PrimaryModel_Pairwise_Wilcox_Factors.csv",   "Part B: Pairwise Wilcoxon on factors with KW p < .10",
)

write_csv(manifest, file.path(csv_dir, "Manifest.csv"))
kable(manifest)
```
