---
title: "15 — Q17 Likert Buckets (Counts + Proportions) vs Factor Scores and Item Statements"
format:
  html:
    toc: true
    toc-depth: 3
output-dir: "15_q17likertbuckets"
execute:
  echo: false
  warning: false
  message: false
editor:
  markdown:
    wrap: 72
---

This report treats Q17 (AI tool familiarity/use) as a participant-level
distribution across the five Likert response buckets:

1. Never heard of this tool
2. Heard of this tool but never used it
3. Rarely use this tool
4. Sometimes use this tool
5. Often use this tool

For each participant we compute both:

- **Counts**: number of tools marked in each bucket (1–5)
- **Proportions**: bucket count divided by the number of tools answered

We then test whether these Q17 bucket metrics correlate with:

1. **Factor scores** (IMI, WritingEfficacy, AIReflection) using existing
   outputs from `09_art_vs_all_factors_items`.
2. **All item-level statements** across the four instruments
   (IMI, WritingEfficacy, AIReflection, BeliefsAboutAI) using existing
   outputs from `09_art_vs_all_factors_items`.

Multiple-comparisons control:
- **BH correction is applied within each Q17 metric** separately for the
  factors table and the items table (i.e., each metric defines a family
  of tests).

Outputs:
- Full correlation tables for **proportions** and **counts** are written
  as separate CSVs for both factors and items.
- Heatmaps are provided for **proportions** (main) and **counts**
  (appendix-style).

---

```{r setup}
library(tidyverse)
library(glue)
library(knitr)
library(forcats)
library(scales)
source("scoring_helpers.R", local = knitr::knit_global())

set.seed(42L)
```

## Configuration

```{r config}
script_dir <- "15_q17likertbuckets"
csv_dir    <- file.path(script_dir, "csv")
plot_dir   <- file.path(script_dir, "plots")

dir.create(csv_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(plot_dir, recursive = TRUE, showWarnings = FALSE)

min_corr_n <- 10L

# Inputs from prior pipeline outputs
q17_long_file <- file.path("07_q17_ai_usePART2", "csv", "Q17_Responses_Long.csv")

factor_scores_file <- file.path("09_art_vs_all_factors_items", "csv", "Other_Instrument_Factor_Scores.csv")
factor_lookup_file <- file.path("09_art_vs_all_factors_items", "csv", "Factor_Lookup.csv")

all_items_file <- file.path("09_art_vs_all_factors_items", "csv", "All_Items_Wide.csv")
item_lookup_file <- file.path("09_art_vs_all_factors_items", "csv", "All_Item_Lookup.csv")

required_files <- c(
  q17_long_file,
  factor_scores_file,
  factor_lookup_file,
  all_items_file,
  item_lookup_file
)

missing_files <- required_files[!file.exists(required_files)]
if (length(missing_files) > 0) {
  stop(
    glue(
      "Missing required inputs:\n- {paste(missing_files, collapse = '\n- ')}\n\n",
      "Run 07_q17_ai_usePART2 and 09_art_vs_all_factors_items first."
    ),
    call. = FALSE
  )
}
```

## Helper Functions

```{r helpers}
safe_spearman <- function(data, predictor, outcome) {
  dat <- data |>
    select(all_of(c(predictor, outcome))) |>
    filter(if_all(everything(), ~ !is.na(.x)))

  if (nrow(dat) < min_corr_n ||
      dplyr::n_distinct(dat[[predictor]]) < 2L ||
      dplyr::n_distinct(dat[[outcome]]) < 2L) {
    return(tibble(
      predictor = predictor,
      outcome = outcome,
      n = nrow(dat),
      rho = NA_real_,
      p_value = NA_real_,
      note = "insufficient variation or sample size"
    ))
  }

  test <- suppressWarnings(
    cor.test(dat[[predictor]], dat[[outcome]], method = "spearman", exact = FALSE)
  )

  tibble(
    predictor = predictor,
    outcome = outcome,
    n = nrow(dat),
    rho = unname(test$estimate),
    p_value = test$p.value,
    note = NA_character_
  )
}

# Apply BH/Bonferroni within each Q17 metric (family-wise per metric).
adjust_p_within_metric <- function(df, metric_col = "q17_metric", p_col = "p_value") {
  df |>
    group_by(.data[[metric_col]]) |>
    mutate(
      p_bh = p.adjust(.data[[p_col]], method = "BH"),
      p_bonferroni = p.adjust(.data[[p_col]], method = "bonferroni")
    ) |>
    ungroup()
}

# Format a bucket label used in tables/plots.
bucket_label <- function(k) {
  c(
    "1" = "Never heard",
    "2" = "Heard, never used",
    "3" = "Rarely use",
    "4" = "Sometimes use",
    "5" = "Often use"
  )[as.character(k)]
}
```

## Load 09 Outputs (Factors + Items)

```{r load-09}
all_factor_scores <- readr::read_csv(factor_scores_file, show_col_types = FALSE) |>
  mutate(participant_id = as.character(participant_id))

factor_lookup <- readr::read_csv(factor_lookup_file, show_col_types = FALSE)

all_item_wide <- readr::read_csv(all_items_file, show_col_types = FALSE) |>
  mutate(participant_id = as.character(participant_id))

item_lookup <- readr::read_csv(item_lookup_file, show_col_types = FALSE)

if (!"participant_id" %in% names(all_factor_scores)) stop("Factor scores missing participant_id", call. = FALSE)
if (!"participant_id" %in% names(all_item_wide)) stop("All items wide missing participant_id", call. = FALSE)

factor_cols <- factor_lookup$factor
item_cols <- item_lookup$item_col

assert_nonempty_df(all_factor_scores, "all_factor_scores")
assert_nonempty_df(all_item_wide, "all_item_wide")
assert_nonempty_df(factor_lookup, "factor_lookup")
assert_nonempty_df(item_lookup, "item_lookup")
```

## Load Q17 Long and Build Participant Bucket Metrics

```{r load-q17}
q17_long <- readr::read_csv(q17_long_file, show_col_types = FALSE)

# Required minimal columns: participant_id and use_score
required_q17_cols <- c("participant_id", "use_score")
missing_q17_cols <- setdiff(required_q17_cols, names(q17_long))
if (length(missing_q17_cols) > 0) {
  stop(
    glue("Q17 long file is missing required columns: {paste(missing_q17_cols, collapse = ', ')}"),
    call. = FALSE
  )
}

q17_long_clean <- q17_long |>
  transmute(
    participant_id = as.character(participant_id),
    use_score = as.integer(use_score)
  ) |>
  filter(!is.na(participant_id), participant_id != "", !is.na(use_score)) |>
  filter(use_score %in% 1:5)

assert_nonempty_df(q17_long_clean, "q17_long_clean")

q17_dist <- q17_long_clean |>
  group_by(participant_id) |>
  summarise(
    q17_tools_answered = n(),
    q17_n_1 = sum(use_score == 1L),
    q17_n_2 = sum(use_score == 2L),
    q17_n_3 = sum(use_score == 3L),
    q17_n_4 = sum(use_score == 4L),
    q17_n_5 = sum(use_score == 5L),
    q17_mean_use = mean(use_score),
    .groups = "drop"
  ) |>
  mutate(
    q17_p_1 = q17_n_1 / q17_tools_answered,
    q17_p_2 = q17_n_2 / q17_tools_answered,
    q17_p_3 = q17_n_3 / q17_tools_answered,
    q17_p_4 = q17_n_4 / q17_tools_answered,
    q17_p_5 = q17_n_5 / q17_tools_answered
  ) |>
  arrange(participant_id)

assert_unique_pid_rows(q17_dist, "participant_id", "q17_dist")

write_csv(q17_dist, file.path(csv_dir, "Q17_Likert_Buckets_PerParticipant.csv"))
```

```{r q17-summary}
q17_bucket_summary <- tibble(
  metric = c(
    "Participants",
    "Tools answered (min)",
    "Tools answered (median)",
    "Tools answered (max)",
    "Mean never heard (count)",
    "Mean heard-only (count)",
    "Mean rarely (count)",
    "Mean sometimes (count)",
    "Mean often (count)",
    "Mean use score (1–5)"
  ),
  value = c(
    nrow(q17_dist),
    min(q17_dist$q17_tools_answered),
    median(q17_dist$q17_tools_answered),
    max(q17_dist$q17_tools_answered),
    mean(q17_dist$q17_n_1),
    mean(q17_dist$q17_n_2),
    mean(q17_dist$q17_n_3),
    mean(q17_dist$q17_n_4),
    mean(q17_dist$q17_n_5),
    mean(q17_dist$q17_mean_use)
  )
)

kable(q17_bucket_summary, caption = "Q17 per-participant bucket summary")
```

## Q17 Metric Lookup

```{r metric-lookup}
q17_metric_lookup <- tribble(
  ~q17_metric, ~q17_label, ~metric_type, ~bucket,
  "q17_n_1", "Never heard (count)", "count", 1L,
  "q17_n_2", "Heard, never used (count)", "count", 2L,
  "q17_n_3", "Rarely use (count)", "count", 3L,
  "q17_n_4", "Sometimes use (count)", "count", 4L,
  "q17_n_5", "Often use (count)", "count", 5L,
  "q17_p_1", "Never heard (prop)", "prop", 1L,
  "q17_p_2", "Heard, never used (prop)", "prop", 2L,
  "q17_p_3", "Rarely use (prop)", "prop", 3L,
  "q17_p_4", "Sometimes use (prop)", "prop", 4L,
  "q17_p_5", "Often use (prop)", "prop", 5L,
  "q17_mean_use", "Mean use (1–5)", "summary", NA_integer_
)

q17_metrics_prop <- q17_metric_lookup |>
  filter(metric_type %in% c("prop", "summary")) |>
  pull(q17_metric)

q17_metrics_count <- q17_metric_lookup |>
  filter(metric_type == "count") |>
  pull(q17_metric)
```

## Merge Datasets

```{r merge}
factor_df <- all_factor_scores |>
  inner_join(q17_dist, by = "participant_id")

item_df <- all_item_wide |>
  inner_join(q17_dist, by = "participant_id")

cat("Q17 x factor overlap N:", nrow(factor_df), "\n")
cat("Q17 x item overlap N:", nrow(item_df), "\n")

assert_unique_pid_rows(factor_df, "participant_id", "factor_df (merged)")
assert_unique_pid_rows(item_df, "participant_id", "item_df (merged)")
```

---

# Part A — Q17 Buckets vs Factor Scores

## A1 — Proportions: Spearman correlations

```{r q17-prop-vs-factors}
q17_factor_corrs_prop <- crossing(
  q17_metric = q17_metrics_prop,
  factor = factor_cols
) |>
  mutate(
    result = map2(factor, q17_metric, ~ safe_spearman(factor_df, .x, .y))
  ) |>
  pull(result) |>
  bind_rows() |>
  rename(
    factor = predictor,
    q17_metric = outcome
  ) |>
  mutate(abs_r = abs(rho)) |>
  adjust_p_within_metric(metric_col = "q17_metric", p_col = "p_value") |>
  left_join(factor_lookup, by = "factor") |>
  left_join(q17_metric_lookup, by = "q17_metric") |>
  mutate(
    survives_bh = !is.na(p_bh) & p_bh < 0.05,
    survives_bonferroni = !is.na(p_bonferroni) & p_bonferroni < 0.05
  ) |>
  arrange(q17_metric, p_bh, p_bonferroni, desc(abs_r))

write_csv(q17_factor_corrs_prop, file.path(csv_dir, "Q17_Proportions_vs_Factors_Correlations.csv"))
```

## A2 — Counts: Spearman correlations (robustness)

```{r q17-count-vs-factors}
q17_factor_corrs_count <- crossing(
  q17_metric = q17_metrics_count,
  factor = factor_cols
) |>
  mutate(
    result = map2(factor, q17_metric, ~ safe_spearman(factor_df, .x, .y))
  ) |>
  pull(result) |>
  bind_rows() |>
  rename(
    factor = predictor,
    q17_metric = outcome
  ) |>
  mutate(abs_r = abs(rho)) |>
  adjust_p_within_metric(metric_col = "q17_metric", p_col = "p_value") |>
  left_join(factor_lookup, by = "factor") |>
  left_join(q17_metric_lookup, by = "q17_metric") |>
  mutate(
    survives_bh = !is.na(p_bh) & p_bh < 0.05,
    survives_bonferroni = !is.na(p_bonferroni) & p_bonferroni < 0.05
  ) |>
  arrange(q17_metric, p_bh, p_bonferroni, desc(abs_r))

write_csv(q17_factor_corrs_count, file.path(csv_dir, "Q17_Counts_vs_Factors_Correlations.csv"))
```

## A3 — Heatmap (Main): Proportions only (+ mean use)

```{r factor-heatmap-prop-data}
heat_q17_metrics_prop <- c("q17_p_1", "q17_p_2", "q17_p_3", "q17_p_4", "q17_p_5", "q17_mean_use")

factor_heat_prop <- q17_factor_corrs_prop |>
  filter(q17_metric %in% heat_q17_metrics_prop) |>
  mutate(
    sig_label = case_when(
      survives_bonferroni ~ "**",
      survives_bh ~ "*",
      TRUE ~ ""
    ),
    cell_label = if_else(
      is.na(rho),
      "",
      paste0(formatC(rho, format = "f", digits = 2), sig_label)
    ),
    q17_label = factor(
      q17_label,
      levels = q17_metric_lookup |>
        filter(q17_metric %in% heat_q17_metrics_prop) |>
        pull(q17_label)
    ),
    display_label = factor(
      display_label,
      levels = factor_lookup |>
        arrange(match(instrument, unique(factor_lookup$instrument)), factor_num) |>
        pull(display_label)
    )
  )
```

```{r factor-heatmap-prop, fig.width=12, fig.height=7.5}
p_factor_heat_prop <- ggplot(factor_heat_prop, aes(x = q17_label, y = display_label, fill = rho)) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = cell_label), size = 3) +
  scale_fill_gradient2(
    low = "#c73e3a",
    mid = "#f7f7f7",
    high = "#4f79b7",
    midpoint = 0,
    limits = c(-1, 1),
    name = "Spearman rho"
  ) +
  labs(
    title = "Q17 Familiarity Buckets (Proportions) vs Factor Scores",
    subtitle = "* BH < .05   ** Bonferroni < .05  |  BH corrected within each Q17 metric",
    x = NULL,
    y = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid = element_blank(),
    axis.text.x = element_text(angle = 20, hjust = 1),
    plot.margin = margin(10, 15, 10, 10)
  )

ggsave(
  filename = file.path(plot_dir, "Q17_Proportions_vs_Factors_Heatmap.png"),
  plot = p_factor_heat_prop,
  width = 12,
  height = 7.5,
  units = "in",
  dpi = 300,
  bg = "white"
)

p_factor_heat_prop
```

## A4 — Heatmap (Appendix): Counts only

```{r factor-heatmap-count-data}
heat_q17_metrics_count <- c("q17_n_1", "q17_n_2", "q17_n_3", "q17_n_4", "q17_n_5")

factor_heat_count <- q17_factor_corrs_count |>
  filter(q17_metric %in% heat_q17_metrics_count) |>
  mutate(
    sig_label = case_when(
      survives_bonferroni ~ "**",
      survives_bh ~ "*",
      TRUE ~ ""
    ),
    cell_label = if_else(
      is.na(rho),
      "",
      paste0(formatC(rho, format = "f", digits = 2), sig_label)
    ),
    q17_label = factor(
      q17_label,
      levels = q17_metric_lookup |>
        filter(q17_metric %in% heat_q17_metrics_count) |>
        pull(q17_label)
    ),
    display_label = factor(
      display_label,
      levels = factor_lookup |>
        arrange(match(instrument, unique(factor_lookup$instrument)), factor_num) |>
        pull(display_label)
    )
  )
```

```{r factor-heatmap-count, fig.width=11, fig.height=7.5}
p_factor_heat_count <- ggplot(factor_heat_count, aes(x = q17_label, y = display_label, fill = rho)) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = cell_label), size = 3) +
  scale_fill_gradient2(
    low = "#c73e3a",
    mid = "#f7f7f7",
    high = "#4f79b7",
    midpoint = 0,
    limits = c(-1, 1),
    name = "Spearman rho"
  ) +
  labs(
    title = "Q17 Familiarity Buckets (Counts) vs Factor Scores",
    subtitle = "* BH < .05   ** Bonferroni < .05  |  BH corrected within each Q17 metric",
    x = NULL,
    y = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid = element_blank(),
    axis.text.x = element_text(angle = 20, hjust = 1),
    plot.margin = margin(10, 15, 10, 10)
  )

ggsave(
  filename = file.path(plot_dir, "Q17_Counts_vs_Factors_Heatmap.png"),
  plot = p_factor_heat_count,
  width = 11,
  height = 7.5,
  units = "in",
  dpi = 300,
  bg = "white"
)

p_factor_heat_count
```

---

# Part B — Q17 Buckets vs All Item Statements

## B1 — Proportions: Spearman correlations

```{r q17-prop-vs-items}
q17_item_corrs_prop <- crossing(
  q17_metric = q17_metrics_prop,
  item_col = item_cols
) |>
  mutate(
    result = map2(item_col, q17_metric, ~ safe_spearman(item_df, .x, .y))
  ) |>
  pull(result) |>
  bind_rows() |>
  rename(
    item_col = predictor,
    q17_metric = outcome
  ) |>
  mutate(abs_r = abs(rho)) |>
  adjust_p_within_metric(metric_col = "q17_metric", p_col = "p_value") |>
  left_join(item_lookup, by = "item_col") |>
  left_join(q17_metric_lookup, by = "q17_metric") |>
  mutate(
    survives_bh = !is.na(p_bh) & p_bh < 0.05,
    survives_bonferroni = !is.na(p_bonferroni) & p_bonferroni < 0.05
  ) |>
  arrange(q17_metric, p_bh, p_bonferroni, desc(abs_r))

write_csv(q17_item_corrs_prop, file.path(csv_dir, "Q17_Proportions_vs_All_Items_Correlations.csv"))
```

## B2 — Counts: Spearman correlations (robustness)

```{r q17-count-vs-items}
q17_item_corrs_count <- crossing(
  q17_metric = q17_metrics_count,
  item_col = item_cols
) |>
  mutate(
    result = map2(item_col, q17_metric, ~ safe_spearman(item_df, .x, .y))
  ) |>
  pull(result) |>
  bind_rows() |>
  rename(
    item_col = predictor,
    q17_metric = outcome
  ) |>
  mutate(abs_r = abs(rho)) |>
  adjust_p_within_metric(metric_col = "q17_metric", p_col = "p_value") |>
  left_join(item_lookup, by = "item_col") |>
  left_join(q17_metric_lookup, by = "q17_metric") |>
  mutate(
    survives_bh = !is.na(p_bh) & p_bh < 0.05,
    survives_bonferroni = !is.na(p_bonferroni) & p_bonferroni < 0.05
  ) |>
  arrange(q17_metric, p_bh, p_bonferroni, desc(abs_r))

write_csv(q17_item_corrs_count, file.path(csv_dir, "Q17_Counts_vs_All_Items_Correlations.csv"))
```

## B3 — Top 30 item correlates (choose one primary Q17 metric)

```{r primary-q17}
# Pick the primary metric for the "Top 30 items" plot.
# Recommended low-end choices:
#   - "q17_p_1" (never heard proportion)
#   - "q17_p_2" (heard-only proportion)
primary_q17_metric <- "q17_p_2"

primary_q17_label <- q17_metric_lookup$q17_label[q17_metric_lookup$q17_metric == primary_q17_metric][[1]]

top_items_primary <- q17_item_corrs_prop |>
  filter(q17_metric == primary_q17_metric, !is.na(rho)) |>
  slice_max(order_by = abs_r, n = 30, with_ties = FALSE) |>
  mutate(
    plot_label = paste0(instrument, " ", item_id, ": ", str_trunc(item_text, 85)),
    plot_label = fct_reorder(plot_label, rho)
  )

write_csv(top_items_primary, file.path(csv_dir, "Q17_PrimaryMetric_Top30_Items.csv"))
```

```{r primary-item-plot, fig.width=12, fig.height=10}
p_top_items <- ggplot(top_items_primary, aes(x = rho, y = plot_label, fill = instrument)) +
  geom_col(width = 0.75) +
  geom_vline(xintercept = 0, color = "gray50", linewidth = 0.5) +
  scale_fill_manual(values = c(
    "IMI" = "#4f79b7",
    "WritingEfficacy" = "#c96b3b",
    "AIReflection" = "#5a9367",
    "BeliefsAboutAI" = "#8c6bb1"
  )) +
  labs(
    title = glue("Top item correlates of {primary_q17_label}"),
    subtitle = "Top 30 items by |Spearman rho| (BH correction computed within Q17 metric family)",
    x = "Spearman rho",
    y = NULL,
    fill = NULL
  ) +
  theme_minimal(base_size = 11) +
  theme(
    panel.grid.minor = element_blank(),
    axis.text.y = element_text(size = 9, lineheight = 0.9),
    legend.position = "bottom"
  )

# ------------------------------------------------------------
# BeliefsAboutAI-only plot: top item correlates for primary Q17 metric
# Paste this chunk AFTER the `primary-item-plot` chunk (after `p_top_items`)
# and BEFORE the `top-by-q17-metric` chunk.
# ------------------------------------------------------------

# Top BeliefsAboutAI items for the chosen primary Q17 metric (from proportion table)
top_beliefs_primary <- q17_item_corrs_prop |>
  filter(
    q17_metric == primary_q17_metric,
    instrument == "BeliefsAboutAI",
    !is.na(rho)
  ) |>
  mutate(abs_r = abs(rho)) |>
  slice_max(order_by = abs_r, n = 20, with_ties = FALSE) |>
  mutate(
    plot_label = paste0("Beliefs ", item_id, ": ", str_trunc(item_text, 100)),
    plot_label = fct_reorder(plot_label, rho)
  )

# Write CSV
write_csv(
  top_beliefs_primary,
  file.path(csv_dir, glue("Q17_{primary_q17_metric}_Top_BeliefsAboutAI_Items.csv"))
)

# Plot
p_beliefs <- ggplot(top_beliefs_primary, aes(x = rho, y = plot_label)) +
  geom_col(width = 0.75, fill = "#8c6bb1") +
  geom_vline(xintercept = 0, color = "gray50", linewidth = 0.5) +
  labs(
    title = glue("Top BeliefsAboutAI item correlates of {primary_q17_label}"),
    subtitle = "Top 20 items by |Spearman rho| (BH correction computed within Q17 metric family)",
    x = "Spearman rho",
    y = NULL
  ) +
  theme_minimal(base_size = 11) +
  theme(
    panel.grid.minor = element_blank(),
    axis.text.y = element_text(size = 9, lineheight = 0.9)
  )

# Save PNG
ggsave(
  filename = file.path(plot_dir, glue("Q17_{primary_q17_metric}_Top_BeliefsAboutAI_Items.png")),
  plot = p_beliefs,
  width = 12,
  height = 7,
  units = "in",
  dpi = 300,
  bg = "white"
)

p_beliefs





ggsave(
  filename = file.path(plot_dir, glue("Q17_{primary_q17_metric}_Top30_Items.png")),
  plot = p_top_items,
  width = 12,
  height = 10.5,
  units = "in",
  dpi = 300,
  bg = "white"
)

p_top_items

## B3 — Top 30 item correlates per Q17 metric (all five buckets)

# --- Loop: one plot per bucket metric ---
walk(q17_metrics_prop[q17_metrics_prop != "q17_mean_use"], function(metric) {
  label <- q17_metric_lookup$q17_label[q17_metric_lookup$q17_metric == metric][[1]]

  top_items <- q17_item_corrs_prop |>
    filter(q17_metric == metric, !is.na(rho)) |>
    slice_max(order_by = abs_r, n = 30, with_ties = FALSE) |>
    mutate(
      plot_label = paste0(instrument, " ", item_id, ": ", str_trunc(item_text, 85)),
      plot_label = fct_reorder(plot_label, rho)
    )

  p <- ggplot(top_items, aes(x = rho, y = plot_label, fill = instrument)) +
    geom_col(width = 0.75) +
    geom_vline(xintercept = 0, color = "gray50", linewidth = 0.5) +
    scale_fill_manual(values = c(
      "IMI"            = "#4f79b7",
      "WritingEfficacy" = "#c96b3b",
      "AIReflection"   = "#5a9367",
      "BeliefsAboutAI" = "#8c6bb1"
    )) +
    labs(
      title    = glue("Top item correlates of: {label}"),
      subtitle = "Top 30 items by |Spearman rho| (BH correction computed within Q17 metric family)",
      x        = "Spearman rho",
      y        = NULL,
      fill     = NULL
    ) +
    theme_minimal(base_size = 11) +
    theme(
      panel.grid.minor = element_blank(),
      axis.text.y      = element_text(size = 9, lineheight = 0.9),
      legend.position  = "bottom"
    )

  ggsave(
    filename = file.path(plot_dir, glue("Q17_{metric}_Top30_Items.png")),
    plot     = p,
    width    = 12,
    height   = 10.5,
    units    = "in",
    dpi      = 300,
    bg       = "white"
  )
})

# --- Combined CSV: all buckets x all items ranked by |rho| ---
all_buckets_ranked <- q17_item_corrs_prop |>
  filter(
    q17_metric != "q17_mean_use",
    !is.na(rho)
  ) |>
  arrange(desc(abs_r)) |>
  select(
    q17_label, instrument, item_id, item_text,
    rho, abs_r, p_value, p_bh, p_bonferroni,
    survives_bh, survives_bonferroni, n
  )

write_csv(all_buckets_ranked, file.path(csv_dir, "Q17_AllBuckets_AllItems_RankedByStrength.csv"))

# --- Combined top-corr plot: best item per bucket, all buckets together ---
top_per_bucket <- q17_item_corrs_prop |>
  filter(
    q17_metric != "q17_mean_use",
    !is.na(rho)
  ) |>
  group_by(q17_metric) |>
  slice_max(order_by = abs_r, n = 10, with_ties = FALSE) |>
  ungroup() |>
  mutate(
    plot_label = paste0(instrument, " ", item_id, ": ", str_trunc(item_text, 70)),
    plot_label = fct_reorder(plot_label, rho),
    q17_label  = factor(
      q17_label,
      levels = q17_metric_lookup |>
        filter(metric_type == "prop") |>
        pull(q17_label)
    )
  )

p_combined <- ggplot(top_per_bucket, aes(x = rho, y = plot_label, fill = instrument)) +
  geom_col(width = 0.75) +
  geom_vline(xintercept = 0, color = "gray50", linewidth = 0.5) +
  scale_fill_manual(values = c(
    "IMI"             = "#4f79b7",
    "WritingEfficacy" = "#c96b3b",
    "AIReflection"    = "#5a9367",
    "BeliefsAboutAI"  = "#8c6bb1"
  )) +
  facet_wrap(~ q17_label, scales = "free_y", ncol = 1) +
  labs(
    title    = "Top 10 item correlates per Q17 familiarity bucket",
    subtitle = "Ranked by |Spearman rho| within each bucket (BH correction within metric family)",
    x        = "Spearman rho",
    y        = NULL,
    fill     = NULL
  ) +
  theme_minimal(base_size = 11) +
  theme(
    panel.grid.minor  = element_blank(),
    axis.text.y       = element_text(size = 8, lineheight = 0.9),
    legend.position   = "bottom",
    strip.text        = element_text(face = "bold", size = 10)
  )

ggsave(
  filename = file.path(plot_dir, "Q17_AllBuckets_Top10_Items_Combined.png"),
  plot     = p_combined,
  width    = 13,
  height   = 22,
  units    = "in",
  dpi      = 300,
  bg       = "white"
)

## B3 — Combined top correlates across all buckets (single ranked plot)

top_combined <- q17_item_corrs_prop |>
  filter(q17_metric != "q17_mean_use", !is.na(rho)) |>
  slice_max(order_by = abs_r, n = 40, with_ties = FALSE) |>
  mutate(
    plot_label = paste0(instrument, " ", item_id, ": ", str_trunc(item_text, 80)),
    # make each row unique in case the same item appears for multiple buckets
    plot_label_unique = paste0(plot_label, "  [", q17_label, "]"),
    plot_label_unique = fct_reorder(plot_label_unique, abs_r)
  )

p_combined <- ggplot(top_combined, aes(x = rho, y = plot_label_unique, fill = q17_label)) +
  geom_col(width = 0.75) +
  geom_vline(xintercept = 0, color = "gray50", linewidth = 0.5) +
  scale_fill_manual(values = c(
    "Never heard (prop)"      = "#b0b0b0",
    "Heard, never used (prop)" = "#4f79b7",
    "Rarely use (prop)"       = "#c96b3b",
    "Sometimes use (prop)"    = "#5a9367",
    "Often use (prop)"        = "#8c6bb1"
  )) +
  labs(
    title    = "Top 40 item correlates across all Q17 familiarity buckets",
    subtitle = "Ranked by |Spearman rho| — color indicates which bucket",
    x        = "Spearman rho",
    y        = NULL,
    fill     = NULL
  ) +
  theme_minimal(base_size = 11) +
  theme(
    panel.grid.minor = element_blank(),
    axis.text.y      = element_text(size = 9, lineheight = 0.9),
    legend.position  = "bottom"
  )

ggsave(
  filename = file.path(plot_dir, "Q17_AllBuckets_TopCorr_Unified_Ranked.png"),
  plot     = p_combined,
  width    = 13,
  height   = 13,
  units    = "in",
  dpi      = 300,
  bg       = "white"
)

## B5 — Flip scores: rho(often use) minus rho(never heard)

# --- Items flip scores ---
flip_items <- q17_item_corrs_prop |>
  filter(q17_metric %in% c("q17_p_1", "q17_p_5"), !is.na(rho)) |>
  select(item_col, q17_metric, rho, instrument, item_id, item_text) |>
  pivot_wider(
    names_from  = q17_metric,
    values_from = rho,
    names_prefix = "rho_"
  ) |>
  rename(rho_never = rho_q17_p_1, rho_often = rho_q17_p_5) |>
  filter(!is.na(rho_never), !is.na(rho_often)) |>
  mutate(
    flip_score = rho_often - rho_never,
    abs_flip   = abs(flip_score)
  ) |>
  arrange(desc(abs_flip))

write_csv(flip_items, file.path(csv_dir, "Q17_FlipScores_Items.csv"))

# Top 30 flip items plot
top_flip_items <- flip_items |>
  slice_max(order_by = abs_flip, n = 30, with_ties = FALSE) |>
  arrange(abs_flip) |>
  mutate(
    plot_label = paste0(instrument, " ", item_id, ": ", str_trunc(item_text, 75)),
    plot_label = factor(plot_label, levels = unique(plot_label))
  ) |>
  select(plot_label, instrument, rho_never, rho_often, flip_score, abs_flip) |>
  pivot_longer(
    cols      = c(rho_never, rho_often),
    names_to  = "bucket",
    values_to = "rho"
  ) |>
  mutate(
    bucket = recode(bucket,
      "rho_never" = "Never heard",
      "rho_often" = "Often use"
    )
  )

p_flip_items <- ggplot(top_flip_items, aes(x = rho, y = plot_label, color = bucket, group = plot_label)) +
  geom_line(color = "gray70", linewidth = 0.8) +
  geom_point(size = 3) +
  geom_vline(xintercept = 0, color = "gray40", linewidth = 0.5) +
  scale_color_manual(values = c(
    "Never heard" = "#b0b0b0",
    "Often use"   = "#8c6bb1"
  )) +
  labs(
    title    = "Top 30 items by flip score (often use rho minus never heard rho)",
    subtitle = "Each line shows the shift from Never heard (gray) to Often use (purple)",
    x        = "Spearman rho",
    y        = NULL,
    color    = NULL
  ) +
  theme_minimal(base_size = 11) +
  theme(
    panel.grid.minor = element_blank(),
    axis.text.y      = element_text(size = 9, lineheight = 0.9),
    legend.position  = "bottom"
  )

ggsave(
  filename = file.path(plot_dir, "Q17_FlipScores_Items_DumbbellPlot.png"),
  plot     = p_flip_items,
  width    = 12,
  height   = 11,
  units    = "in",
  dpi      = 300,
  bg       = "white"
)

# --- Factor flip scores ---
flip_factors <- q17_factor_corrs_prop |>
  filter(q17_metric %in% c("q17_p_1", "q17_p_5"), !is.na(rho)) |>
  select(factor, q17_metric, rho, instrument, display_label) |>
  pivot_wider(
    names_from  = q17_metric,
    values_from = rho,
    names_prefix = "rho_"
  ) |>
  rename(rho_never = rho_q17_p_1, rho_often = rho_q17_p_5) |>
  filter(!is.na(rho_never), !is.na(rho_often)) |>
  mutate(
    flip_score = rho_often - rho_never,
    abs_flip   = abs(flip_score)
  ) |>
  arrange(desc(abs_flip))

write_csv(flip_factors, file.path(csv_dir, "Q17_FlipScores_Factors.csv"))

# Factor flip heatmap
flip_factors_heat <- flip_factors |>
  mutate(
    display_label = fct_reorder(display_label, flip_score)
  ) |>
  select(display_label, instrument, rho_never, rho_often, flip_score) |>
  pivot_longer(
    cols      = c(rho_never, rho_often, flip_score),
    names_to  = "metric",
    values_to = "value"
  ) |>
  mutate(
    metric = recode(metric,
      "rho_never" = "Never heard",
      "rho_often" = "Often use",
      "flip_score" = "Flip score\n(often − never)"
    ),
    metric = factor(metric, levels = c("Never heard", "Often use", "Flip score\n(often − never)"))
  )

p_flip_factors_heat <- ggplot(flip_factors_heat, aes(x = metric, y = display_label, fill = value)) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = formatC(value, format = "f", digits = 2)), size = 3) +
  scale_fill_gradient2(
    low      = "#c73e3a",
    mid      = "#f7f7f7",
    high     = "#4f79b7",
    midpoint = 0,
    limits   = c(-1, 1),
    name     = "rho / flip"
  ) +
  labs(
    title    = "Factor flip scores: Never heard vs Often use",
    subtitle = "Flip score = rho(often use) − rho(never heard)",
    x        = NULL,
    y        = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid   = element_blank(),
    axis.text.x  = element_text(angle = 10, hjust = 0.5),
    plot.margin  = margin(10, 15, 10, 10)
  )

ggsave(
  filename = file.path(plot_dir, "Q17_FlipScores_Factors_Heatmap.png"),
  plot     = p_flip_factors_heat,
  width    = 9,
  height   = 6,
  units    = "in",
  dpi      = 300,
  bg       = "white"
)

```

## B4 — Strongest item signals by Q17 metric (summary table; proportions)

```{r top-by-q17-metric}
top_by_q17_metric <- q17_item_corrs_prop |>
  filter(!is.na(rho)) |>
  group_by(q17_metric, q17_label) |>
  slice_max(order_by = abs_r, n = 8, with_ties = FALSE) |>
  ungroup() |>
  select(q17_label, instrument, item_id, item_text, rho, p_bh, p_bonferroni, n) |>
  mutate(
    rho = round(rho, 3),
    p_bh = round(p_bh, 4),
    p_bonferroni = round(p_bonferroni, 4)
  )

write_csv(top_by_q17_metric, file.path(csv_dir, "Q17_Proportions_Top_Item_Signals_By_Q17_Metric.csv"))
kable(top_by_q17_metric, caption = "Top item signals (8) by each Q17 proportion metric (ranked by |rho|)")
```

---

## Output Manifest

```{r manifest}
manifest <- tribble(
  ~file, ~description,
  "Q17_Likert_Buckets_PerParticipant.csv", "Per-participant Q17 bucket counts + proportions + mean use",
  "Q17_Proportions_vs_Factors_Correlations.csv", "Spearman rho: Q17 proportion metrics (and mean) vs factor scores (BH within metric)",
  "Q17_Counts_vs_Factors_Correlations.csv", "Spearman rho: Q17 count metrics vs factor scores (BH within metric)",
  "Q17_Proportions_vs_All_Items_Correlations.csv", "Spearman rho: Q17 proportion metrics (and mean) vs all items (BH within metric)",
  "Q17_Counts_vs_All_Items_Correlations.csv", "Spearman rho: Q17 count metrics vs all items (BH within metric)",
  "Q17_PrimaryMetric_Top30_Items.csv", "Top 30 item correlates for chosen primary Q17 metric (from proportion table)",
  "Q17_Proportions_Top_Item_Signals_By_Q17_Metric.csv", "Top 8 item correlates per Q17 proportion metric"
)

write_csv(manifest, file.path(csv_dir, "Manifest.csv"))
kable(manifest)
```