---
title: "18 - Composite Correlations"
format:
  html:
    toc: true
    toc-depth: 3
    embed-resources: true
output-dir: "18_composite_correlations"
execute:
  echo: false
  warning: false
  message: false
editor:
  markdown:
    wrap: 72
---

# Purpose

This companion report re-runs the downstream factor-correlation families
using the unit-weighted composite scores from script `17`, rather than
tenBerge EFA factor scores. It does not refit any EFA models.

```{r setup}
library(tidyverse)
library(knitr)
library(openxlsx)
source("scoring_helpers.R", local = knitr::knit_global())

script_dir <- "18_composite_correlations"
csv_dir <- file.path(script_dir, "csv")
plot_dir <- file.path(script_dir, "plots")
workbook_dir <- "18_composite_workbook"
dir.create(csv_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(plot_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(workbook_dir, recursive = TRUE, showWarnings = FALSE)

composite_scores_file <- file.path("17_composite_scoring", "csv", "Composite_Scores_Wide.csv")
composite_specs_file <- file.path("17_composite_scoring", "csv", "Composite_Specs.csv")
composite_item_membership_file <- file.path("17_composite_scoring", "csv", "Composite_Item_Membership.csv")
unassigned_items_file <- file.path("17_composite_scoring", "csv", "Unassigned_Items.csv")
art_scores_file <- file.path("07_art_vs_all_factors_items", "csv", "ART_Scored.csv")
efa_art_primary_file <- file.path("07_art_vs_all_factors_items", "csv", "ART_vs_Factors_Correlations.csv")
efa_art_beliefs_file <- file.path("16_exploratory_beliefs", "csv", "ART_vs_Beliefs_Exploratory_Factors.csv")
q17_bucket_file <- file.path("14_q17_deeper_dive", "csv", "Q17_Likert_Buckets_PerParticipant.csv")
q17_long_file <- file.path("09_q17_ai_use", "csv", "Q17_Responses_Long.csv")
named_model_file <- file.path("13_model_use_vs_factors_items", "csv", "Model_Use_Factor_Item_Merged.csv")
order_ready_file <- file.path("06_order_effects", "csv", "Order_Effects_Analysis_Ready.csv")
efa_order_file <- file.path("06_order_effects", "csv", "All_Factors_With_Exploratory_Beliefs_Order_Stratified_Correlations.csv")
efa_factor_scores_file <- file.path("05_interesting_findings", "csv", "Factor_Scores_All_Instruments.csv")
efa_factor_lookup_file <- file.path("05_interesting_findings", "csv", "Factor_Name_Map.csv")
efa_beliefs_scores_file <- file.path("16_exploratory_beliefs", "csv", "Beliefs_Exploratory_Factor_Scores.csv")
efa_beliefs_lookup_file <- file.path("16_exploratory_beliefs", "csv", "Beliefs_Exploratory_Factor_Lookup.csv")
efa_cross_factor_file <- file.path("16_exploratory_beliefs", "csv", "Beliefs_Exploratory_Cross_Factor_Heatmap_Matrix.csv")
workbook_file <- file.path(workbook_dir, "Composite_Workbook.xlsx")

instrument_order <- c("IMI", "WritingEfficacy", "AIReflection", "BeliefsAboutAI")

pal <- c(
  "IMI" = "#4f79b7",
  "WritingEfficacy" = "#c96b3b",
  "AIReflection" = "#5a9367",
  "BeliefsAboutAI" = "#8c6bb1",
  "ART" = "#67717a",
  "Q17" = "#2f7f77",
  "ModelUse" = "#7c6aa3"
)

theme_corr <- function(base_size = 11) {
  theme_minimal(base_size = base_size) +
    theme(
      panel.grid.minor = element_blank(),
      panel.grid.major = element_blank(),
      axis.text.x = element_text(angle = 35, hjust = 1),
      legend.position = "bottom"
    )
}

sig_suffix <- function(p_bh, p_bonf) {
  case_when(
    !is.na(p_bonf) & p_bonf < 0.05 ~ "**",
    !is.na(p_bh) & p_bh < 0.05 ~ "*",
    TRUE ~ ""
  )
}

safe_spearman <- function(df, x, y) {
  d <- df |>
    select(all_of(c(x, y))) |>
    mutate(across(everything(), as.numeric)) |>
    drop_na()

  if (nrow(d) < 5L ||
      dplyr::n_distinct(d[[x]]) < 2L ||
      dplyr::n_distinct(d[[y]]) < 2L) {
    return(tibble(n = nrow(d), rho = NA_real_, p = NA_real_))
  }

  ct <- suppressWarnings(cor.test(d[[x]], d[[y]], method = "spearman", exact = FALSE))
  tibble(n = nrow(d), rho = unname(ct$estimate), p = ct$p.value)
}

run_corr_grid <- function(df, xs, ys, family) {
  crossing(x = xs, y = ys) |>
    mutate(result = map2(x, y, ~ safe_spearman(df, .x, .y))) |>
    unnest(result) |>
    mutate(
      abs_rho = abs(rho),
      p_bh = p.adjust(p, method = "BH"),
      p_bonf = p.adjust(p, method = "bonferroni"),
      survives_bh = !is.na(p_bh) & p_bh < 0.05,
      survives_bonferroni = !is.na(p_bonf) & p_bonf < 0.05,
      family = family
    ) |>
    arrange(p_bh, desc(abs_rho))
}

adjust_within <- function(df, group_col) {
  df |>
    group_by(across(all_of(group_col))) |>
    mutate(
      p_bh = p.adjust(p, method = "BH"),
      p_bonf = p.adjust(p, method = "bonferroni"),
      survives_bh = !is.na(p_bh) & p_bh < 0.05,
      survives_bonferroni = !is.na(p_bonf) & p_bonf < 0.05
    ) |>
    ungroup()
}

read_efa_scores_lookup <- function() {
  efa_scores <- read_csv(efa_factor_scores_file, show_col_types = FALSE) |>
    inner_join(
      read_csv(efa_beliefs_scores_file, show_col_types = FALSE) |>
        select(participant_id, Beliefs_UtilityComfort, Beliefs_FutureAIIntent, Beliefs_ConcernHarms),
      by = "participant_id"
    )

  efa_lookup <- bind_rows(
    read_csv(efa_factor_lookup_file, show_col_types = FALSE) |>
      transmute(
        factor,
        instrument,
        factor_id = short_factor,
        factor_num = as.integer(factor_num),
        proposed_name,
        display_label
      ),
    read_csv(efa_beliefs_lookup_file, show_col_types = FALSE) |>
      transmute(
        factor,
        instrument,
        factor_id = paste0("F", as.integer(factor_num)),
        factor_num = as.integer(factor_num),
        proposed_name,
        display_label
      )
  ) |>
    mutate(
      proposed_name = if_else(
        factor == "Beliefs_FutureAIIntent",
        "Future AI Orientation",
        proposed_name
      ),
      display_label = if_else(
        factor == "Beliefs_FutureAIIntent",
        "Beliefs F2 -> Future AI Orientation",
        display_label
      ),
      instrument_order = match(instrument, instrument_order)
    ) |>
    arrange(instrument_order, factor_num)

  list(scores = efa_scores, lookup = efa_lookup)
}

plot_side_by_side_heatmap <- function(plot_df, x_col, y_col, label_col, facet_col, title, subtitle, width, height, filename_base) {
  p <- ggplot(plot_df, aes(x = .data[[x_col]], y = .data[[y_col]], fill = rho)) +
    geom_tile(color = "white", linewidth = 0.55) +
    geom_text(aes(label = .data[[label_col]]), size = 2.8) +
    facet_wrap(as.formula(paste("~", facet_col)), nrow = 1) +
    scale_fill_gradient2(
      low = "#b3584b",
      mid = "white",
      high = "#3f6fa8",
      midpoint = 0,
      limits = c(-1, 1),
      name = "rho"
    ) +
    labs(
      title = title,
      subtitle = subtitle,
      x = NULL,
      y = NULL
    ) +
    theme_corr(base_size = 10) +
    theme(
      strip.text = element_text(face = "bold"),
      axis.text.x = element_text(size = 7.5, angle = 35, hjust = 1),
      axis.text.y = element_text(size = 7.5)
    )

  ggsave(file.path(plot_dir, paste0(filename_base, ".png")), p, width = width, height = height, units = "in", dpi = 300, bg = "white")
  ggsave(file.path(plot_dir, paste0(filename_base, ".pdf")), p, width = width, height = height, units = "in", bg = "white")
  p
}

fisher_z_compare <- function(rho_a, n_a, rho_b, n_b) {
  if (any(is.na(c(rho_a, n_a, rho_b, n_b))) || n_a <= 3L || n_b <= 3L) {
    return(NA_real_)
  }

  rho_a <- pmin(pmax(rho_a, -0.999999), 0.999999)
  rho_b <- pmin(pmax(rho_b, -0.999999), 0.999999)
  z <- (atanh(rho_a) - atanh(rho_b)) / sqrt((1 / (n_a - 3)) + (1 / (n_b - 3)))
  2 * pnorm(-abs(z))
}

safe_spearman_value <- function(df, x, y) {
  safe_spearman(df, x, y) |>
    select(n, rho, p)
}

order_stratified_pair <- function(df, factor_x, factor_y) {
  full <- safe_spearman_value(df, factor_x, factor_y)
  traditional_first <- safe_spearman_value(
    df |> filter(order == "Traditional_First"),
    factor_x,
    factor_y
  )
  ai_first <- safe_spearman_value(
    df |> filter(order == "AI_First"),
    factor_x,
    factor_y
  )

  tibble(
    factor_x,
    factor_y,
    Full_n = full$n,
    Traditional_First_n = traditional_first$n,
    AI_First_n = ai_first$n,
    Full_rho = full$rho,
    Traditional_First_rho = traditional_first$rho,
    AI_First_rho = ai_first$rho,
    Full_p = full$p,
    Traditional_First_p = traditional_first$p,
    AI_First_p = ai_first$p,
    fisher_p = fisher_z_compare(
      traditional_first$rho,
      traditional_first$n,
      ai_first$rho,
      ai_first$n
    ),
    rho_diff = traditional_first$rho - ai_first$rho
  )
}
```

# Inputs

```{r inputs}
composite_scores <- read_csv(composite_scores_file, show_col_types = FALSE)
composite_lookup <- read_csv(composite_specs_file, show_col_types = FALSE) |>
  select(instrument, factor, factor_id, factor_num, proposed_name, display_label, n_items) |>
  mutate(
    instrument_order = match(instrument, instrument_order),
    factor_num = as.integer(factor_num)
  ) |>
  arrange(instrument_order, factor_num)

composite_cols <- composite_lookup$factor
missing_composites <- setdiff(composite_cols, names(composite_scores))
if (length(missing_composites) > 0) {
  stop(
    paste0("Composite score file is missing columns: ", paste(missing_composites, collapse = ", ")),
    call. = FALSE
  )
}

factor_levels <- composite_lookup$display_label

composite_scores |>
  summarise(n_participants = n(), across(all_of(composite_cols), ~ sum(!is.na(.x)), .names = "{.col}_n")) |>
  pivot_longer(-n_participants, names_to = "factor_n_col", values_to = "n_nonmissing") |>
  slice_head(n = 6) |>
  kable(caption = "Composite score availability preview")
```

# Composite x Composite Correlations

```{r cross-composite-correlations}
factor_pairs <- combn(composite_cols, 2, simplify = FALSE) |>
  map_dfr(~ tibble(factor_x = .x[1], factor_y = .x[2]))

composite_corr_unique <- factor_pairs |>
  mutate(result = map2(factor_x, factor_y, ~ safe_spearman(composite_scores, .x, .y))) |>
  unnest(result) |>
  mutate(
    abs_rho = abs(rho),
    p_bh = p.adjust(p, method = "BH"),
    p_bonf = p.adjust(p, method = "bonferroni"),
    survives_bh = !is.na(p_bh) & p_bh < 0.05,
    survives_bonferroni = !is.na(p_bonf) & p_bonf < 0.05
  ) |>
  left_join(
    composite_lookup |>
      transmute(factor_x = factor, instrument_x = instrument, label_x = display_label),
    by = "factor_x"
  ) |>
  left_join(
    composite_lookup |>
      transmute(factor_y = factor, instrument_y = instrument, label_y = display_label),
    by = "factor_y"
  ) |>
  arrange(p_bh, desc(abs_rho))

composite_corr_diag <- tibble(
  factor_x = composite_cols,
  factor_y = composite_cols,
  rho = 1,
  p = NA_real_,
  n = map_int(composite_cols, ~ sum(!is.na(composite_scores[[.x]]))),
  abs_rho = 1,
  p_bh = NA_real_,
  p_bonf = NA_real_,
  survives_bh = NA,
  survives_bonferroni = NA
) |>
  left_join(
    composite_lookup |>
      transmute(factor_x = factor, instrument_x = instrument, label_x = display_label),
    by = "factor_x"
  ) |>
  left_join(
    composite_lookup |>
      transmute(factor_y = factor, instrument_y = instrument, label_y = display_label),
    by = "factor_y"
  )

composite_corr_heat <- bind_rows(
  composite_corr_unique,
  composite_corr_unique |>
    transmute(
      factor_x = factor_y,
      factor_y = factor_x,
      rho, p, n, abs_rho, p_bh, p_bonf, survives_bh, survives_bonferroni,
      instrument_x = instrument_y,
      instrument_y = instrument_x,
      label_x = label_y,
      label_y = label_x
    ),
  composite_corr_diag
)

write_csv(
  composite_corr_unique,
  file.path(csv_dir, "Composite_Cross_Factor_Correlations_Unique.csv")
)
write_csv(
  composite_corr_heat,
  file.path(csv_dir, "Composite_Cross_Factor_Heatmap_Matrix.csv")
)

composite_corr_unique |>
  mutate(across(c(rho, p, p_bh, p_bonf), ~ round(.x, 4))) |>
  slice_head(n = 20) |>
  kable(caption = "Top composite x composite Spearman correlations")
```

```{r cross-composite-heatmap, fig.width=12, fig.height=9}
cross_heat_df <- composite_corr_heat |>
  mutate(
    label_x = factor(label_x, levels = factor_levels),
    label_y = factor(label_y, levels = rev(factor_levels)),
    cell_label = case_when(
      factor_x == factor_y ~ "",
      is.na(rho) ~ "",
      TRUE ~ paste0(formatC(rho, format = "f", digits = 2), sig_suffix(p_bh, p_bonf))
    )
  )

p_cross_heat <- ggplot(cross_heat_df, aes(x = label_x, y = label_y, fill = rho)) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = cell_label), size = 3) +
  scale_fill_gradient2(
    low = "#b3584b",
    mid = "white",
    high = "#3f6fa8",
    midpoint = 0,
    limits = c(-1, 1),
    name = "rho"
  ) +
  labs(
    title = "Cross-Instrument Composite Correlation Heatmap",
    subtitle = "* BH < .05; ** Bonferroni < .05",
    x = NULL,
    y = NULL
  ) +
  theme_corr(base_size = 10) +
  theme(
    axis.text.y = element_text(size = 8),
    axis.text.x = element_text(size = 8, angle = 35, hjust = 1)
  )

ggsave(
  file.path(plot_dir, "Composite_Cross_Factor_Heatmap.png"),
  p_cross_heat,
  width = 12,
  height = 9,
  units = "in",
  dpi = 300,
  bg = "white"
)
ggsave(
  file.path(plot_dir, "Composite_Cross_Factor_Heatmap.pdf"),
  p_cross_heat,
  width = 12,
  height = 9,
  units = "in",
  bg = "white"
)

p_cross_heat
```

# EFA vs Composite: Survey Factor x Factor

```{r efa-composite-cross-factor-comparison, fig.width=16, fig.height=8.5}
efa_bundle <- read_efa_scores_lookup()
efa_factor_lookup <- efa_bundle$lookup
efa_factor_cols <- efa_factor_lookup$factor
efa_factor_levels <- efa_factor_lookup$display_label

efa_cross_heat <- read_csv(efa_cross_factor_file, show_col_types = FALSE) |>
  mutate(scoring = "EFA factor scores")

composite_cross_heat_compare <- composite_corr_heat |>
  mutate(scoring = "Simple mean composites")

cross_compare_df <- bind_rows(
  efa_cross_heat,
  composite_cross_heat_compare
) |>
  mutate(
    scoring = factor(scoring, levels = c("EFA factor scores", "Simple mean composites")),
    label_x = factor(label_x, levels = efa_factor_levels),
    label_y = factor(label_y, levels = rev(efa_factor_levels)),
    cell_label = case_when(
      factor_x == factor_y ~ "",
      is.na(rho) ~ "",
      TRUE ~ paste0(formatC(rho, format = "f", digits = 2), sig_suffix(p_bh, p_bonf))
    )
  )

p_cross_compare <- plot_side_by_side_heatmap(
  cross_compare_df,
  x_col = "label_x",
  y_col = "label_y",
  label_col = "cell_label",
  facet_col = "scoring",
  title = "Survey Factor x Factor Correlations: EFA vs Simple Mean Scoring",
  subtitle = "* BH < .05; ** Bonferroni < .05",
  width = 16,
  height = 8.5,
  filename_base = "EFA_vs_Composite_Cross_Factor_Heatmap"
)

efa_unique_for_diff <- efa_cross_heat |>
  filter(factor_x < factor_y) |>
  transmute(
    factor_x,
    factor_y,
    label_x,
    label_y,
    efa_rho = rho,
    efa_p_bh = p_bh,
    efa_p_bonf = p_bonf
  )

composite_unique_for_diff <- composite_corr_unique |>
  transmute(
    factor_x,
    factor_y,
    composite_rho = rho,
    composite_p_bh = p_bh,
    composite_p_bonf = p_bonf
  )

cross_scoring_diff <- efa_unique_for_diff |>
  inner_join(composite_unique_for_diff, by = c("factor_x", "factor_y")) |>
  mutate(
    rho_difference_composite_minus_efa = composite_rho - efa_rho,
    abs_difference = abs(rho_difference_composite_minus_efa),
    direction_change = sign(efa_rho) != sign(composite_rho)
  ) |>
  arrange(desc(abs_difference))

write_csv(cross_scoring_diff, file.path(csv_dir, "EFA_vs_Composite_Cross_Factor_Differences.csv"))

p_cross_compare
```

```{r efa-composite-cross-factor-difference-table}
cross_scoring_diff |>
  slice_head(n = 15) |>
  mutate(across(c(efa_rho, composite_rho, rho_difference_composite_minus_efa, efa_p_bh, composite_p_bh), ~ round(.x, 3))) |>
  transmute(
    `Factor 1` = label_x,
    `Factor 2` = label_y,
    `EFA rho` = efa_rho,
    `Composite rho` = composite_rho,
    `Composite - EFA` = rho_difference_composite_minus_efa,
    `Sign changed` = direction_change,
    `EFA BH p` = efa_p_bh,
    `Composite BH p` = composite_p_bh
  ) |>
  kable(caption = "Largest factor x factor differences between EFA factor scores and simple mean composites")
```

# Composite Factor x Factor Order Effects

```{r composite-order-stratified-correlations}
order_lookup <- read_csv(order_ready_file, show_col_types = FALSE) |>
  distinct(participant_id, order) |>
  mutate(order = factor(order, levels = c("Traditional_First", "AI_First")))

composite_order_df <- composite_scores |>
  inner_join(order_lookup, by = "participant_id")

composite_order_pairs <- combn(composite_cols, 2, simplify = FALSE) |>
  map_dfr(~ order_stratified_pair(composite_order_df, .x[1], .x[2])) |>
  mutate(
    fisher_p_bh = p.adjust(fisher_p, method = "BH"),
    fisher_p_bonf = p.adjust(fisher_p, method = "bonferroni"),
    fisher_sig = case_when(
      !is.na(fisher_p_bonf) & fisher_p_bonf < 0.05 ~ "Bonferroni p < .05",
      !is.na(fisher_p_bh) & fisher_p_bh < 0.05 ~ "BH p < .05",
      !is.na(fisher_p) & fisher_p < 0.05 ~ "raw p < .05",
      TRUE ~ "not significant"
    )
  ) |>
  left_join(
    composite_lookup |>
      transmute(factor_x = factor, instrument_x = instrument, label_x = display_label),
    by = "factor_x"
  ) |>
  left_join(
    composite_lookup |>
      transmute(factor_y = factor, instrument_y = instrument, label_y = display_label),
    by = "factor_y"
  ) |>
  mutate(
    pair_label = paste(label_x, label_y, sep = " x "),
    comparison_family = case_when(
      instrument_x == "BeliefsAboutAI" | instrument_y == "BeliefsAboutAI" ~
        "Includes exploratory Beliefs composite",
      TRUE ~ "Locked IMI/WritingEfficacy/AIReflection composites"
    )
  ) |>
  arrange(fisher_p_bh, fisher_p, desc(abs(rho_diff)))

write_csv(
  composite_order_pairs,
  file.path(csv_dir, "Composite_Factor_Order_Stratified_Correlations.csv")
)

composite_order_pairs |>
  slice_head(n = 20) |>
  mutate(across(c(
    Full_rho,
    Traditional_First_rho,
    AI_First_rho,
    rho_diff,
    fisher_p,
    fisher_p_bh,
    fisher_p_bonf
  ), ~ round(.x, 3))) |>
  transmute(
    `Factor 1` = label_x,
    `Factor 2` = label_y,
    `Full rho` = Full_rho,
    `Traditional-first rho` = Traditional_First_rho,
    `AI-first rho` = AI_First_rho,
    `Trad - AI` = rho_diff,
    `Fisher p` = fisher_p,
    `BH p` = fisher_p_bh,
    `Bonf p` = fisher_p_bonf,
    `Multiplicity` = fisher_sig
  ) |>
  kable(caption = "Composite factor x factor correlations stratified by task order")
```

# EFA vs Composite: Factor x Factor Order Effects

```{r efa-composite-order-effect-comparison, fig.width=18, fig.height=11}
make_pair_id <- function(x, y) {
  map2_chr(x, y, ~ paste(sort(c(.x, .y)), collapse = "__"))
}

pair_label_lookup <- composite_order_pairs |>
  mutate(pair_id = make_pair_id(factor_x, factor_y)) |>
  distinct(pair_id, label_x, label_y, pair_label, comparison_family)

efa_order_pairs <- read_csv(efa_order_file, show_col_types = FALSE) |>
  transmute(
    factor_x = col_x,
    factor_y = col_y,
    pair_id = make_pair_id(col_x, col_y),
    scoring = "EFA factor scores",
    Full_n,
    Traditional_First_n,
    AI_First_n,
    Full_rho,
    Traditional_First_rho,
    AI_First_rho,
    fisher_p,
    fisher_p_bh,
    fisher_p_bonf = fisher_p_bonferroni,
    rho_diff
  ) |>
  left_join(pair_label_lookup, by = "pair_id")

composite_order_compare_pairs <- composite_order_pairs |>
  transmute(
    factor_x,
    factor_y,
    pair_id = make_pair_id(factor_x, factor_y),
    scoring = "Simple mean composites",
    Full_n,
    Traditional_First_n,
    AI_First_n,
    Full_rho,
    Traditional_First_rho,
    AI_First_rho,
    fisher_p,
    fisher_p_bh,
    fisher_p_bonf,
    rho_diff,
    label_x,
    label_y,
    pair_label,
    comparison_family
  )

order_scoring_compare_long <- bind_rows(
  efa_order_pairs,
  composite_order_compare_pairs
) |>
  mutate(
    scoring = factor(scoring, levels = c("EFA factor scores", "Simple mean composites")),
    significance = case_when(
      !is.na(fisher_p_bonf) & fisher_p_bonf < 0.05 ~ "Bonferroni < .05",
      !is.na(fisher_p_bh) & fisher_p_bh < 0.05 ~ "BH < .05",
      !is.na(fisher_p) & fisher_p < 0.05 ~ "Nominal < .05",
      TRUE ~ "Not significant"
    ),
    p_label = case_when(
      !is.na(fisher_p_bonf) & fisher_p_bonf < 0.01 ~ "Bonf p < .01",
      !is.na(fisher_p_bonf) & fisher_p_bonf < 0.05 ~ "Bonf p < .05",
      !is.na(fisher_p_bh) & fisher_p_bh < 0.05 ~ "BH p < .05",
      !is.na(fisher_p) & fisher_p < 0.05 ~ "p < .05",
      TRUE ~ ""
    )
  )

order_scoring_diff <- order_scoring_compare_long |>
  select(
    pair_id,
    scoring,
    label_x,
    label_y,
    pair_label,
    comparison_family,
    Traditional_First_rho,
    AI_First_rho,
    rho_diff,
    fisher_p,
    fisher_p_bh,
    fisher_p_bonf,
    significance,
    p_label
  ) |>
  pivot_wider(
    names_from = scoring,
    values_from = c(
      Traditional_First_rho,
      AI_First_rho,
      rho_diff,
      fisher_p,
      fisher_p_bh,
      fisher_p_bonf,
      significance,
      p_label
    ),
    names_glue = "{.value}_{scoring}"
  ) |>
  mutate(
    rho_diff_change_composite_minus_efa =
      `rho_diff_Simple mean composites` - `rho_diff_EFA factor scores`,
    abs_rho_diff_change = abs(rho_diff_change_composite_minus_efa),
    same_order_direction = sign(`rho_diff_EFA factor scores`) ==
      sign(`rho_diff_Simple mean composites`)
  ) |>
  arrange(
    pmin(`fisher_p_bh_EFA factor scores`, `fisher_p_bh_Simple mean composites`, na.rm = TRUE),
    desc(pmax(abs(`rho_diff_EFA factor scores`), abs(`rho_diff_Simple mean composites`), na.rm = TRUE))
  )

write_csv(
  order_scoring_compare_long,
  file.path(csv_dir, "EFA_vs_Composite_Order_Effects_Long.csv")
)
write_csv(
  order_scoring_diff,
  file.path(csv_dir, "EFA_vs_Composite_Order_Effect_Differences.csv")
)

belief_order_pair_levels <- order_scoring_diff |>
  filter(comparison_family == "Includes exploratory Beliefs composite") |>
  arrange(`rho_diff_EFA factor scores`) |>
  mutate(pair_label_wrapped = str_wrap(pair_label, width = 50)) |>
  pull(pair_label_wrapped)

order_compare_plot_df <- order_scoring_compare_long |>
  filter(comparison_family == "Includes exploratory Beliefs composite") |>
  mutate(
    pair_label_wrapped = str_wrap(pair_label, width = 50),
    pair_label_wrapped = factor(pair_label_wrapped, levels = belief_order_pair_levels),
    significance = factor(
      significance,
      levels = c("Bonferroni < .05", "BH < .05", "Nominal < .05", "Not significant")
    ),
    hjust_label = if_else(rho_diff >= 0, -0.08, 1.08)
  )

# Right-edge "table" region: per-row Traditional-first and AI-first rho values
rho_col_trad_x <- 1.08
rho_col_ai_x <- 1.32
rho_table_divider_x <- 0.94
rho_table_header_y <- length(belief_order_pair_levels) + 1.6
rho_col_trad_color <- "#a15c22"
rho_col_ai_color <- "#0f766e"

order_rho_table_df <- order_compare_plot_df |>
  select(scoring, pair_label_wrapped, Traditional_First_rho, AI_First_rho) |>
  pivot_longer(
    c(Traditional_First_rho, AI_First_rho),
    names_to = "order_group",
    values_to = "group_rho"
  ) |>
  mutate(
    col_x = if_else(order_group == "Traditional_First_rho", rho_col_trad_x, rho_col_ai_x),
    col_color = if_else(
      order_group == "Traditional_First_rho",
      rho_col_trad_color,
      rho_col_ai_color
    ),
    rho_label = if_else(
      is.na(group_rho),
      "--",
      scales::number(group_rho, accuracy = 0.01, style_negative = "minus")
    )
  )

order_rho_header_df <- tibble(
  col_x = c(rho_col_trad_x, rho_col_ai_x),
  col_y = rho_table_header_y,
  header_label = c("Trad-first\nrho", "AI-first\nrho"),
  col_color = c(rho_col_trad_color, rho_col_ai_color)
)

p_order_scoring_side_by_side <- ggplot(
  order_compare_plot_df,
  aes(x = rho_diff, y = pair_label_wrapped, fill = significance)
) +
  geom_vline(xintercept = 0, color = "#bdbdbd", linewidth = 0.8) +
  geom_col(width = 0.72, alpha = 0.95) +
  geom_text(
    data = \(d) filter(d, p_label != ""),
    aes(label = p_label, hjust = hjust_label),
    size = 3.1,
    color = "#3f3f3f"
  ) +
  annotate(
    "segment",
    x = rho_table_divider_x,
    xend = rho_table_divider_x,
    y = 0.4,
    yend = rho_table_header_y - 0.5,
    color = "#d9d9d9",
    linewidth = 0.5
  ) +
  geom_text(
    data = order_rho_table_df,
    aes(x = col_x, y = pair_label_wrapped, label = rho_label, color = col_color),
    inherit.aes = FALSE,
    size = 2.9
  ) +
  geom_text(
    data = order_rho_header_df,
    aes(x = col_x, y = col_y, label = header_label, color = col_color),
    inherit.aes = FALSE,
    fontface = "bold",
    size = 3.1,
    lineheight = 0.9
  ) +
  scale_color_identity() +
  facet_wrap(vars(scoring), nrow = 1) +
  scale_fill_manual(
    values = c(
      "Bonferroni < .05" = "#7b2cbf",
      "BH < .05" = "#1b9e77",
      "Nominal < .05" = "#e69500",
      "Not significant" = "#b8b8b8"
    ),
    drop = FALSE
  ) +
  scale_x_continuous(
    limits = c(min(c(order_compare_plot_df$rho_diff, -0.95), na.rm = TRUE), 1.44),
    breaks = seq(-0.8, 0.8, by = 0.2),
    labels = scales::number_format(accuracy = 0.01)
  ) +
  scale_y_discrete(expand = expansion(add = c(0.6, 2.4))) +
  coord_cartesian(clip = "off") +
  labs(
    title = "Order-group rho differences involving exploratory Beliefs factors",
    subtitle = paste(
      "Bars show Traditional-First rho minus AI-First rho;",
      "panels compare EFA factor scores with simple mean composites.",
      "Right columns list each order group's Spearman rho."
    ),
    x = "rho difference",
    y = NULL,
    fill = NULL,
    caption = paste(
      "Fisher z p-values compare order groups within each scoring method.",
      "Multiplicity corrections are applied within the 27 exploratory-Beliefs pair family."
    )
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "top",
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    strip.text = element_text(face = "bold", size = 12),
    axis.text.y = element_text(size = 7.6),
    plot.title = element_text(face = "bold", size = 18),
    plot.subtitle = element_text(size = 11, color = "#666666"),
    plot.caption = element_text(size = 9.5, color = "#7a7a7a"),
    plot.margin = margin(12, 70, 12, 12)
  )

ggsave(
  file.path(plot_dir, "EFA_vs_Composite_Beliefs_Order_Rho_Diff_SideBySide.png"),
  p_order_scoring_side_by_side,
  width = 18,
  height = 11,
  units = "in",
  dpi = 300,
  bg = "white"
)
ggsave(
  file.path(plot_dir, "EFA_vs_Composite_Beliefs_Order_Rho_Diff_SideBySide.pdf"),
  p_order_scoring_side_by_side,
  width = 18,
  height = 11,
  units = "in",
  bg = "white"
)

order_scoring_diff |>
  slice_head(n = 15) |>
  mutate(across(
    where(is.numeric),
    ~ round(.x, 3)
  )) |>
  transmute(
    `Factor pair` = pair_label,
    `EFA Trad-AI` = `rho_diff_EFA factor scores`,
    `Composite Trad-AI` = `rho_diff_Simple mean composites`,
    `Composite - EFA` = rho_diff_change_composite_minus_efa,
    `Same direction` = same_order_direction,
    `EFA BH p` = `fisher_p_bh_EFA factor scores`,
    `Composite BH p` = `fisher_p_bh_Simple mean composites`
  ) |>
  kable(caption = "EFA vs composite order-effect differences for matched factor pairs")

p_order_scoring_side_by_side
```

# ART vs Composites

```{r art-correlations}
art_metric_lookup <- tibble(
  art_metric = c(
    "art_real_hits",
    "art_fake_false_alarms",
    "art_net_real_minus_fake"
  ),
  art_label = c(
    "Real hits",
    "False alarms",
    "ART net"
  )
)

art_scores <- read_csv(art_scores_file, show_col_types = FALSE)

art_df <- art_scores |>
  select(participant_id, all_of(art_metric_lookup$art_metric)) |>
  inner_join(composite_scores, by = "participant_id")

art_corrs <- run_corr_grid(
  art_df,
  art_metric_lookup$art_metric,
  composite_cols,
  "art_vs_composites"
) |>
  rename(art_metric = x, factor = y) |>
  left_join(art_metric_lookup, by = "art_metric") |>
  left_join(composite_lookup, by = "factor") |>
  arrange(p_bh, desc(abs_rho))

art_ranking_primary <- art_corrs |>
  filter(art_metric == "art_net_real_minus_fake") |>
  arrange(desc(abs_rho), p_bh, p_bonf)

write_csv(art_corrs, file.path(csv_dir, "ART_vs_Composites_Correlations.csv"))
write_csv(art_ranking_primary, file.path(csv_dir, "ART_Net_vs_Composites_Ranked.csv"))

art_corrs |>
  select(art_label, instrument, display_label, n, rho, p, p_bh, p_bonf) |>
  mutate(across(c(rho, p, p_bh, p_bonf), ~ round(.x, 4))) |>
  slice_head(n = 20) |>
  kable(caption = "ART metrics vs composite scores")
```

```{r art-heatmap, fig.width=10, fig.height=7}
art_heat_df <- art_corrs |>
  mutate(
    art_label = factor(art_label, levels = art_metric_lookup$art_label),
    display_label = factor(display_label, levels = rev(factor_levels)),
    cell_label = case_when(
      is.na(rho) ~ "",
      TRUE ~ paste0(formatC(rho, format = "f", digits = 2), sig_suffix(p_bh, p_bonf))
    )
  )

p_art_heat <- ggplot(art_heat_df, aes(x = art_label, y = display_label, fill = rho)) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = cell_label), size = 3) +
  scale_fill_gradient2(
    low = "#c73e3a",
    mid = "#f7f7f7",
    high = "#4f79b7",
    midpoint = 0,
    limits = c(-1, 1),
    name = "Spearman rho"
  ) +
  labs(
    title = "ART vs Composite Scores",
    subtitle = "* BH < .05   ** Bonferroni < .05",
    x = NULL,
    y = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid = element_blank(),
    axis.text.x = element_text(angle = 15, hjust = 1),
    plot.margin = margin(10, 15, 10, 10)
  )

ggsave(
  file.path(plot_dir, "ART_vs_Composites_Heatmap.png"),
  p_art_heat,
  width = 10,
  height = 7,
  units = "in",
  dpi = 300,
  bg = "white"
)
ggsave(
  file.path(plot_dir, "ART_vs_Composites_Heatmap.pdf"),
  p_art_heat,
  width = 10,
  height = 7,
  units = "in",
  bg = "white"
)

p_art_heat
```

# EFA vs Composite: ART Anchors

```{r efa-composite-art-comparison, fig.width=16, fig.height=7.5}
efa_art_primary <- read_csv(efa_art_primary_file, show_col_types = FALSE) |>
  transmute(
    art_metric,
    factor,
    n,
    rho,
    p = p_value,
    p_bh,
    p_bonf = p_bonferroni,
    art_label,
    instrument,
    factor_num = as.integer(factor_num),
    proposed_name,
    display_label
  )

efa_art_beliefs <- read_csv(efa_art_beliefs_file, show_col_types = FALSE) |>
  transmute(
    art_metric,
    factor,
    n,
    rho,
    p,
    p_bh,
    p_bonf,
    art_label,
    instrument,
    factor_num = as.integer(factor_num),
    proposed_name,
    display_label
  )

efa_art_compare <- bind_rows(efa_art_primary, efa_art_beliefs) |>
  filter(art_metric %in% art_metric_lookup$art_metric) |>
  select(art_metric, factor, n, rho, p, p_bh, p_bonf) |>
  left_join(
    efa_factor_lookup |>
      select(factor, instrument, factor_num, proposed_name, display_label),
    by = "factor"
  ) |>
  left_join(art_metric_lookup, by = "art_metric") |>
  mutate(scoring = "EFA factor scores")

composite_art_compare <- art_corrs |>
  filter(art_metric %in% art_metric_lookup$art_metric) |>
  mutate(scoring = "Simple mean composites")

art_compare_df <- bind_rows(efa_art_compare, composite_art_compare) |>
  mutate(
    art_label = recode(
      art_metric,
      art_net_real_minus_fake = "ART net",
      art_fake_false_alarms = "False alarms",
      art_real_hits = "Real hits",
      .default = art_label
    ),
    art_label = factor(art_label, levels = c("ART net", "False alarms", "Real hits")),
    display_label = factor(display_label, levels = rev(efa_factor_levels)),
    scoring = factor(scoring, levels = c("EFA factor scores", "Simple mean composites")),
    cell_label = case_when(
      is.na(rho) ~ "",
      TRUE ~ paste0(formatC(rho, format = "f", digits = 2), sig_suffix(p_bh, p_bonf))
    )
  )

p_art_compare <- plot_side_by_side_heatmap(
  art_compare_df,
  x_col = "art_label",
  y_col = "display_label",
  label_col = "cell_label",
  facet_col = "scoring",
  title = "Survey Factors x ART Metrics: EFA vs Simple Mean Scoring",
  subtitle = "Restricted to ART net, false alarms, and real hits. * BH < .05; ** Bonferroni < .05",
  width = 16,
  height = 7.5,
  filename_base = "EFA_vs_Composite_ART_Heatmap"
)

art_scoring_diff <- efa_art_compare |>
  select(art_metric, factor, art_label, display_label, efa_rho = rho, efa_p_bh = p_bh) |>
  inner_join(
    composite_art_compare |>
      select(art_metric, factor, composite_rho = rho, composite_p_bh = p_bh),
    by = c("art_metric", "factor")
  ) |>
  mutate(
    rho_difference_composite_minus_efa = composite_rho - efa_rho,
    abs_difference = abs(rho_difference_composite_minus_efa),
    direction_change = sign(efa_rho) != sign(composite_rho)
  ) |>
  arrange(desc(abs_difference))

write_csv(art_scoring_diff, file.path(csv_dir, "EFA_vs_Composite_ART_Differences.csv"))

p_art_compare
```

# Q17 AI-Use vs Composites

```{r q17-correlations}
q17_bucket <- read_csv(q17_bucket_file, show_col_types = FALSE)

q17_metric_lookup <- tibble(
  q17_metric = c(
    "q17_p_1",
    "q17_p_2",
    "q17_p_3",
    "q17_p_4",
    "q17_p_5",
    "q17_mean_use",
    "q17_n_3",
    "q17_n_4",
    "q17_n_5"
  ),
  q17_label = c(
    "Prop. never heard",
    "Prop. heard, never used",
    "Prop. rarely use",
    "Prop. regularly use",
    "Prop. often use",
    "Mean use score",
    "Count rarely use",
    "Count regularly use",
    "Count often use"
  )
)

q17_df <- q17_bucket |>
  select(participant_id, all_of(q17_metric_lookup$q17_metric)) |>
  inner_join(composite_scores, by = "participant_id")

q17_corrs <- crossing(
  q17_metric = q17_metric_lookup$q17_metric,
  factor = composite_cols
) |>
  mutate(result = map2(factor, q17_metric, ~ safe_spearman(q17_df, .x, .y))) |>
  unnest(result) |>
  mutate(abs_rho = abs(rho), family = "q17_vs_composites") |>
  adjust_within("q17_metric") |>
  left_join(q17_metric_lookup, by = "q17_metric") |>
  left_join(composite_lookup, by = "factor") |>
  arrange(q17_metric, p_bh, desc(abs_rho))

write_csv(q17_corrs, file.path(csv_dir, "Q17_AI_Use_vs_Composites_Correlations.csv"))

q17_corrs |>
  select(q17_label, instrument, display_label, n, rho, p, p_bh, p_bonf) |>
  mutate(across(c(rho, p, p_bh, p_bonf), ~ round(.x, 4))) |>
  slice_head(n = 20) |>
  kable(caption = "Q17 AI-use metrics vs composite scores")
```

```{r q17-heatmap, fig.width=12, fig.height=7.5}
q17_heat_metrics <- c("q17_p_1", "q17_p_2", "q17_p_3", "q17_p_4", "q17_p_5", "q17_mean_use")

q17_heat_df <- q17_corrs |>
  filter(q17_metric %in% q17_heat_metrics) |>
  mutate(
    q17_label = factor(
      q17_label,
      levels = q17_metric_lookup |>
        filter(q17_metric %in% q17_heat_metrics) |>
        pull(q17_label)
    ),
    display_label = factor(display_label, levels = factor_levels),
    cell_label = case_when(
      is.na(rho) ~ "",
      TRUE ~ paste0(formatC(rho, format = "f", digits = 2), sig_suffix(p_bh, p_bonf))
    )
  )

p_q17_heat <- ggplot(q17_heat_df, aes(x = q17_label, y = display_label, fill = rho)) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = cell_label), size = 3) +
  scale_fill_gradient2(
    low = "#c73e3a",
    mid = "#f7f7f7",
    high = "#4f79b7",
    midpoint = 0,
    limits = c(-1, 1),
    name = "Spearman rho"
  ) +
  labs(
    title = "Q17 Familiarity Buckets vs Composite Scores",
    subtitle = "* BH < .05   ** Bonferroni < .05  |  BH corrected within each Q17 metric",
    x = NULL,
    y = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid = element_blank(),
    axis.text.x = element_text(angle = 20, hjust = 1),
    plot.margin = margin(10, 15, 10, 10)
  )

ggsave(
  file.path(plot_dir, "Q17_AI_Use_vs_Composites_Heatmap.png"),
  p_q17_heat,
  width = 12,
  height = 7.5,
  units = "in",
  dpi = 300,
  bg = "white"
)
ggsave(
  file.path(plot_dir, "Q17_AI_Use_vs_Composites_Heatmap.pdf"),
  p_q17_heat,
  width = 12,
  height = 7.5,
  units = "in",
  bg = "white"
)

p_q17_heat
```

# EFA vs Composite: Q17 Filtered Bucket Counts

```{r q17-filtered-bucket-correlations}
q17_long <- read_csv(q17_long_file, show_col_types = FALSE) |>
  mutate(use_score = as.numeric(use_score))

q17_tool_summary <- q17_long |>
  group_by(tool) |>
  summarise(
    n_participants = n_distinct(participant_id),
    heard_pct = mean(use_score >= 2, na.rm = TRUE),
    ever_used_pct = mean(use_score >= 3, na.rm = TRUE),
    regular_use_pct = mean(use_score >= 4, na.rm = TRUE),
    often_use_pct = mean(use_score == 5, na.rm = TRUE),
    sd_use = sd(use_score, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(ever_used_pct), desc(regular_use_pct), tool)

q17_retained_tools <- q17_tool_summary |>
  filter(ever_used_pct >= .10, sd_use > 0) |>
  pull(tool)

q17_filtered_counts <- q17_long |>
  filter(tool %in% q17_retained_tools, !is.na(use_score)) |>
  group_by(participant_id) |>
  summarise(
    q17_filtered_n_1 = sum(use_score == 1, na.rm = TRUE),
    q17_filtered_n_2 = sum(use_score == 2, na.rm = TRUE),
    q17_filtered_n_3 = sum(use_score == 3, na.rm = TRUE),
    q17_filtered_n_4 = sum(use_score == 4, na.rm = TRUE),
    q17_filtered_n_5 = sum(use_score == 5, na.rm = TRUE),
    q17_filtered_regular_or_often = sum(use_score >= 4, na.rm = TRUE),
    q17_filtered_ever_used = sum(use_score >= 3, na.rm = TRUE),
    .groups = "drop"
  )

q17_filtered_metric_lookup <- tibble(
  q17_metric = c(
    "q17_filtered_n_1",
    "q17_filtered_n_2",
    "q17_filtered_n_3",
    "q17_filtered_n_4",
    "q17_filtered_n_5",
    "q17_filtered_regular_or_often",
    "q17_filtered_ever_used"
  ),
  q17_label = c(
    "Count never heard",
    "Count heard only",
    "Count rarely use",
    "Count sometimes use",
    "Count often use",
    "Count sometimes/often",
    "Count ever used"
  )
)

run_q17_filtered_corrs <- function(score_df, lookup_df, scoring_label) {
  merged_df <- q17_filtered_counts |>
    inner_join(score_df |> select(participant_id, all_of(lookup_df$factor)), by = "participant_id")

  run_corr_grid(
    merged_df,
    q17_filtered_metric_lookup$q17_metric,
    lookup_df$factor,
    paste0("q17_filtered_counts_", scoring_label)
  ) |>
    rename(q17_metric = x, factor = y) |>
    left_join(q17_filtered_metric_lookup, by = "q17_metric") |>
    left_join(lookup_df, by = "factor") |>
    mutate(scoring = scoring_label) |>
    arrange(q17_metric, p_bh, desc(abs_rho))
}

q17_filtered_efa_corrs <- run_q17_filtered_corrs(
  efa_bundle$scores,
  efa_factor_lookup,
  "EFA factor scores"
)

q17_filtered_composite_corrs <- run_q17_filtered_corrs(
  composite_scores,
  composite_lookup,
  "Simple mean composites"
)

q17_filtered_corrs <- bind_rows(q17_filtered_efa_corrs, q17_filtered_composite_corrs)

write_csv(q17_tool_summary, file.path(csv_dir, "Q17_Filtered_Tool_Summary.csv"))
write_csv(tibble(tool = q17_retained_tools), file.path(csv_dir, "Q17_Filtered_Retained_Tools.csv"))
write_csv(q17_filtered_corrs, file.path(csv_dir, "Q17_Filtered_Bucket_Counts_vs_Factors_EFA_Composite.csv"))

q17_filtered_corrs |>
  filter(q17_metric %in% c("q17_filtered_n_3", "q17_filtered_n_4", "q17_filtered_n_5")) |>
  select(scoring, q17_label, instrument, display_label, n, rho, p, p_bh, p_bonf) |>
  mutate(across(c(rho, p, p_bh, p_bonf), ~ round(.x, 4))) |>
  arrange(scoring, q17_label, p_bh) |>
  slice_head(n = 24) |>
  kable(caption = "Filtered Q17 bucket-count correlations for used-tool response levels")
```

```{r q17-filtered-bucket-heatmap, fig.width=16, fig.height=7.5}
q17_filtered_heat_metrics <- c(
  "q17_filtered_n_3",
  "q17_filtered_n_4",
  "q17_filtered_n_5",
  "q17_filtered_regular_or_often",
  "q17_filtered_ever_used"
)

q17_filtered_heat_df <- q17_filtered_corrs |>
  filter(q17_metric %in% q17_filtered_heat_metrics) |>
  mutate(
    q17_label = factor(
      q17_label,
      levels = q17_filtered_metric_lookup |>
        filter(q17_metric %in% q17_filtered_heat_metrics) |>
        pull(q17_label)
    ),
    display_label = factor(display_label, levels = rev(efa_factor_levels)),
    scoring = factor(scoring, levels = c("EFA factor scores", "Simple mean composites")),
    cell_label = case_when(
      is.na(rho) ~ "",
      TRUE ~ paste0(formatC(rho, format = "f", digits = 2), sig_suffix(p_bh, p_bonf))
    )
  )

p_q17_filtered_compare <- plot_side_by_side_heatmap(
  q17_filtered_heat_df,
  x_col = "q17_label",
  y_col = "display_label",
  label_col = "cell_label",
  facet_col = "scoring",
  title = "Survey Factors x Q17 Filtered Bucket Counts: EFA vs Simple Mean Scoring",
  subtitle = paste0(
    "Retained ",
    length(q17_retained_tools),
    " tools with ever-used rate >= 10%; bucket scores are participant-level counts. * BH < .05; ** Bonferroni < .05"
  ),
  width = 16,
  height = 7.5,
  filename_base = "EFA_vs_Composite_Q17_Filtered_Bucket_Counts_Heatmap"
)

q17_filtered_diff <- q17_filtered_efa_corrs |>
  select(q17_metric, factor, q17_label, display_label, efa_rho = rho, efa_p_bh = p_bh) |>
  inner_join(
    q17_filtered_composite_corrs |>
      select(q17_metric, factor, composite_rho = rho, composite_p_bh = p_bh),
    by = c("q17_metric", "factor")
  ) |>
  mutate(
    rho_difference_composite_minus_efa = composite_rho - efa_rho,
    abs_difference = abs(rho_difference_composite_minus_efa),
    direction_change = sign(efa_rho) != sign(composite_rho)
  ) |>
  arrange(desc(abs_difference))

write_csv(q17_filtered_diff, file.path(csv_dir, "EFA_vs_Composite_Q17_Filtered_Bucket_Count_Differences.csv"))

p_q17_filtered_compare
```

# Named Model Use vs Composites

```{r named-model-correlations}
model_lookup <- tibble(
  model_label = c("ChatGPT", "Claude", "Gemini", "Copilot")
)

model_scores <- read_csv(named_model_file, show_col_types = FALSE) |>
  select(participant_id, all_of(model_lookup$model_label))

model_df <- model_scores |>
  inner_join(composite_scores, by = "participant_id")

model_corrs <- crossing(
  model_label = model_lookup$model_label,
  factor = composite_cols
) |>
  mutate(result = map2(model_label, factor, ~ safe_spearman(model_df, .x, .y))) |>
  unnest(result) |>
  mutate(abs_rho = abs(rho), family = "named_model_use_vs_composites") |>
  adjust_within("model_label") |>
  left_join(composite_lookup, by = "factor") |>
  arrange(model_label, p_bh, desc(abs_rho))

write_csv(model_corrs, file.path(csv_dir, "Named_Model_Use_vs_Composites_Correlations.csv"))

model_corrs |>
  select(model_label, instrument, display_label, n, rho, p, p_bh, p_bonf) |>
  mutate(across(c(rho, p, p_bh, p_bonf), ~ round(.x, 4))) |>
  kable(caption = "Named model use vs composite scores")
```

```{r named-model-heatmap, fig.width=10, fig.height=6.5}
model_heat_df <- model_corrs |>
  mutate(
    model_label = factor(model_label, levels = model_lookup$model_label),
    display_label = factor(display_label, levels = factor_levels),
    cell_label = case_when(
      is.na(rho) ~ "",
      TRUE ~ paste0(formatC(rho, format = "f", digits = 2), sig_suffix(p_bh, p_bonf))
    )
  )

p_model_heat <- ggplot(model_heat_df, aes(x = model_label, y = display_label, fill = rho)) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = cell_label), size = 3) +
  scale_fill_gradient2(
    low = "#c73e3a",
    mid = "#f7f7f7",
    high = "#4f79b7",
    midpoint = 0,
    limits = c(-1, 1),
    name = "Spearman rho"
  ) +
  labs(
    title = "Named Model Use vs Composite Scores",
    subtitle = "* BH < .05   ** Bonferroni < .05  |  BH corrected within each model",
    x = "Primary AI model use score predictor",
    y = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid = element_blank(),
    axis.text.x = element_text(angle = 20, hjust = 1),
    plot.margin = margin(10, 15, 10, 10)
  )

ggsave(
  file.path(plot_dir, "Named_Model_Use_vs_Composites_Heatmap.png"),
  p_model_heat,
  width = 10,
  height = 6.5,
  units = "in",
  dpi = 300,
  bg = "white"
)
ggsave(
  file.path(plot_dir, "Named_Model_Use_vs_Composites_Heatmap.pdf"),
  p_model_heat,
  width = 10,
  height = 6.5,
  units = "in",
  bg = "white"
)

p_model_heat
```

# Combined Ranked Output

```{r combined-ranked}
all_ranked_correlations <- bind_rows(
  composite_corr_unique |>
    transmute(
      source = "composite_x_composite",
      predictor = label_x,
      outcome = label_y,
      n,
      rho,
      p,
      p_bh,
      p_bonf,
      abs_rho
    ),
  art_corrs |>
    transmute(
      source = "art_vs_composites",
      predictor = art_label,
      outcome = display_label,
      n,
      rho,
      p,
      p_bh,
      p_bonf,
      abs_rho
    ),
  q17_corrs |>
    transmute(
      source = "q17_vs_composites",
      predictor = q17_label,
      outcome = display_label,
      n,
      rho,
      p,
      p_bh,
      p_bonf,
      abs_rho
    ),
  model_corrs |>
    transmute(
      source = "named_model_use_vs_composites",
      predictor = model_label,
      outcome = display_label,
      n,
      rho,
      p,
      p_bh,
      p_bonf,
      abs_rho
    )
) |>
  arrange(p_bh, desc(abs_rho))

write_csv(
  all_ranked_correlations,
  file.path(csv_dir, "Composite_All_Correlations_Ranked.csv")
)
```

# Composite Workbook

```{r composite-workbook}
item_membership <- read_csv(composite_item_membership_file, show_col_types = FALSE) |>
  mutate(
    instrument_order = match(instrument, instrument_order),
    factor_num = as.integer(factor_num),
    item_id = as.integer(item_id),
    item_col = paste0(instrument, "_Q", item_id),
    item_header_base = str_squish(item_text),
    item_reference = paste0(instrument, " Q", item_id),
    reverse_scoring_note = case_when(
      instrument == "IMI" & item_id %in% imi_reverse_items ~
        "reverse scored: 8 - raw score; IMI uses 1-7, so min + max = 8",
      instrument == "BeliefsAboutAI" & item_id %in% beliefs_reverse_items ~
        paste(
          "reverse scored upstream as 6 - raw score because Beliefs uses 1-5",
          "and min + max = 6"
        ),
      TRUE ~ NA_character_
    ),
    item_reference = if_else(
      is.na(reverse_scoring_note),
      item_reference,
      paste0(item_reference, "\n(", reverse_scoring_note, ")")
    ),
    item_header = paste0(item_header_base, "\n", item_reference)
  ) |>
  arrange(instrument_order, factor_num, item_id)

unassigned_items <- read_csv(unassigned_items_file, show_col_types = FALSE)

read_clean_item_scores <- function(instrument_name, path, item_col_name) {
  read_csv(path, show_col_types = FALSE) |>
    transmute(
      instrument = instrument_name,
      participant_id,
      item_id = as.integer(.data[[item_col_name]]),
      score = as.numeric(score)
    )
}

item_scores_long <- bind_rows(
  read_clean_item_scores(
    "IMI",
    file.path("01_audit_cleaning", "cleaned", "IMI_cleaned.csv"),
    "item_code"
  ),
  read_clean_item_scores(
    "WritingEfficacy",
    file.path("01_audit_cleaning", "cleaned", "WritingEfficacy_cleaned.csv"),
    "item_code"
  ) |>
    mutate(score = (score / 25) + 1),
  read_clean_item_scores(
    "AIReflection",
    file.path("01_audit_cleaning", "cleaned", "AI_Reflection_cleaned.csv"),
    "item_num"
  ),
  read_clean_item_scores(
    "BeliefsAboutAI",
    file.path("02_efa_exports", "efa", "BeliefsAboutAI_EFA_Primary.csv"),
    "item_num"
  )
)

assigned_item_scores <- item_scores_long |>
  inner_join(
    item_membership |>
      select(instrument, item_id, factor, factor_id, factor_num, item_col),
    by = c("instrument", "item_id")
  ) |>
  mutate(
    score = if_else(factor == "Beliefs_ConcernHarms", 6 - score, score)
  )

item_cols <- item_membership$item_col

item_scores_wide <- assigned_item_scores |>
  select(participant_id, item_col, score) |>
  distinct() |>
  pivot_wider(names_from = item_col, values_from = score)

format_likert_range <- function(item_ids) {
  ids <- sort(unique(as.integer(item_ids)))
  if (length(ids) > 1L && all(diff(ids) == 1L)) {
    return(paste0("Likerts Q", min(ids), "-Q", max(ids)))
  }
  paste0("Likerts ", paste0("Q", ids, collapse = ", "))
}

factor_item_ranges <- item_membership |>
  group_by(factor) |>
  summarise(
    likert_range = format_likert_range(item_id),
    .groups = "drop"
  )

composite_workbook_lookup <- composite_lookup |>
  left_join(factor_item_ranges, by = "factor")

workbook_column_map <- bind_rows(
  composite_workbook_lookup |>
    transmute(
      source_column = factor,
      workbook_column = paste0(proposed_name, "\n", instrument, " ", factor_id, "\n", likert_range),
      column_type = "composite"
    ),
  item_membership |>
    transmute(
      source_column = item_col,
      workbook_column = item_header,
      column_type = "assigned_item"
    )
)

participant_scores_internal <- composite_scores |>
  select(participant_id, all_of(composite_cols)) |>
  left_join(item_scores_wide, by = "participant_id") |>
  select(participant_id, all_of(composite_cols), all_of(item_cols)) |>
  mutate(
    base_sample = if_all(
      all_of(c("IMI_MR1", "WSE_MR1", "AIRefl_MR1")),
      ~ !is.na(.x)
    )
  ) |>
  arrange(desc(base_sample), participant_id) |>
  select(-base_sample)

participant_scores_workbook <- participant_scores_internal |>
  rename_with(
    ~ if_else(
      .x %in% workbook_column_map$source_column,
      workbook_column_map$workbook_column[match(.x, workbook_column_map$source_column)],
      .x
    )
  )

participant_source_to_display <- tibble(
  source_column = names(participant_scores_internal),
  display_column = names(participant_scores_workbook),
  col_index = seq_along(participant_scores_workbook)
)

base_sample_order_check <- composite_scores |>
  transmute(
    participant_id,
    base_sample = if_all(
      all_of(c("IMI_MR1", "WSE_MR1", "AIRefl_MR1")),
      ~ !is.na(.x)
    )
  ) |>
  count(base_sample, name = "n_participants")

summary_workbook <- composite_scores |>
  pivot_longer(all_of(composite_cols), names_to = "factor", values_to = "score") |>
  group_by(factor) |>
  summarise(
    n_nonmissing = sum(!is.na(score)),
    mean = mean(score, na.rm = TRUE),
    sd = sd(score, na.rm = TRUE),
    median = median(score, na.rm = TRUE),
    min = min(score, na.rm = TRUE),
    max = max(score, na.rm = TRUE),
    .groups = "drop"
  ) |>
  left_join(
    composite_lookup |>
      select(instrument, factor, factor_id, factor_num, proposed_name, display_label),
    by = "factor"
  ) |>
  arrange(match(instrument, instrument_order), factor_num) |>
  select(instrument, factor, factor_id, factor_num, proposed_name, display_label, everything())

factor_fill_lookup <- tribble(
  ~instrument,        ~factor_num, ~fill,
  "IMI",             1L,          "#1D4ED8",
  "IMI",             2L,          "#3B82F6",
  "IMI",             3L,          "#93C5FD",
  "WritingEfficacy", 1L,          "#B45309",
  "WritingEfficacy", 2L,          "#F59E0B",
  "WritingEfficacy", 3L,          "#FCD34D",
  "AIReflection",    1L,          "#047857",
  "AIReflection",    2L,          "#34D399",
  "BeliefsAboutAI",  1L,          "#6D28D9",
  "BeliefsAboutAI",  2L,          "#A855F7",
  "BeliefsAboutAI",  3L,          "#C084FC"
)

item_fill_lookup <- tibble(
  instrument = instrument_order,
  item_fill = c("#DBEAFE", "#FEF3C7", "#D1FAE5", "#EDE9FE")
)

neutral_unassigned_fill <- "#D9D9D9"
header_fill <- "#F3F4F6"
cell_border_colour <- "#7A7A7A"

composite_color_legend <- composite_workbook_lookup |>
  left_join(factor_fill_lookup, by = c("instrument", "factor_num")) |>
  transmute(
    entry_type = "Composite factor column",
    source_column = factor,
    column_name = paste0(proposed_name, "\n", instrument, " ", factor_id, "\n", likert_range),
    fill_hex = fill,
    instrument,
    factor = factor,
    factor_label = display_label,
    factor_name = proposed_name,
    item_id = NA_integer_,
    item_text = NA_character_,
    scale_note = case_when(
      factor == "Beliefs_ConcernHarms" ~
        "Composite is on the higher concern/harms scale.",
      TRUE ~ "Composite is the row mean of assigned clean items."
    )
  )

item_color_legend <- item_membership |>
  left_join(factor_fill_lookup, by = c("instrument", "factor_num")) |>
  transmute(
    entry_type = "Assigned raw item column",
    source_column = item_col,
    column_name = item_header,
    fill_hex = fill,
    instrument,
    factor,
    factor_label = display_label,
    factor_name = proposed_name,
    item_id,
    item_text,
    scale_note = case_when(
      instrument == "WritingEfficacy" ~
        "Shown on converted (x/25)+1 scale, not original 0-100 slider.",
      factor == "Beliefs_ConcernHarms" ~
        "Shown on higher concern/harms item scale (6 - upstream reverse-scored item), matching the composite orientation.",
      !is.na(reverse_scoring_note) ~
        paste0("Shown on scored item scale used for composite averaging; ", reverse_scoring_note, "."),
      TRUE ~ "Shown on the scored item scale used for composite averaging."
    )
  )

unassigned_color_legend <- if (nrow(unassigned_items) > 0) {
  unassigned_items |>
    mutate(
      source_column = paste0(instrument, "_Q", as.integer(item_id)),
      column_name = str_squish(item_text),
      factor = primary_factor_id
    ) |>
    transmute(
      entry_type = "Unassigned item, not shown on Participant Scores",
      source_column,
      column_name,
      fill_hex = neutral_unassigned_fill,
      instrument,
      factor,
      factor_label = NA_character_,
      factor_name = NA_character_,
      item_id = as.integer(item_id),
      item_text,
      scale_note = paste0("Failed script 17 clean-item rule: ", unassigned_reason)
    )
} else {
  tibble(
    entry_type = character(),
    source_column = character(),
    column_name = character(),
    fill_hex = character(),
    instrument = character(),
    factor = character(),
    factor_label = character(),
    factor_name = character(),
    item_id = integer(),
    item_text = character(),
    scale_note = character()
  )
}

legend_workbook <- bind_rows(
  composite_color_legend,
  item_color_legend,
  unassigned_color_legend
) |>
  arrange(
    match(instrument, instrument_order),
    entry_type != "Composite factor column",
    factor,
    item_id
  )

wb <- openxlsx::createWorkbook()
openxlsx::addWorksheet(wb, "Participant Scores")
openxlsx::addWorksheet(wb, "Legend")
openxlsx::addWorksheet(wb, "Summary")

openxlsx::writeData(
  wb,
  "Participant Scores",
  as.data.frame(t(names(participant_scores_workbook))),
  colNames = FALSE
)
openxlsx::writeData(
  wb,
  "Participant Scores",
  participant_scores_workbook,
  startRow = 2,
  colNames = FALSE
)
openxlsx::writeData(wb, "Legend", legend_workbook)
openxlsx::writeData(wb, "Summary", summary_workbook)

header_style <- openxlsx::createStyle(
  fgFill = header_fill,
  textDecoration = "bold",
  border = "TopBottomLeftRight",
  borderColour = cell_border_colour,
  halign = "center",
  valign = "top",
  wrapText = TRUE
)
participant_id_style <- openxlsx::createStyle(
  fgFill = "#FFFFFF",
  textDecoration = "bold",
  border = "TopBottomLeftRight",
  borderColour = cell_border_colour
)
wrap_top_style <- openxlsx::createStyle(wrapText = TRUE, valign = "top")

openxlsx::addStyle(
  wb,
  "Participant Scores",
  header_style,
  rows = 1,
  cols = seq_along(participant_scores_workbook),
  gridExpand = TRUE,
  stack = TRUE
)

composite_display_cols <- participant_source_to_display |>
  filter(source_column %in% composite_cols) |>
  pull(col_index)

item_display_cols <- participant_source_to_display |>
  filter(source_column %in% item_cols) |>
  pull(col_index)
openxlsx::addStyle(
  wb,
  "Participant Scores",
  participant_id_style,
  rows = 1:(nrow(participant_scores_workbook) + 1),
  cols = 1,
  gridExpand = TRUE,
  stack = TRUE
)

composite_column_styles <- composite_lookup |>
  left_join(factor_fill_lookup, by = c("instrument", "factor_num")) |>
  transmute(source_column = factor, fill_hex = fill) |>
  left_join(participant_source_to_display, by = "source_column") |>
  filter(!is.na(col_index))

item_column_styles <- item_membership |>
  left_join(factor_fill_lookup, by = c("instrument", "factor_num")) |>
  transmute(source_column = item_col, fill_hex = fill) |>
  distinct() |>
  left_join(participant_source_to_display, by = "source_column") |>
  filter(!is.na(col_index))

walk2(composite_column_styles$col_index, composite_column_styles$fill_hex, function(col_i, fill_i) {
  openxlsx::addStyle(
    wb,
    "Participant Scores",
    openxlsx::createStyle(
      fgFill = fill_i,
      border = "TopBottomLeftRight",
      borderColour = cell_border_colour
    ),
    rows = 2:(nrow(participant_scores_workbook) + 1),
    cols = col_i,
    gridExpand = TRUE,
    stack = TRUE
  )
})

walk2(item_column_styles$col_index, item_column_styles$fill_hex, function(col_i, fill_i) {
  openxlsx::addStyle(
    wb,
    "Participant Scores",
    openxlsx::createStyle(
      fgFill = fill_i,
      border = "TopBottomLeftRight",
      borderColour = cell_border_colour
    ),
    rows = 2:(nrow(participant_scores_workbook) + 1),
    cols = col_i,
    gridExpand = TRUE,
    stack = TRUE
  )
})

legend_fill_cols <- match("fill_hex", names(legend_workbook))
if (!is.na(legend_fill_cols) && nrow(legend_workbook) > 0) {
  walk(seq_len(nrow(legend_workbook)), function(row_i) {
    fill_i <- legend_workbook$fill_hex[[row_i]]
    openxlsx::addStyle(
      wb,
      "Legend",
      openxlsx::createStyle(fgFill = fill_i),
      rows = row_i + 1,
      cols = legend_fill_cols,
      gridExpand = TRUE,
      stack = TRUE
    )
  })
}

for (sheet_name in c("Participant Scores", "Legend", "Summary")) {
  sheet_cols <- switch(
    sheet_name,
    "Participant Scores" = seq_along(participant_scores_workbook),
    "Legend" = seq_along(legend_workbook),
    "Summary" = seq_along(summary_workbook)
  )
  openxlsx::addStyle(
    wb,
    sheet_name,
    header_style,
    rows = 1,
    cols = sheet_cols,
    gridExpand = TRUE,
    stack = TRUE
  )
  openxlsx::freezePane(wb, sheet_name, firstRow = TRUE)
  openxlsx::addFilter(wb, sheet_name, row = 1, cols = sheet_cols)
}

openxlsx::setColWidths(wb, "Participant Scores", cols = 1, widths = 18)
openxlsx::setColWidths(
  wb,
  "Participant Scores",
  cols = composite_display_cols,
  widths = 18
)
openxlsx::setColWidths(
  wb,
  "Participant Scores",
  cols = item_display_cols,
  widths = 42
)
openxlsx::setRowHeights(wb, "Participant Scores", rows = 1, heights = 140)

openxlsx::setColWidths(wb, "Legend", cols = 1:ncol(legend_workbook), widths = "auto")
openxlsx::setColWidths(wb, "Legend", cols = match("column_name", names(legend_workbook)), widths = 60)
openxlsx::setColWidths(wb, "Legend", cols = match("item_text", names(legend_workbook)), widths = 70)
openxlsx::setColWidths(wb, "Legend", cols = match("scale_note", names(legend_workbook)), widths = 55)
openxlsx::addStyle(
  wb,
  "Legend",
  wrap_top_style,
  rows = 1:(nrow(legend_workbook) + 1),
  cols = c(
    match("column_name", names(legend_workbook)),
    match("item_text", names(legend_workbook)),
    match("scale_note", names(legend_workbook))
  ),
  gridExpand = TRUE,
  stack = TRUE
)
openxlsx::setColWidths(wb, "Summary", cols = 1:ncol(summary_workbook), widths = "auto")

openxlsx::saveWorkbook(wb, workbook_file, overwrite = TRUE)

workbook_check <- tibble(
  workbook_path = workbook_file,
  file_exists = file.exists(workbook_file),
  file_size_bytes = file.info(workbook_file)$size,
  sheet_names = paste(openxlsx::getSheetNames(workbook_file), collapse = "; "),
  base_sample_rows_first = base_sample_order_check |>
    filter(base_sample) |>
    pull(n_participants),
  additional_rows_after_base = base_sample_order_check |>
    filter(!base_sample) |>
    pull(n_participants),
  google_sheets_note = "Not uploaded from this environment; openxlsx xlsx formatting generally survives Google Sheets import, but verify fills after upload."
)

write_csv(workbook_check, file.path(csv_dir, "Composite_Workbook_Check.csv"))

workbook_participant_readback <- openxlsx::read.xlsx(
  workbook_file,
  sheet = "Participant Scores",
  sep.names = " "
)

expected_workbook_headers <- names(participant_scores_workbook) |>
  str_replace_all("\\n", " ")
base_sample_readback_cols <- expected_workbook_headers[
  match(c("IMI_MR1", "WSE_MR1", "AIRefl_MR1"), names(participant_scores_internal))
]

header_mismatch_count <- sum(names(workbook_participant_readback) != expected_workbook_headers)
participant_id_mismatch_count <- sum(
  workbook_participant_readback$participant_id != participant_scores_workbook$participant_id,
  na.rm = TRUE
)

numeric_mismatch_count <- map_int(2:ncol(participant_scores_workbook), function(col_i) {
  expected <- suppressWarnings(as.numeric(participant_scores_workbook[[col_i]]))
  observed <- suppressWarnings(as.numeric(workbook_participant_readback[[col_i]]))
  both_na <- is.na(expected) & is.na(observed)
  different <- abs(expected - observed) > 1e-10
  sum(!both_na & (is.na(different) | different))
}) |>
  sum()

workbook_audit <- tibble(
  audit_check = c(
    "expected_sheets_present",
    "participant_scores_dimensions_match",
    "participant_scores_headers_match",
    "participant_ids_match",
    "participant_numeric_cells_match",
    "base_sample_rows_are_first_82",
    "additional_rows_are_last_9"
  ),
  pass = c(
    identical(
      openxlsx::getSheetNames(workbook_file),
      c("Participant Scores", "Legend", "Summary")
    ),
    identical(dim(workbook_participant_readback), dim(participant_scores_workbook)),
    header_mismatch_count == 0,
    participant_id_mismatch_count == 0,
    numeric_mismatch_count == 0,
    all(complete.cases(
      workbook_participant_readback[1:82, base_sample_readback_cols]
    )),
    all(!complete.cases(
      workbook_participant_readback[83:nrow(workbook_participant_readback), base_sample_readback_cols]
    ))
  ),
  detail = c(
    paste(openxlsx::getSheetNames(workbook_file), collapse = "; "),
    paste(dim(workbook_participant_readback), collapse = " x "),
    paste0(header_mismatch_count, " header mismatches"),
    paste0(participant_id_mismatch_count, " participant_id mismatches"),
    paste0(numeric_mismatch_count, " numeric cell mismatches"),
    "Rows 1-82 have nonmissing IMI F1, WritingEfficacy F1, and AIReflection F1",
    "Rows 83-91 are the additional Beliefs-only participants"
  )
)

write_csv(workbook_audit, file.path(csv_dir, "Composite_Workbook_Audit.csv"))

if (!all(workbook_audit$pass)) {
  stop(
    paste(
      "Composite workbook audit failed:",
      paste(workbook_audit$audit_check[!workbook_audit$pass], collapse = ", ")
    ),
    call. = FALSE
  )
}

workbook_check |>
  kable(caption = "Composite workbook local open check")
```

# Output Manifest

```{r manifest}
manifest <- tibble(
  output_type = c(
    "cross_composite_correlations",
    "cross_composite_heatmap_matrix",
    "cross_composite_heatmap_png",
    "cross_composite_heatmap_pdf",
    "efa_composite_cross_factor_difference_csv",
    "efa_composite_cross_factor_heatmap_png",
    "efa_composite_cross_factor_heatmap_pdf",
    "composite_order_stratified_correlations",
    "efa_composite_order_effects_long",
    "efa_composite_order_effect_differences",
    "efa_composite_beliefs_order_rho_diff_side_by_side_png",
    "efa_composite_beliefs_order_rho_diff_side_by_side_pdf",
    "art_correlations",
    "art_net_ranked",
    "art_heatmap_png",
    "art_heatmap_pdf",
    "efa_composite_art_difference_csv",
    "efa_composite_art_heatmap_png",
    "efa_composite_art_heatmap_pdf",
    "q17_correlations",
    "q17_heatmap_png",
    "q17_heatmap_pdf",
    "q17_filtered_tool_summary",
    "q17_filtered_retained_tools",
    "q17_filtered_bucket_correlations",
    "efa_composite_q17_filtered_difference_csv",
    "efa_composite_q17_filtered_heatmap_png",
    "efa_composite_q17_filtered_heatmap_pdf",
    "named_model_correlations",
    "named_model_heatmap_png",
    "named_model_heatmap_pdf",
    "all_ranked_correlations",
    "composite_workbook",
    "composite_workbook_check",
    "composite_workbook_audit"
  ),
  path = c(
    file.path(csv_dir, "Composite_Cross_Factor_Correlations_Unique.csv"),
    file.path(csv_dir, "Composite_Cross_Factor_Heatmap_Matrix.csv"),
    file.path(plot_dir, "Composite_Cross_Factor_Heatmap.png"),
    file.path(plot_dir, "Composite_Cross_Factor_Heatmap.pdf"),
    file.path(csv_dir, "EFA_vs_Composite_Cross_Factor_Differences.csv"),
    file.path(plot_dir, "EFA_vs_Composite_Cross_Factor_Heatmap.png"),
    file.path(plot_dir, "EFA_vs_Composite_Cross_Factor_Heatmap.pdf"),
    file.path(csv_dir, "Composite_Factor_Order_Stratified_Correlations.csv"),
    file.path(csv_dir, "EFA_vs_Composite_Order_Effects_Long.csv"),
    file.path(csv_dir, "EFA_vs_Composite_Order_Effect_Differences.csv"),
    file.path(plot_dir, "EFA_vs_Composite_Beliefs_Order_Rho_Diff_SideBySide.png"),
    file.path(plot_dir, "EFA_vs_Composite_Beliefs_Order_Rho_Diff_SideBySide.pdf"),
    file.path(csv_dir, "ART_vs_Composites_Correlations.csv"),
    file.path(csv_dir, "ART_Net_vs_Composites_Ranked.csv"),
    file.path(plot_dir, "ART_vs_Composites_Heatmap.png"),
    file.path(plot_dir, "ART_vs_Composites_Heatmap.pdf"),
    file.path(csv_dir, "EFA_vs_Composite_ART_Differences.csv"),
    file.path(plot_dir, "EFA_vs_Composite_ART_Heatmap.png"),
    file.path(plot_dir, "EFA_vs_Composite_ART_Heatmap.pdf"),
    file.path(csv_dir, "Q17_AI_Use_vs_Composites_Correlations.csv"),
    file.path(plot_dir, "Q17_AI_Use_vs_Composites_Heatmap.png"),
    file.path(plot_dir, "Q17_AI_Use_vs_Composites_Heatmap.pdf"),
    file.path(csv_dir, "Q17_Filtered_Tool_Summary.csv"),
    file.path(csv_dir, "Q17_Filtered_Retained_Tools.csv"),
    file.path(csv_dir, "Q17_Filtered_Bucket_Counts_vs_Factors_EFA_Composite.csv"),
    file.path(csv_dir, "EFA_vs_Composite_Q17_Filtered_Bucket_Count_Differences.csv"),
    file.path(plot_dir, "EFA_vs_Composite_Q17_Filtered_Bucket_Counts_Heatmap.png"),
    file.path(plot_dir, "EFA_vs_Composite_Q17_Filtered_Bucket_Counts_Heatmap.pdf"),
    file.path(csv_dir, "Named_Model_Use_vs_Composites_Correlations.csv"),
    file.path(plot_dir, "Named_Model_Use_vs_Composites_Heatmap.png"),
    file.path(plot_dir, "Named_Model_Use_vs_Composites_Heatmap.pdf"),
    file.path(csv_dir, "Composite_All_Correlations_Ranked.csv"),
    workbook_file,
    file.path(csv_dir, "Composite_Workbook_Check.csv"),
    file.path(csv_dir, "Composite_Workbook_Audit.csv")
  ),
  description = c(
    "Unique Spearman correlations among all unit-weighted composite scores",
    "Full symmetric matrix for the composite x composite heatmap",
    "Heatmap of cross-instrument composite correlations",
    "PDF version of the cross-instrument composite heatmap",
    "Largest factor x factor rho differences between EFA factor scores and simple mean composites",
    "Side-by-side EFA vs composite factor x factor heatmap",
    "PDF version of the side-by-side EFA vs composite factor x factor heatmap",
    "Simple mean composite factor x factor Spearman correlations split by order group with Fisher z-test",
    "Long-format matched EFA vs composite factor x factor order-effect comparison",
    "Wide-format matched EFA vs composite factor x factor order-effect differences",
    "Side-by-side EFA vs composite plot of Traditional-first minus AI-first rho differences for exploratory Beliefs pairs",
    "PDF version of side-by-side exploratory Beliefs order-difference plot",
    "Spearman correlations between ART net, false alarms, real hits and composite scores",
    "ART net correlations ranked by absolute rho",
    "Heatmap of ART metrics vs composite scores",
    "PDF version of the ART vs composite heatmap",
    "Largest ART rho differences between EFA factor scores and simple mean composites",
    "Side-by-side EFA vs composite ART heatmap restricted to ART net, false alarms, and real hits",
    "PDF version of the side-by-side EFA vs composite ART heatmap",
    "Spearman correlations between Q17 AI-use metrics and composite scores",
    "Heatmap of Q17 AI-use metrics vs composite scores",
    "PDF version of the Q17 vs composite heatmap",
    "Tool-level Q17 prevalence and variance summary used for filtered bucket scoring",
    "Tools retained for Q17 filtered bucket-count scoring",
    "Filtered Q17 bucket-count correlations for EFA factor scores and simple mean composites",
    "Largest filtered Q17 bucket-count rho differences between EFA factor scores and simple mean composites",
    "Side-by-side EFA vs composite Q17 filtered bucket-count heatmap",
    "PDF version of the side-by-side EFA vs composite Q17 filtered bucket-count heatmap",
    "Spearman correlations between named-model use and composite scores",
    "Heatmap of named-model use vs composite scores",
    "PDF version of the named-model use vs composite heatmap",
    "Combined ranked table across composite, ART, Q17, and named-model families",
    "Three-tab XLSX workbook with participant scores, color legend, and composite summary",
    "Local check that the XLSX file exists and exposes the expected sheets",
    "Readback audit comparing saved workbook participant scores against generated source values"
  )
)

write_csv(manifest, file.path(csv_dir, "Composite_Correlations_Manifest.csv"))
manifest |>
  kable(caption = "Composite correlations output manifest")
```
