---
title: "18 - Composite Correlations"
format:
  html:
    toc: true
    toc-depth: 3
    embed-resources: true
output-dir: "18_composite_correlations"
execute:
  echo: false
  warning: false
  message: false
editor:
  markdown:
    wrap: 72
---

# Purpose

This companion report re-runs the downstream factor-correlation families
using the unit-weighted composite scores from script `17`, rather than
tenBerge EFA factor scores. It does not refit any EFA models.

```{r setup}
library(tidyverse)
library(knitr)
library(openxlsx)

script_dir <- "18_composite_correlations"
csv_dir <- file.path(script_dir, "csv")
plot_dir <- file.path(script_dir, "plots")
workbook_dir <- "18_composite_workbook"
dir.create(csv_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(plot_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(workbook_dir, recursive = TRUE, showWarnings = FALSE)

composite_scores_file <- file.path("17_composite_scoring", "csv", "Composite_Scores_Wide.csv")
composite_specs_file <- file.path("17_composite_scoring", "csv", "Composite_Specs.csv")
composite_item_membership_file <- file.path("17_composite_scoring", "csv", "Composite_Item_Membership.csv")
unassigned_items_file <- file.path("17_composite_scoring", "csv", "Unassigned_Items.csv")
art_scores_file <- file.path("07_art_vs_all_factors_items", "csv", "ART_Scored.csv")
q17_bucket_file <- file.path("14_q17_deeper_dive", "csv", "Q17_Likert_Buckets_PerParticipant.csv")
named_model_file <- file.path("13_model_use_vs_factors_items", "csv", "Model_Use_Factor_Item_Merged.csv")
workbook_file <- file.path(workbook_dir, "Composite_Workbook.xlsx")

instrument_order <- c("IMI", "WritingEfficacy", "AIReflection", "BeliefsAboutAI")

pal <- c(
  "IMI" = "#4f79b7",
  "WritingEfficacy" = "#c96b3b",
  "AIReflection" = "#5a9367",
  "BeliefsAboutAI" = "#8c6bb1",
  "ART" = "#67717a",
  "Q17" = "#2f7f77",
  "ModelUse" = "#7c6aa3"
)

theme_corr <- function(base_size = 11) {
  theme_minimal(base_size = base_size) +
    theme(
      panel.grid.minor = element_blank(),
      panel.grid.major = element_blank(),
      axis.text.x = element_text(angle = 35, hjust = 1),
      legend.position = "bottom"
    )
}

sig_suffix <- function(p_bh, p_bonf) {
  case_when(
    !is.na(p_bonf) & p_bonf < 0.05 ~ "**",
    !is.na(p_bh) & p_bh < 0.05 ~ "*",
    TRUE ~ ""
  )
}

safe_spearman <- function(df, x, y) {
  d <- df |>
    select(all_of(c(x, y))) |>
    mutate(across(everything(), as.numeric)) |>
    drop_na()

  if (nrow(d) < 5L ||
      dplyr::n_distinct(d[[x]]) < 2L ||
      dplyr::n_distinct(d[[y]]) < 2L) {
    return(tibble(n = nrow(d), rho = NA_real_, p = NA_real_))
  }

  ct <- suppressWarnings(cor.test(d[[x]], d[[y]], method = "spearman", exact = FALSE))
  tibble(n = nrow(d), rho = unname(ct$estimate), p = ct$p.value)
}

run_corr_grid <- function(df, xs, ys, family) {
  crossing(x = xs, y = ys) |>
    mutate(result = map2(x, y, ~ safe_spearman(df, .x, .y))) |>
    unnest(result) |>
    mutate(
      abs_rho = abs(rho),
      p_bh = p.adjust(p, method = "BH"),
      p_bonf = p.adjust(p, method = "bonferroni"),
      survives_bh = !is.na(p_bh) & p_bh < 0.05,
      survives_bonferroni = !is.na(p_bonf) & p_bonf < 0.05,
      family = family
    ) |>
    arrange(p_bh, desc(abs_rho))
}

adjust_within <- function(df, group_col) {
  df |>
    group_by(across(all_of(group_col))) |>
    mutate(
      p_bh = p.adjust(p, method = "BH"),
      p_bonf = p.adjust(p, method = "bonferroni"),
      survives_bh = !is.na(p_bh) & p_bh < 0.05,
      survives_bonferroni = !is.na(p_bonf) & p_bonf < 0.05
    ) |>
    ungroup()
}
```

# Inputs

```{r inputs}
composite_scores <- read_csv(composite_scores_file, show_col_types = FALSE)
composite_lookup <- read_csv(composite_specs_file, show_col_types = FALSE) |>
  select(instrument, factor, factor_id, factor_num, proposed_name, display_label, n_items) |>
  mutate(
    instrument_order = match(instrument, instrument_order),
    factor_num = as.integer(factor_num)
  ) |>
  arrange(instrument_order, factor_num)

composite_cols <- composite_lookup$factor
missing_composites <- setdiff(composite_cols, names(composite_scores))
if (length(missing_composites) > 0) {
  stop(
    paste0("Composite score file is missing columns: ", paste(missing_composites, collapse = ", ")),
    call. = FALSE
  )
}

factor_levels <- composite_lookup$display_label

composite_scores |>
  summarise(n_participants = n(), across(all_of(composite_cols), ~ sum(!is.na(.x)), .names = "{.col}_n")) |>
  pivot_longer(-n_participants, names_to = "factor_n_col", values_to = "n_nonmissing") |>
  slice_head(n = 6) |>
  kable(caption = "Composite score availability preview")
```

# Composite x Composite Correlations

```{r cross-composite-correlations}
factor_pairs <- combn(composite_cols, 2, simplify = FALSE) |>
  map_dfr(~ tibble(factor_x = .x[1], factor_y = .x[2]))

composite_corr_unique <- factor_pairs |>
  mutate(result = map2(factor_x, factor_y, ~ safe_spearman(composite_scores, .x, .y))) |>
  unnest(result) |>
  mutate(
    abs_rho = abs(rho),
    p_bh = p.adjust(p, method = "BH"),
    p_bonf = p.adjust(p, method = "bonferroni"),
    survives_bh = !is.na(p_bh) & p_bh < 0.05,
    survives_bonferroni = !is.na(p_bonf) & p_bonf < 0.05
  ) |>
  left_join(
    composite_lookup |>
      transmute(factor_x = factor, instrument_x = instrument, label_x = display_label),
    by = "factor_x"
  ) |>
  left_join(
    composite_lookup |>
      transmute(factor_y = factor, instrument_y = instrument, label_y = display_label),
    by = "factor_y"
  ) |>
  arrange(p_bh, desc(abs_rho))

composite_corr_diag <- tibble(
  factor_x = composite_cols,
  factor_y = composite_cols,
  rho = 1,
  p = NA_real_,
  n = map_int(composite_cols, ~ sum(!is.na(composite_scores[[.x]]))),
  abs_rho = 1,
  p_bh = NA_real_,
  p_bonf = NA_real_,
  survives_bh = NA,
  survives_bonferroni = NA
) |>
  left_join(
    composite_lookup |>
      transmute(factor_x = factor, instrument_x = instrument, label_x = display_label),
    by = "factor_x"
  ) |>
  left_join(
    composite_lookup |>
      transmute(factor_y = factor, instrument_y = instrument, label_y = display_label),
    by = "factor_y"
  )

composite_corr_heat <- bind_rows(
  composite_corr_unique,
  composite_corr_unique |>
    transmute(
      factor_x = factor_y,
      factor_y = factor_x,
      rho, p, n, abs_rho, p_bh, p_bonf, survives_bh, survives_bonferroni,
      instrument_x = instrument_y,
      instrument_y = instrument_x,
      label_x = label_y,
      label_y = label_x
    ),
  composite_corr_diag
)

write_csv(
  composite_corr_unique,
  file.path(csv_dir, "Composite_Cross_Factor_Correlations_Unique.csv")
)
write_csv(
  composite_corr_heat,
  file.path(csv_dir, "Composite_Cross_Factor_Heatmap_Matrix.csv")
)

composite_corr_unique |>
  mutate(across(c(rho, p, p_bh, p_bonf), ~ round(.x, 4))) |>
  slice_head(n = 20) |>
  kable(caption = "Top composite x composite Spearman correlations")
```

```{r cross-composite-heatmap, fig.width=12, fig.height=9}
cross_heat_df <- composite_corr_heat |>
  mutate(
    label_x = factor(label_x, levels = factor_levels),
    label_y = factor(label_y, levels = rev(factor_levels)),
    cell_label = case_when(
      factor_x == factor_y ~ "",
      is.na(rho) ~ "",
      TRUE ~ paste0(formatC(rho, format = "f", digits = 2), sig_suffix(p_bh, p_bonf))
    )
  )

p_cross_heat <- ggplot(cross_heat_df, aes(x = label_x, y = label_y, fill = rho)) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = cell_label), size = 3) +
  scale_fill_gradient2(
    low = "#b3584b",
    mid = "white",
    high = "#3f6fa8",
    midpoint = 0,
    limits = c(-1, 1),
    name = "rho"
  ) +
  labs(
    title = "Cross-Instrument Composite Correlation Heatmap",
    subtitle = "* BH < .05; ** Bonferroni < .05",
    x = NULL,
    y = NULL
  ) +
  theme_corr(base_size = 10) +
  theme(
    axis.text.y = element_text(size = 8),
    axis.text.x = element_text(size = 8, angle = 35, hjust = 1)
  )

ggsave(
  file.path(plot_dir, "Composite_Cross_Factor_Heatmap.png"),
  p_cross_heat,
  width = 12,
  height = 9,
  units = "in",
  dpi = 300,
  bg = "white"
)
ggsave(
  file.path(plot_dir, "Composite_Cross_Factor_Heatmap.pdf"),
  p_cross_heat,
  width = 12,
  height = 9,
  units = "in",
  bg = "white"
)

p_cross_heat
```

# ART vs Composites

```{r art-correlations}
art_metric_lookup <- tibble(
  art_metric = c(
    "art_total_selected",
    "art_real_hits",
    "art_fake_false_alarms",
    "art_neutral_selected",
    "art_unknown_selected",
    "art_net_real_minus_fake",
    "art_hit_rate",
    "art_false_alarm_rate"
  ),
  art_label = c(
    "Total selected",
    "Real hits",
    "False alarms",
    "Neutral selected",
    "Unknown selected",
    "ART net",
    "Hit rate",
    "False-alarm rate"
  )
)

art_scores <- read_csv(art_scores_file, show_col_types = FALSE)

art_df <- art_scores |>
  select(participant_id, all_of(art_metric_lookup$art_metric)) |>
  inner_join(composite_scores, by = "participant_id")

art_corrs <- run_corr_grid(
  art_df,
  art_metric_lookup$art_metric,
  composite_cols,
  "art_vs_composites"
) |>
  rename(art_metric = x, factor = y) |>
  left_join(art_metric_lookup, by = "art_metric") |>
  left_join(composite_lookup, by = "factor") |>
  arrange(p_bh, desc(abs_rho))

art_ranking_primary <- art_corrs |>
  filter(art_metric == "art_net_real_minus_fake") |>
  arrange(desc(abs_rho), p_bh, p_bonf)

write_csv(art_corrs, file.path(csv_dir, "ART_vs_Composites_Correlations.csv"))
write_csv(art_ranking_primary, file.path(csv_dir, "ART_Net_vs_Composites_Ranked.csv"))

art_corrs |>
  select(art_label, instrument, display_label, n, rho, p, p_bh, p_bonf) |>
  mutate(across(c(rho, p, p_bh, p_bonf), ~ round(.x, 4))) |>
  slice_head(n = 20) |>
  kable(caption = "ART metrics vs composite scores")
```

```{r art-heatmap, fig.width=10, fig.height=7}
art_heat_df <- art_corrs |>
  mutate(
    art_label = factor(art_label, levels = art_metric_lookup$art_label),
    display_label = factor(display_label, levels = rev(factor_levels)),
    cell_label = case_when(
      is.na(rho) ~ "",
      TRUE ~ paste0(formatC(rho, format = "f", digits = 2), sig_suffix(p_bh, p_bonf))
    )
  )

p_art_heat <- ggplot(art_heat_df, aes(x = art_label, y = display_label, fill = rho)) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = cell_label), size = 3) +
  scale_fill_gradient2(
    low = "#c73e3a",
    mid = "#f7f7f7",
    high = "#4f79b7",
    midpoint = 0,
    limits = c(-1, 1),
    name = "Spearman rho"
  ) +
  labs(
    title = "ART vs Composite Scores",
    subtitle = "* BH < .05   ** Bonferroni < .05",
    x = NULL,
    y = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid = element_blank(),
    axis.text.x = element_text(angle = 15, hjust = 1),
    plot.margin = margin(10, 15, 10, 10)
  )

ggsave(
  file.path(plot_dir, "ART_vs_Composites_Heatmap.png"),
  p_art_heat,
  width = 10,
  height = 7,
  units = "in",
  dpi = 300,
  bg = "white"
)
ggsave(
  file.path(plot_dir, "ART_vs_Composites_Heatmap.pdf"),
  p_art_heat,
  width = 10,
  height = 7,
  units = "in",
  bg = "white"
)

p_art_heat
```

# Q17 AI-Use vs Composites

```{r q17-correlations}
q17_bucket <- read_csv(q17_bucket_file, show_col_types = FALSE)

q17_metric_lookup <- tibble(
  q17_metric = c(
    "q17_p_1",
    "q17_p_2",
    "q17_p_3",
    "q17_p_4",
    "q17_p_5",
    "q17_mean_use",
    "q17_n_3",
    "q17_n_4",
    "q17_n_5"
  ),
  q17_label = c(
    "Prop. never heard",
    "Prop. heard, never used",
    "Prop. rarely use",
    "Prop. regularly use",
    "Prop. often use",
    "Mean use score",
    "Count rarely use",
    "Count regularly use",
    "Count often use"
  )
)

q17_df <- q17_bucket |>
  select(participant_id, all_of(q17_metric_lookup$q17_metric)) |>
  inner_join(composite_scores, by = "participant_id")

q17_corrs <- crossing(
  q17_metric = q17_metric_lookup$q17_metric,
  factor = composite_cols
) |>
  mutate(result = map2(factor, q17_metric, ~ safe_spearman(q17_df, .x, .y))) |>
  unnest(result) |>
  mutate(abs_rho = abs(rho), family = "q17_vs_composites") |>
  adjust_within("q17_metric") |>
  left_join(q17_metric_lookup, by = "q17_metric") |>
  left_join(composite_lookup, by = "factor") |>
  arrange(q17_metric, p_bh, desc(abs_rho))

write_csv(q17_corrs, file.path(csv_dir, "Q17_AI_Use_vs_Composites_Correlations.csv"))

q17_corrs |>
  select(q17_label, instrument, display_label, n, rho, p, p_bh, p_bonf) |>
  mutate(across(c(rho, p, p_bh, p_bonf), ~ round(.x, 4))) |>
  slice_head(n = 20) |>
  kable(caption = "Q17 AI-use metrics vs composite scores")
```

```{r q17-heatmap, fig.width=12, fig.height=7.5}
q17_heat_metrics <- c("q17_p_1", "q17_p_2", "q17_p_3", "q17_p_4", "q17_p_5", "q17_mean_use")

q17_heat_df <- q17_corrs |>
  filter(q17_metric %in% q17_heat_metrics) |>
  mutate(
    q17_label = factor(
      q17_label,
      levels = q17_metric_lookup |>
        filter(q17_metric %in% q17_heat_metrics) |>
        pull(q17_label)
    ),
    display_label = factor(display_label, levels = factor_levels),
    cell_label = case_when(
      is.na(rho) ~ "",
      TRUE ~ paste0(formatC(rho, format = "f", digits = 2), sig_suffix(p_bh, p_bonf))
    )
  )

p_q17_heat <- ggplot(q17_heat_df, aes(x = q17_label, y = display_label, fill = rho)) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = cell_label), size = 3) +
  scale_fill_gradient2(
    low = "#c73e3a",
    mid = "#f7f7f7",
    high = "#4f79b7",
    midpoint = 0,
    limits = c(-1, 1),
    name = "Spearman rho"
  ) +
  labs(
    title = "Q17 Familiarity Buckets vs Composite Scores",
    subtitle = "* BH < .05   ** Bonferroni < .05  |  BH corrected within each Q17 metric",
    x = NULL,
    y = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid = element_blank(),
    axis.text.x = element_text(angle = 20, hjust = 1),
    plot.margin = margin(10, 15, 10, 10)
  )

ggsave(
  file.path(plot_dir, "Q17_AI_Use_vs_Composites_Heatmap.png"),
  p_q17_heat,
  width = 12,
  height = 7.5,
  units = "in",
  dpi = 300,
  bg = "white"
)
ggsave(
  file.path(plot_dir, "Q17_AI_Use_vs_Composites_Heatmap.pdf"),
  p_q17_heat,
  width = 12,
  height = 7.5,
  units = "in",
  bg = "white"
)

p_q17_heat
```

# Named Model Use vs Composites

```{r named-model-correlations}
model_lookup <- tibble(
  model_label = c("ChatGPT", "Claude", "Gemini", "Copilot")
)

model_scores <- read_csv(named_model_file, show_col_types = FALSE) |>
  select(participant_id, all_of(model_lookup$model_label))

model_df <- model_scores |>
  inner_join(composite_scores, by = "participant_id")

model_corrs <- crossing(
  model_label = model_lookup$model_label,
  factor = composite_cols
) |>
  mutate(result = map2(model_label, factor, ~ safe_spearman(model_df, .x, .y))) |>
  unnest(result) |>
  mutate(abs_rho = abs(rho), family = "named_model_use_vs_composites") |>
  adjust_within("model_label") |>
  left_join(composite_lookup, by = "factor") |>
  arrange(model_label, p_bh, desc(abs_rho))

write_csv(model_corrs, file.path(csv_dir, "Named_Model_Use_vs_Composites_Correlations.csv"))

model_corrs |>
  select(model_label, instrument, display_label, n, rho, p, p_bh, p_bonf) |>
  mutate(across(c(rho, p, p_bh, p_bonf), ~ round(.x, 4))) |>
  kable(caption = "Named model use vs composite scores")
```

```{r named-model-heatmap, fig.width=10, fig.height=6.5}
model_heat_df <- model_corrs |>
  mutate(
    model_label = factor(model_label, levels = model_lookup$model_label),
    display_label = factor(display_label, levels = factor_levels),
    cell_label = case_when(
      is.na(rho) ~ "",
      TRUE ~ paste0(formatC(rho, format = "f", digits = 2), sig_suffix(p_bh, p_bonf))
    )
  )

p_model_heat <- ggplot(model_heat_df, aes(x = model_label, y = display_label, fill = rho)) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = cell_label), size = 3) +
  scale_fill_gradient2(
    low = "#c73e3a",
    mid = "#f7f7f7",
    high = "#4f79b7",
    midpoint = 0,
    limits = c(-1, 1),
    name = "Spearman rho"
  ) +
  labs(
    title = "Named Model Use vs Composite Scores",
    subtitle = "* BH < .05   ** Bonferroni < .05  |  BH corrected within each model",
    x = "Primary AI model use score predictor",
    y = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid = element_blank(),
    axis.text.x = element_text(angle = 20, hjust = 1),
    plot.margin = margin(10, 15, 10, 10)
  )

ggsave(
  file.path(plot_dir, "Named_Model_Use_vs_Composites_Heatmap.png"),
  p_model_heat,
  width = 10,
  height = 6.5,
  units = "in",
  dpi = 300,
  bg = "white"
)
ggsave(
  file.path(plot_dir, "Named_Model_Use_vs_Composites_Heatmap.pdf"),
  p_model_heat,
  width = 10,
  height = 6.5,
  units = "in",
  bg = "white"
)

p_model_heat
```

# Combined Ranked Output

```{r combined-ranked}
all_ranked_correlations <- bind_rows(
  composite_corr_unique |>
    transmute(
      source = "composite_x_composite",
      predictor = label_x,
      outcome = label_y,
      n,
      rho,
      p,
      p_bh,
      p_bonf,
      abs_rho
    ),
  art_corrs |>
    transmute(
      source = "art_vs_composites",
      predictor = art_label,
      outcome = display_label,
      n,
      rho,
      p,
      p_bh,
      p_bonf,
      abs_rho
    ),
  q17_corrs |>
    transmute(
      source = "q17_vs_composites",
      predictor = q17_label,
      outcome = display_label,
      n,
      rho,
      p,
      p_bh,
      p_bonf,
      abs_rho
    ),
  model_corrs |>
    transmute(
      source = "named_model_use_vs_composites",
      predictor = model_label,
      outcome = display_label,
      n,
      rho,
      p,
      p_bh,
      p_bonf,
      abs_rho
    )
) |>
  arrange(p_bh, desc(abs_rho))

write_csv(
  all_ranked_correlations,
  file.path(csv_dir, "Composite_All_Correlations_Ranked.csv")
)
```

# Composite Workbook

```{r composite-workbook}
item_membership <- read_csv(composite_item_membership_file, show_col_types = FALSE) |>
  mutate(
    instrument_order = match(instrument, instrument_order),
    factor_num = as.integer(factor_num),
    item_id = as.integer(item_id),
    item_col = paste0(instrument, "_Q", item_id),
    item_header_base = str_squish(item_text),
    item_reference = paste0(instrument, " Q", item_id),
    item_header = paste0(item_header_base, "\n", item_reference)
  ) |>
  arrange(instrument_order, factor_num, item_id)

unassigned_items <- read_csv(unassigned_items_file, show_col_types = FALSE)

read_clean_item_scores <- function(instrument_name, path, item_col_name) {
  read_csv(path, show_col_types = FALSE) |>
    transmute(
      instrument = instrument_name,
      participant_id,
      item_id = as.integer(.data[[item_col_name]]),
      score = as.numeric(score)
    )
}

item_scores_long <- bind_rows(
  read_clean_item_scores(
    "IMI",
    file.path("01_audit_cleaning", "cleaned", "IMI_cleaned.csv"),
    "item_code"
  ),
  read_clean_item_scores(
    "WritingEfficacy",
    file.path("01_audit_cleaning", "cleaned", "WritingEfficacy_cleaned.csv"),
    "item_code"
  ) |>
    mutate(score = (score / 25) + 1),
  read_clean_item_scores(
    "AIReflection",
    file.path("01_audit_cleaning", "cleaned", "AI_Reflection_cleaned.csv"),
    "item_num"
  ),
  read_clean_item_scores(
    "BeliefsAboutAI",
    file.path("02_efa_exports", "efa", "BeliefsAboutAI_EFA_Primary.csv"),
    "item_num"
  )
)

assigned_item_scores <- item_scores_long |>
  inner_join(
    item_membership |>
      select(instrument, item_id, factor, factor_id, factor_num, item_col),
    by = c("instrument", "item_id")
  ) |>
  mutate(
    score = if_else(factor == "Beliefs_ConcernHarms", 6 - score, score)
  )

item_cols <- item_membership$item_col

item_scores_wide <- assigned_item_scores |>
  select(participant_id, item_col, score) |>
  distinct() |>
  pivot_wider(names_from = item_col, values_from = score)

format_likert_range <- function(item_ids) {
  ids <- sort(unique(as.integer(item_ids)))
  if (length(ids) > 1L && all(diff(ids) == 1L)) {
    return(paste0("Likerts Q", min(ids), "-Q", max(ids)))
  }
  paste0("Likerts ", paste0("Q", ids, collapse = ", "))
}

factor_item_ranges <- item_membership |>
  group_by(factor) |>
  summarise(
    likert_range = format_likert_range(item_id),
    .groups = "drop"
  )

composite_workbook_lookup <- composite_lookup |>
  left_join(factor_item_ranges, by = "factor")

workbook_column_map <- bind_rows(
  composite_workbook_lookup |>
    transmute(
      source_column = factor,
      workbook_column = paste0(proposed_name, "\n", instrument, " ", factor_id, "\n", likert_range),
      column_type = "composite"
    ),
  item_membership |>
    transmute(
      source_column = item_col,
      workbook_column = item_header,
      column_type = "assigned_item"
    )
)

participant_scores_internal <- composite_scores |>
  select(participant_id, all_of(composite_cols)) |>
  left_join(item_scores_wide, by = "participant_id") |>
  select(participant_id, all_of(composite_cols), all_of(item_cols)) |>
  mutate(
    base_sample = if_all(
      all_of(c("IMI_MR1", "WSE_MR1", "AIRefl_MR1")),
      ~ !is.na(.x)
    )
  ) |>
  arrange(desc(base_sample), participant_id) |>
  select(-base_sample)

participant_scores_workbook <- participant_scores_internal |>
  rename_with(
    ~ if_else(
      .x %in% workbook_column_map$source_column,
      workbook_column_map$workbook_column[match(.x, workbook_column_map$source_column)],
      .x
    )
  )

participant_source_to_display <- tibble(
  source_column = names(participant_scores_internal),
  display_column = names(participant_scores_workbook),
  col_index = seq_along(participant_scores_workbook)
)

base_sample_order_check <- composite_scores |>
  transmute(
    participant_id,
    base_sample = if_all(
      all_of(c("IMI_MR1", "WSE_MR1", "AIRefl_MR1")),
      ~ !is.na(.x)
    )
  ) |>
  count(base_sample, name = "n_participants")

summary_workbook <- composite_scores |>
  pivot_longer(all_of(composite_cols), names_to = "factor", values_to = "score") |>
  group_by(factor) |>
  summarise(
    n_nonmissing = sum(!is.na(score)),
    mean = mean(score, na.rm = TRUE),
    sd = sd(score, na.rm = TRUE),
    median = median(score, na.rm = TRUE),
    min = min(score, na.rm = TRUE),
    max = max(score, na.rm = TRUE),
    .groups = "drop"
  ) |>
  left_join(
    composite_lookup |>
      select(instrument, factor, factor_id, factor_num, proposed_name, display_label),
    by = "factor"
  ) |>
  arrange(match(instrument, instrument_order), factor_num) |>
  select(instrument, factor, factor_id, factor_num, proposed_name, display_label, everything())

factor_fill_lookup <- tribble(
  ~instrument,        ~factor_num, ~fill,
  "IMI",             1L,          "#1D4ED8",
  "IMI",             2L,          "#3B82F6",
  "IMI",             3L,          "#93C5FD",
  "WritingEfficacy", 1L,          "#B45309",
  "WritingEfficacy", 2L,          "#F59E0B",
  "WritingEfficacy", 3L,          "#FCD34D",
  "AIReflection",    1L,          "#047857",
  "AIReflection",    2L,          "#34D399",
  "BeliefsAboutAI",  1L,          "#6D28D9",
  "BeliefsAboutAI",  2L,          "#A855F7",
  "BeliefsAboutAI",  3L,          "#C084FC"
)

item_fill_lookup <- tibble(
  instrument = instrument_order,
  item_fill = c("#DBEAFE", "#FEF3C7", "#D1FAE5", "#EDE9FE")
)

neutral_unassigned_fill <- "#D9D9D9"
header_fill <- "#F3F4F6"
cell_border_colour <- "#7A7A7A"

composite_color_legend <- composite_workbook_lookup |>
  left_join(factor_fill_lookup, by = c("instrument", "factor_num")) |>
  transmute(
    entry_type = "Composite factor column",
    source_column = factor,
    column_name = paste0(proposed_name, "\n", instrument, " ", factor_id, "\n", likert_range),
    fill_hex = fill,
    instrument,
    factor = factor,
    factor_label = display_label,
    factor_name = proposed_name,
    item_id = NA_integer_,
    item_text = NA_character_,
    scale_note = case_when(
      factor == "Beliefs_ConcernHarms" ~
        "Composite is on the higher concern/harms scale.",
      TRUE ~ "Composite is the row mean of assigned clean items."
    )
  )

item_color_legend <- item_membership |>
  left_join(factor_fill_lookup, by = c("instrument", "factor_num")) |>
  transmute(
    entry_type = "Assigned raw item column",
    source_column = item_col,
    column_name = item_header,
    fill_hex = fill,
    instrument,
    factor,
    factor_label = display_label,
    factor_name = proposed_name,
    item_id,
    item_text,
    scale_note = case_when(
      instrument == "WritingEfficacy" ~
        "Shown on converted (x/25)+1 scale, not original 0-100 slider.",
      factor == "Beliefs_ConcernHarms" ~
        "Shown on higher concern/harms item scale (6 - upstream reverse-scored item), matching the composite orientation.",
      TRUE ~ "Shown on the scored item scale used for composite averaging."
    )
  )

unassigned_color_legend <- if (nrow(unassigned_items) > 0) {
  unassigned_items |>
    mutate(
      source_column = paste0(instrument, "_Q", as.integer(item_id)),
      column_name = str_squish(item_text),
      factor = primary_factor_id
    ) |>
    transmute(
      entry_type = "Unassigned item, not shown on Participant Scores",
      source_column,
      column_name,
      fill_hex = neutral_unassigned_fill,
      instrument,
      factor,
      factor_label = NA_character_,
      factor_name = NA_character_,
      item_id = as.integer(item_id),
      item_text,
      scale_note = paste0("Failed script 17 clean-item rule: ", unassigned_reason)
    )
} else {
  tibble(
    entry_type = character(),
    source_column = character(),
    column_name = character(),
    fill_hex = character(),
    instrument = character(),
    factor = character(),
    factor_label = character(),
    factor_name = character(),
    item_id = integer(),
    item_text = character(),
    scale_note = character()
  )
}

legend_workbook <- bind_rows(
  composite_color_legend,
  item_color_legend,
  unassigned_color_legend
) |>
  arrange(
    match(instrument, instrument_order),
    entry_type != "Composite factor column",
    factor,
    item_id
  )

wb <- openxlsx::createWorkbook()
openxlsx::addWorksheet(wb, "Participant Scores")
openxlsx::addWorksheet(wb, "Legend")
openxlsx::addWorksheet(wb, "Summary")

openxlsx::writeData(
  wb,
  "Participant Scores",
  as.data.frame(t(names(participant_scores_workbook))),
  colNames = FALSE
)
openxlsx::writeData(
  wb,
  "Participant Scores",
  participant_scores_workbook,
  startRow = 2,
  colNames = FALSE
)
openxlsx::writeData(wb, "Legend", legend_workbook)
openxlsx::writeData(wb, "Summary", summary_workbook)

header_style <- openxlsx::createStyle(
  fgFill = header_fill,
  textDecoration = "bold",
  border = "TopBottomLeftRight",
  borderColour = cell_border_colour,
  halign = "center",
  valign = "top",
  wrapText = TRUE
)
participant_id_style <- openxlsx::createStyle(
  fgFill = "#FFFFFF",
  textDecoration = "bold",
  border = "TopBottomLeftRight",
  borderColour = cell_border_colour
)
wrap_top_style <- openxlsx::createStyle(wrapText = TRUE, valign = "top")

openxlsx::addStyle(
  wb,
  "Participant Scores",
  header_style,
  rows = 1,
  cols = seq_along(participant_scores_workbook),
  gridExpand = TRUE,
  stack = TRUE
)

composite_display_cols <- participant_source_to_display |>
  filter(source_column %in% composite_cols) |>
  pull(col_index)

item_display_cols <- participant_source_to_display |>
  filter(source_column %in% item_cols) |>
  pull(col_index)
openxlsx::addStyle(
  wb,
  "Participant Scores",
  participant_id_style,
  rows = 1:(nrow(participant_scores_workbook) + 1),
  cols = 1,
  gridExpand = TRUE,
  stack = TRUE
)

composite_column_styles <- composite_lookup |>
  left_join(factor_fill_lookup, by = c("instrument", "factor_num")) |>
  transmute(source_column = factor, fill_hex = fill) |>
  left_join(participant_source_to_display, by = "source_column") |>
  filter(!is.na(col_index))

item_column_styles <- item_membership |>
  left_join(factor_fill_lookup, by = c("instrument", "factor_num")) |>
  transmute(source_column = item_col, fill_hex = fill) |>
  distinct() |>
  left_join(participant_source_to_display, by = "source_column") |>
  filter(!is.na(col_index))

walk2(composite_column_styles$col_index, composite_column_styles$fill_hex, function(col_i, fill_i) {
  openxlsx::addStyle(
    wb,
    "Participant Scores",
    openxlsx::createStyle(
      fgFill = fill_i,
      border = "TopBottomLeftRight",
      borderColour = cell_border_colour
    ),
    rows = 2:(nrow(participant_scores_workbook) + 1),
    cols = col_i,
    gridExpand = TRUE,
    stack = TRUE
  )
})

walk2(item_column_styles$col_index, item_column_styles$fill_hex, function(col_i, fill_i) {
  openxlsx::addStyle(
    wb,
    "Participant Scores",
    openxlsx::createStyle(
      fgFill = fill_i,
      border = "TopBottomLeftRight",
      borderColour = cell_border_colour
    ),
    rows = 2:(nrow(participant_scores_workbook) + 1),
    cols = col_i,
    gridExpand = TRUE,
    stack = TRUE
  )
})

legend_fill_cols <- match("fill_hex", names(legend_workbook))
if (!is.na(legend_fill_cols) && nrow(legend_workbook) > 0) {
  walk(seq_len(nrow(legend_workbook)), function(row_i) {
    fill_i <- legend_workbook$fill_hex[[row_i]]
    openxlsx::addStyle(
      wb,
      "Legend",
      openxlsx::createStyle(fgFill = fill_i),
      rows = row_i + 1,
      cols = legend_fill_cols,
      gridExpand = TRUE,
      stack = TRUE
    )
  })
}

for (sheet_name in c("Participant Scores", "Legend", "Summary")) {
  sheet_cols <- switch(
    sheet_name,
    "Participant Scores" = seq_along(participant_scores_workbook),
    "Legend" = seq_along(legend_workbook),
    "Summary" = seq_along(summary_workbook)
  )
  openxlsx::addStyle(
    wb,
    sheet_name,
    header_style,
    rows = 1,
    cols = sheet_cols,
    gridExpand = TRUE,
    stack = TRUE
  )
  openxlsx::freezePane(wb, sheet_name, firstRow = TRUE)
  openxlsx::addFilter(wb, sheet_name, row = 1, cols = sheet_cols)
}

openxlsx::setColWidths(wb, "Participant Scores", cols = 1, widths = 18)
openxlsx::setColWidths(
  wb,
  "Participant Scores",
  cols = composite_display_cols,
  widths = 18
)
openxlsx::setColWidths(
  wb,
  "Participant Scores",
  cols = item_display_cols,
  widths = 42
)
openxlsx::setRowHeights(wb, "Participant Scores", rows = 1, heights = 140)

openxlsx::setColWidths(wb, "Legend", cols = 1:ncol(legend_workbook), widths = "auto")
openxlsx::setColWidths(wb, "Legend", cols = match("column_name", names(legend_workbook)), widths = 60)
openxlsx::setColWidths(wb, "Legend", cols = match("item_text", names(legend_workbook)), widths = 70)
openxlsx::setColWidths(wb, "Legend", cols = match("scale_note", names(legend_workbook)), widths = 55)
openxlsx::addStyle(
  wb,
  "Legend",
  wrap_top_style,
  rows = 1:(nrow(legend_workbook) + 1),
  cols = c(
    match("column_name", names(legend_workbook)),
    match("item_text", names(legend_workbook)),
    match("scale_note", names(legend_workbook))
  ),
  gridExpand = TRUE,
  stack = TRUE
)
openxlsx::setColWidths(wb, "Summary", cols = 1:ncol(summary_workbook), widths = "auto")

openxlsx::saveWorkbook(wb, workbook_file, overwrite = TRUE)

workbook_check <- tibble(
  workbook_path = workbook_file,
  file_exists = file.exists(workbook_file),
  file_size_bytes = file.info(workbook_file)$size,
  sheet_names = paste(openxlsx::getSheetNames(workbook_file), collapse = "; "),
  base_sample_rows_first = base_sample_order_check |>
    filter(base_sample) |>
    pull(n_participants),
  additional_rows_after_base = base_sample_order_check |>
    filter(!base_sample) |>
    pull(n_participants),
  google_sheets_note = "Not uploaded from this environment; openxlsx xlsx formatting generally survives Google Sheets import, but verify fills after upload."
)

write_csv(workbook_check, file.path(csv_dir, "Composite_Workbook_Check.csv"))

workbook_participant_readback <- openxlsx::read.xlsx(
  workbook_file,
  sheet = "Participant Scores",
  sep.names = " "
)

expected_workbook_headers <- names(participant_scores_workbook) |>
  str_replace_all("\\n", " ")
base_sample_readback_cols <- expected_workbook_headers[
  match(c("IMI_MR1", "WSE_MR1", "AIRefl_MR1"), names(participant_scores_internal))
]

header_mismatch_count <- sum(names(workbook_participant_readback) != expected_workbook_headers)
participant_id_mismatch_count <- sum(
  workbook_participant_readback$participant_id != participant_scores_workbook$participant_id,
  na.rm = TRUE
)

numeric_mismatch_count <- map_int(2:ncol(participant_scores_workbook), function(col_i) {
  expected <- suppressWarnings(as.numeric(participant_scores_workbook[[col_i]]))
  observed <- suppressWarnings(as.numeric(workbook_participant_readback[[col_i]]))
  both_na <- is.na(expected) & is.na(observed)
  different <- abs(expected - observed) > 1e-10
  sum(!both_na & (is.na(different) | different))
}) |>
  sum()

workbook_audit <- tibble(
  audit_check = c(
    "expected_sheets_present",
    "participant_scores_dimensions_match",
    "participant_scores_headers_match",
    "participant_ids_match",
    "participant_numeric_cells_match",
    "base_sample_rows_are_first_82",
    "additional_rows_are_last_9"
  ),
  pass = c(
    identical(
      openxlsx::getSheetNames(workbook_file),
      c("Participant Scores", "Legend", "Summary")
    ),
    identical(dim(workbook_participant_readback), dim(participant_scores_workbook)),
    header_mismatch_count == 0,
    participant_id_mismatch_count == 0,
    numeric_mismatch_count == 0,
    all(complete.cases(
      workbook_participant_readback[1:82, base_sample_readback_cols]
    )),
    all(!complete.cases(
      workbook_participant_readback[83:nrow(workbook_participant_readback), base_sample_readback_cols]
    ))
  ),
  detail = c(
    paste(openxlsx::getSheetNames(workbook_file), collapse = "; "),
    paste(dim(workbook_participant_readback), collapse = " x "),
    paste0(header_mismatch_count, " header mismatches"),
    paste0(participant_id_mismatch_count, " participant_id mismatches"),
    paste0(numeric_mismatch_count, " numeric cell mismatches"),
    "Rows 1-82 have nonmissing IMI F1, WritingEfficacy F1, and AIReflection F1",
    "Rows 83-91 are the additional Beliefs-only participants"
  )
)

write_csv(workbook_audit, file.path(csv_dir, "Composite_Workbook_Audit.csv"))

if (!all(workbook_audit$pass)) {
  stop(
    paste(
      "Composite workbook audit failed:",
      paste(workbook_audit$audit_check[!workbook_audit$pass], collapse = ", ")
    ),
    call. = FALSE
  )
}

workbook_check |>
  kable(caption = "Composite workbook local open check")
```

# Output Manifest

```{r manifest}
manifest <- tibble(
  output_type = c(
    "cross_composite_correlations",
    "cross_composite_heatmap_matrix",
    "cross_composite_heatmap_png",
    "cross_composite_heatmap_pdf",
    "art_correlations",
    "art_net_ranked",
    "art_heatmap_png",
    "art_heatmap_pdf",
    "q17_correlations",
    "q17_heatmap_png",
    "q17_heatmap_pdf",
    "named_model_correlations",
    "named_model_heatmap_png",
    "named_model_heatmap_pdf",
    "all_ranked_correlations",
    "composite_workbook",
    "composite_workbook_check",
    "composite_workbook_audit"
  ),
  path = c(
    file.path(csv_dir, "Composite_Cross_Factor_Correlations_Unique.csv"),
    file.path(csv_dir, "Composite_Cross_Factor_Heatmap_Matrix.csv"),
    file.path(plot_dir, "Composite_Cross_Factor_Heatmap.png"),
    file.path(plot_dir, "Composite_Cross_Factor_Heatmap.pdf"),
    file.path(csv_dir, "ART_vs_Composites_Correlations.csv"),
    file.path(csv_dir, "ART_Net_vs_Composites_Ranked.csv"),
    file.path(plot_dir, "ART_vs_Composites_Heatmap.png"),
    file.path(plot_dir, "ART_vs_Composites_Heatmap.pdf"),
    file.path(csv_dir, "Q17_AI_Use_vs_Composites_Correlations.csv"),
    file.path(plot_dir, "Q17_AI_Use_vs_Composites_Heatmap.png"),
    file.path(plot_dir, "Q17_AI_Use_vs_Composites_Heatmap.pdf"),
    file.path(csv_dir, "Named_Model_Use_vs_Composites_Correlations.csv"),
    file.path(plot_dir, "Named_Model_Use_vs_Composites_Heatmap.png"),
    file.path(plot_dir, "Named_Model_Use_vs_Composites_Heatmap.pdf"),
    file.path(csv_dir, "Composite_All_Correlations_Ranked.csv"),
    workbook_file,
    file.path(csv_dir, "Composite_Workbook_Check.csv"),
    file.path(csv_dir, "Composite_Workbook_Audit.csv")
  ),
  description = c(
    "Unique Spearman correlations among all unit-weighted composite scores",
    "Full symmetric matrix for the composite x composite heatmap",
    "Heatmap of cross-instrument composite correlations",
    "PDF version of the cross-instrument composite heatmap",
    "Spearman correlations between ART metrics and composite scores",
    "ART net correlations ranked by absolute rho",
    "Heatmap of ART metrics vs composite scores",
    "PDF version of the ART vs composite heatmap",
    "Spearman correlations between Q17 AI-use metrics and composite scores",
    "Heatmap of Q17 AI-use metrics vs composite scores",
    "PDF version of the Q17 vs composite heatmap",
    "Spearman correlations between named-model use and composite scores",
    "Heatmap of named-model use vs composite scores",
    "PDF version of the named-model use vs composite heatmap",
    "Combined ranked table across composite, ART, Q17, and named-model families",
    "Three-tab XLSX workbook with participant scores, color legend, and composite summary",
    "Local check that the XLSX file exists and exposes the expected sheets",
    "Readback audit comparing saved workbook participant scores against generated source values"
  )
)

write_csv(manifest, file.path(csv_dir, "Composite_Correlations_Manifest.csv"))
manifest |>
  kable(caption = "Composite correlations output manifest")
```
