---
title: "Exploratory BeliefsAboutAI 6-22 Factor Correlations"
format:
  html:
    toc: true
    toc-depth: 3
    embed-resources: true
output-dir: "exploratory_beliefs_6_22"
editor: visual
---

# Purpose

This side report tests an exploratory three-factor `BeliefsAboutAI` scoring path using items `6-22`.
It does not modify the numbered production pipeline. The current README describes `BeliefsAboutAI`
as item-level in the locked workflow because the full 22-item battery failed the factorability gate.
Here, the goal is narrower: test whether the theoretically coherent `6-22` subset yields interpretable
factor-level correlations with the same outcome families used by the main scripts.

The most valid plots to recreate from the README pipeline are factor-level plots:

- script `06`: cross-instrument factor heatmap
- script `07`: ART vs factor scores heatmap
- script `14`/`15`: Q17 AI-use breadth/bucket vs factor scores heatmap
- script `12`: named model use vs factor scores heatmap

```{r setup}
#| message: false
#| warning: false

library(tidyverse)
library(psych)
library(glue)
library(knitr)

source("scoring_helpers.R")

set.seed(42L)

script_dir <- "exploratory_beliefs_6_22"
csv_dir <- file.path(script_dir, "csv")
plot_dir <- file.path(script_dir, "plots")
dir.create(csv_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(plot_dir, recursive = TRUE, showWarnings = FALSE)

factor_score_method <- "tenBerge"

pal <- c(
  "IMI" = "#4f79b7",
  "WritingEfficacy" = "#c96b3b",
  "AIReflection" = "#5a9367",
  "BeliefsAboutAI" = "#8c6bb1",
  "ART" = "#67717a",
  "Q17" = "#2f7f77",
  "ModelUse" = "#7c6aa3"
)

theme_corr <- function(base_size = 11) {
  theme_minimal(base_size = base_size) +
    theme(
      panel.grid.minor = element_blank(),
      panel.grid.major = element_blank(),
      axis.text.x = element_text(angle = 35, hjust = 1),
      legend.position = "bottom"
    )
}

safe_spearman <- function(df, x, y) {
  d <- df |>
    select(all_of(c(x, y))) |>
    mutate(across(everything(), as.numeric)) |>
    drop_na()

  if (nrow(d) < 5 || sd(d[[x]]) == 0 || sd(d[[y]]) == 0) {
    return(tibble(n = nrow(d), rho = NA_real_, p = NA_real_))
  }

  ct <- suppressWarnings(cor.test(d[[x]], d[[y]], method = "spearman", exact = FALSE))
  tibble(n = nrow(d), rho = unname(ct$estimate), p = ct$p.value)
}

run_corr_grid <- function(df, xs, ys, family) {
  crossing(x = xs, y = ys) |>
    mutate(result = map2(x, y, ~ safe_spearman(df, .x, .y))) |>
    unnest(result) |>
    mutate(
      abs_rho = abs(rho),
      p_bh = p.adjust(p, method = "BH"),
      p_bonf = p.adjust(p, method = "bonferroni"),
      survives_bh = p_bh < 0.05,
      survives_bonferroni = p_bonf < 0.05,
      family = family
    ) |>
    arrange(p_bh, desc(abs_rho))
}

format_p <- function(x) {
  case_when(
    is.na(x) ~ "",
    x < .001 ~ "<.001",
    TRUE ~ formatC(x, format = "f", digits = 3)
  )
}

sig_suffix <- function(p_bh, p_bonf) {
  case_when(
    !is.na(p_bonf) & p_bonf < .05 ~ "**",
    !is.na(p_bh) & p_bh < .05 ~ "*",
    TRUE ~ ""
  )
}
```

# Build Beliefs 6-22 Factors

```{r beliefs-factor-scores}
beliefs_long <- read_csv(
  file.path("02_efa_exports", "efa", "BeliefsAboutAI_EFA_Primary.csv"),
  show_col_types = FALSE
) |>
  mutate(score = as.numeric(score), item_id = as.integer(item_num))

beliefs_item_text <- beliefs_long |>
  distinct(item_id, item_text)

beliefs_wide <- beliefs_long |>
  filter(item_id %in% 6:22) |>
  select(participant_id, item_id, score) |>
  mutate(item_id = as.character(item_id)) |>
  pivot_wider(names_from = item_id, values_from = score) |>
  arrange(participant_id)

beliefs_matrix <- beliefs_wide |>
  select(-participant_id) |>
  mutate(across(everything(), as.integer)) |>
  as.data.frame()

beliefs_poly <- compute_polychoric_safe(beliefs_matrix)

beliefs_fa <- suppressWarnings(
  psych::fa(
    r = beliefs_poly$rho,
    nfactors = 3,
    n.obs = nrow(beliefs_matrix),
    fm = "minres",
    rotate = "oblimin"
  )
)

beliefs_factor_order <- factor_order_by_variance(
  beliefs_fa$loadings,
  context_label = "Beliefs 6-22 factor ordering"
)

beliefs_loadings_ordered <- unclass(beliefs_fa$loadings)[, beliefs_factor_order, drop = FALSE]
colnames(beliefs_loadings_ordered) <- paste0("MR", seq_len(3))

beliefs_fa_ordered <- beliefs_fa
beliefs_fa_ordered$loadings <- beliefs_loadings_ordered
class(beliefs_fa_ordered$loadings) <- c("loadings")

beliefs_scores_raw <- psych::factor.scores(
  x = as.matrix(beliefs_matrix),
  f = beliefs_fa_ordered,
  rho = beliefs_poly$rho,
  method = factor_score_method
)

beliefs_factor_scores <- bind_scores_with_ids(
  participant_ids = beliefs_wide$participant_id,
  score_matrix = beliefs_scores_raw$scores,
  context_label = "Beliefs 6-22 factor scores"
) |>
  rename(
    Beliefs_UtilityComfort = MR1,
    Beliefs_AdoptionOrientation = MR2,
    Beliefs_LowConcern = MR3
  ) |>
  # Items 17-20 were already reverse-scored upstream. This flip makes positive
  # values mean stronger concern/harms endorsement for interpretation.
  mutate(Beliefs_ConcernHarms = -Beliefs_LowConcern) |>
  select(
    participant_id,
    Beliefs_UtilityComfort,
    Beliefs_AdoptionOrientation,
    Beliefs_ConcernHarms,
    Beliefs_LowConcern
  )

beliefs_loadings_tbl <- as_tibble(beliefs_loadings_ordered, rownames = "item_id") |>
  mutate(item_id = as.integer(item_id)) |>
  left_join(beliefs_item_text, by = "item_id") |>
  relocate(item_id, item_text)

beliefs_kmo <- psych::KMO(beliefs_poly$rho)
beliefs_model_summary <- tibble(
  model = "BeliefsAboutAI items 6-22, 3-factor polychoric minres oblimin",
  n = nrow(beliefs_matrix),
  kmo = as.numeric(beliefs_kmo$MSA),
  rmsea = as.numeric(beliefs_fa$RMSEA[1]),
  tli = as.numeric(beliefs_fa$TLI),
  rmsr = as.numeric(beliefs_fa$rms),
  factor_correlation_12 = as.numeric(beliefs_fa_ordered$Phi[1, 2]),
  factor_correlation_13 = as.numeric(beliefs_fa_ordered$Phi[1, 3]),
  factor_correlation_23 = as.numeric(beliefs_fa_ordered$Phi[2, 3]),
  note = "Beliefs_ConcernHarms is sign-flipped from reversed items 17-20 so higher means more concern/harms endorsement."
)

belief_factor_lookup <- tibble(
  factor = c("Beliefs_UtilityComfort", "Beliefs_AdoptionOrientation", "Beliefs_ConcernHarms"),
  instrument = "BeliefsAboutAI",
  factor_num = 1:3,
  proposed_name = c("Utility & Comfort", "Adoption Orientation", "Concern & Harms"),
  display_label = c(
    "Beliefs F1 -> Utility & Comfort",
    "Beliefs F2 -> Adoption Orientation",
    "Beliefs F3 -> Concern & Harms"
  )
)

write_csv(beliefs_factor_scores, file.path(csv_dir, "Beliefs_6_22_Factor_Scores.csv"))
write_csv(beliefs_loadings_tbl, file.path(csv_dir, "Beliefs_6_22_Loadings.csv"))
write_csv(beliefs_model_summary, file.path(csv_dir, "Beliefs_6_22_Model_Summary.csv"))
write_csv(belief_factor_lookup, file.path(csv_dir, "Beliefs_6_22_Factor_Lookup.csv"))

beliefs_model_summary |>
  mutate(across(c(kmo, rmsea, tli, rmsr, starts_with("factor_correlation")), ~ round(.x, 3))) |>
  kable(caption = "BeliefsAboutAI 6-22 factor model summary")
```

```{r loadings-table}
beliefs_loadings_tbl |>
  mutate(across(starts_with("MR"), ~ round(.x, 3))) |>
  kable(caption = "BeliefsAboutAI 6-22 ordered factor loadings")
```

```{r loadings-plot, fig.width=9.5, fig.height=7}
loading_factor_lookup <- tibble(
  factor_id = c("MR1", "MR2", "MR3"),
  factor_label = c(
    "F1: Utility & Comfort",
    "F2: Adoption Orientation",
    "F3: Low Concern / Low Harms"
  )
)

loading_plot_df <- beliefs_loadings_tbl |>
  pivot_longer(
    cols = starts_with("MR"),
    names_to = "factor_id",
    values_to = "loading"
  ) |>
  left_join(loading_factor_lookup, by = "factor_id") |>
  group_by(item_id) |>
  mutate(
    primary_abs_loading = max(abs(loading), na.rm = TRUE),
    secondary_abs_loading = sort(abs(loading), decreasing = TRUE)[2],
    loading_gap = primary_abs_loading - secondary_abs_loading,
    cross_loading_item = primary_abs_loading >= 0.40 &
      secondary_abs_loading >= 0.30 &
      loading_gap < 0.15
  ) |>
  ungroup() |>
  mutate(
    item_label = paste0(item_id, ". ", str_trunc(item_text, 74)),
    item_label = fct_reorder(item_label, item_id),
    factor_label = factor(factor_label, levels = loading_factor_lookup$factor_label),
    cell_label = formatC(loading, format = "f", digits = 2)
  )

cross_loading_note <- loading_plot_df |>
  filter(cross_loading_item) |>
  distinct(item_id) |>
  arrange(item_id) |>
  pull(item_id)

loading_subtitle <- if (length(cross_loading_note) == 0) {
  "All loading values shown; no cross-loading items flagged by .40/.30/gap < .15 rule"
} else {
  paste0(
    "All loading values shown; cross-loading items flagged: ",
    paste(cross_loading_note, collapse = ", ")
  )
}

p_loadings <- ggplot(loading_plot_df, aes(x = factor_label, y = item_label, fill = loading)) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = cell_label), size = 3) +
  geom_point(
    data = loading_plot_df |> filter(cross_loading_item, abs(loading) >= 0.30),
    aes(x = factor_label, y = item_label),
    inherit.aes = FALSE,
    shape = 21,
    size = 3.3,
    stroke = 0.9,
    color = "#222222",
    fill = NA
  ) +
  scale_fill_gradient2(
    low = "#b3584b",
    mid = "white",
    high = "#3f6fa8",
    midpoint = 0,
    limits = c(-1, 1),
    name = "loading"
  ) +
  labs(
    title = "BeliefsAboutAI 6-22 Factor Loadings",
    subtitle = loading_subtitle,
    x = NULL,
    y = NULL,
    caption = "Outlined cells mark items that meet the cross-loading rule on at least two factors."
  ) +
  theme_minimal(base_size = 10) +
  theme(
    panel.grid = element_blank(),
    axis.text.x = element_text(angle = 20, hjust = 1),
    axis.text.y = element_text(size = 8, lineheight = 0.9),
    legend.position = "bottom",
    plot.caption = element_text(color = "gray35")
  )

ggsave(
  file.path(plot_dir, "Beliefs_6_22_Loadings_Heatmap.png"),
  p_loadings,
  width = 9.5,
  height = 7,
  units = "in",
  dpi = 300,
  bg = "white"
)
ggsave(
  file.path(plot_dir, "Beliefs_6_22_Loadings_Heatmap.pdf"),
  p_loadings,
  width = 9.5,
  height = 7,
  units = "in",
  bg = "white"
)

p_loadings
```

# Cross-Instrument Factor Correlations

This recreates the script `06` factor heatmap, now adding the three exploratory Beliefs factors.

```{r cross-factor-correlations}
existing_factor_scores <- read_csv(
  file.path("06_interesting_findings", "csv", "Factor_Scores_All_Instruments.csv"),
  show_col_types = FALSE
)

existing_factor_lookup <- read_csv(
  file.path("06_interesting_findings", "csv", "Factor_Name_Map.csv"),
  show_col_types = FALSE
) |>
  transmute(
    factor,
    instrument,
    factor_num = as.integer(factor_num),
    proposed_name,
    display_label = case_when(
      factor == "IMI_MR1" ~ "IMI F1 -> Interest & Enjoyment",
      factor == "IMI_MR2" ~ "IMI F2 -> Effort & Importance",
      factor == "IMI_MR3" ~ "IMI F3 -> Perceived Competence",
      factor == "WSE_MR1" ~ "WritingEfficacy F1 -> Writing Competence",
      factor == "WSE_MR2" ~ "WritingEfficacy F2 -> Self-Regulation",
      factor == "WSE_MR3" ~ "WritingEfficacy F3 -> Resource & Planning",
      factor == "AIRefl_MR1" ~ "AIReflection F1 -> Ownership & Usefulness",
      factor == "AIRefl_MR2" ~ "AIReflection F2 -> Enjoyment & Satisfaction",
      TRUE ~ display_label
    )
  )

all_factor_scores <- existing_factor_scores |>
  inner_join(
    beliefs_factor_scores |>
      select(participant_id, Beliefs_UtilityComfort, Beliefs_AdoptionOrientation, Beliefs_ConcernHarms),
    by = "participant_id"
  )

all_factor_lookup <- bind_rows(existing_factor_lookup, belief_factor_lookup)
all_factor_cols <- all_factor_lookup$factor

factor_pairs <- combn(all_factor_cols, 2, simplify = FALSE) |>
  map_dfr(~ tibble(factor_x = .x[1], factor_y = .x[2]))

factor_corr_unique <- factor_pairs |>
  mutate(result = map2(factor_x, factor_y, ~ safe_spearman(all_factor_scores, .x, .y))) |>
  unnest(result) |>
  mutate(
    abs_rho = abs(rho),
    p_bh = p.adjust(p, method = "BH"),
    p_bonf = p.adjust(p, method = "bonferroni"),
    survives_bh = p_bh < .05,
    survives_bonferroni = p_bonf < .05
  ) |>
  left_join(
    all_factor_lookup |> transmute(factor_x = factor, instrument_x = instrument, label_x = display_label),
    by = "factor_x"
  ) |>
  left_join(
    all_factor_lookup |> transmute(factor_y = factor, instrument_y = instrument, label_y = display_label),
    by = "factor_y"
  ) |>
  arrange(p_bh, desc(abs_rho))

factor_corr_diag <- tibble(
  factor_x = all_factor_cols,
  factor_y = all_factor_cols,
  rho = 1,
  p = NA_real_,
  n = map_int(all_factor_cols, ~ sum(!is.na(all_factor_scores[[.x]]))),
  abs_rho = 1,
  p_bh = NA_real_,
  p_bonf = NA_real_,
  survives_bh = NA,
  survives_bonferroni = NA
) |>
  left_join(
    all_factor_lookup |> transmute(factor_x = factor, instrument_x = instrument, label_x = display_label),
    by = "factor_x"
  ) |>
  left_join(
    all_factor_lookup |> transmute(factor_y = factor, instrument_y = instrument, label_y = display_label),
    by = "factor_y"
  )

factor_corr_heat <- bind_rows(
  factor_corr_unique,
  factor_corr_unique |>
    transmute(
      factor_x = factor_y,
      factor_y = factor_x,
      rho, p, n, abs_rho, p_bh, p_bonf, survives_bh, survives_bonferroni,
      instrument_x = instrument_y,
      instrument_y = instrument_x,
      label_x = label_y,
      label_y = label_x
    ),
  factor_corr_diag
)

write_csv(factor_corr_unique, file.path(csv_dir, "Beliefs_6_22_Cross_Factor_Correlations_Unique.csv"))
write_csv(factor_corr_heat, file.path(csv_dir, "Beliefs_6_22_Cross_Factor_Heatmap_Matrix.csv"))

factor_corr_unique |>
  filter(instrument_x == "BeliefsAboutAI" | instrument_y == "BeliefsAboutAI") |>
  transmute(
    beliefs_factor = if_else(instrument_x == "BeliefsAboutAI", label_x, label_y),
    other_factor = if_else(instrument_x == "BeliefsAboutAI", label_y, label_x),
    n, rho, p, p_bh, p_bonf
  ) |>
  mutate(across(c(rho, p, p_bh, p_bonf), ~ round(.x, 4))) |>
  arrange(p_bh) |>
  kable(caption = "Exploratory Beliefs factors vs existing survey factors")
```

```{r cross-factor-heatmap, fig.width=12, fig.height=9}
factor_levels <- all_factor_lookup |>
  mutate(
    instrument_order = match(
      instrument,
      c("IMI", "WritingEfficacy", "AIReflection", "BeliefsAboutAI")
    )
  ) |>
  arrange(instrument_order, factor_num) |>
  pull(display_label)

factor_heat_plot_df <- factor_corr_heat |>
  mutate(
    label_x = factor(label_x, levels = factor_levels),
    label_y = factor(label_y, levels = rev(factor_levels)),
    cell_label = case_when(
      factor_x == factor_y ~ "",
      is.na(rho) ~ "",
      TRUE ~ paste0(formatC(rho, format = "f", digits = 2), sig_suffix(p_bh, p_bonf))
    )
  )

p_cross_factor_heat <- ggplot(factor_heat_plot_df, aes(x = label_x, y = label_y, fill = rho)) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = cell_label), size = 3) +
  scale_fill_gradient2(
    low = "#b3584b",
    mid = "white",
    high = "#3f6fa8",
    midpoint = 0,
    limits = c(-1, 1),
    name = "rho"
  ) +
  labs(
    title = "Cross-Instrument Factor Heatmap with Beliefs 6-22 Factors",
    subtitle = "* BH < .05; ** Bonferroni < .05",
    x = NULL,
    y = NULL
  ) +
  theme_corr(base_size = 10) +
  theme(axis.text.y = element_text(size = 8), axis.text.x = element_text(size = 8, angle = 35, hjust = 1))

ggsave(
  file.path(plot_dir, "Beliefs_6_22_Cross_Factor_Heatmap.png"),
  p_cross_factor_heat,
  width = 12,
  height = 9,
  units = "in",
  dpi = 300,
  bg = "white"
)
ggsave(
  file.path(plot_dir, "Beliefs_6_22_Cross_Factor_Heatmap.pdf"),
  p_cross_factor_heat,
  width = 12,
  height = 9,
  units = "in",
  bg = "white"
)

p_cross_factor_heat
```

# ART vs Beliefs Factors

This recreates the factor-level ART heatmap from script `07`, restricted to the exploratory
Beliefs factors.

```{r art-correlations}
art_metric_lookup <- tibble(
  art_metric = c(
    "art_total_selected",
    "art_real_hits",
    "art_fake_false_alarms",
    "art_neutral_selected",
    "art_unknown_selected",
    "art_net_real_minus_fake",
    "art_hit_rate",
    "art_false_alarm_rate"
  ),
  art_label = c(
    "Total selected",
    "Real hits",
    "False alarms",
    "Neutral selected",
    "Unknown selected",
    "ART net",
    "Hit rate",
    "False-alarm rate"
  )
)

art_scores <- read_csv(file.path("07_art_vs_all_factors_items", "csv", "ART_Scored.csv"), show_col_types = FALSE)
art_factor_df <- art_scores |>
  inner_join(beliefs_factor_scores |> select(participant_id, all_of(belief_factor_lookup$factor)), by = "participant_id")

art_corrs <- run_corr_grid(
  art_factor_df,
  art_metric_lookup$art_metric,
  belief_factor_lookup$factor,
  "art_vs_beliefs_factors"
) |>
  rename(art_metric = x, factor = y) |>
  left_join(art_metric_lookup, by = "art_metric") |>
  left_join(belief_factor_lookup, by = "factor") |>
  arrange(p_bh, desc(abs_rho))

write_csv(art_corrs, file.path(csv_dir, "ART_vs_Beliefs_6_22_Factors.csv"))

art_corrs |>
  select(art_label, display_label, n, rho, p, p_bh, p_bonf) |>
  mutate(across(c(rho, p, p_bh, p_bonf), ~ round(.x, 4))) |>
  slice_head(n = 20) |>
  kable(caption = "ART metrics vs exploratory Beliefs factors")
```

```{r art-heatmap, fig.width=9, fig.height=4.8}
art_heat_df <- art_corrs |>
  mutate(
    art_label = factor(art_label, levels = art_metric_lookup$art_label),
    display_label = factor(display_label, levels = rev(belief_factor_lookup$display_label)),
    cell_label = paste0(formatC(rho, format = "f", digits = 2), sig_suffix(p_bh, p_bonf))
  )

p_art_heat <- ggplot(art_heat_df, aes(x = art_label, y = display_label, fill = rho)) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = cell_label), size = 3.2) +
  scale_fill_gradient2(low = "#b3584b", mid = "white", high = "#3f6fa8", midpoint = 0, limits = c(-.65, .65), name = "rho") +
  labs(
    title = "ART vs Beliefs 6-22 Factor Scores",
    subtitle = "* BH < .05; ** Bonferroni < .05",
    x = NULL,
    y = NULL
  ) +
  theme_corr()

ggsave(file.path(plot_dir, "ART_vs_Beliefs_6_22_Factors_Heatmap.png"), p_art_heat, width = 9, height = 4.8, units = "in", dpi = 300, bg = "white")
ggsave(file.path(plot_dir, "ART_vs_Beliefs_6_22_Factors_Heatmap.pdf"), p_art_heat, width = 9, height = 4.8, units = "in", bg = "white")

p_art_heat
```

# Q17 AI-Use Breadth vs Beliefs Factors

This recreates the Q17 factor heatmap logic from scripts `14` and `15`, focusing on participant-level
use breadth and response proportions.

```{r q17-correlations}
q17_long <- read_csv(file.path("09_q17_ai_use", "csv", "Q17_Responses_Long.csv"), show_col_types = FALSE) |>
  mutate(use_score = as.numeric(use_score))

q17_bucket <- q17_long |>
  group_by(participant_id) |>
  summarise(
    q17_mean = mean(use_score, na.rm = TRUE),
    q17_p_never = mean(use_score == 1, na.rm = TRUE),
    q17_p_heard_never = mean(use_score == 2, na.rm = TRUE),
    q17_p_rarely = mean(use_score == 3, na.rm = TRUE),
    q17_p_regular = mean(use_score == 4, na.rm = TRUE),
    q17_p_often = mean(use_score == 5, na.rm = TRUE),
    q17_breadth_ge3 = sum(use_score >= 3, na.rm = TRUE),
    q17_breadth_ge4 = sum(use_score >= 4, na.rm = TRUE),
    .groups = "drop"
  )

q17_metric_lookup <- tibble(
  q17_metric = c(
    "q17_mean",
    "q17_breadth_ge3",
    "q17_breadth_ge4",
    "q17_p_never",
    "q17_p_heard_never",
    "q17_p_rarely",
    "q17_p_regular",
    "q17_p_often"
  ),
  q17_label = c(
    "Mean use score",
    "Breadth: used at least rarely",
    "Breadth: regular/often use",
    "Prop. never heard",
    "Prop. heard, never used",
    "Prop. rarely use",
    "Prop. regularly use",
    "Prop. often use"
  )
)

q17_factor_df <- q17_bucket |>
  inner_join(beliefs_factor_scores |> select(participant_id, all_of(belief_factor_lookup$factor)), by = "participant_id")

q17_corrs <- run_corr_grid(
  q17_factor_df,
  q17_metric_lookup$q17_metric,
  belief_factor_lookup$factor,
  "q17_buckets_vs_beliefs_factors"
) |>
  rename(q17_metric = x, factor = y) |>
  left_join(q17_metric_lookup, by = "q17_metric") |>
  left_join(belief_factor_lookup, by = "factor") |>
  arrange(p_bh, desc(abs_rho))

write_csv(q17_corrs, file.path(csv_dir, "Q17_Buckets_vs_Beliefs_6_22_Factors.csv"))

q17_corrs |>
  select(q17_label, display_label, n, rho, p, p_bh, p_bonf) |>
  mutate(across(c(rho, p, p_bh, p_bonf), ~ round(.x, 4))) |>
  slice_head(n = 20) |>
  kable(caption = "Q17 use metrics vs exploratory Beliefs factors")
```

```{r q17-heatmap, fig.width=10, fig.height=4.8}
q17_heat_df <- q17_corrs |>
  mutate(
    q17_label = factor(q17_label, levels = q17_metric_lookup$q17_label),
    display_label = factor(display_label, levels = rev(belief_factor_lookup$display_label)),
    cell_label = paste0(formatC(rho, format = "f", digits = 2), sig_suffix(p_bh, p_bonf))
  )

p_q17_heat <- ggplot(q17_heat_df, aes(x = q17_label, y = display_label, fill = rho)) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = cell_label), size = 3.2) +
  scale_fill_gradient2(low = "#b3584b", mid = "white", high = "#3f6fa8", midpoint = 0, limits = c(-.65, .65), name = "rho") +
  labs(
    title = "Q17 AI-Use Breadth and Buckets vs Beliefs 6-22 Factors",
    subtitle = "* BH < .05; ** Bonferroni < .05",
    x = NULL,
    y = NULL
  ) +
  theme_corr()

ggsave(file.path(plot_dir, "Q17_vs_Beliefs_6_22_Factors_Heatmap.png"), p_q17_heat, width = 10, height = 4.8, units = "in", dpi = 300, bg = "white")
ggsave(file.path(plot_dir, "Q17_vs_Beliefs_6_22_Factors_Heatmap.pdf"), p_q17_heat, width = 10, height = 4.8, units = "in", bg = "white")

p_q17_heat
```

# Named Model Use vs Beliefs Factors

This recreates the named-model use heatmap from script `12`, restricted to the four focal tools.

```{r named-model-correlations}
models <- c(
  "ChatGPT (including DALL-E) by OpenAI",
  "Claude by Anthropic",
  "Gemini (formerly Bard) by Google",
  "Copilot (Bing Chat) by Microsoft"
)

model_wide <- q17_long |>
  filter(tool %in% models) |>
  mutate(
    model = case_when(
      str_detect(tool, "ChatGPT") ~ "ChatGPT",
      str_detect(tool, "Claude") ~ "Claude",
      str_detect(tool, "Gemini") ~ "Gemini",
      str_detect(tool, "Copilot") ~ "Copilot",
      TRUE ~ tool
    ),
    model_col = paste0("model_", model)
  ) |>
  select(participant_id, model_col, use_score) |>
  pivot_wider(names_from = model_col, values_from = use_score)

model_lookup <- tibble(
  model_col = c("model_ChatGPT", "model_Claude", "model_Gemini", "model_Copilot"),
  model_label = c("ChatGPT", "Claude", "Gemini", "Copilot")
)

model_factor_df <- model_wide |>
  inner_join(beliefs_factor_scores |> select(participant_id, all_of(belief_factor_lookup$factor)), by = "participant_id")

model_corrs <- run_corr_grid(
  model_factor_df,
  model_lookup$model_col,
  belief_factor_lookup$factor,
  "named_model_use_vs_beliefs_factors"
) |>
  rename(model_col = x, factor = y) |>
  left_join(model_lookup, by = "model_col") |>
  left_join(belief_factor_lookup, by = "factor") |>
  arrange(p_bh, desc(abs_rho))

write_csv(model_corrs, file.path(csv_dir, "Named_Model_Use_vs_Beliefs_6_22_Factors.csv"))

model_corrs |>
  select(model_label, display_label, n, rho, p, p_bh, p_bonf) |>
  mutate(across(c(rho, p, p_bh, p_bonf), ~ round(.x, 4))) |>
  kable(caption = "Named model use vs exploratory Beliefs factors")
```

```{r named-model-heatmap, fig.width=7.8, fig.height=4.8}
model_heat_df <- model_corrs |>
  mutate(
    model_label = factor(model_label, levels = model_lookup$model_label),
    display_label = factor(display_label, levels = rev(belief_factor_lookup$display_label)),
    cell_label = paste0(formatC(rho, format = "f", digits = 2), sig_suffix(p_bh, p_bonf))
  )

p_model_heat <- ggplot(model_heat_df, aes(x = model_label, y = display_label, fill = rho)) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = cell_label), size = 3.4) +
  scale_fill_gradient2(low = "#b3584b", mid = "white", high = "#3f6fa8", midpoint = 0, limits = c(-.65, .65), name = "rho") +
  labs(
    title = "Named Model Use vs Beliefs 6-22 Factors",
    subtitle = "* BH < .05; ** Bonferroni < .05",
    x = NULL,
    y = NULL
  ) +
  theme_corr()

ggsave(file.path(plot_dir, "Named_Model_Use_vs_Beliefs_6_22_Factors_Heatmap.png"), p_model_heat, width = 7.8, height = 4.8, units = "in", dpi = 300, bg = "white")
ggsave(file.path(plot_dir, "Named_Model_Use_vs_Beliefs_6_22_Factors_Heatmap.pdf"), p_model_heat, width = 7.8, height = 4.8, units = "in", bg = "white")

p_model_heat
```

# AI Concern vs Q17 Frequency

For concern, the most defensible Q17 readout is layered:

- broad participant-level use metrics from scripts `14`/`15`
- all-tool frequency correlations, one row per Q17 tool
- bucketed descriptive checks for focal tools, especially ChatGPT

The concern factor is scored so higher values mean stronger concern/harms endorsement.
Negative correlations therefore mean higher use is associated with lower AI concern.

```{r q17-concern-followup}
q17_concern_long <- q17_long |>
  inner_join(
    beliefs_factor_scores |> select(participant_id, Beliefs_ConcernHarms),
    by = "participant_id"
  ) |>
  filter(!is.na(use_score), !is.na(Beliefs_ConcernHarms)) |>
  mutate(
    use_bucket = factor(
      use_score,
      levels = 1:5,
      labels = c(
        "Never heard",
        "Heard, never used",
        "Rarely use",
        "Sometimes use",
        "Often use"
      )
    )
  )

concern_q17_aggregate <- q17_corrs |>
  filter(factor == "Beliefs_ConcernHarms") |>
  select(q17_metric, q17_label, n, rho, p, p_bh, p_bonf) |>
  arrange(p_bh, desc(abs(rho)))

write_csv(
  concern_q17_aggregate,
  file.path(csv_dir, "Q17_Aggregate_Metrics_vs_Beliefs_ConcernHarms.csv")
)

concern_tool_corrs <- q17_concern_long |>
  group_by(tool) |>
  summarise(
    n_participants = n_distinct(participant_id),
    score_sd = sd(use_score, na.rm = TRUE),
    concern_sd = sd(Beliefs_ConcernHarms, na.rm = TRUE),
    result = list(safe_spearman(cur_data(), "use_score", "Beliefs_ConcernHarms")),
    .groups = "drop"
  ) |>
  unnest(result) |>
  select(tool, n = n_participants, score_sd, concern_sd, rho, p) |>
  mutate(
    abs_rho = abs(rho),
    p_bh = p.adjust(p, method = "BH"),
    p_bonf = p.adjust(p, method = "bonferroni"),
    survives_bh = p_bh < .05,
    survives_bonferroni = p_bonf < .05
  ) |>
  arrange(p_bh, desc(abs_rho))

write_csv(
  concern_tool_corrs,
  file.path(csv_dir, "Q17_AllTools_vs_Beliefs_ConcernHarms.csv")
)

concern_tool_buckets <- q17_concern_long |>
  group_by(tool, use_score, use_bucket) |>
  summarise(
    n = n_distinct(participant_id),
    mean_concern = mean(Beliefs_ConcernHarms, na.rm = TRUE),
    median_concern = median(Beliefs_ConcernHarms, na.rm = TRUE),
    sd_concern = sd(Beliefs_ConcernHarms, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(tool, use_score)

write_csv(
  concern_tool_buckets,
  file.path(csv_dir, "Q17_AllTools_Concern_By_Use_Bucket.csv")
)

concern_tool_kruskal <- q17_concern_long |>
  group_by(tool) |>
  group_modify(~ {
    d <- .x |> filter(!is.na(use_score), !is.na(Beliefs_ConcernHarms))
    if (n_distinct(d$use_score) < 2L || nrow(d) < 10L) {
      return(tibble(statistic = NA_real_, p = NA_real_, n = nrow(d), buckets = n_distinct(d$use_score)))
    }
    kt <- suppressWarnings(kruskal.test(Beliefs_ConcernHarms ~ factor(use_score), data = d))
    tibble(
      statistic = unname(kt$statistic),
      p = kt$p.value,
      n = nrow(d),
      buckets = n_distinct(d$use_score)
    )
  }) |>
  ungroup() |>
  mutate(
    p_bh = p.adjust(p, method = "BH"),
    p_bonf = p.adjust(p, method = "bonferroni")
  ) |>
  arrange(p_bh, p)

write_csv(
  concern_tool_kruskal,
  file.path(csv_dir, "Q17_AllTools_Concern_Kruskal_By_Use_Bucket.csv")
)

concern_q17_aggregate |>
  mutate(across(c(rho, p, p_bh, p_bonf), ~ round(.x, 4))) |>
  kable(caption = "Aggregate Q17 metrics vs Beliefs F3 concern/harms")

concern_tool_corrs |>
  slice_head(n = 12) |>
  mutate(across(c(rho, p, p_bh, p_bonf), ~ round(.x, 4))) |>
  select(tool, n, rho, p, p_bh, p_bonf, survives_bh, survives_bonferroni) |>
  kable(caption = "Top Q17 tool-frequency correlations with Beliefs F3 concern/harms")
```

```{r q17-concern-aggregate-plot, fig.width=8.8, fig.height=4.8}
concern_aggregate_plot_df <- concern_q17_aggregate |>
  mutate(
    q17_label = factor(q17_label, levels = rev(q17_metric_lookup$q17_label)),
    sig_label = sig_suffix(p_bh, p_bonf),
    label_hjust = if_else(rho < 0, 1.15, -0.15)
  )

p_concern_aggregate <- ggplot(concern_aggregate_plot_df, aes(x = rho, y = q17_label)) +
  geom_vline(xintercept = 0, color = "gray65", linewidth = 0.4) +
  geom_segment(aes(x = 0, xend = rho, yend = q17_label), color = "#8aa6a1", linewidth = 0.8) +
  geom_point(aes(fill = p_bh < .05), shape = 21, size = 3.4, color = "#254f4a") +
  geom_text(aes(label = paste0(formatC(rho, format = "f", digits = 2), sig_label), hjust = label_hjust), size = 3.1) +
  scale_fill_manual(values = c("TRUE" = pal["Q17"], "FALSE" = "white"), guide = "none") +
  coord_cartesian(xlim = c(-.35, .2), clip = "off") +
  labs(
    title = "Beliefs F3 Concern/Harms vs Aggregate Q17 Use Metrics",
    subtitle = "Negative rho means more frequent or broader use is associated with lower concern",
    x = "Spearman rho",
    y = NULL
  ) +
  theme_minimal(base_size = 11) +
  theme(panel.grid.minor = element_blank())

ggsave(file.path(plot_dir, "Q17_Aggregate_vs_Beliefs_ConcernHarms_DotPlot.png"), p_concern_aggregate, width = 8.8, height = 4.8, units = "in", dpi = 300, bg = "white")
ggsave(file.path(plot_dir, "Q17_Aggregate_vs_Beliefs_ConcernHarms_DotPlot.pdf"), p_concern_aggregate, width = 8.8, height = 4.8, units = "in", bg = "white")

p_concern_aggregate
```

```{r q17-concern-tool-plot, fig.width=9.2, fig.height=6}
concern_tool_plot_df <- concern_tool_corrs |>
  filter(!is.na(rho)) |>
  slice_max(abs_rho, n = 15, with_ties = FALSE) |>
  mutate(
    tool_label = str_wrap(tool, width = 34),
    tool_label = fct_reorder(tool_label, rho),
    sig_label = sig_suffix(p_bh, p_bonf),
    label_hjust = if_else(rho < 0, 1.15, -0.15)
  )

p_concern_tools <- ggplot(concern_tool_plot_df, aes(x = rho, y = tool_label)) +
  geom_vline(xintercept = 0, color = "gray65", linewidth = 0.4) +
  geom_segment(aes(x = 0, xend = rho, yend = tool_label), color = "#8aa6a1", linewidth = 0.8) +
  geom_point(aes(fill = p_bh < .05), shape = 21, size = 3.4, color = "#254f4a") +
  geom_text(aes(label = paste0(formatC(rho, format = "f", digits = 2), sig_label), hjust = label_hjust), size = 3.1) +
  scale_fill_manual(values = c("TRUE" = pal["Q17"], "FALSE" = "white"), guide = "none") +
  coord_cartesian(xlim = c(-.45, .45), clip = "off") +
  labs(
    title = "Beliefs F3 Concern/Harms vs Individual Q17 Tool Frequency",
    subtitle = "Top 15 by |Spearman rho| across all Q17 tools; * BH < .05; ** Bonferroni < .05",
    x = "Spearman rho",
    y = NULL
  ) +
  theme_minimal(base_size = 11) +
  theme(panel.grid.minor = element_blank())

ggsave(file.path(plot_dir, "Q17_AllTools_vs_Beliefs_ConcernHarms_DotPlot.png"), p_concern_tools, width = 9.2, height = 6, units = "in", dpi = 300, bg = "white")
ggsave(file.path(plot_dir, "Q17_AllTools_vs_Beliefs_ConcernHarms_DotPlot.pdf"), p_concern_tools, width = 9.2, height = 6, units = "in", bg = "white")

p_concern_tools
```

```{r q17-concern-chatgpt-boxplot, fig.width=8.8, fig.height=5}
chatgpt_concern <- q17_concern_long |>
  filter(str_detect(tool, "ChatGPT")) |>
  mutate(use_bucket = fct_drop(use_bucket))

p_chatgpt_concern <- ggplot(chatgpt_concern, aes(x = use_bucket, y = Beliefs_ConcernHarms)) +
  geom_boxplot(width = 0.58, outlier.shape = NA, fill = "#d7e7e4", color = "#254f4a") +
  geom_jitter(width = 0.12, height = 0, alpha = 0.55, size = 1.8, color = "#254f4a") +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 3, fill = "white", color = "#7b3f35") +
  labs(
    title = "Beliefs F3 Concern/Harms by ChatGPT Use Frequency",
    subtitle = "Higher factor score means stronger concern/harms endorsement; diamond marks group mean",
    x = NULL,
    y = "Beliefs F3 concern/harms score"
  ) +
  theme_minimal(base_size = 11) +
  theme(
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle = 20, hjust = 1)
  )

ggsave(file.path(plot_dir, "Q17_ChatGPT_Use_Bucket_vs_Beliefs_ConcernHarms.png"), p_chatgpt_concern, width = 8.8, height = 5, units = "in", dpi = 300, bg = "white")
ggsave(file.path(plot_dir, "Q17_ChatGPT_Use_Bucket_vs_Beliefs_ConcernHarms.pdf"), p_chatgpt_concern, width = 8.8, height = 5, units = "in", bg = "white")

p_chatgpt_concern
```

# Top Signals Across Families

```{r top-signal-table-plot, fig.width=10, fig.height=8}
top_all <- bind_rows(
  factor_corr_unique |>
    filter(instrument_x == "BeliefsAboutAI" | instrument_y == "BeliefsAboutAI") |>
    transmute(
      source = "Survey factor",
      predictor = if_else(instrument_x == "BeliefsAboutAI", label_y, label_x),
      beliefs_factor = if_else(instrument_x == "BeliefsAboutAI", label_x, label_y),
      n, rho, p, p_bh, p_bonf
    ),
  art_corrs |>
    transmute(source = "ART", predictor = art_label, beliefs_factor = display_label, n, rho, p, p_bh, p_bonf),
  q17_corrs |>
    transmute(source = "Q17", predictor = q17_label, beliefs_factor = display_label, n, rho, p, p_bh, p_bonf),
  model_corrs |>
    transmute(source = "Named model", predictor = model_label, beliefs_factor = display_label, n, rho, p, p_bh, p_bonf)
) |>
  mutate(
    abs_rho = abs(rho),
    signal_label = paste0(source, ": ", predictor, "\n", beliefs_factor)
  ) |>
  arrange(p_bh, desc(abs_rho))

write_csv(top_all, file.path(csv_dir, "Beliefs_6_22_All_Correlations_Ranked.csv"))

top_all |>
  slice_head(n = 25) |>
  mutate(across(c(rho, p, p_bh, p_bonf), ~ round(.x, 4))) |>
  select(source, predictor, beliefs_factor, n, rho, p, p_bh, p_bonf) |>
  kable(caption = "Top exploratory Beliefs 6-22 factor correlations")

top_plot_df <- top_all |>
  filter(!is.na(rho)) |>
  slice_head(n = 25) |>
  mutate(
    signal_label = str_trunc(signal_label, 95),
    signal_label = fct_reorder(signal_label, rho)
  )

p_top <- ggplot(top_plot_df, aes(x = rho, y = signal_label, fill = source)) +
  geom_col(width = 0.75) +
  geom_vline(xintercept = 0, color = "gray50", linewidth = 0.5) +
  scale_fill_manual(values = c(
    "Survey factor" = pal["BeliefsAboutAI"],
    "ART" = pal["ART"],
    "Q17" = pal["Q17"],
    "Named model" = pal["ModelUse"]
  )) +
  labs(
    title = "Top Exploratory Correlations for Beliefs 6-22 Factors",
    subtitle = "Ranked by within-family BH-adjusted p-value, then |rho|",
    x = "Spearman rho",
    y = NULL,
    fill = NULL
  ) +
  theme_minimal(base_size = 11) +
  theme(
    panel.grid.minor = element_blank(),
    axis.text.y = element_text(size = 8),
    legend.position = "bottom"
  )

ggsave(file.path(plot_dir, "Beliefs_6_22_Top_Correlations.png"), p_top, width = 10, height = 8, units = "in", dpi = 300, bg = "white")
ggsave(file.path(plot_dir, "Beliefs_6_22_Top_Correlations.pdf"), p_top, width = 10, height = 8, units = "in", bg = "white")

p_top
```

# Export Manifest

```{r manifest}
manifest <- tibble(
  output_type = c(
    "model_summary",
    "factor_scores",
    "loadings",
    "loadings_heatmap",
    "factor_lookup",
    "cross_factor_correlations",
    "cross_factor_heatmap_matrix",
    "art_correlations",
    "q17_correlations",
    "q17_concern_aggregate",
    "q17_concern_all_tools",
    "q17_concern_by_tool_bucket",
    "q17_concern_kruskal_by_tool",
    "named_model_correlations",
    "all_ranked_correlations"
  ),
  path = c(
    file.path(csv_dir, "Beliefs_6_22_Model_Summary.csv"),
    file.path(csv_dir, "Beliefs_6_22_Factor_Scores.csv"),
    file.path(csv_dir, "Beliefs_6_22_Loadings.csv"),
    file.path(plot_dir, "Beliefs_6_22_Loadings_Heatmap.png"),
    file.path(csv_dir, "Beliefs_6_22_Factor_Lookup.csv"),
    file.path(csv_dir, "Beliefs_6_22_Cross_Factor_Correlations_Unique.csv"),
    file.path(csv_dir, "Beliefs_6_22_Cross_Factor_Heatmap_Matrix.csv"),
    file.path(csv_dir, "ART_vs_Beliefs_6_22_Factors.csv"),
    file.path(csv_dir, "Q17_Buckets_vs_Beliefs_6_22_Factors.csv"),
    file.path(csv_dir, "Q17_Aggregate_Metrics_vs_Beliefs_ConcernHarms.csv"),
    file.path(csv_dir, "Q17_AllTools_vs_Beliefs_ConcernHarms.csv"),
    file.path(csv_dir, "Q17_AllTools_Concern_By_Use_Bucket.csv"),
    file.path(csv_dir, "Q17_AllTools_Concern_Kruskal_By_Use_Bucket.csv"),
    file.path(csv_dir, "Named_Model_Use_vs_Beliefs_6_22_Factors.csv"),
    file.path(csv_dir, "Beliefs_6_22_All_Correlations_Ranked.csv")
  ),
  description = c(
    "Beliefs 6-22 EFA/KMO summary",
    "tenBerge factor scores for the exploratory Beliefs 6-22 model",
    "Ordered factor loadings for the exploratory Beliefs model",
    "Heatmap of Beliefs 6-22 factor loadings with cross-loading items outlined",
    "Display labels for exploratory Beliefs factors",
    "Unique factor-factor correlations including exploratory Beliefs factors",
    "Symmetric factor heatmap matrix including exploratory Beliefs factors",
    "ART metrics vs exploratory Beliefs factors",
    "Q17 use metrics vs exploratory Beliefs factors",
    "Aggregate Q17 use metrics vs Beliefs F3 concern/harms",
    "Individual Q17 tool frequency vs Beliefs F3 concern/harms",
    "Beliefs F3 concern/harms descriptives by Q17 use bucket for each tool",
    "Kruskal-Wallis checks for Beliefs F3 concern/harms across Q17 use buckets for each tool",
    "Named model use scores vs exploratory Beliefs factors",
    "Combined ranked table across factor, ART, Q17, and named-model families"
  )
)

write_csv(manifest, file.path(csv_dir, "Beliefs_6_22_Manifest.csv"))
manifest |>
  kable(caption = "Exploratory Beliefs 6-22 output manifest")
```
