---
title: "Participant Profiles from Validated Factor Scores"
format:
  html:
    toc: true
    toc-depth: 2
output-dir: "10_participant_profiles"
execute:
  echo: false
  warning: false
  message: false
---

This report builds exploratory participant profiles using only the
validated factor-score structure from the three factorable instruments:
`IMI`, `WritingEfficacy`, and `AIReflection`.

Clustering inputs:

- `IMI` factors
- `WritingEfficacy` factors
- `AIReflection` factors

Descriptive overlays only:

- `ART` metrics
- `Q17` AI-use indices
- `BeliefsAboutAI` theme averages
- order assignment

This is intentional. `BeliefsAboutAI` did not support a clean factor
solution, so it is used to describe profiles, not to define them.

```{r setup}
library(tidyverse)
library(cluster)
library(glue)
library(knitr)
source("scoring_helpers.R", local = knitr::knit_global())

set.seed(42L)
```

## Setup

```{r config}
script_dir <- "10_participant_profiles"
csv_dir <- file.path(script_dir, "csv")
plot_dir <- file.path(script_dir, "plots")
dir.create(csv_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(plot_dir, recursive = TRUE, showWarnings = FALSE)

factor_merged_file <- file.path("09_art_vs_all_factors_items", "csv", "ART_Factor_Merged.csv")
factor_lookup_file <- file.path("09_art_vs_all_factors_items", "csv", "Factor_Lookup.csv")
q17_index_file <- file.path("07_q17_ai_use", "csv", "Q17_Participant_AI_Use_Index.csv")
master_wide_file <- file.path("02_efa_exports", "Final_Master_Wide.csv")

required_files <- c(
  factor_merged_file,
  factor_lookup_file,
  q17_index_file,
  master_wide_file
)

missing_files <- required_files[!file.exists(required_files)]
if (length(missing_files) > 0) {
  stop(
    paste0(
      "Participant profiling is missing required inputs: ",
      paste(missing_files, collapse = ", ")
    ),
    call. = FALSE
  )
}

candidate_k_values <- 2:5
min_cluster_size_floor <- 8L
preferred_profile_labels <- c(
  "AI-Receptive but Less Confident Writers",
  "Strategic but AI-Skeptical Writers",
  "Engaged, Self-Regulated Writers"
)
```

## Load Data

```{r load-data}
factor_df <- read_csv(factor_merged_file, show_col_types = FALSE) |>
  mutate(participant_id = as.character(participant_id))

factor_lookup <- read_csv(factor_lookup_file, show_col_types = FALSE)
q17_index <- read_csv(q17_index_file, show_col_types = FALSE) |>
  mutate(participant_id = as.character(participant_id))
master_wide <- read_csv(master_wide_file, show_col_types = FALSE) |>
  mutate(participant_id = as.character(participant_id))

factor_cols <- factor_lookup$factor

required_factor_cols <- c(
  "participant_id", "order", "art_net_real_minus_fake",
  "art_real_hits", "art_fake_false_alarms", "art_adjusted_rate",
  factor_cols
)

assert_required_columns(factor_df, required_factor_cols, "ART_Factor_Merged")
assert_expected_count(nrow(factor_df), 82L, "participant profiling factor rows")
assert_unique_pid_rows(factor_df, "participant_id", "participant profiling factor rows")
assert_no_missing_values(factor_df, c("participant_id", factor_cols), "participant profiling factors")

assert_required_columns(
  q17_index,
  c("participant_id", "ai_tools_heard_n", "ai_tools_used_n", "ai_tools_regular_n", "ai_use_mean"),
  "Q17_Participant_AI_Use_Index"
)
assert_unique_pid_rows(q17_index, "participant_id", "Q17 participant index")

assert_required_columns(
  master_wide,
  c("participant_id", "order", "condition_1", "condition_2"),
  "Final_Master_Wide"
)
assert_unique_pid_rows(master_wide, "participant_id", "Final_Master_Wide")
```

## Beliefs Theme Averages

```{r beliefs-themes}
beliefs_theme_map <- tribble(
  ~item_num, ~theme,
  1L,  "AI Literacy and Limitations",
  2L,  "AI Literacy and Limitations",
  3L,  "AI Literacy and Limitations",
  4L,  "AI Literacy and Limitations",
  5L,  "AI Literacy and Limitations",
  6L,  "Academic Utility",
  7L,  "Academic Utility",
  8L,  "Academic Utility",
  9L,  "Academic Utility",
  10L, "Psychological Comfort and Anonymity",
  11L, "Psychological Comfort and Anonymity",
  12L, "Psychological Comfort and Anonymity",
  13L, "Practical Convenience",
  14L, "Practical Convenience",
  15L, "Practical Convenience",
  16L, "Practical Convenience",
  17L, "Risks and Concerns",
  18L, "Risks and Concerns",
  19L, "Risks and Concerns",
  20L, "Risks and Concerns",
  21L, "Future Integration",
  22L, "Future Integration"
)

beliefs_cols <- paste0("Beliefs_", beliefs_theme_map$item_num)
assert_required_columns(master_wide, beliefs_cols, "Final_Master_Wide beliefs columns")

beliefs_theme_long <- master_wide |>
  select(participant_id, all_of(beliefs_cols)) |>
  pivot_longer(
    cols = all_of(beliefs_cols),
    names_to = "belief_item",
    values_to = "score"
  ) |>
  mutate(item_num = as.integer(str_remove(belief_item, "Beliefs_"))) |>
  left_join(beliefs_theme_map, by = "item_num") |>
  group_by(participant_id, theme) |>
  summarise(theme_mean = mean(as.numeric(score), na.rm = TRUE), .groups = "drop")

beliefs_theme_scores <- beliefs_theme_long |>
  mutate(theme_col = paste0("BeliefsTheme_", str_replace_all(theme, "[^A-Za-z0-9]+", "_"))) |>
  select(participant_id, theme_col, theme_mean) |>
  pivot_wider(names_from = theme_col, values_from = theme_mean)

beliefs_theme_lookup <- beliefs_theme_long |>
  distinct(theme) |>
  mutate(theme_col = paste0("BeliefsTheme_", str_replace_all(theme, "[^A-Za-z0-9]+", "_")))
```

## Build Analysis Frame

```{r analysis-frame}
analysis_df <- factor_df |>
  left_join(
    q17_index |>
      select(
        participant_id,
        ai_tools_heard_n,
        ai_tools_used_n,
        ai_tools_regular_n,
        ai_tools_often_n,
        ai_use_mean,
        ai_use_mean_heard_only
      ),
    by = "participant_id"
  ) |>
  left_join(
    master_wide |>
      select(participant_id, condition_1, condition_2),
    by = "participant_id"
  ) |>
  left_join(beliefs_theme_scores, by = "participant_id")

assert_expected_count(nrow(analysis_df), 82L, "participant profiling analysis rows")
assert_unique_pid_rows(analysis_df, "participant_id", "participant profiling analysis rows")
```

## Cluster Selection

```{r cluster-selection}
factor_matrix_scaled <- analysis_df |>
  select(all_of(factor_cols)) |>
  as.matrix() |>
  scale() |>
  unclass()

row.names(factor_matrix_scaled) <- analysis_df$participant_id

dist_obj <- dist(factor_matrix_scaled)
hc_fit <- hclust(dist_obj, method = "ward.D2")

candidate_k_values <- candidate_k_values[candidate_k_values < nrow(factor_matrix_scaled)]

cluster_eval <- map_dfr(candidate_k_values, function(k) {
  membership <- cutree(hc_fit, k = k)
  cluster_sizes <- table(membership)
  sil <- cluster::silhouette(membership, dist_obj)

  tibble(
    k = k,
    avg_silhouette = mean(sil[, "sil_width"]),
    min_cluster_size = min(cluster_sizes),
    max_cluster_size = max(cluster_sizes),
    size_pattern = paste(as.integer(cluster_sizes), collapse = "/")
  )
})

valid_cluster_eval <- cluster_eval |>
  filter(min_cluster_size >= min_cluster_size_floor)

best_cluster_row <- if (nrow(valid_cluster_eval) > 0) {
  valid_cluster_eval |>
    arrange(desc(avg_silhouette), k) |>
    slice(1)
} else {
  cluster_eval |>
    arrange(desc(avg_silhouette), k) |>
    slice(1)
}

best_k <- best_cluster_row$k[[1]]

cluster_levels <- c(
  preferred_profile_labels[seq_len(min(best_k, length(preferred_profile_labels)))],
  if (best_k > length(preferred_profile_labels)) {
    paste0("Profile_", seq(length(preferred_profile_labels) + 1L, best_k))
  } else {
    character()
  }
)

write_csv(cluster_eval, file.path(csv_dir, "Cluster_Model_Selection.csv"))
```

```{r cluster-selection-table}
knitr::kable(cluster_eval)
```

## Assign Profiles

```{r assign-profiles}
raw_membership <- cutree(hc_fit, k = best_k)

profile_order <- tibble(
  participant_id = analysis_df$participant_id,
  raw_cluster = raw_membership
) |>
  left_join(
    tibble(participant_id = analysis_df$participant_id, pc1 = prcomp(factor_matrix_scaled)$x[, 1]),
    by = "participant_id"
  ) |>
  group_by(raw_cluster) |>
  summarise(cluster_pc1_mean = mean(pc1), .groups = "drop") |>
  arrange(cluster_pc1_mean) |>
  mutate(
    profile_num = row_number(),
    cluster = cluster_levels[profile_num]
  )

analysis_df <- analysis_df |>
  mutate(raw_cluster = raw_membership) |>
  left_join(profile_order, by = "raw_cluster") |>
  mutate(cluster = factor(cluster, levels = cluster_levels)) |>
  select(-raw_cluster, -cluster_pc1_mean)

cluster_sizes <- analysis_df |>
  count(cluster, name = "n", .drop = FALSE) |>
  mutate(cluster = as.character(cluster))

assert_expected_count(sum(cluster_sizes$n), 82L, "participant profiling total clustered participants")
write_csv(cluster_sizes, file.path(csv_dir, "Cluster_Sizes.csv"))
```

## Factor-Based Profile Signatures

```{r profile-signatures}
factor_centroids <- analysis_df |>
  group_by(cluster) |>
  summarise(
    n = n(),
    across(all_of(factor_cols), mean),
    .groups = "drop"
  )

factor_centroids_long <- factor_centroids |>
  pivot_longer(
    cols = all_of(factor_cols),
    names_to = "factor",
    values_to = "mean_factor_score"
  ) |>
  left_join(factor_lookup, by = "factor")

factor_centroid_z <- factor_centroids_long |>
  group_by(factor) |>
  mutate(profile_z = as.numeric(scale(mean_factor_score))) |>
  ungroup()

profile_top_strengths <- factor_centroid_z |>
  group_by(cluster) |>
  slice_max(order_by = profile_z, n = 2, with_ties = FALSE) |>
  summarise(top_strengths = paste(proposed_name, collapse = " | "), .groups = "drop")

profile_top_lows <- factor_centroid_z |>
  group_by(cluster) |>
  slice_min(order_by = profile_z, n = 2, with_ties = FALSE) |>
  summarise(top_lows = paste(proposed_name, collapse = " | "), .groups = "drop")

profile_signatures <- profile_top_strengths |>
  left_join(profile_top_lows, by = "cluster") |>
  left_join(cluster_sizes, by = "cluster") |>
  relocate(n, .after = cluster)

write_csv(profile_signatures, file.path(csv_dir, "Profile_Signatures.csv"))
```

```{r profile-signature-table}
knitr::kable(profile_signatures)
```

## External Profile Descriptives

```{r external-descriptives}
beliefs_theme_cols <- beliefs_theme_lookup$theme_col

profile_summary <- analysis_df |>
  group_by(cluster) |>
  summarise(
    n = n(),
    prop_traditional_first = mean(order == "Traditional_First"),
    art_net_mean = mean(art_net_real_minus_fake),
    art_net_sd = sd(art_net_real_minus_fake),
    art_adjusted_mean = mean(art_adjusted_rate),
    art_real_hits_mean = mean(art_real_hits),
    art_false_alarm_mean = mean(art_fake_false_alarms),
    ai_use_mean = mean(ai_use_mean, na.rm = TRUE),
    ai_use_mean_heard_only = mean(ai_use_mean_heard_only, na.rm = TRUE),
    ai_tools_heard_mean = mean(ai_tools_heard_n, na.rm = TRUE),
    ai_tools_used_mean = mean(ai_tools_used_n, na.rm = TRUE),
    ai_tools_often_mean = mean(ai_tools_often_n, na.rm = TRUE),
    ai_tools_regular_mean = mean(ai_tools_regular_n, na.rm = TRUE),
    across(all_of(beliefs_theme_cols), ~ mean(.x, na.rm = TRUE)),
    .groups = "drop"
  ) |>
  left_join(profile_signatures |> select(cluster, top_strengths, top_lows), by = "cluster")

write_csv(profile_summary, file.path(csv_dir, "Profile_External_Summary.csv"))
```

```{r external-summary-table}
profile_summary |>
  mutate(
    prop_traditional_first = round(prop_traditional_first, 3),
    art_net_mean = round(art_net_mean, 2),
    art_adjusted_mean = round(art_adjusted_mean, 3),
    ai_use_mean = round(ai_use_mean, 2)
  ) |>
  knitr::kable()
```

## PCA Map of Participants

```{r pca-data}
pca_fit <- prcomp(factor_matrix_scaled, center = FALSE, scale. = FALSE)

pca_df <- tibble(
  participant_id = analysis_df$participant_id,
  PC1 = pca_fit$x[, 1],
  PC2 = pca_fit$x[, 2]
) |>
  left_join(
    analysis_df |>
      select(participant_id, cluster),
    by = "participant_id"
  )

pca_cluster_centers <- pca_df |>
  group_by(cluster) |>
  summarise(
    PC1 = mean(PC1),
    PC2 = mean(PC2),
    .groups = "drop"
  )
```

```{r pca-plot, fig.width=9.5, fig.height=6.5}
pca_plot <- ggplot(pca_df, aes(x = PC1, y = PC2, color = cluster)) +
  geom_point(size = 2.5, alpha = 0.85) +
  geom_point(
    data = pca_cluster_centers,
    aes(x = PC1, y = PC2, color = cluster),
    size = 6,
    shape = 4,
    stroke = 1.4,
    inherit.aes = FALSE
  ) +
  labs(
    title = "Participant Profiles in Factor Space",
    subtitle = glue("Ward hierarchical clustering on standardized factor scores (k = {best_k})"),
    x = "PC1",
    y = "PC2",
    color = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.minor = element_blank(),
    legend.position = "bottom"
  )

ggsave(
  filename = file.path(plot_dir, "Participant_Profiles_PCA.png"),
  plot = pca_plot,
  width = 10,
  height = 7,
  units = "in",
  dpi = 300,
  bg = "white"
)

ggsave(
  filename = file.path(plot_dir, "Participant_Profiles_PCA.pdf"),
  plot = pca_plot,
  width = 10,
  height = 7,
  units = "in",
  bg = "white"
)

pca_plot
```

## Factor Heatmap by Profile

```{r heatmap-data}
heatmap_df <- factor_centroid_z |>
  mutate(
    display_label = factor(
      display_label,
      levels = factor_lookup |>
        arrange(match(instrument, c("IMI", "WritingEfficacy", "AIReflection")), factor_num) |>
        pull(display_label)
    ),
    cluster = factor(cluster, levels = cluster_levels),
    cell_label = formatC(profile_z, format = "f", digits = 2)
  )
```

```{r heatmap-plot, fig.width=10, fig.height=6.8}
heatmap_plot <- ggplot(heatmap_df, aes(x = cluster, y = display_label, fill = profile_z)) +
  geom_tile(color = "white", linewidth = 0.6) +
  geom_text(aes(label = cell_label), size = 3) +
  scale_fill_gradient2(
    low = "#c73e3a",
    mid = "#f7f7f7",
    high = "#4f79b7",
    midpoint = 0,
    name = "Profile z"
  ) +
  labs(
    title = "Profile Heatmap Across Validated Factors",
    subtitle = "Positive values indicate that the profile is elevated on that factor relative to other profiles",
    x = NULL,
    y = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid = element_blank(),
    axis.text.x = element_text(face = "bold"),
    plot.margin = margin(10, 15, 10, 10)
  )

ggsave(
  filename = file.path(plot_dir, "Participant_Profile_Factor_Heatmap.png"),
  plot = heatmap_plot,
  width = 11,
  height = 7.5,
  units = "in",
  dpi = 300,
  bg = "white"
)

ggsave(
  filename = file.path(plot_dir, "Participant_Profile_Factor_Heatmap.pdf"),
  plot = heatmap_plot,
  width = 11,
  height = 7.5,
  units = "in",
  bg = "white"
)

heatmap_plot
```

## Participant-Level Export

```{r participant-export}
participant_profiles <- analysis_df |>
  select(
    participant_id,
    cluster,
    order,
    condition_1,
    condition_2,
    art_net_real_minus_fake,
    art_adjusted_rate,
    art_real_hits,
    art_fake_false_alarms,
    ai_use_mean,
    ai_use_mean_heard_only,
    ai_tools_heard_n,
    ai_tools_used_n,
    ai_tools_often_n,
    ai_tools_regular_n,
    all_of(factor_cols),
    all_of(beliefs_theme_cols)
  )

write_csv(participant_profiles, file.path(csv_dir, "Participant_Profile_Assignments.csv"))
write_csv(factor_centroids, file.path(csv_dir, "Profile_Factor_Centroids_Raw.csv"))
write_csv(factor_centroid_z, file.path(csv_dir, "Profile_Factor_Centroids_Z.csv"))
```

## Summary

```{r summary}
summary_table <- tibble(
  metric = c(
    "Participants clustered",
    "Validated factor inputs",
    "Chosen number of profiles",
    "Best average silhouette",
    "Minimum profile size",
    "Maximum profile size"
  ),
  value = c(
    nrow(analysis_df),
    length(factor_cols),
    best_k,
    round(best_cluster_row$avg_silhouette[[1]], 3),
    min(cluster_sizes$n),
    max(cluster_sizes$n)
  )
)

knitr::kable(summary_table)
```

## Output Manifest

```{r manifest}
manifest <- tibble(
  object = c(
    "cluster_model_selection",
    "cluster_sizes",
    "profile_signatures",
    "profile_external_summary",
    "participant_profile_assignments",
    "profile_factor_centroids_raw",
    "profile_factor_centroids_z"
  ),
  file = c(
    "Cluster_Model_Selection.csv",
    "Cluster_Sizes.csv",
    "Profile_Signatures.csv",
    "Profile_External_Summary.csv",
    "Participant_Profile_Assignments.csv",
    "Profile_Factor_Centroids_Raw.csv",
    "Profile_Factor_Centroids_Z.csv"
  )
)

write_csv(manifest, file.path(csv_dir, "Participant_Profiles_Manifest.csv"))

knitr::kable(manifest)
```
